### 2021-08-25 analyses.RmD
- setting up repo - changed initial submission already strongly

---
title: "Who Needs Privacy? Exploring the relationship between personality and need for privacy"
subtitle: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 90)
```

```{r r-setup, include=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse", "td")

# load packages
lapply(packages, library, character.only = TRUE)

# readability function
readability = function(data){
  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
  textstat_readability(data, measure = reading_estimates) %>% 
    as.data.frame %>% 
    mutate(average = rowMeans(select(., -document)))
}
```

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")

# define vars and labels
vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", 
                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC", 
                   "HEX_ALT")
vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
                       "Social Self-Esteem", "Social Boldness", "Sociability", "Liveliness",
                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                       "Organization", "Diligence", "Perfectionism", "Prudence", 
                       "Aesthetic Appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
                       "Altruism")

vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")
vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
                       "Agreeableness", "Conscientiousness", "Openness")

vars_pri <- c("NFP_INF", "NFP_PSY", "NFP_PHY", "NFP_CNC", "NFP_SPA", 
              "NFP_GOV", "NFP_INT", "NFP_ANO", "NFP_COM", "NFP_GEN")
vars_pri_txt <- c("Informational", "Psychological", "Physical", "Concealment", "Personal Space", 
                  "Government", "Interpersonal", "Anonymity", "Companies", "General")

vars_ses <- c("age", "gender", "ethnicity", "relationship", "college", "income", "conservatism")

```

# Items

All items were answered on a 7-point scale with the following options:

"To what extent do you agree or disagree with the following statements?"

(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree

## Personality
### Honesty Humility
#### Sincerity

 - If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
 - I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
 - If I want something from someone, I will laugh at that person's worst jokes.
 - I wouldn't pretend to like someone just to get that person to do favors for me.

```{r}
model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
```

#### Fairness

 - If I knew that I could never get caught, I would be willing to steal a million dollars.
 - I would be tempted to buy stolen property if I were financially tight.
 - I would never accept a bribe, even if it were very large.
 - I’d be tempted to use counterfeit money, if I were sure I could get away with it.

```{r}
model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
```

#### Greed Avoidance

 - Having a lot of money is not especially important to me.
 - I would like to live in a very expensive, high-class neighborhood.
 - I would like to be seen driving around in a very expensive car.
 - I would get a lot of pleasure from owning expensive luxury goods.

```{r}
model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
```

#### Modesty

 - I am an ordinary person who is no better than others.
 - I wouldn’t want people to treat me as though I were superior to them.
 - I think that I am entitled to more respect than the average person is.
 - I want people to know that I am an important person of high status.

```{r}
model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
```

### Emotionality
#### Fearfulness

 - I would feel afraid if I had to travel in bad weather conditions.
 - I don’t mind doing jobs that involve dangerous work.
 - When it comes to physical danger, I am very fearful.
 - Even in an emergency I wouldn't feel like panicking.

```{r}
model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
```

#### Anxiety

 - I sometimes can't help worrying about little things.
 - I worry a lot less than most people do.
 - I rarely, if ever, have trouble sleeping due to stress or anxiety.
 - I get very anxious when waiting to hear about an important decision.

```{r}
model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"
```

#### Dependence
 - When I suffer from a painful experience, I need someone to make me feel comfortable.
 - I can handle difficult situations without needing emotional support from anyone else.
 - Whenever I feel worried about something, I want to share my concern with another person.
 - I rarely discuss my problems with other people.

```{r}
model <- "HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04"
```

#### Sentimentality

 - I feel like crying when I see other people crying.
 - When someone I know well is unhappy, I can almost feel that person's pain myself.
 - I feel strong emotions when someone close to me is going away for a long time.
 - I remain unemotional even in situations where most people get very sentimental.

```{r}
model <- "HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04"
```

### Extraversion
#### Social Self-Esteem

 - I feel reasonably satisfied with myself overall.
 - I think that most people like some aspects of my personality.
 - I feel that I am an unpopular person.
 - Even in an emergency I wouldn't feel like panicking.

```{r}
model <- "HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04"
```

#### Social Boldness

 - I rarely express my opinions in group meetings.
 - In social situations, I'm usually the one who makes the first move.
 - When I'm in a group of people, I'm often the one who speaks on behalf of the group.
 - I tend to feel quite self-conscious when speaking in front of a group of people.

```{r}
model <- "HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04"
```

#### Sociability

 - I avoid making "small talk" with people.
 - I enjoy having lots of people around to talk with.
 - I prefer jobs that involve active social interaction to those that involve working alone.
 - The first thing that I always do in a new place is to make friends.

```{r}
model <- "HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04"
```

#### Liveliness

 - I am energetic nearly all the time.
 - On most days, I feel cheerful and optimistic.
 - People often tell me that I should try to cheer up.
 - Most people are more upbeat and dynamic than I generally am.

```{r}
model <- "HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04"
```

### Agreeableness
#### Forgiveness

 - I rarely hold a grudge, even against people who have badly wronged me.
 - My attitude toward people who have treated me badly is "forgive and forget".
 - If someone has cheated me once, I will always feel suspicious of that person.
 - I find it hard to fully forgive someone who has done something mean to me.

```{r}
model <- "HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04"
```

#### Gentleness

 - People sometimes tell me that I am too critical of others.
 - I generally accept people’s faults without complaining about them.
 - I tend to be lenient in judging other people.
 - Even when people make a lot of mistakes, I rarely say anything negative.

```{r}
model <- "HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04"
```

#### Flexibility

 - People sometimes tell me that I'm too stubborn.
 - I am usually quite flexible in my opinions when people disagree with me.
 - When people tell me that I’m wrong, my first reaction is to argue with them.
 - I find it hard to compromise with people when I really think I’m right.

```{r}
model <- "HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04"
```

#### Patience

 - People think of me as someone who has a quick temper.
 - I rarely feel anger, even when people treat me quite badly.
 - Most people tend to get angry more quickly than I do.
 - I find it hard to keep my temper when people insult me.

```{r}
model <- "HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04"
```

### Conscientiousness
#### Organization

 - I clean my office or home quite frequently.
 - I plan ahead and organize things, to avoid scrambling at the last minute.
 - People often joke with me about the messiness of my room or desk.
 - When working, I sometimes have difficulties due to being disorganized.

```{r}
model <- "HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04"
```

#### Diligence

 - When working, I often set ambitious goals for myself.
 - I often push myself very hard when trying to achieve a goal.
 - Often when I set a goal, I end up quitting without having reached it.
 - I do only the minimum amount of work needed to get by.

```{r}
model <- "HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04"
```

#### Perfectionism

 - I often check my work over repeatedly to find any mistakes.
 - When working on something, I don't pay much attention to small details.
 - I always try to be accurate in my work, even at the expense of time.
 - People often call me a perfectionist.

```{r}
model <- "HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04"
```

#### Prudence

 - I make decisions based on the feeling of the moment rather than on careful thought.
 - I make a lot of mistakes because I don't think before I act.
 - I don’t allow my impulses to govern my behavior.
 - I prefer to do whatever comes to mind, rather than stick to a plan.

```{r}
model <- "HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04"
```

### Openness
#### Aesthetic Appreciation

 - I would be quite bored by a visit to an art gallery.
 - I wouldn't spend my time reading a book of poetry.
 - If I had the opportunity, I would like to attend a classical music concert.
 - Sometimes I like to just watch the wind as it blows through the trees.

```{r}
model <- "HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04"
```

#### Inquisitiveness

 - I'm interested in learning about the history and politics of other countries.
 - I enjoy looking at maps of different places.
 - I would be very bored by a book about the history of science and technology.
 - I’ve never really enjoyed looking through an encyclopedia.

```{r}
model <- "HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04"
```

#### Creativeness

 - I would like a job that requires following a routine rather than being creative.
 - I would enjoy creating a work of art, such as a novel, a song, or a painting.
 - People have often told me that I have a good imagination.
 - I don't think of myself as the artistic or creative type.

```{r}
model <- "HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04"
```

#### Unconventionality

 - I think that paying attention to radical ideas is a waste of time.
 - I like people who have unconventional views.
 - I think of myself as a somewhat eccentric person.
 - I find it boring to discuss philosophy.

```{r}
model <- "HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04"
```

### Altruism

 - I have sympathy for people who are less fortunate than I am.
 - I try to give generously to those in need.
 - It wouldn’t bother me to harm someone I didn’t like.
 - People see me as a hard-hearted person.

```{r}
model <- "HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04"
```

## Need for privacy
### Informational

 - I would prefer that little is known about me. 
 - In general, I prefer to remain incognito. 
 - I don’t want my personal data to be publicly accessible. 
 - Not everyone has to know everything about me.

```{r}
model <- "NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04"
```

### Psychological

 - I don’t like to talk about personal issues unless others do it first.
 - There are a lot of things about me that I don’t like to talk about with others. 
 - I feel uncomfortable when others tell me private things about their lives. 
 - It is hard for me to talk about my feelings and inner thoughts.

```{r}
model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
```

### Physiological

 - I don’t like it when strangers come too close to me. 
 - I feel uncomfortable when others enter my flat or room unannounced. 
 - I don’t like to stand in a dense crowd of people. 
 - I don’t like to sit next to a stranger on the tram or bus.

```{r}
model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
```

### Privacy from other People

 - My need for privacy is so strong that it prevents me from using social media actively. 
 - I don’t feel I need to tell my friends all my secrets.
 - I feel I need to protect my privacy from other people.
 - I prefer it when others don’t know much about me.

```{r}
model <- "NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04"
```

#### Validation

### Privacy from Government

 - I need government agencies to respect my privacy, even if that makes catching criminals harder.,
 - I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
 - I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
 - I feel I need to protect my privacy from government agencies.

```{r}
model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
```

#### Validation

### Privacy need anonymity

 - I need to be able to use a fake account on social network sites to preserve my privacy. 
 - I feel I need to avoid places with video surveillance.
 - I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
 - I need to be able to surf the Internet anonymously. (new)

```{r}
model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
```

#### Validation

### Privacy from Companies

 - I’m willing to pay more for products or services so that companies don’t have to sell my data.
 - I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
 - I don’t want companies to gather information about me, even if that reduces the quality of their services.
 - I feel I need to protect my privacy from companies.

```{r}
model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
```

#### Validation

### General Need for privacy

 - I need a lot of privacy.
 - Privacy is very important to me.
 - I think a lot about how I can protect my privacy.
 - I need a lot of time for myself.

```{r}
model <- "NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04"
```

#### Validation

# Power Analyses

To estimate sample size, we conducted a rudimentary power analysis. That is, we planned for a two-sided correlation of r = .1. We adopted a balanced alpha and beta error approach. Because we were in exploration mode, we aimed for a high statistical power and relaxed alpha. Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget. Instead, we opted for an error rate of 10%.

```{r}
sesoi <- .1

# a priori power analyses
pwr.r.test(r = sesoi, sig.level = .05, power = .95) ## too expensive
```

A 5% error rate would imply collecting 1.293 participants, which was outside of our budget.

```{r}
pwr.r.test(r = sesoi, sig.level = .1, power = .9)
```

A 10% error rate would imply collecting 853 participants, which was within our budget.

```{r}
power <- pwr.r.test(r = sesoi, sig.level = .05, power = .8)
print(power)
power_n <- power$n
```

# Results
## Facets

```{r}
model_fac <- "
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
age =~ AGE
gender =~ GEN
ethnicity =~ ETH
relationship =~ REL_
college =~ COL_
income =~ INC
conservatism =~ CON
"
fit_fac <- sem(model_fac, d, estimator = "ML", fixed.x = TRUE)
summary(fit_fac, standardized = TRUE)

d_fac <- 
  standardizedsolution(fit_fac, ci = TRUE, level = .90) %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri)

fig_fac <- ggplot(d_fac, aes(x = est.std, y = lhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
  facet_wrap(vars(rhs), nrow = 1)

# tab_results <- data.frame(
#   tab_results_raw[1 : length(vars_pers_fac), ]$std.all,
#   tab_results_raw[(1 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 2), ]$std.all,
#   tab_results_raw[(2 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 3), ]$std.all,
#   tab_results_raw[(3 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 4), ]$std.all,
#   tab_results_raw[(4 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 5), ]$std.all,
#   tab_results_raw[(5 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 6), ]$std.all,
#   tab_results_raw[(6 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 7), ]$std.all,
#   tab_results_raw[(7 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 8), ]$std.all,
#   tab_results_raw[(8 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 9), ]$std.all,
#   tab_results_raw[(9 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 10), ]$std.all
# )
# names(tab_results) <- vars_pri
# rownames(tab_results) <- vars_pers_fac
```

## Factors

Factor or dimensions.

```{r}
model_dim <- "
HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04

HEX_EMO =~ HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN
HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04

HEX_EXT =~ HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV
HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04

HEX_AGR =~ HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT
HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04

HEX_CNS =~ HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU
HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04

HEX_OPN =~ HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC
HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04

NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
"
fit_dim <- sem(model_dim, d, estimator = "ML", fixed.x = TRUE)
summary(fit_dim, standardized = TRUE)

# extract results
d_dim <- 
  standardizedsolution(fit_dim, ci = TRUE, level = .90) %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri)

fig_dim <- ggplot(d_dim, aes(x = est.std, y = lhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
  facet_wrap(vars(rhs), nrow = 1)

# tab_results <- data.frame(
#   tab_results_raw[1 : length(vars_pers_dim), ]$std.all,
#   tab_results_raw[(1 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 2), ]$std.all,
#   tab_results_raw[(2 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 3), ]$std.all,
#   tab_results_raw[(3 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 4), ]$std.all,
#   tab_results_raw[(4 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 5), ]$std.all,
#   tab_results_raw[(5 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 6), ]$std.all,
#   tab_results_raw[(6 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 7), ]$std.all,
#   tab_results_raw[(7 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 8), ]$std.all,
#   tab_results_raw[(8 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 9), ]$std.all,
#   tab_results_raw[(9 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 10), ]$std.all
# )
# names(tab_results) <- vars_pri
# rownames(tab_results) <- vars_pers_dim
```

## SES

```{r}
model_ses <- "
age =~ AGE
gender =~ GEN
ethnicity =~ ETH
relationship =~ REL_
college =~ COL_
income =~ INC
conservatism =~ CON
NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
"
fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
summary(fit_ses, standardized = TRUE)

# extract results
d_ses <- 
  standardizedsolution(fit_ses, ci = TRUE, level = .90) %>% 
  as.data.frame() %>% 
  filter(op == "~~", lhs %in% vars_ses, rhs %in% vars_pri)

fig_ses <- ggplot(d_ses, aes(x = est.std, y = lhs)) +
  geom_point() +
  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
  facet_wrap(vars(rhs), nrow = 1)

# tab_results <- data.frame(
#   tab_results_raw[1 : length(vars_ses), ]$std.all,
#   tab_results_raw[(1 * length(vars_ses) + 1) : (length(vars_ses) * 2), ]$std.all,
#   tab_results_raw[(2 * length(vars_ses) + 1) : (length(vars_ses) * 3), ]$std.all,
#   tab_results_raw[(3 * length(vars_ses) + 1) : (length(vars_ses) * 4), ]$std.all,
#   tab_results_raw[(4 * length(vars_ses) + 1) : (length(vars_ses) * 5), ]$std.all,
#   tab_results_raw[(5 * length(vars_ses) + 1) : (length(vars_ses) * 6), ]$std.all,
#   tab_results_raw[(6 * length(vars_ses) + 1) : (length(vars_ses) * 7), ]$std.all,
#   tab_results_raw[(7 * length(vars_ses) + 1) : (length(vars_ses) * 8), ]$std.all,
#   tab_results_raw[(8 * length(vars_ses) + 1) : (length(vars_ses) * 9), ]$std.all,
#   tab_results_raw[(9 * length(vars_ses) + 1) : (length(vars_ses) * 10), ]$std.all
# )
# names(tab_results) <- vars_pri
# rownames(tab_results) <- vars_ses
```

```{r}
save.image("data/workspace.RData")
```

### 2021-08-25 analyses_readability.Rmd
- setting up repo - changed initial submission already strongly

---
title: "Readability analyses of items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 90)
```

```{r r-setup, include=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse", "td")

# load packages
lapply(packages, library, character.only = TRUE)

# readability function
readability = function(data){
  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
  textstat_readability(data, measure = reading_estimates) %>% 
    as.data.frame %>% 
    mutate(average = rowMeans(select(., -document)))
}
```

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")
```

Below, we develop several new items for need for privacy. To validate items, we follow the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and calculate the following four reading scores: Flesch–Kincaid reading grade (FK), Gunning Fog Index (GFI), Coleman Liau Index (CLI), and the Powers-Sumner-Kearl Variation of the Dale and Chall Readability formula (DC).

To have a benchmark, we calculated the readability of the HEXACO items. It was as follows:

```{r}
items_hexaco <- c(
  "If I want something from a person I dislike, I will act very nicely toward that person in order to get it.", 
 "I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.", 
 "If I want something from someone, I will laugh at that person's worst jokes.", 
 "I wouldn't pretend to like someone just to get that person to do favors for me.", 
 "If I knew that I could never get caught, I would be willing to steal a million dollars.", 
 "I would be tempted to buy stolen property if I were financially tight.", 
 "I would never accept a bribe, even if it were very large.", 
 "I’d be tempted to use counterfeit money, if I were sure I could get away with it.", 
 "Having a lot of money is not especially important to me.", 
 "I would like to live in a very expensive, high-class neighborhood.", 
 "I would like to be seen driving around in a very expensive car.", 
 "I would get a lot of pleasure from owning expensive luxury goods.", 
 "I am an ordinary person who is no better than others.", 
 "I wouldn’t want people to treat me as though I were superior to them.", 
 "I think that I am entitled to more respect than the average person is.", 
 "I want people to know that I am an important person of high status.", 
 "I would feel afraid if I had to travel in bad weather conditions.", 
 "I don’t mind doing jobs that involve dangerous work.", 
 "When it comes to physical danger, I am very fearful.", 
 "Even in an emergency I wouldn't feel like panicking.", 
 "I sometimes can't help worrying about little things.", 
 "I worry a lot less than most people do.", 
 "I rarely, if ever, have trouble sleeping due to stress or anxiety.", 
 "I get very anxious when waiting to hear about an important decision.", 
 "When I suffer from a painful experience, I need someone to make me feel comfortable.", 
 "I can handle difficult situations without needing emotional support from anyone else.", 
 "Whenever I feel worried about something, I want to share my concern with another person.", 
 "I rarely discuss my problems with other people.", 
 "I feel like crying when I see other people crying.", 
 "When someone I know well is unhappy, I can almost feel that person's pain myself.", 
 "I feel strong emotions when someone close to me is going away for a long time.", 
 "I remain unemotional even in situations where most people get very sentimental.", 
 "I feel reasonably satisfied with myself overall.", 
 "I think that most people like some aspects of my personality.", 
 "I feel that I am an unpopular person.", 
 "Even in an emergency I wouldn't feel like panicking.", 
 "I rarely express my opinions in group meetings.", 
 "In social situations, I'm usually the one who makes the first move.", 
 "When I'm in a group of people, I'm often the one who speaks on behalf of the group.", 
 "I tend to feel quite self-conscious when speaking in front of a group of people.", 
 "I avoid making 'small talk' with people.", 
 "I enjoy having lots of people around to talk with.", 
 "I prefer jobs that involve active social interaction to those that involve working alone.", 
 "The first thing that I always do in a new place is to make friends.", 
 "I am energetic nearly all the time.", 
 "On most days, I feel cheerful and optimistic.", 
 "People often tell me that I should try to cheer up.", 
 "Most people are more upbeat and dynamic than I generally am.", 
 "I rarely hold a grudge, even against people who have badly wronged me.", 
 "My attitude toward people who have treated me badly is 'forgive and forget'.", 
 "If someone has cheated me once, I will always feel suspicious of that person.", 
 "I find it hard to fully forgive someone who has done something mean to me.", 
 "People sometimes tell me that I am too critical of others.", 
 "I generally accept people’s faults without complaining about them.", 
 "I tend to be lenient in judging other people.", 
 "Even when people make a lot of mistakes, I rarely say anything negative.", 
 "People sometimes tell me that I'm too stubborn.", 
 "I am usually quite flexible in my opinions when people disagree with me.", 
 "When people tell me that I’m wrong, my first reaction is to argue with them.", 
 "I find it hard to compromise with people when I really think I’m right.", 
 "People think of me as someone who has a quick temper.", 
 "I rarely feel anger, even when people treat me quite badly.", 
 "Most people tend to get angry more quickly than I do.", 
 "I find it hard to keep my temper when people insult me.", 
 "I clean my office or home quite frequently.", 
 "I plan ahead and organize things, to avoid scrambling at the last minute.", 
 "People often joke with me about the messiness of my room or desk.", 
 "When working, I sometimes have difficulties due to being disorganized.", 
 "When working, I often set ambitious goals for myself.", 
 "I often push myself very hard when trying to achieve a goal.", 
 "Often when I set a goal, I end up quitting without having reached it.", 
 "I do only the minimum amount of work needed to get by.", 
 "I often check my work over repeatedly to find any mistakes.", 
 "When working on something, I don't pay much attention to small details.", 
 "I always try to be accurate in my work, even at the expense of time.", 
 "People often call me a perfectionist.", 
 "I make decisions based on the feeling of the moment rather than on careful thought.", 
 "I make a lot of mistakes because I don't think before I act.", 
 "I don’t allow my impulses to govern my behavior.", 
 "I prefer to do whatever comes to mind, rather than stick to a plan.", 
 "I would be quite bored by a visit to an art gallery.", 
 "I wouldn't spend my time reading a book of poetry.", 
 "If I had the opportunity, I would like to attend a classical music concert.", 
 "Sometimes I like to just watch the wind as it blows through the trees.", 
 "I'm interested in learning about the history and politics of other countries.", 
 "I enjoy looking at maps of different places.", 
 "I would be very bored by a book about the history of science and technology.", 
 "I’ve never really enjoyed looking through an encyclopedia.", 
 "I would like a job that requires following a routine rather than being creative.", 
 "I would enjoy creating a work of art, such as a novel, a song, or a painting.", 
 "People have often told me that I have a good imagination.", 
 "I don't think of myself as the artistic or creative type.", 
 "I think that paying attention to radical ideas is a waste of time.", 
 "I like people who have unconventional views.", 
 "I think of myself as a somewhat eccentric person.", 
 "I find it boring to discuss philosophy.", 
 "I have sympathy for people who are less fortunate than I am.", 
 "I try to give generously to those in need.", 
 "It wouldn’t bother me to harm someone I didn’t like.", 
 "People see me as a hard-hearted person."
)
readability_hexaco <- readability(items_hexaco)
readability_hexaco <- colMeans(select(readability_hexaco, -document))
readability_hexaco <- data.frame(document = "HEXACO", as.list(readability_hexaco))
readability_hexaco
```

Readability was good. The results means that, on average, understanding the items requires seven years of schooling.

# Privacy from Government

 - I need government agencies to respect my privacy, even if that hinders a greater societal cause, such as catching criminals.
 - I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.
 - I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.
 - I feel I need to protect my privacy from government agencies.

```{r}
items_old <- c(
 "I need government agencies to respect my privacy, even if that hinders a greater societal cause, such as catching criminals.",
 "I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.",
 "I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.",
 "I feel I need to protect my privacy from government agencies."
)
readability(items_old) %>% rbind(readability_hexaco)
```

Items 1, 2 and 3 show rather high scores. Try to formulate easier.

New items:

 - I need government agencies to respect my privacy, even if that makes catching criminals harder.,
 - I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
 - I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
 - I feel I need to protect my privacy from government agencies.

```{r}
items_new <- c(
 "I need government agencies to respect my privacy, even if that makes catching criminals harder.",
 "I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.",
  "I don’t want government agencies to track my communication, even if that stops terrorist attacks.",
  "I feel I need to protect my privacy from government agencies."
)
readability(items_new) %>% rbind(readability_hexaco)
```

A bit better, but not much.

```{r}
model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
```

# Privacy from other People

 - My need for privacy is so strong that it prevents me from using social media actively. 
 - I don’t feel I need to tell my friends all my secrets.
 - I feel I need to protect my privacy from other people.
 - I prefer it when others don’t know much about me.

```{r}
items <- c(
 "My need for privacy is so strong that it prevents me from using social media actively.",
 "I don’t feel I need to tell my friends all my secrets.",
 "I feel I need to protect my privacy from other people.",
 "I prefer it when others don’t know much about me."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability looks good!

```{r}
model <- "NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04"
```

# Privacy need anonymity

 - I need to be able to use a fake account on social network sites to preserve my privacy. 
 - I feel I need to avoid places with video surveillance.
 - I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
 - I need to be able to surf the Internet anonymously. (new)

```{r}
items <- c(
 "I need to be able to use a fake account on social network sites to preserve my privacy.",
 "I feel I need to avoid places with video surveillance.",
 "I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.",
 "I need to be able to surf the Internet anonymously."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability looks good!

```{r}
model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
```

# Privacy from Companies

 - I’m willing to pay more for products or services so that companies don’t have to sell my data.
 - I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
 - I don’t want companies to gather information about me, even if that reduces the quality of their services.
 - I feel I need to protect my privacy from companies.

```{r}
items <- c(
 "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
 "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
 "I don’t want companies to collect data about me, even if that makes their services worse.",
 "I feel I need to protect my privacy from companies."
)
readability(items) %>% rbind(readability_hexaco)
```

Items 3 seems to be a bit too difficult. Try to make easier.

```{r}
items <- c(
 "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
 "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
 "I don’t want companies to gather information about me, even if that lowers the quality of their services.",
 "I feel I need to protect my privacy from companies."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability now much better.

```{r}
model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
```

# General Need for privacy

 - I need a lot of privacy.
 - Privacy is very important to me.
 - I think a lot about how I can protect my privacy.
 - I need a lot of time for myself.

```{r}
items <- c(
  "I need a lot of privacy.",
  "Privacy is very important to me.",
  "I think a lot about how I can protect my privacy.",
  "I need a lot of time for myself."
)
readability(items) %>% rbind(readability_hexaco)
```

Readability was good.

### 2021-08-25 index.Rmd
- setting up repo - changed initial submission already strongly

---
title: "Who needs privacy?"
---

On this website, you can find the companion material for the paper _Who needs privacy? Exploring the relation between personality and need for privacy_.

You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf). You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.

This website is produced directly from the project's [github repository](https://github.com/tdienlin/who_needs_privacy_rr). You can download the material and the data, file an issue, or submit a pull request.

### 2021-08-25 items.rmd
- setting up repo - changed initial submission already strongly

---
title: "Items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
# pdf_document:
#   toc: TRUE
---

All items were answered on a 7-point scale with the following options:

"To what extent do you agree or disagree with the following statements?"

(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree

# Personality
## Honesty Humility
### Sincerity

 1. If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
 1. I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
 1. If I want something from someone, I will laugh at that person's worst jokes.
 1. I wouldn't pretend to like someone just to get that person to do favors for me.

### Fairness

 1. If I knew that I could never get caught, I would be willing to steal a million dollars.
 1. I would be tempted to buy stolen property if I were financially tight.
 1. I would never accept a bribe, even if it were very large.
 1. I’d be tempted to use counterfeit money, if I were sure I could get away with it.

### Greed Avoidance

 1. Having a lot of money is not especially important to me.
 1. I would like to live in a very expensive, high-class neighborhood.
 1. I would like to be seen driving around in a very expensive car.
 1. I would get a lot of pleasure from owning expensive luxury goods.

### Modesty

 1. I am an ordinary person who is no better than others.
 1. I wouldn’t want people to treat me as though I were superior to them.
 1. I think that I am entitled to more respect than the average person is.
 1. I want people to know that I am an important person of high status.

## Emotionality
### Fearfulness

 1. I would feel afraid if I had to travel in bad weather conditions.
 1. I don’t mind doing jobs that involve dangerous work.
 1. When it comes to physical danger, I am very fearful.
 1. Even in an emergency I wouldn't feel like panicking.

### Anxiety

 1. I sometimes can't help worrying about little things.
 1. I worry a lot less than most people do.
 1. I rarely, if ever, have trouble sleeping due to stress or anxiety.
 1. I get very anxious when waiting to hear about an important decision.

### Dependence
 1. When I suffer from a painful experience, I need someone to make me feel comfortable.
 1. I can handle difficult situations without needing emotional support from anyone else.
 1. Whenever I feel worried about something, I want to share my concern with another person.
 1. I rarely discuss my problems with other people.

### Sentimentality

 1. I feel like crying when I see other people crying.
 1. When someone I know well is unhappy, I can almost feel that person's pain myself.
 1. I feel strong emotions when someone close to me is going away for a long time.
 1. I remain unemotional even in situations where most people get very sentimental.

## Extraversion
### Social Self-Esteem

 1. I feel reasonably satisfied with myself overall.
 1. I think that most people like some aspects of my personality.
 1. I feel that I am an unpopular person.
 1. Even in an emergency I wouldn't feel like panicking.

### Social Boldness

 1. I rarely express my opinions in group meetings.
 1. In social situations, I'm usually the one who makes the first move.
 1. When I'm in a group of people, I'm often the one who speaks on behalf of the group.
 1. I tend to feel quite self-conscious when speaking in front of a group of people.

### Sociability

 1. I avoid making "small talk" with people.
 1. I enjoy having lots of people around to talk with.
 1. I prefer jobs that involve active social interaction to those that involve working alone.
 1. The first thing that I always do in a new place is to make friends.

### Liveliness

 1. I am energetic nearly all the time.
 1. On most days, I feel cheerful and optimistic.
 1. People often tell me that I should try to cheer up.
 1. Most people are more upbeat and dynamic than I generally am.

## Agreeableness
### Forgiveness

 1. I rarely hold a grudge, even against people who have badly wronged me.
 1. My attitude toward people who have treated me badly is "forgive and forget".
 1. If someone has cheated me once, I will always feel suspicious of that person.
 1. I find it hard to fully forgive someone who has done something mean to me.

### Gentleness

 1. People sometimes tell me that I am too critical of others.
 1. I generally accept people’s faults without complaining about them.
 1. I tend to be lenient in judging other people.
 1. Even when people make a lot of mistakes, I rarely say anything negative.

### Flexibility

 1. People sometimes tell me that I'm too stubborn.
 1. I am usually quite flexible in my opinions when people disagree with me.
 1. When people tell me that I’m wrong, my first reaction is to argue with them.
 1. I find it hard to compromise with people when I really think I’m right.

### Patience

 1. People think of me as someone who has a quick temper.
 1. I rarely feel anger, even when people treat me quite badly.
 1. Most people tend to get angry more quickly than I do.
 1. I find it hard to keep my temper when people insult me.

## Conscientiousness
### Organization

 1. I clean my office or home quite frequently.
 1. I plan ahead and organize things, to avoid scrambling at the last minute.
 1. People often joke with me about the messiness of my room or desk.
 1. When working, I sometimes have difficulties due to being disorganized.

### Diligence

 1. When working, I often set ambitious goals for myself.
 1. I often push myself very hard when trying to achieve a goal.
 1. Often when I set a goal, I end up quitting without having reached it.
 1. I do only the minimum amount of work needed to get by.

### Perfectionism

 1. I often check my work over repeatedly to find any mistakes.
 1. When working on something, I don't pay much attention to small details.
 1. I always try to be accurate in my work, even at the expense of time.
 1. People often call me a perfectionist.

### Prudence

 1. I make decisions based on the feeling of the moment rather than on careful thought.
 1. I make a lot of mistakes because I don't think before I act.
 1. I don’t allow my impulses to govern my behavior.
 1. I prefer to do whatever comes to mind, rather than stick to a plan.

## Openness
### Aesthetic Appreciation

 1. I would be quite bored by a visit to an art gallery.
 1. I wouldn't spend my time reading a book of poetry.
 1. If I had the opportunity, I would like to attend a classical music concert.
 1. Sometimes I like to just watch the wind as it blows through the trees.

### Inquisitiveness

 1. I'm interested in learning about the history and politics of other countries.
 1. I enjoy looking at maps of different places.
 1. I would be very bored by a book about the history of science and technology.
 1. I’ve never really enjoyed looking through an encyclopedia.

### Creativeness

 1. I would like a job that requires following a routine rather than being creative.
 1. I would enjoy creating a work of art, such as a novel, a song, or a painting.
 1. People have often told me that I have a good imagination.
 1. I don't think of myself as the artistic or creative type.

### Unconventionality

 1. I think that paying attention to radical ideas is a waste of time.
 1. I like people who have unconventional views.
 1. I think of myself as a somewhat eccentric person.
 1. I find it boring to discuss philosophy.

## Altruism

 1. I have sympathy for people who are less fortunate than I am.
 1. I try to give generously to those in need.
 1. It wouldn’t bother me to harm someone I didn’t like.
 1. People see me as a hard-hearted person.

# Need for privacy
## Informational

 1. I would prefer that little is known about me. 
 1. In general, I prefer to remain incognito. 
 1. I don’t want my personal data to be publicly accessible. 
 1. Not everyone has to know everything about me.

## Psychological

 1. I don’t like to talk about personal issues unless others do it first.
 1. There are a lot of things about me that I don’t like to talk about with others. 
 1. I feel uncomfortable when others tell me private things about their lives. 
 1. It is hard for me to talk about my feelings and inner thoughts.

## Physiological

 1. I don’t like it when strangers come too close to me. 
 1. I feel uncomfortable when others enter my flat or room unannounced. 
 1. I don’t like to stand in a dense crowd of people. 
 1. I don’t like to sit next to a stranger on the tram or bus.

## Social

 1. My need for privacy is so strong that it prevents me from using social media actively. 
 1. I don’t feel I need to tell my friends all my secrets.
 1. I feel I need to protect my privacy from other people.
 1. I prefer it when others don’t know much about me.

## Privacy from Government

 1. I need government agencies to respect my privacy, even if that makes catching criminals harder.,
 1. I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
 1. I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
 1. I feel I need to protect my privacy from government agencies.

## Privacy need anonymity

 1. I need to be able to use a fake account on social network sites to preserve my privacy. 
 1. I feel I need to avoid places with video surveillance.
 1. I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
 1. I need to be able to surf the Internet anonymously. (new)

## Privacy from Companies

 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
 1. I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
 1. I don’t want companies to gather information about me, even if that reduces the quality of their services.
 1. I feel I need to protect my privacy from companies.

## General Need for privacy

 1. I need a lot of privacy.
 1. Privacy is very important to me.
 1. I think a lot about how I can protect my privacy.
 1. I need a lot of time for myself.

### 2021-08-25 proposal.Rmd
- setting up repo - changed initial submission already strongly

---
title             : "Who Needs Privacy? Exploring the relation between personality and need for privacy"
shorttitle        : "Who Needs Privacy?"

author: 
  - name          : "Tobias Dienlin"
    affiliation   : "1"
    corresponding : yes
    address       : "University of Vienna, Department of Communication, 1090 Vienna, Austria"
    email         : "tobias.dienlin@univie.ac.at"
  - name          : "Miriam Metzger"
    affiliation   : "2"
    email         : "metzger@ucsb.edu"

affiliation:
  - id            : "1"
    institution   : "University of Vienna"
  - id            : "2"
    institution   : "University of California Santa Barbara"

authornote: |
  Tobias Dienlin, Department of Communication, University of Vienna, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.

  Competing Interests: Both authors declare no competing interests.

  Data Accessibility Statement: All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/7ncpk/).

  Funding Information: During the conception and data collection of the prestudy, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported a research stay at UCSB. During some time working on the article and while at University of Hohenheim, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy". TD is now funded by a regular and not-tenured assistant professorship at University of Vienna. MM is funded by a regular and tenured full professorship at UCSB.

# In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/).

# Author contribution: conception and design: TD, MM; acquisition of data: MM, TD; code: TD; analysis and interpretation of data: TD, MM; First draft: TD; Revisions & Comments: TD & MM

abstract          : "Privacy is an important societal topic. Living in an information age, people constantly have to decide what information to share, which service to use, or when to communicate. All these decisions are reflective of and determined by the users' need for privacy. It is relevant to understand who needs more and who needs less privacy, because desiring privacy often requires justification. For example, well-known statements such as 'who has nothing to hide has nothing to fear' imply that people who desire privacy are suspicious. Although such suspicions might be justified in some cases, it could also be that people desiring more privacy are just more introverted, anxious, creative, or prudent. In this study we, hence, plan to explore the relation between personality and the need for privacy. Personality factors and facets will be operationalized using the HEXACO personality inventory. Need for privacy will be captured with a multidimensional approach, including informational and social privacy, need for privacy from government agencies, or need fro privacy from companies. Adopting an exploratory analytical framework, we will collect a sample of more than 800 respondents representative of the US in terms of age, gender, and ethnicity. The relations between personality and privacy will be explored using structural equation modeling. Potential implications will be discussed."
keywords          : "Privacy, need for privacy, personality, HEXACO, structural equation modeling"

bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
  - \note{\clearpage}
---

```{r analysis-preferences, include=F}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
                      fig.pos = 'h')
```

```{r setup, include=F}
# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
              "magrittr", "papaja", "semPlot", "td", "tidyverse")
lapply(packages, library, character.only = TRUE)
load("data/workspace.RData")

# export references
r_refs(file = "bibliography/r-references.bib")
```

In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016], privacy has become a major topic of public and academic interest. 
Despite the topic's importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
Why do some people feel they need or desire more privacy than others do, and how do these people differ from one another?

We believe it is relevant to understand better this research questions, because people who desire privacy are often confronted to justify their need for privacy. 
For example, well-known statements such as 'who has nothing to hide has nothing to fear' imply that people who desire privacy are suspicious.
Indeed, it is only logical that people who commit crimes and who are insincere in fact benefit from more privacy.
However, it could also be that people desiring more privacy are just more introverted, anxious, creative, or prudent. 
We therefore believe that a better understanding of the relation between personality and privacy is relevant. 
Also from an academic perspective, several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155]
However, to date there is almost no empirical research that can be used to deduce well-informed hypotheses. 
As a result, the main question of this paper is: 
What are personality factors and facets that best explain peoples' felt need for privacy?

## The Need for Privacy

Because orivacy as a theoretical concept is complicated and contested [@nissenbaumPrivacyContextTechnology2010, p. 71], we first outline our own understanding of privacy. 
First and foremost, privacy captures the extent of (a) _voluntary_ (b) _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967]. 
Several models suggest that privacy is multi-dimensional. 
For example, in a theory-driven treatise [@burgoonPrivacyCommunication1982] argued that privacy has four dimensions: informational, social, psychological, and physical privacy. 
[@pedersenDimensionsPrivacy1979], by contrast, conducted an empirical factor analysis initially starting with 94 items and found that privacy exists on six dimensions: 
reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. 
Next, [@schwartzSocialPsychologyPrivacy1968] or [@masurPrivatheitOnlineKommunikation2018] differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies). 
The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1]. 
<!-- Finally, one can also distinguish between the objective privacy context (e.g., how many users can actually read a post on an SNS?), subjective privacy perceptions (e.g., how many users people _think_ can read a post on an SNS?), and resulting privacy behaviors (e.g., how much do people self-disclose?) [@dienlinPrivacyProcessModel2014]. -->

For the purpose of this study, we will hence employ a multifaceted model of need for privacy.
We fill focus on (a) vertical privacy with regard to people's felt need for withdrawal from government surveillance and private companies, (b) horizontal privacy in terms of the perceived need for withdrawal from other people, psychological and physical privacy, and (c) both horizontal and vertical privacy as captured by people's felt need for informational privacy, anonymity, and privacy in general.

<!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->
According to @trepteNeedPrivacy2017, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs such as safety, sexuality, recovery, or contemplation.
Specifically, [@westinPrivacyFreedom1967] defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships). 
Not least, privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], which is necessary for attaining social support, initiating relationships, and getting close to other people [@omarzuDisclosureDecisionModel2000].

On the other hand, however, privacy also has negative aspects. 
For example, it can be problematic if there is too much privacy.
Human beings are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
The fact that privacy fosters self-disclosure presents also a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010]. 
Privacy can also help conceal power-asymmetries, wrongdoing, or violence and other crimes. 
The dialectical tension between the positive and negative aspects of privacy likely causes variability across individuals in their need for privacy.

## Predicting the Need for Privacy

What role does personality play in determining individual-level variations in need for privacy?
So far, not a lot of studies have analyzed this question explicitly.
We are aware of only two studies that conducted an empirical analysis [pedersenPersonalityCorrelatesPrivacy1982, @hosmanRelationshipsNeedPrivacy1991].
And as there is no established theory connecting privacy and personality, it is difficult to deduce precise and well-informed hypotheses. 
As a result, in this study we adopt an exploratory perspective.
Not to miss potentially relevant personality factors and facets, we will adopt a large-scale perspective on personality.

To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018], which is in the tradition of Big Five approach [@johnBigFiveTrait1999] and which represents a broad understanding of personality.
The HEXACO inventory measures overall six factors (see below), which each have four more specific facets. 
Including the facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations with the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and include also specific personality facets.
Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility plus a facet labeled Altruism, which seem promising to investigate the nothing to hide argument. 
We chose 
<!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
In what follows, we briefly present all factors and outline how they and selected facets might relate to privacy.

<!-- The rationales that we outline below should hence be considered tentative suggestions toward a theory of personality and privacy. Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be formed. -->

Our reasoning further was guided by another central theoretical tenet. 
As suggested above, privacy can be either positive or negative. 
Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_. 
Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat. 
It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976].

### Honesty-Humility

More controversially, it has been argued by some that people need privacy because they have something to hide. 
The so-called nothing-to-hide argument states that “If you have nothing to hide, you have nothing to fear.” 
As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
Only those who are engaged in illegal activities have a reason to hide this information” [@Solove.2007, p. 753]. 
Hence, another potential predictor of why people need privacy could also be a so-called "lack" of integrity.

Because integrity is a delicate concept, let us first try to define it conceptually. 
Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity “incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness” [@Connelly.2006, p. 82]. 
In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator definition, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.

It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy. 
People who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would surely disapprove of their activities [@Petronio.2010]. 
Hence, the government and other people are more likely to be perceived as a threat, which should render anonymity  a resource. 
As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].

There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity. 
For example, studies have found that surveillance can reduce cheating behaviors [@Corcoran.1987; @Covey.1989]. 
@Covey.1989 for example asked students to solve an impossible maze. 
In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
In the low surveillance condition, the experimenter remained behind the students where he or she could not see the students. 
Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors). 
Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013a], people who felt they needed more privacy were also less authentic on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28). 
Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence also reason that the concept of integrity might relate to a person’s perceived need for privacy. 
Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy [@Junglas.2008]. 
Finally, @pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem: 
Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24). 
While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as moral, nice, fair, unselfish, good, honest, and reputable (p. 12).

In conclusion, we could imagine that lack of integrity may indeed relate to an increased felt need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities. 
Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers. 
Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.

### Emotionality

Next, it seems possible that the need for privacy is also related to people's level of general anxiety [which is a subdimension of neuroticism, @Costa.1992b]. 
General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened. 
With regard to interpersonal privacy, one could argue that people who are anxious are more likely to feel that social interactions pose a greater risk and threat [especially with strangers or weak ties; @Granovetter.1973], which is why anxious people might desire more privacy. 
Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content [@Dienlin.2016a]. 
On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.

Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy. 
Despite the fact that only 18% of all Americans trust their government "to do what is right" [@PewResearchCenter.2017], almost everyone agrees that "it's the government's job to keep the country safe," with most people also being satisfied with the government's job [@PewResearchCenter.2015c]. 
Hence, for anxious individuals, the government might be seen as a resource rather than a threat. 
It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks [@Greenwald.2013], implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.

### Extraversion

First, we argue that need for privacy should be closely related to a person's sociability or gregariousness [which is a subdimension of extraversion, @Costa.1992b]. 
Sociability captures whether people prefer to spend their time alone or with company. 
It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @Buss.2001]. 
Put differently, given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.

This rationale is supported by several empirical studies: 
People who score higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, have been shown to desire less privacy [@Morton.2013]; people who describe themselves as introverted thinkers are more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people are more likely to report invasions of privacy [@Stone.1986].

### Agreeableness

### Openness to Experience

Similarly, it could be that an individual's felt need for privacy is related to a general tendency to avoid risks, to deliberate, and to plan carefully [deliberation is a subdimension of conscientiousness, @Costa.1992b]. 
Risk avoidance captures the degree to which people prefer to abstain from taking risks. 
If other people are considered a threat, people who are risk averse should desire more interpersonal privacy, because they may feel greater risk associated with disclosure of personal information. 
The most cautious strategy to minimize risks of information disclosure would be, arguably, to keep as much information as possible private. 
Somewhat related, empirical studies report that people who think that their privacy is at risk are less likely to disclose information online [e.g., @Bol.2018]. 
Moreover, research suggests that conscientious people are slightly more concerned about their privacy [@Junglas.2008]. 
But as above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, in order for the government to be able to avert potential threats. 
In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study.

### Traditionality

Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @Costa.1992b]. 
Traditionalism measures whether people prefer to stick with their usual routines. 
Computers and the Internet have rendered the world increasingly knowable: 
Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles. 
Given that digital information is persistent, searchable, reproducible, and scalable [@boyd.2008c], this allows for unprecedented means and degrees of surveillance. 
Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information [@Johnson.2010]. 
Hence, in order to be part of contemporary life, it seems necessary to give up some privacy. 
However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.

Empirical research does find that older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy [@Fife.2012]. 
On the other hand, @Junglas.2008 report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite pattern of results. 
Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three contexts measured in this study.

### Socio-demographic variables

Finally, it has often been shown that socio-demographic variables such as sex, age, and affluence can relate to the need for privacy [@Park.2015; @Tifferet.2019; @Weinberger.2017b; @Trepte.2013a]. 
Although these variables do not specifically address our research question at hand they will be included as control variables---not least as their omission could lead to spurious results or an inflation of false positives.

# Method

This section describes how we determine the sample size, data exclusions, the analyses, and all measures in the study.

## Sample

Participants will be collected from the professional online survey panel Prolific. 
The sample will be representative of the US regarding age, gender, and ethnicity. 
The study received IRB approval from University of Vienna. 
We calculated that participation will take approximately 15 minutes. 
We paid participants were paid \$ 2.56 for participation, equaling an hourly wage of \$ 9,81.

To determine sample size, we ran a priori power analyses. 
The final analyses will be conducted using structural equation modeling, for which exact power analyses are difficult to obtain. 
We hence conducted power analyses using two-sided bivariate correlations. 
Hence, power analysis are not exact but only a rough guide to determine minimum sample size.

We based our power analysis on a smallest effect size of interest. 
We only consider effects at least as great as _r_ = .10 as sufficient support for our theoretical rationales [@cohenPowerPrimer1992]. 
Because we adopt an exploratory perspective, we do not want to miss potentially existing effects. 
We opted for a balanced alpha and beta error approach, because we consider both errors to be equally relevant. 
In conclusion, in our study we assume an alpha error of 10% and a beta error of 10%, representing a power of 90%. 
Hence, we will use two inference criteria: Effects need to show a p-value below _p_ = 10% and an effect size of at least _r_ = .10. 
Together, power analyses revealed a minimum sample size of _N_ = `r power_n %>% round(0)`.

We will individually check responses for patterns such as straight-lining or missing of inverted items, making sure to remove only clear cases. 
We will automatically exclude participants who miss two attention checks. 
Participants who miss one attention check will be checked carefully regarding response patterns. 
We will remove participants if they should report ages below the minimum participation age of 18 years. 
We will exclude respondents if they answer less than 50% of all questions. 
The remaining missing responses will be imputed using predictive mean matching. 
We will remove respondents with exceedingly fast responses, namely below three standard deviations of the medium response time.

## Data Analyses

The factorial validity of the measures and the hypotheses will be tested with structural equation modeling (SEM). 
If Mardia’s test shows that the assumption of multivariate normality is violated, we will use the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator. 
We will test each scale in a confirmatory factor analysis. 
To avoid overfiting the models to the data, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@Kline.2016]. 
If the models' fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
If these changes do not yield sufficient fit, we will drop malfunctioning items. 
If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
EFAs will be run using maximum likelihood estimation and oblimin rotation [@Osborne.2004b, p. 7]. 
If more than one dimension was revealed, we will implement bifactor model solutions.[^1] 
Bifactor models retain a general measure of the variable, and it is not necessary to introduce novel subdimensions. 
If no adequate bifactor model can be found, we will proceed by deleting items with low loadings on the general factor and/or the specific factors. 
If also after deletion of individual items no bifactor solution should emerge, using a subset of the items we will extract a single factor with sufficient factorial validity.

[^1]: Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor). 
In addition, at least two additional factors are implemented that explain the variance in a subset of the items. The general factor and the specific factors are orthogonal. 
Bifactor models are nested within hierarchical models. 
For more information on bifactor models, see @Kline.2016, p. 319. 
Note that we will not specify a bifactor model of need for privacy, because we are explicitly interested in the relations between the personality facets and the three dimensions of need for privacy.

To answer our research question, we will analyze the variables' bivariate relations. 
To assess better the variables' potential causal effect, we will also ran a multiple structural regression model. 
Because we were interested in a complex model (overall, eight predictors and three outcomes) but the sample was comparatively small, we simplified the model. 
To this end, instead of a fully latent structural regression model we conducted a partially latent structural regression model, in which the predictor variables were modeled as single indicators while controlling for measurement error [@Kline.2016, p. 214]. 
To get high-quality single indicators of the predictors, we computed the average of the model predicted values / latent factor scores, which we extracted from the CFAs. 
If the CFAs showed a unidimensional solution, we used the model predicted values for this latent factor; if the CFAs produced a multidimensional solution, we used the model predicted values for the general latent factor.

Finally, combining several items into a latent factors helps to reduce and condense information, while partialing out error. 
At the same time, and although above we explicated our analysis pipeline, this approach still maintains several researcher degrees of freedom. 
We hence emphasize that we will adapt the models only to achieve satisfactory factorial validity and not to cherry-pick significant material. 
To provide a broader picture, in the online supplementary material (OSM) we will also share the results of the unaltered factors and how the personality factors predicted reach need for privacy item individually.

## Measures

All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
A list of all the items that were used (including deleted ones), results of CFAs/EFAs, as well as item statistics and their distribution plots can be found or will later be reported in the OSM.

[^2] Note that the HEXACO inventory normally uses 5-point scales. 
Because we were not interested in comparing absolute values across studies, we used 7-point scales to have a uniform answer format for all items, which in addition likely increase meaningful variance.

### Need for privacy

Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of a scale that is both encompassing and up-to-date. 
Hence, we use both extant scales and newly developed ad-hoc scales, some of which were already pretested. 
Ad-hoc scales were tentatively validated. 
We (a) collected qualitative feedback from three different privacy experts, (b) tested and adapted the items using four established readability indices [i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula; see, e.g.,, @patalayAssessingReadabilitySelfreported2018], and (c) like @frenerDevelopmentValidationNeed2021 will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations.

Overall, we will collect 32 items measuring need for privacy, with eight subdimensions consisting of four items each. 
Three subdimensions were adopted from @frenerDevelopmentValidationNeed2021 -- namely psychological, informational, and physiological privacy -- which build on Burgoon's @burgoonPrivacyCommunication1982 privacy theory. 
Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, we also measured a social privacy dimension, which in a prestudy showed satisfactory fit. 
We then measured need for privacy on a societal level. 
The first subdimension was government surveillance, which represents the extent to which people want the government to abstain from collecting information about them. 
The second dimension was anonymity, which captures the extent to which people feel the need to avoid identification. 
Both scales were pretested and showed good factorial validity. 
Third, we measured need for privacy from companies using four self-designed items. 
Finally, we self-developed also a general measure of need for privacy.

### Personality

Personality will be measured using the HEXACO personality inventory. 
The inventory consists of six factors with four dimensions each, including the additional meta scale "altruism". 
We will predict need for privacy first using the factors and then using the facets.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
<div id = "refs"></div>
\endgroup

### 2021-08-25 proposal.Rmd
- saved

@@
   Tobias Dienlin, Department of Communication, University of Vienna, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
-
-  Competing Interests: Both authors declare no competing interests.
-
-  Data Accessibility Statement: All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/7ncpk/).
-
-  Funding Information: During the conception and data collection of the prestudy, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported a research stay at UCSB.
-During some time working on the article and while at University of Hohenheim, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy".
-TD is now funded by a regular and not-tenured assistant professorship at University of Vienna.
-MM is funded by a regular and tenured full professorship at UCSB.
-
-# In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/).
-
-# Author contribution: conception and design: TD, MM; acquisition of data: MM, TD; code: TD; analysis and interpretation of data: TD, MM; First draft: TD; Revisions & Comments: TD & MM
 
@@
 
-To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018], which is in the tradition of Big Five approach [@johnBigFiveTrait1999] and which represents a broad understanding of personality.
-The HEXACO inventory measures overall six factors (see below), which each have four more specific facets. 
-Including the facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
-(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations with the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
+To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
+The HEXACO model is in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
+It measures overall six factors (see below), which have four specific facets each. 
+Building not only on factors but also facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
+(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
 Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and include also specific personality facets.
-Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility plus a facet labeled Altruism, which seem promising to investigate the nothing to hide argument. 
-We chose 
+Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility, plus a facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
 <!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
@@
 \endgroup
+
+# Contributions
+
+Conception and design: TD, MM. Data acquisition: TD. Code: TD. Analysis and interpretation of data: TD, MM; First draft: TD; Revisions & Comments: TD & MM.
+
+# Funding Information
+
+During the conception and data collection of the prestudy, TD was funded by The German Academic Scholarship Foundation (German: Studienstiftung des deutschen Volkes), which financially supported a research stay at UCSB.
+During some time working on the article and while at University of Hohenheim, TD was funded by the Volkswagen Foundation (German: Volkswagenstiftung), grant "Transformations of Privacy".
+TD is now funded by a regular and not-tenured assistant professorship at University of Vienna.
+MM is funded by a regular and tenured full professorship at UCSB.
+
+# Competing Interests
+
+Both authors declare no competing interests.
+
+# Supplementary Material
+
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/7ncpk/).
+The paper also has a companion website where all materials can be accessed ().
+
+# Data Accessibility Statement
+
+The data will be shared on the open science framework (https://osf.io/7ncpk/).
+
+# In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/).

### 2021-08-26 proposal.Rmd
- prepared as github website

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+# output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 Several models suggest that privacy is multi-dimensional. 
-For example, in a theory-driven treatise [@burgoonPrivacyCommunication1982] argued that privacy has four dimensions: informational, social, psychological, and physical privacy. 
-[@pedersenDimensionsPrivacy1979], by contrast, conducted an empirical factor analysis initially starting with 94 items and found that privacy exists on six dimensions: 
+For example, in a theory-driven treatise @burgoonPrivacyCommunication1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy. 
+@pedersenDimensionsPrivacy1979, by contrast, conducted an empirical factor analysis of overall 94 items and found six dimensions of privacy: 
 reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. 
-Next, [@schwartzSocialPsychologyPrivacy1968] or [@masurPrivatheitOnlineKommunikation2018] differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
-The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
+Next, @schwartzSocialPsychologyPrivacy1968 or @masurPrivatheitOnlineKommunikation2018 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
+
+<!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
+-->
 <!-- Finally, one can also distinguish between the objective privacy context (e.g., how many users can actually read a post on an SNS?), subjective privacy perceptions (e.g., how many users people _think_ can read a post on an SNS?), and resulting privacy behaviors (e.g., how much do people self-disclose?) [@dienlinPrivacyProcessModel2014].
@@
 According to @trepteNeedPrivacy2017, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs such as safety, sexuality, recovery, or contemplation.
-Specifically, [@westinPrivacyFreedom1967] defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Specifically, @westinPrivacyFreedom1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
 Not least, privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], which is necessary for attaining social support, initiating relationships, and getting close to other people [@omarzuDisclosureDecisionModel2000].
 
-On the other hand, however, privacy also has negative aspects. 
-For example, it can be problematic if there is too much privacy.
+On the other hand, however, privacy can also have negative aspects. 
+For example, it is possible to have too much privacy.
 Human beings are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
 The fact that privacy fosters self-disclosure presents also a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010].
-Privacy can also help conceal power-asymmetries, wrongdoing, or violence and other crimes. 
+Privacy can also help conceal power-asymmetries, wrongdoing, or crimes such as violence or theft.
 The dialectical tension between the positive and negative aspects of privacy likely causes variability across individuals in their need for privacy. 
+In this study we now ask, what role does personality play in determining individual-level variations in need for privacy?
 
@@
 
-What role does personality play in determining individual-level variations in need for privacy?
-So far, not a lot of studies have analyzed this question explicitly.
-We are aware of only two studies that conducted an empirical analysis [pedersenPersonalityCorrelatesPrivacy1982, @hosmanRelationshipsNeedPrivacy1991].
-And as there is no established theory connecting privacy and personality, it is difficult to deduce precise and well-informed hypotheses. 
+So far, not a lot of studies have explicitly analyzed the relation between personality and need for privacy.
+We are aware of only two studies that conducted an empirical analysis [@pedersenPersonalityCorrelatesPrivacy1982, @hosmanRelationshipsNeedPrivacy1991].
+And as there is no established theory connecting privacy and personality, it is difficult to formulate precise and well-informed hypotheses. 
 As a result, in this study we adopt an exploratory perspective.
-Not to miss potentially relevant personality factors and facets, we will adopt a large-scale perspective on personality.
+We will adopt a large-scale perspective on personality, in order not to miss potentially relevant personality factors and facets.
 
 To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
-The HEXACO model is in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
+The HEXACO model stands in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
 It measures overall six factors (see below), which have four specific facets each. 
@@
 (For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
-Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and include also specific personality facets.
-Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility, plus a facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
+Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets.
 <!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
@@
 ### Honesty-Humility
+
+Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility, plus a facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
 
@@
 We calculated that participation will take approximately 15 minutes. 
-We paid participants were paid \$ 2.56 for participation, equaling an hourly wage of \$ 9,81.
+We will pay participants \$ 2.56 for participation, equaling an hourly wage of \$ 9,81.
 
@@
 The final analyses will be conducted using structural equation modeling, for which exact power analyses are difficult to obtain. 
-We hence conducted power analyses using two-sided bivariate correlations. 
-Hence, power analysis are not exact but only a rough guide to determine minimum sample size.
+We hence conducted tentative power analyses using two-sided bivariate correlations. 
+Hence, power analysis are not exact but only a rough guide to get a better idea of the required minimum sample size.
 
-We based our power analysis on a smallest effect size of interest. 
+We based our power analysis on a smallest effect size of interest (SESOI).
 We only consider effects at least as great as _r_ = .10 as sufficient support for our theoretical rationales [@cohenPowerPrimer1992]. 
@@
 
-# In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/).
+<!-- In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/). -->

### 2021-08-26 proposal.Rmd
- minor changes

@@
 (For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
-Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets.
+Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled Honesty Humility, plus another facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
+<!-- Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets. -->
 <!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
@@
 ### Honesty-Humility
-
-Notably, in addition to the Big Five the HEXACO model includes a sixth factor labeled Honesty Humility, plus a facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
 

### 2021-08-26 items.rmd
- updated for website

@@
       toc_depth: 3
-bibliography      : 
-  - "bibliography/r-references.bib"
-  - "bibliography/references.bib"
-# pdf_document:
-#   toc: TRUE
 ---

### 2021-10-21 proposal.Rmd
- first rough "finish" of new theoretical background, now focussing on HEXACO - updated literature and bib

@@
 
-Because orivacy as a theoretical concept is complicated and contested [@nissenbaumPrivacyContextTechnology2010, p. 71], we first outline our own understanding of privacy. 
-First and foremost, privacy captures the extent of (a) _voluntary_ (b) _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967]. 
+The theoretical concept of privacy is complicated and contested [@nissenbaumPrivacyContextTechnology2010, p. 71].
+Thus, we first outline our own understanding of privacy. 
+First and foremost, privacy captures a _withdrawal_ from others or from society in general, which (b) happens _voluntarily_ and with _control_ [@westinPrivacyFreedom1967]. 
 Several models suggest that privacy is multi-dimensional. 
@@
 It measures overall six factors (see below), which have four specific facets each. 
-Building not only on factors but also facets seems helpful because we do not expect that need for privacy will relate closely to the overarching factors.
+We build not only on general factors but also specific facets, because we do not expect that the also very specific need for privacy will relate closely to the overarching factors.
 (For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
@@
 <!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
-In what follows, we briefly present all factors and outline how they and selected facets might relate to privacy.
+In what follows, we briefly present all factors and provide some tentative thoughts on how they and selected facets might relate to privacy.
 
@@
 
-Our reasoning further was guided by another central theoretical tenet. 
-As suggested above, privacy can be either positive or negative. 
-Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_. 
-Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat. 
-It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976].
+<!-- Our reasoning further was guided by another central theoretical tenet.  -->
+<!-- As suggested above, privacy can be either positive or negative.  -->
+<!-- Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_.  -->
+<!-- Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat.  -->
+<!-- It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976]. -->
 
@@
 
-More controversially, it has been argued by some that people need privacy because they have something to hide. 
-The so-called nothing-to-hide argument states that “If you have nothing to hide, you have nothing to fear.” 
-As described by Solove, the nothing-to-hide argument says that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
-Only those who are engaged in illegal activities have a reason to hide this information” [@Solove.2007, p. 753]. 
-Hence, another potential predictor of why people need privacy could also be a so-called "lack" of integrity.
+Honesty-Humility consists of the facets "sincerity", "fairness", "greed avoidance", and "modesty".
+We could imagine that honesty-humility relates to need for privacy for several reasons.
+First, it has often been argued that people need privacy because they have something to hide (are hence less honest, sincere, or fair).
+The so-called _nothing-to-hide argument_ states that “If you have nothing to hide, you have nothing to fear.” 
+<!-- As described by Solove, the nothing-to-hide argument says that -->
+For example, the nothing-to-hide argument implies that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
+Only those who are engaged in illegal activities have a reason to hide this information” [@soloveVeGotNothing2007, p. 753]. 
+<!-- Hence, a potential predictor of why people need privacy could be how honest, correct, sincere, or benign they are. -->
 
-Because integrity is a delicate concept, let us first try to define it conceptually. 
-Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity “incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness” [@Connelly.2006, p.
+<!-- Because integrity is a delicate concept, let us first try to define it conceptually.  -->
+<!-- Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity “incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness” [@Connelly.2006, p.
 82].
-In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator definition, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
-
-It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy. 
-People who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would surely disapprove of their activities [@Petronio.2010].
+-->
+<!-- In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator definition, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
+-->
+<!-- It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy.  -->
+Logically, people who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would surely disapprove of their activities [@petronioCommunicationPrivacyManagement2010].
 Hence, the government and other people are more likely to be perceived as a threat, which should render anonymity a resource. 
-As a consequence, people with lower integrity might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
-
-There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity. 
-For example, studies have found that surveillance can reduce cheating behaviors [@Corcoran.1987; @Covey.1989]. 
-@Covey.1989 for example asked students to solve an impossible maze. 
+As a consequence, people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
+<!-- There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity.  -->
+For example, studies have found that surveillance can reduce cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
+@coveySelfmonitoringSurveillanceIncentive1989 for example asked students to solve an impossible maze. 
 In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
 In the low surveillance condition, the experimenter remained behind the students where he or she could not see the students. 
-Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more integrity (i.e., fewer cheating behaviors). 
-Next, in a longitudinal sample with 457 respondents in Germany [@Trepte.2013a], people who felt they needed more privacy were also less authentic on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
-Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence also reason that the concept of integrity might relate to a person’s perceived need for privacy. 
-Somewhat related, it has been found that people who are more agreeable are also moderately less concerned about their privacy [@Junglas.2008]. 
-Finally, @pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem: 
-Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24). 
-While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as moral, nice, fair, unselfish, good, honest, and reputable (p.
-12).
+Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more honesty (i.e., fewer cheating behaviors). 
+Next, in a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
+<!-- Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence also reason that the concept of integrity might relate to a person’s perceived need for privacy.
+-->
 
-In conclusion, we could imagine that lack of integrity may indeed relate to an increased felt need for privacy from government surveillance, as governments have the legitimate power to prosecute illegal activities.
-Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
-Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
+In conclusion, we could imagine that lack of honesty may indeed relate to an increased felt need for privacy, especially when it comes to government surveillance.
+<!-- , as governments have the legitimate power to prosecute illegal activities.  -->
+<!-- Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
+-->
+<!-- Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
+-->
 
@@
 
-Next, it seems possible that the need for privacy is also related to people's level of general anxiety [which is a subdimension of neuroticism, @Costa.1992b]. 
+Next, it seems possible that the need for privacy is also related to people's level of emotionality. 
+Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
 General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened. 
-With regard to interpersonal privacy, one could argue that people who are anxious are more likely to feel that social interactions pose a greater risk and threat [especially with strangers or weak ties; @Granovetter.1973], which is why anxious people might desire more privacy.
-Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content [@Dienlin.2016a].
+With regard to interpersonal privacy, one could argue that people who are anxious are more likely to consider social interactions a risk or threat [especially with strangers or weak ties; @granovetterStrengthWeakTies1973], which is why anxious people might desire more privacy.
+Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
 On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
@@
 Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy. 
-Despite the fact that only 18% of all Americans trust their government "to do what is right" [@PewResearchCenter.2017], almost everyone agrees that "it's the government's job to keep the country safe," with most people also being satisfied with the government's job [@PewResearchCenter.2015c].
+Despite the fact that only 18% of all Americans trust their government "to do what is right" [@pewresearchcenterPublicTrustGovernment2017], almost everyone agrees that "it's the government's job to keep the country safe," while most people are also satisfied with the government's job [pewresearchcenterDistrustHowAmericans2015].
 Hence, for anxious individuals, the government might be seen as a resource rather than a threat. 
-It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks [@Greenwald.2013], implying that people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
+It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks.
+Therefore, people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
 
@@
 
-First, we argue that need for privacy should be closely related to a person's sociability or gregariousness [which is a subdimension of extraversion, @Costa.1992b]. 
-Sociability captures whether people prefer to spend their time alone or with company. 
-It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @Buss.2001].
+Extraversion is comprised of the facets social self-esteem, social boldness, sociability, and liveliness.
+Arguably, extraversion is the factor that should correspond most closely to need for privacy.
+This especially pertains to sociability, which captures whether people prefer to spend their time alone or with company. 
+It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].
 Put differently, given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
@@
 This rationale is supported by several empirical studies: 
-People who score higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, have been shown to desire less privacy [@Morton.2013]; people who describe themselves as introverted thinkers are more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people are more likely to report invasions of privacy [@Stone.1986].
+People who score higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, have been shown to desire less privacy [@mortonMeasuringInherentPrivacy2013]; people who describe themselves as introverted thinkers are more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people are more likely to report invasions of privacy [@stoneRelationshipIntroversionExtraversion1986].
+
+Finally, @pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem: 
+Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
+
+<!-- While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as moral, nice, fair, unselfish, good, honest, and reputable (p.
+12).
+-->
 
@@
 
-### Openness to Experience
+Agreeableness is captured by the facets forgiveness, gentleness, flexibility, and patience.
+It is not entirely clear whether or not agreeableness relates to need for privacy.
+Notably, it has been found that people who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+Because need for privacy and privacy concerns are closely related, it seems possible that more agreeable people desire less privacy.
 
-Similarly, it could be that an individual's felt need for privacy is related to a general tendency to avoid risks, to deliberate, and to plan carefully [deliberation is a subdimension of conscientiousness, @Costa.1992b].
-Risk avoidance captures the degree to which people prefer to abstain from taking risks. 
-If other people are considered a threat, people who are risk averse should desire more interpersonal privacy, because they may feel greater risk associated with disclosure of personal information. 
-The most cautious strategy to minimize risks of information disclosure would be, arguably, to keep as much information as possible private. 
-Somewhat related, empirical studies report that people who think that their privacy is at risk are less likely to disclose information online [e.g., @Bol.2018]. 
-Moreover, research suggests that conscientious people are slightly more concerned about their privacy [@Junglas.2008]. 
-But as above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, in order for the government to be able to avert potential threats. 
+### Conscientiousness
+
+Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
+Arguably, all facets are about being in control, about reducing potential risks, and avoiding future costs.
+And because privacy is much about control, it seems likely that an individual's felt need for privacy relates to their general tendency to avoid risks, to deliberate, and to plan ahead carefully. 
+<!-- Risk avoidance captures the degree to which people prefer to abstain from taking risks.  -->
+If other people are considered a threat, people who are risk averse might desire more interpersonal privacy.
+<!-- , because they may feel greater risk associated with disclosure of personal information.  -->
+The most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private. 
+Somewhat related, empirical studies report that people who consider their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
+Moreover, conscientious people are slightly more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+But as above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats. 
 In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study.
 
-### Traditionality
+### Openness to Experiences
 
-Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @Costa.1992b]. 
-Traditionalism measures whether people prefer to stick with their usual routines. 
-Computers and the Internet have rendered the world increasingly knowable: 
-Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles. 
-Given that digital information is persistent, searchable, reproducible, and scalable [@boyd.2008c], this allows for unprecedented means and degrees of surveillance. 
-Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information [@Johnson.2010]. 
-Hence, in order to be part of contemporary life, it seems necessary to give up some privacy. 
-However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.
+Openness to experiences comprises the facets aesthetic appreciation, inquisitiveness, creativeness, and unconventionality.
+Openness to experience is also considered a measure of intellect and education.
+More educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
+@junglasPersonalityTraitsConcern2008 reported that openness to experience is positively related to privacy concern, supporting this reasoning.
 
-Empirical research does find that older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy [@Fife.2012]. 
-On the other hand, @Junglas.2008 report that openness to experience is positively related to privacy concern, which would argue in favor of the exact opposite pattern of results. 
-Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three contexts measured in this study.
+On the other hand, openness is by definition the opposite of privacy, and people who are more open to experience news aspects might proritize privacy, for example when it comes to testing a new social medium.
+Many new digital practices such as online interaction, purchases, or information seeking pose a risk to privacy.
+People who are less open to new experiences might not care so much about the potential benefits but rather what could be lost, prioritizing privacy.
+
+<!-- Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @Costa.1992b].  -->
+<!-- Traditionalism measures whether people prefer to stick with their usual routines.  -->
+<!-- Computers and the Internet have rendered the world increasingly knowable:  -->
+<!-- Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.  -->
+<!-- Given that digital information is persistent, searchable, reproducible, and scalable [@boyd.2008c], this allows for unprecedented means and degrees of surveillance.  -->
+<!-- Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information [@Johnson.2010].  -->
+<!-- Hence, in order to be part of contemporary life, it seems necessary to give up some privacy.  -->
+<!-- However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.  -->
+
+<!-- <!-- Empirical research does find that older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy [@Fife.2012].  -->
+<!-- Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three contexts measured in this study. -->
 
@@
 
-Finally, it has often been shown that socio-demographic variables such as sex, age, and affluence can relate to the need for privacy [@Park.2015; @Tifferet.2019; @Weinberger.2017b; @Trepte.2013a]. 
-Although these variables do not specifically address our research question at hand they will be included as control variables---not least as their omission could lead to spurious results or an inflation of false positives.
+Finally, it has often been shown that socio-demographic variables such as sex, age, education, and affluence can relate to the need for privacy. 
+For example, in a study with 3.072 people from Germany, women desired more informational and physical privacy, while man needed more psychological privacy [@frenerDevelopmentValidationNeed2021].
+In a nationally representative study of the US and Japan, in both countries people who were older and who had higher income levels reported more privacy concerns.
+As reported above, more educated people possess also more privacy knowledge [@parkDigitalLiteracyPrivacy2013].
 
@@
 We will test each scale in a confirmatory factor analysis. 
-To avoid overfiting the models to the data, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@Kline.2016]. 
+To avoid overfiting the models to the data, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
 If the models' fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
@@
 If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
-EFAs will be run using maximum likelihood estimation and oblimin rotation [@Osborne.2004b, p. 7]. 
+EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
 If more than one dimension was revealed, we will implement bifactor model solutions.[^1] 
@@
 Bifactor models are nested within hierarchical models. 
-For more information on bifactor models, see @Kline.2016, p. 319. 
+For more information on bifactor models, see @klinePrinciplesPracticeStructural2016, p. 319. 
 Note that we will not specify a bifactor model of need for privacy, because we are explicitly interested in the relations between the personality facets and the three dimensions of need for privacy.
@@
 Because we were interested in a complex model (overall, eight predictors and three outcomes) but the sample was comparatively small, we simplified the model. 
-To this end, instead of a fully latent structural regression model we conducted a partially latent structural regression model, in which the predictor variables were modeled as single indicators while controlling for measurement error [@Kline.2016, p.
+To this end, instead of a fully latent structural regression model we conducted a partially latent structural regression model, in which the predictor variables were modeled as single indicators while controlling for measurement error [@klinePrinciplesPracticeStructural2016, p.
 214].
@@
 
-[^2] Note that the HEXACO inventory normally uses 5-point scales. 
+[^2]: Note that the HEXACO inventory normally uses 5-point scales. 
 Because we were not interested in comparing absolute values across studies, we used 7-point scales to have a uniform answer format for all items, which in addition likely increase meaningful variance.
@@
 Ad-hoc scales were tentatively validated. 
-We (a) collected qualitative feedback from three different privacy experts, (b) tested and adapted the items using four established readability indices [i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula; see, e.g.,, @patalayAssessingReadabilitySelfreported2018], and (c) like @frenerDevelopmentValidationNeed2021 will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations.
+We (a) collected qualitative feedback from three different privacy experts, (b) tested and adapted the items using four established readability indices [i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula; see, e.g., @patalayAssessingReadabilitySelfreported2018], and (c) like @frenerDevelopmentValidationNeed2021 will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations.
 
@@
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+<!-- \begingroup -->
+<!-- \setlength{\parindent}{-0.5in} -->
+<!-- \setlength{\leftskip}{0.5in} -->
 <div id = "refs"></div>
-\endgroup
+<!-- \endgroup -->
 

### 2021-10-25 proposal.Rmd
minor content updates.

@@
 ---
-title             : "Who Needs Privacy? Exploring the relation between personality and need for privacy"
+title             : "Who needs privacy? Exploring the relation between personality and need for privacy"
 shorttitle        : "Who Needs Privacy?"
@@
 Living in an information age, people constantly have to decide what information to share, which service to use, or when to communicate.
-All these decisions are reflective of and determined by the users' need for privacy.
+All of these decisions are reflective of and determined by the users' need for privacy.
 It is relevant to understand who needs more and who needs less privacy, because desiring privacy often requires justification.
-For example, well-known statements such as 'who has nothing to hide has nothing to fear' imply that people who desire privacy are suspicious.
-Although such suspicions might be justified in some cases, it could also be that people desiring more privacy are just more introverted, anxious, creative, or prudent.
+For example, the nothing-to-hide statement -- i.e., 'someone who has nothing to hide has nothing to fear' -- imply that people who desire privacy are suspicious.
+Although such suspicions might be justified in some cases, there exist many alternative legitimate explanations why people desire privacy.
+For example, they could be more introverted, hesitant, creative, or prudent.
 In this study we, hence, plan to explore the relation between personality and the need for privacy.
 Personality factors and facets will be operationalized using the HEXACO personality inventory.
-Need for privacy will be captured with a multidimensional approach, including informational and social privacy, need for privacy from government agencies, or need fro privacy from companies.
-Adopting an exploratory analytical framework, we will collect a sample of more than 800 respondents representative of the US in terms of age, gender, and ethnicity.
-The relations between personality and privacy will be explored using structural equation modeling.
-Potential implications will be discussed."
+Need for privacy will be captured with a multidimensional approach, including informational and social privacy, need for privacy from government agencies, or need for privacy from companies.
+We will collect a sample of more than 800 respondents, which are representative of the US in terms of age, gender, and ethnicity.
+The relations between personality and privacy will be explored using structural equation modeling."
 keywords          : "Privacy, need for privacy, personality, HEXACO, structural equation modeling"
@@
 
-In light of the increasing digitization of everyday life, which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016], privacy has become a major topic of public and academic interest.
+Amidst the increasing digitization of everyday life, 
+<!-- which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016],  -->
+privacy has become a major topic of public and academic interest. 
 Despite the topic's importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
-Why do some people feel they need or desire more privacy than others do, and how do these people differ from one another?
+Why do some people feel they need or desire more privacy than others, and how do these people differ from one another?
 
-We believe it is relevant to understand better this research questions, because people who desire privacy are often confronted to justify their need for privacy. 
+We believe it is relevant to understand better this research question, because people who desire privacy are often asked to justify their need for privacy. 
 For example, well-known statements such as 'who has nothing to hide has nothing to fear' imply that people who desire privacy are suspicious.
-Indeed, it is only logical that people who commit crimes and who are insincere in fact benefit from more privacy.
-However, it could also be that people desiring more privacy are just more introverted, anxious, creative, or prudent. 
+Granted, it is only logical that people who commit crimes and who are insincere in fact benefit from more privacy.
+However, there exist many other alternative reasons why people need privacy.
+For example, it could also be that people who need more privacy are just more introverted, hesitant, creative, or prudent. 
 We therefore believe that a better understanding of the relation between personality and privacy is relevant.
-Also from an academic perspective, several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155]
-However, to date there is almost no empirical research that can be used to deduce well-informed hypotheses. 
-As a result, the main question of this paper is: 
-What are personality factors and facets that best explain peoples' felt need for privacy?
+
+This research question is relevant also from an academic perspective. 
+Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
+However, to date there is almost no empirical research that can be used to develop well-informed hypotheses. 
+As a result, with this paper we would like to answer the following question:  
+What personality factors and facets best explain peoples' felt need for privacy?
 
@@
 Thus, we first outline our own understanding of privacy. 
-First and foremost, privacy captures a _withdrawal_ from others or from society in general, which (b) happens _voluntarily_ and with _control_ [@westinPrivacyFreedom1967]. 
+First and foremost, privacy captures a _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967].
+This withdrawal (b) happens _voluntarily_ and is under a person's _control_ [@westinPrivacyFreedom1967]. 
 Several models suggest that privacy is multi-dimensional. 
@@
 reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. 
-Next, @schwartzSocialPsychologyPrivacy1968 or @masurPrivatheitOnlineKommunikation2018 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
+@schwartzSocialPsychologyPrivacy1968 or @masurPrivatheitOnlineKommunikation2018 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
 
@@
 According to @trepteNeedPrivacy2017, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs such as safety, sexuality, recovery, or contemplation.
-Specifically, @westinPrivacyFreedom1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (i.e., the desire to avoid being manipulated and dominated), (3) emotional release (i.e., the release of tension from social role demands), and (4) protected communication (i.e., the ability to foster intimate relationships).
+Specifically, @westinPrivacyFreedom1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
 Not least, privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], which is necessary for attaining social support, initiating relationships, and getting close to other people [@omarzuDisclosureDecisionModel2000].
@@
 On the other hand, however, privacy can also have negative aspects. 
-For example, it is possible to have too much privacy.
+It is possible to have too much privacy.
 Human beings are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
-The fact that privacy fosters self-disclosure presents also a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010].
+Privacy fostering self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010]. 
 Privacy can also help conceal power-asymmetries, wrongdoing, or crimes such as violence or theft.
-The dialectical tension between the positive and negative aspects of privacy likely causes variability across individuals in their need for privacy. 
-In this study we now ask, what role does personality play in determining individual-level variations in need for privacy?
+The dialectical tension between the positive and negative aspects of privacy thus causes variability across individuals in their need for privacy.
+
+<!-- In this study we now ask, what role does personality play in determining individual-level variations in need for privacy? -->
 
@@
 
-So far, not a lot of studies have explicitly analyzed the relation between personality and need for privacy.
-We are aware of only two studies that conducted an empirical analysis [@pedersenPersonalityCorrelatesPrivacy1982, @hosmanRelationshipsNeedPrivacy1991].
+So far, not a lot of studies have analyzed the relation between personality and need for privacy explicitly.
+We are aware of only two studies that conducted an empirical analysis [@pedersenPersonalityCorrelatesPrivacy1982; @hosmanRelationshipsNeedPrivacy1991].
 And as there is no established theory connecting privacy and personality, it is difficult to formulate precise and well-informed hypotheses. 
-As a result, in this study we adopt an exploratory perspective.
-We will adopt a large-scale perspective on personality, in order not to miss potentially relevant personality factors and facets.
+As a result, in this study we adopt a more _exploratory_ perspective.
+We implement a large-scale perspective on personality, in order not to miss potentially relevant personality factors and facets.
 
 To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
-The HEXACO model stands in the tradition of Big Five approach [@johnBigFiveTrait1999], and it represents a broad understanding of personality.
+The HEXACO model stands in the tradition of Big Five approach [@johnBigFiveTrait1999] and represents a broad understanding of personality.
 It measures overall six factors (see below), which have four specific facets each. 
-We build not only on general factors but also specific facets, because we do not expect that the also very specific need for privacy will relate closely to the overarching factors.
-(For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].)
-Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled Honesty Humility, plus another facet labeled Altruism, which together seem promising to investigate the nothing to hide argument.
+We build not only on general factors but also specific facets because we do not expect that the even more specific need for privacy dimensions will relate closely to overarching personality factors.
+(For example, privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors; @bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008.)
+Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled Honesty Humility, 
+<!-- plus another facet labeled Altruism,  -->
+which seems promising to investigate the nothing to hide argument.
 <!-- Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets. -->
 <!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
-In what follows, we briefly present all factors and provide some tentative thoughts on how they and selected facets might relate to privacy.
+In what follows, we briefly present all factors and provide some tentative thoughts on how they and several selected facets might relate to privacy.
 
@@
 
-Honesty-Humility consists of the facets "sincerity", "fairness", "greed avoidance", and "modesty".
+Honesty-Humility consists of the facets sincerity, fairness, greed avoidance, and modesty.
 We could imagine that honesty-humility relates to need for privacy for several reasons.
-First, it has often been argued that people need privacy because they have something to hide (are hence less honest, sincere, or fair).
+First, one can often hear that people need privacy because they have something to hide (are hence less honest, sincere, or fair).
 The so-called _nothing-to-hide argument_ states that “If you have nothing to hide, you have nothing to fear.” 
 <!-- As described by Solove, the nothing-to-hide argument says that -->
-For example, the nothing-to-hide argument implies that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
+The argument for example implies that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
 Only those who are engaged in illegal activities have a reason to hide this information” [@soloveVeGotNothing2007, p. 753]. 
@@
 <!-- It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy.  -->
-Logically, people who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would surely disapprove of their activities [@petronioCommunicationPrivacyManagement2010].
+Logically, people who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would sanction their activities [@petronioCommunicationPrivacyManagement2010].
 Hence, the government and other people are more likely to be perceived as a threat, which should render anonymity a resource. 
@@
 <!-- There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity.  -->
-For example, studies have found that surveillance can reduce cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
+
+Empirical studies have found that surveillance can indeed reduce cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
 @coveySelfmonitoringSurveillanceIncentive1989 for example asked students to solve an impossible maze. 
@@
 
-Next, it seems possible that the need for privacy is also related to people's level of emotionality. 
+Next, it seems possible that need for privacy is also related to a person's level of emotionality. 
 Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
 General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened. 
-With regard to interpersonal privacy, one could argue that people who are anxious are more likely to consider social interactions a risk or threat [especially with strangers or weak ties; @granovetterStrengthWeakTies1973], which is why anxious people might desire more privacy.
-Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
+With regard to interpersonal privacy, one could argue that people who are anxious are more likely to consider social interactions a risk or threat [especially with strangers or weak ties, @granovetterStrengthWeakTies1973], which is why anxious people might desire more privacy.
+Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
 On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
@@
 Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy. 
-Despite the fact that only 18% of all Americans trust their government "to do what is right" [@pewresearchcenterPublicTrustGovernment2017], almost everyone agrees that "it's the government's job to keep the country safe," while most people are also satisfied with the government's job [pewresearchcenterDistrustHowAmericans2015].
+Despite the fact that only 18% of all Americans trust their government "to do what is right" [@pewresearchcenterPublicTrustGovernment2017], almost everyone agrees that "it's the government's job to keep the country safe," while most people are also satisfied with the government's job [@pewresearchcenterDistrustHowAmericans2015].
 Hence, for anxious individuals, the government might be seen as a resource rather than a threat. 
@@
 
-Extraversion is comprised of the facets social self-esteem, social boldness, sociability, and liveliness.
+Extraversion comprises the facets social self-esteem, social boldness, sociability, and liveliness.
 Arguably, extraversion is the factor that should correspond most closely to need for privacy.
-This especially pertains to sociability, which captures whether people prefer to spend their time alone or with company. 
+This especially pertains to the facet sociability, which captures whether people prefer to spend their time alone or with company. 
 It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].

### 2021-10-25 proposal.Rmd
changes to theory

@@
 abstract          : "Privacy is an important societal topic.
-Living in an information age, people constantly have to decide what information to share, which service to use, or when to communicate.
+Living in an information age, people constantly have to decide what information to share, which service to use, when to communicate.
 All of these decisions are reflective of and determined by the users' need for privacy.
-It is relevant to understand who needs more and who needs less privacy, because desiring privacy often requires justification.
-For example, the nothing-to-hide statement -- i.e., 'someone who has nothing to hide has nothing to fear' -- imply that people who desire privacy are suspicious.
-Although such suspicions might be justified in some cases, there exist many alternative legitimate explanations why people desire privacy.
+We believe that it is relevant to understand who needs more and who needs less privacy, for example because desiring privacy often requires justification.
+The nothing-to-hide statement -- i.e., 'someone who has nothing to hide has nothing to fear' -- implies that people who desire privacy are suspicious.
+Although such suspicions might be justified in some cases, there are many alternative legitimate explanations as to why people desire privacy.
 For example, they could be more introverted, hesitant, creative, or prudent.
-In this study we, hence, plan to explore the relation between personality and the need for privacy.
+In this study we hence plan to explore the relation between personality and the need for privacy.
 Personality factors and facets will be operationalized using the HEXACO personality inventory.
 Need for privacy will be captured with a multidimensional approach, including informational and social privacy, need for privacy from government agencies, or need for privacy from companies.
-We will collect a sample of more than 800 respondents, which are representative of the US in terms of age, gender, and ethnicity.
+We will collect a sample of more than 800 respondents, which will be representative of the US in terms of age, gender, and ethnicity.
 The relations between personality and privacy will be explored using structural equation modeling."
@@
 Despite the topic's importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
-Why do some people feel they need or desire more privacy than others, and how do these people differ from one another?
+Why do some people feel they need more privacy than others, and how do these people differ from one another?
 
-We believe it is relevant to understand better this research question, because people who desire privacy are often asked to justify their need for privacy. 
-For example, well-known statements such as 'who has nothing to hide has nothing to fear' imply that people who desire privacy are suspicious.
-Granted, it is only logical that people who commit crimes and who are insincere in fact benefit from more privacy.
-However, there exist many other alternative reasons why people need privacy.
+We believe it is relevant to understand better this research question, because people who desire privacy are often asked to justify themselves. 
+For example, the so-called _nothing-to-hide argument_ states that “If you have nothing to hide, you have nothing to fear”. 
+<!-- As described by Solove, the nothing-to-hide argument says that -->
+The argument implies that people who desire privacy are suspicious. 
+For example, once can often hear that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
+Only those who are engaged in illegal activities have a reason to hide this information” [@soloveVeGotNothing2007, p. 753].
+And granted, it is only logical that people who commit crimes and who are insincere would in fact benefit from more privacy.
+However, there exist many other alternative reasons as to why people need privacy.
 For example, it could also be that people who need more privacy are just more introverted, hesitant, creative, or prudent. 
-We therefore believe that a better understanding of the relation between personality and privacy is relevant.
+We therefore believe that a better understanding of the relation between personality and privacy is relevant from a societal perspective.
 
-This research question is relevant also from an academic perspective. 
+Also from an academic perspective, this research question is topical. 
 Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
@@
 Thus, we first outline our own understanding of privacy. 
-First and foremost, privacy captures a _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967].
+First and foremost, privacy captures a _withdrawal_ from others, or from society in general [@westinPrivacyFreedom1967].
 This withdrawal (b) happens _voluntarily_ and is under a person's _control_ [@westinPrivacyFreedom1967]. 
@@
 For example, in a theory-driven treatise @burgoonPrivacyCommunication1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy. 
-@pedersenDimensionsPrivacy1979, by contrast, conducted an empirical factor analysis of overall 94 items and found six dimensions of privacy: 
+@pedersenDimensionsPrivacy1979 conducted an empirical factor analysis of overall 94 items and found six dimensions of privacy: 
 reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. 
-@schwartzSocialPsychologyPrivacy1968 or @masurPrivatheitOnlineKommunikation2018 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
+@schwartzSocialPsychologyPrivacy1968 and @masurPrivatheitOnlineKommunikation2018 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
 
@@
 <!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->
-According to @trepteNeedPrivacy2017, the need for privacy is a secondary need---it is not an end in itself, but rather a way to satisfy other more fundamental needs such as safety, sexuality, recovery, or contemplation.
+According to @trepteNeedPrivacy2017, the need for privacy is a secondary need---it is not an end in itself, but rather a means to satisfy other more fundamental needs such as safety, sexuality, recovery, or contemplation.
 Specifically, @westinPrivacyFreedom1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
@@
 Human beings are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
-Privacy fostering self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010]. 
+The fact that privacy fosters self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010].
 Privacy can also help conceal power-asymmetries, wrongdoing, or crimes such as violence or theft.
-The dialectical tension between the positive and negative aspects of privacy thus causes variability across individuals in their need for privacy.
+The dialectical tension between the positive and negative aspects of privacy thus might cause variability across individuals in their need for privacy.
 
@@
 We are aware of only two studies that conducted an empirical analysis [@pedersenPersonalityCorrelatesPrivacy1982; @hosmanRelationshipsNeedPrivacy1991].
-And as there is no established theory connecting privacy and personality, it is difficult to formulate precise and well-informed hypotheses. 
+And as there is no established theory connecting privacy and personality, it is difficult to formulate precise and well-informed a priori hypotheses. 
 As a result, in this study we adopt a more _exploratory_ perspective.
-We implement a large-scale perspective on personality, in order not to miss potentially relevant personality factors and facets.
+We implement a large-scale operationalization on personality, in order not to miss potentially relevant personality factors and facets.
 
 To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
-The HEXACO model stands in the tradition of Big Five approach [@johnBigFiveTrait1999] and represents a broad understanding of personality.
+The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999]
+<!-- and represents a broad understanding of personality-->
+.
 It measures overall six factors (see below), which have four specific facets each. 
-We build not only on general factors but also specific facets because we do not expect that the even more specific need for privacy dimensions will relate closely to overarching personality factors.
+We include also the specific facets because we do not expect that the even more specific need for privacy dimensions will relate closely to overarching general personality factors.
 (For example, privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors; @bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008.)
+
 Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled Honesty Humility, 
 <!-- plus another facet labeled Altruism,  -->
-which seems promising to investigate the nothing to hide argument.
+which seems promising to investigate the nothing-to-hide-argument.
 <!-- Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets. -->
@@
 Honesty-Humility consists of the facets sincerity, fairness, greed avoidance, and modesty.
-We could imagine that honesty-humility relates to need for privacy for several reasons.
-First, one can often hear that people need privacy because they have something to hide (are hence less honest, sincere, or fair).
-The so-called _nothing-to-hide argument_ states that “If you have nothing to hide, you have nothing to fear.” 
-<!-- As described by Solove, the nothing-to-hide argument says that -->
-The argument for example implies that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
-Only those who are engaged in illegal activities have a reason to hide this information” [@soloveVeGotNothing2007, p. 753]. 
+According to the nothing-to-hide argument, one could assume that people might need privacy because they have something to hide---that is, because they are hence less honest, sincere, or fair.
 <!-- Hence, a potential predictor of why people need privacy could be how honest, correct, sincere, or benign they are. -->
-
 <!-- Because integrity is a delicate concept, let us first try to define it conceptually.  -->
@@
 Logically, people who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would sanction their activities [@petronioCommunicationPrivacyManagement2010].
-Hence, the government and other people are more likely to be perceived as a threat, which should render anonymity a resource. 
-As a consequence, people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
+Hence, the government and other people are more likely to be perceived as a threat, which should render privacy a resource. 
+As a consequence, once could argue that people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
 <!-- There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity.  -->
@@
 In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
-In the low surveillance condition, the experimenter remained behind the students where he or she could not see the students. 
+In the low surveillance condition, the experimenter remained behind the students where they could not see the students. 
 Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more honesty (i.e., fewer cheating behaviors). 
@@
 
-In conclusion, we could imagine that lack of honesty may indeed relate to an increased felt need for privacy, especially when it comes to government surveillance.
+In conclusion, it seems possible that lack of honesty may indeed relate to an increased felt need for privacy, especially when it comes to government surveillance.
 <!-- , as governments have the legitimate power to prosecute illegal activities.  -->

### 2021-10-25 analyses.RmD
- finished first rough overhaul of introduction and methods

@@
 To estimate sample size, we conducted a rudimentary power analysis.
-That is, we planned for a two-sided correlation of r = .1.
+That is, we planned for a two-sided correlation of _r_ = .1.
 We adopted a balanced alpha and beta error approach.
-Because we were in exploration mode, we aimed for a high statistical power and relaxed alpha.
+Because we were in "exploration mode", we aimed for a high statistical power and hence relaxed alpha.
 Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget.
@@
 pwr.r.test(r = sesoi, sig.level = .05, power = .95) ## too expensive
+power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
 ```
@@
 pwr.r.test(r = sesoi, sig.level = .1, power = .9)
+power_n_90 <- pwr.r.test(r = sesoi, sig.level = .1, power = .9)$n
 ```
@@
 A 10% error rate would imply collecting 853 participants, which was within our budget.
-
-```{r}
-power <- pwr.r.test(r = sesoi, sig.level = .05, power = .8)
-print(power)
-power_n <- power$n
-```
 

### 2021-10-25 proposal.Rmd
- finished first rough overhaul of introduction and methods

@@
 We believe that it is relevant to understand who needs more and who needs less privacy, for example because desiring privacy often requires justification.
-The nothing-to-hide statement -- i.e., 'someone who has nothing to hide has nothing to fear' -- implies that people who desire privacy are suspicious.
+The nothing-to-hide statement---i.e., 'someone who has nothing to hide has nothing to fear'---implies that people who desire privacy are suspicious.
 Although such suspicions might be justified in some cases, there are many alternative legitimate explanations as to why people desire privacy.
@@
 
-Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled Honesty Humility, 
-<!-- plus another facet labeled Altruism,  -->
+Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled honesty-humility, 
+plus another additional meta-facet labeled altruism,
 which seems promising to investigate the nothing-to-hide-argument.
@@
 
-### Honesty-Humility
+### Honesty-Humility & Altriusm
 
-Honesty-Humility consists of the facets sincerity, fairness, greed avoidance, and modesty.
-According to the nothing-to-hide argument, one could assume that people might need privacy because they have something to hide---that is, because they are hence less honest, sincere, or fair.
+Honesty-humility consists of the facets sincerity, fairness, greed avoidance, and modesty.
+The meta-facet altruism measures benevolence toward others and consists of items such as "It wouldn’t bother me to harm someone I didn’t like."
+According to the nothing-to-hide argument, one could assume that people might need privacy because they have something to hide---that is, because they are hence less honest, sincere, fair or benevolent.
 <!-- Hence, a potential predictor of why people need privacy could be how honest, correct, sincere, or benign they are. -->
@@
 Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more honesty (i.e., fewer cheating behaviors). 
+When playing the ultimatum/dictator game, people share less if the game is double blind (Fähr & Gächter, 2000; Gaulin & McBurney, 2001).
 Next, in a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
@@
 Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
-General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened. 
+<!-- General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened.  -->
 With regard to interpersonal privacy, one could argue that people who are anxious are more likely to consider social interactions a risk or threat [especially with strangers or weak ties, @granovetterStrengthWeakTies1973], which is why anxious people might desire more privacy.
-Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
+Somewhat related, prior empirical research showed that people who are more concerned about their privacy are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
 On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
@@
 It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks.
-Therefore, people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity.
+That said, the relation could also be inverse, such that more anxious people desire more privacy.
+It is plausible that anxiety correlates with being in favor of government surveillance of _others_; however, this does not necessarily extend to someone’s _own_ data. 
+If the government is perceived as a threat, as often expressed by minority groups, than it would follow that they ask for more privacy for themselves.
+<!-- Therefore, people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity. -->
 
@@
 Extraversion comprises the facets social self-esteem, social boldness, sociability, and liveliness.
-Arguably, extraversion is the factor that should correspond most closely to need for privacy.
-This especially pertains to the facet sociability, which captures whether people prefer to spend their time alone or with company. 
+Arguably, extraversion is the factor that should correspond most closely to the need for privacy.
+This especially pertains to the facet sociability, which captures whether people prefer to spend their time alone or in company. 
 It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].
 Put differently, given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
+One could even make the case that need for privacy and extraversion are conceptually the same, and that need for privacy is just a different label for the same underlying personality trait. 
+Interestingly, we are not aware of a personality inventory that explicitly refers to privacy.
 
-This rationale is supported by several empirical studies: 
-People who score higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, have been shown to desire less privacy [@mortonMeasuringInherentPrivacy2013]; people who describe themselves as introverted thinkers are more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people are more likely to report invasions of privacy [@stoneRelationshipIntroversionExtraversion1986].
-
-Finally, @pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem: 
+Several empirical studies support the relation.
+People who scored higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, desired less privacy [@mortonMeasuringInherentPrivacy2013]; people who described themselves as introverted thinkers were more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people were more likely to report invasions of privacy [@stoneRelationshipIntroversionExtraversion1986].
+@pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem (but note, general self-esteem, not social self-esteem): 
 Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
@@
 Agreeableness is captured by the facets forgiveness, gentleness, flexibility, and patience.
-It is not entirely clear whether or not agreeableness relates to need for privacy.
-Notably, it has been found that people who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+It is not entirely clear whether or how agreeableness might relate to the need for privacy.
+Potentially noteworthy is that people who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
 Because need for privacy and privacy concerns are closely related, it seems possible that more agreeable people desire less privacy.
@@
 Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
-Arguably, all facets are about being in control, about reducing potential risks, and avoiding future costs.
-And because privacy is much about control, it seems likely that an individual's felt need for privacy relates to their general tendency to avoid risks, to deliberate, and to plan ahead carefully. 
+Arguably, all facets are more or less about being in control, about reducing potential risks, and avoiding future costs.
+And because privacy is much about control (see above), we could imagine that an individual's felt need for privacy relates to their general tendency to avoid risks, to deliberate, and to plan ahead carefully.
 <!-- Risk avoidance captures the degree to which people prefer to abstain from taking risks.  -->
-If other people are considered a threat, people who are risk averse might desire more interpersonal privacy.
+Especially if other people are considered a threat, people who are risk averse might desire more interpersonal privacy.
 <!-- , because they may feel greater risk associated with disclosure of personal information.  -->
 The most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private.
-Somewhat related, empirical studies report that people who consider their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
+
+Relatedly, empirical studies report that people who consider their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
 Moreover, conscientious people are slightly more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
 But as above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats. 
-In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study.
+<!-- In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study. -->
 
@@
 Openness to experience is also considered a measure of intellect and education.
-More educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
-@junglasPersonalityTraitsConcern2008 reported that openness to experience is positively related to privacy concern, supporting this reasoning.
+This is only a personal impression, but sometimes it feels that advocates of privacy seem to come from the higher educational echelons of society, that they are the intellectual elites, for example when citing Orwell's 1984.
+Potentially related to this, empirical studies showed that more educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
+Supporting this reasoning, @junglasPersonalityTraitsConcern2008 reported that openness to experience is positively related to privacy concern.
 
-On the other hand, openness is by definition the opposite of privacy, and people who are more open to experience news aspects might proritize privacy, for example when it comes to testing a new social medium.
-Many new digital practices such as online interaction, purchases, or information seeking pose a risk to privacy.
-People who are less open to new experiences might not care so much about the potential benefits but rather what could be lost, prioritizing privacy.
+On the other hand, openness is by definition the opposite of privacy, and people who are more open to experience new aspects might _not_ prioritize privacy, for example when it comes to testing a new social medium.
+Many new digital practices such as online interaction, purchases, or information seeking pose a risk to privacy, but offer many exciting new benefits.
+People who are more open to new experiences might not care so much about the potential downsides, but rather on what could be achieved.
 
@@
 
-Finally, it has often been shown that socio-demographic variables such as sex, age, education, and affluence can relate to the need for privacy. 
-For example, in a study with 3.072 people from Germany, women desired more informational and physical privacy, while man needed more psychological privacy [@frenerDevelopmentValidationNeed2021].
+Finally, it seems likely that the need for privacy is also related to sociodemographic variables, such as sex, age, education, and affluence. 
+For example, in a study with 3.072 people from Germany, it was found that women desired more informational and physical privacy, while man needed more psychological privacy [@frenerDevelopmentValidationNeed2021].
 In a nationally representative study of the US and Japan, in both countries people who were older and who had higher income levels reported more privacy concerns.
-As reported above, more educated people possess also more privacy knowledge [@parkDigitalLiteracyPrivacy2013].
+As reported above, more educated people possess also more privacy knowledge [@parkDigitalLiteracyPrivacy2013], and it could be that they desire more privacy.
+We are also curious how ethnicity might correspond to need for privacy, and could well imagine that non-white groups desire more privacy from the government---but not necessarily from other people.
+We additionally investigate wheter a person's relationship status corresponds to their expressed need for privacy.
+Last, we also investigate whether one's political position is related to the need for privacy.
+We could imagine that more right-leaning people desire more privacy from the government, but not necessarily from other people.
 
@@
 
+## Prestudy
+
+We ran a prestudy, which is published as preprint [@dienlinWhoNeedsPrivacy2019].
+This study was submitted initially, but rejected for several empirical and conceptual reasons (for example, insufficient statistical power).
+This proposal aims to remedy these shortcomings.
+In the prestudy, we tested several self-developed items, which are reported below.
+
 ## Sample
@@
 Participants will be collected from the professional online survey panel Prolific. 
-The sample will be representative of the US regarding age, gender, and ethnicity. 
+The sample will be representative of the US in terms of age, gender, and ethnicity. 
 The study received IRB approval from University of Vienna. 
 We calculated that participation will take approximately 15 minutes. 
-We will pay participants \$ 2.56 for participation, equaling an hourly wage of \$ 9,81.
+We will pay participants \$ 2.56 for participation, which equals an hourly wage of \$ 9,81.
 
 To determine sample size, we ran a priori power analyses. 
-The final analyses will be conducted using structural equation modeling, for which exact power analyses are difficult to obtain. 
+Note that the final analyses will be conducted using structural equation modeling, for which exact power analyses are difficult to obtain. 
 We hence conducted tentative power analyses using two-sided bivariate correlations. 
-Hence, power analysis are not exact but only a rough guide to get a better idea of the required minimum sample size.
+Hence, the following power analyses are not exact but only a rough guide to get a better idea of the required minimum sample size.
 
 We based our power analysis on a smallest effect size of interest (SESOI).
-We only consider effects at least as great as _r_ = .10 as sufficient support for our theoretical rationales [@cohenPowerPrimer1992]. 
-Because we adopt an exploratory perspective, we do not want to miss potentially existing effects. 
-We opted for a balanced alpha and beta error approach, because we consider both errors to be equally relevant. 
-In conclusion, in our study we assume an alpha error of 10% and a beta error of 10%, representing a power of 90%. 
+We only considered effects at least as great as _r_ = .10 as sufficiently relevant to constitute support for an effect's existence [@cohenPowerPrimer1992]. 
+Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%).
+We adopted an exploratory perspective, and aimed not to miss potentially existing effects (beta error).
+We opted for an approach where alpha and beta error are balanced/equal, because we consider both errors to be equally relevant. 
+A power analysis with an alpha and beta error of 5% and an effect size of _r_ = .10 required a sample size of _N_ = `r power_n_95 %>% round(0)`, which was outside of our budget.
+If we slightly relaxed the error rate to 10%, power analyses showed that we would need a sample size of _N_ = `r power_n_90 %>% round(0)`, which was within our budget, and which will hence be the minimum sample size we plan to collect.
 Hence, we will use two inference criteria: Effects need to show a p-value below _p_ = 10% and an effect size of at least _r_ = .10.
-Together, power analyses revealed a minimum sample size of _N_ = `r power_n %>% round(0)`.
 
@@
 We will automatically exclude participants who miss two attention checks. 
-Participants who miss one attention check will be checked carefully regarding response patterns. 
-We will remove participants if they should report ages below the minimum participation age of 18 years. 
+Participants who miss one attention check will be checked individually regarding response patterns. 
+We will remove participants below the minimum participation age of 18 years. 
 We will exclude respondents if they answer less than 50% of all questions. 
@@
 
-## Data Analyses
+## Data Analyses and Decision Pipeline
 
@@
 We will test each scale in a confirmatory factor analysis. 
-To avoid overfiting the models to the data, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
-If the models' fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
+To avoid overfiting, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
+If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
 If these changes do not yield sufficient fit, we will drop malfunctioning items.
+
 If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
 EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
-If more than one dimension was revealed, we will implement bifactor model solutions.[^1] 
-Bifactor models retain a general measure of the variable, and it is not necessary to introduce novel subdimensions. 
+If more than one dimension will be revealed, we will implement bifactor model solutions.[^1] 
+Bifactor models retain a general measure of the variable, and make it unneccesary to introduce novel (and potentially overfitted) subdimensions. 
 If no adequate bifactor model can be found, we will proceed by deleting items with low loadings on the general factor and/or the specific factors. 
-If also after deletion of individual items no bifactor solution should emerge, using a subset of the items we will extract a single factor with sufficient factorial validity.
+If also after deletion of individual items no bifactor solution should emerge, we will use a subset of the items to extract a single factor with sufficient factorial validity.
 
@@
 
-To answer our research question, we will analyze the variables' bivariate relations. 
-To assess better the variables' potential causal effect, we will also ran a multiple structural regression model. 
-Because we were interested in a complex model (overall, eight predictors and three outcomes) but the sample was comparatively small, we simplified the model. 
-To this end, instead of a fully latent structural regression model we conducted a partially latent structural regression model, in which the predictor variables were modeled as single indicators while controlling for measurement error [@klinePrinciplesPracticeStructural2016, p.
+We want to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
+Hence, to answer our research question, we will analyze the variables' bivariate relations in a joint model combining all variables. 
+First, we will predict need for privacy using the factors, and then using the facets. 
+To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model, which we will report in the companion website.
+Based on reviewer feedback, we will also test which items best predict need for privacy, and report these items in our companion website.
+
+Because both analyses require highly complex model (overall, 24 personality factors, 7 socio-demographic variables, and potentially 8 privacy dimensions), it might be that we need to simply the model.
+To this end, instead of a fully latent structural regression model we will then conduct a partially latent structural regression model, in which the predictor variables will be modeled as single indicators while controlling for measurement error [@klinePrinciplesPracticeStructural2016, p.
 214].
-To get high-quality single indicators of the predictors, we computed the average of the model predicted values / latent factor scores, which we extracted from the CFAs. 
-If the CFAs showed a unidimensional solution, we used the model predicted values for this latent factor; if the CFAs produced a multidimensional solution, we used the model predicted values for the general latent factor.
+To get high-quality single indicators of the predictors, we will compute the average of the model predicted values / latent factor scores, which we can be extracted from the CFAs. 
+If the CFAs will show a unidimensional solution, we will use the model predicted values for this latent factor; if the CFAs will produce a multidimensional solution, we will use the model predicted values for the general latent factor.
 
-Finally, combining several items into a latent factors helps to reduce and condense information, while partialing out error. 
-At the same time, and although above we explicated our analysis pipeline, this approach still maintains several researcher degrees of freedom. 
-We hence emphasize that we will adapt the models only to achieve satisfactory factorial validity and not to cherry-pick significant material. 
-To provide a broader picture, in the online supplementary material (OSM) we will also share the results of the unaltered factors and how the personality factors predicted reach need for privacy item individually.
+Fully latent SEMs seldom work instantly and often require modifications to achieve satisfactory model fit.
+Although above we explicated our analysis pipeline, we are aware that this approach still maintains some researcher degrees of freedom. 
+We hence emphasize that we will adapt the models only to achieve satisfactory factorial validity, but not to cherry-pick significant results.
+We adopt this latent modeling approach because we consider it superior to regular analyses such as regression based models of manifest variables [@klinePrinciplesPracticeStructural2016]. 
+Combining several items into a latent factors helps reduce and condense information, while partialing out error and thereby reducing noise.
+To provide the complete picture, in the online supplementary material (OSM) we will also share the results of the unaltered latent factors and of regular regression.
 
@@
 All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
-A list of all the items that were used (including deleted ones), results of CFAs/EFAs, as well as item statistics and their distribution plots can be found or will later be reported in the OSM.
+A list of all the items that we will use are reported in the online supplementary material. 
+We will later report also the results of the CFAs/EFAs, as well as item statistics and their distribution plots.
 
@@
 
-Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of a scale that is both encompassing and up-to-date.
-Hence, we use both extant scales and newly developed ad-hoc scales, some of which were already pretested. 
-Ad-hoc scales were tentatively validated. 
-We (a) collected qualitative feedback from three different privacy experts, (b) tested and adapted the items using four established readability indices [i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula; see, e.g., @patalayAssessingReadabilitySelfreported2018], and (c) like @frenerDevelopmentValidationNeed2021 will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations.
+Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of an encompassing up-to-date scale.
+Hence, we use both extant scales and self-developed items, some of which were tested in our prestudy. 
+Ad-hoc scales were or will be (tentatively) validated using the following procedure:
+We (a) collected qualitative feedback from three different privacy experts; (b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and tested (and adapted) the items using four established readability indices [i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula]; (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations; (d) all items will be analyzed in confirmatory factor analyses as outline above.
 
 Overall, we will collect 32 items measuring need for privacy, with eight subdimensions consisting of four items each. 
-Three subdimensions were adopted from @frenerDevelopmentValidationNeed2021 -- namely psychological, informational, and physiological privacy -- which build on Burgoon's @burgoonPrivacyCommunication1982 privacy theory.
-Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, we also measured a social privacy dimension, which in a prestudy showed satisfactory fit.
+Three subdimensions build on Burgoon's @burgoonPrivacyCommunication1982 privacy theory and were adopted from @frenerDevelopmentValidationNeed2021---namely psychological, informational, and physiological privacy.
+Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, we also measured a social privacy dimension, which in the prestudy showed satisfactory fit.
 We then measured need for privacy on a societal level. 
@@
 The inventory consists of six factors with four dimensions each, including the additional meta scale "altruism".
-We will predict need for privacy first using the factors and then using the facets.
 
@@
 
-All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/7ncpk/).
-The paper also has a companion website where all materials can be accessed ().
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/e47yw/).
+The paper also has a companion website where all materials can be accessed (https://tdienlin.github.io/Who_Needs_Privacy_RR/proposal.html).
 
@@
 
-The data will be shared on the open science framework (https://osf.io/7ncpk/).
+The data will be shared on the open science framework (https://osf.io/e47yw/) and on github.
 

### 2021-10-25 proposal.Rmd
- small changes to Intro

@@
 Put differently, given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
-One could even make the case that need for privacy and extraversion are conceptually the same, and that need for privacy is just a different label for the same underlying personality trait. 
-Interestingly, we are not aware of a personality inventory that explicitly refers to privacy.
+One could even make the case that need for (interpersonal) privacy and extraversion are conceptually the same, and that need for privacy is just a different label for the same underlying personality trait.
+That said, we are not aware of a personality inventory that explicitly refers to privacy,
+and besides, as we outline above privacy is multidimensional and aspects such as need for privacy from the government or anonymity appear to be different conceptually.
 
@@
 The remaining missing responses will be imputed using predictive mean matching. 
-We will remove respondents with exceedingly fast responses, namely below three standard deviations of the medium response time.
+We will remove respondents with unrealistically fast responses, namely below three standard deviations of the medium response time.
 
@@
 
+As a "reality check", we will test items for potential ceiling and floor effects. 
+If means are below 0.5 or above 6.5, these items will be excluded.
 The factorial validity of the measures and the hypotheses will be tested with structural equation modeling (SEM). 

### 2021-10-25 proposal.Rmd
- updated version before sending to Miriam

@@
 Living in an information age, people constantly have to decide what information to share, which service to use, when to communicate.
-All of these decisions are reflective of and determined by the users' need for privacy.
+All of these decisions are reflective of and determined by a person's need for privacy.
 We believe that it is relevant to understand who needs more and who needs less privacy, for example because desiring privacy often requires justification.
-The nothing-to-hide statement---i.e., 'someone who has nothing to hide has nothing to fear'---implies that people who desire privacy are suspicious.
+The nothing-to-hide statement---'someone who has nothing to hide has nothing to fear'---implies that people who desire privacy are suspicious.
 Although such suspicions might be justified in some cases, there are many alternative legitimate explanations as to why people desire privacy.
@@
 # output            : papaja::apa6_pdf
-# output            : papaja::apa6_word
+output            : papaja::apa6_word
 header-includes:
@@
 
-We believe it is relevant to understand better this research question, because people who desire privacy are often asked to justify themselves. 
+We believe it is relevant to address this research question, because people who desire privacy are often asked to justify themselves. 
 For example, the so-called _nothing-to-hide argument_ states that “If you have nothing to hide, you have nothing to fear”. 
 <!-- As described by Solove, the nothing-to-hide argument says that -->
-The argument implies that people who desire privacy are suspicious. 
-For example, once can often hear that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
+It implies that people who desire privacy are suspicious. 
+For example, once can sometimes hear that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
 Only those who are engaged in illegal activities have a reason to hide this information” [@soloveVeGotNothing2007, p. 753].
+
 And granted, it is only logical that people who commit crimes and who are insincere would in fact benefit from more privacy.
@@
 
-Also from an academic perspective, this research question is topical. 
+But also from an academic perspective, this research question is topical. 
 Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
 However, to date there is almost no empirical research that can be used to develop well-informed hypotheses.
+
 As a result, with this paper we would like to answer the following question:
@@
 
-The theoretical concept of privacy is complicated and contested [@nissenbaumPrivacyContextTechnology2010, p. 71].
-Thus, we first outline our own understanding of privacy. 
+We first outline our own understanding of privacy, because the theoretical concept of privacy is complicated and contested [@nissenbaumPrivacyContextTechnology2010, p. 71]. 
 First and foremost, privacy captures a _withdrawal_ from others, or from society in general [@westinPrivacyFreedom1967].
@@
 For the purpose of this study, we will hence employ a multifaceted model of need for privacy.
-We fill focus on (a) vertical privacy with regard to people's felt need for withdrawal from government surveillance and private companies, (b) horizontal privacy in terms of the perceived need for withdrawal from other people, psychological and physical privacy, and (c) both horizontal and vertical privacy as captured by people's felt need for informational privacy, anonymity, and privacy in general.
+We fill focus on (a) vertical privacy with regard to people's felt need for withdrawal from government surveillance and private companies; (b) horizontal privacy in terms of the perceived need for withdrawal from other people, psychological privacy, and physical privacy; and (c) both horizontal and vertical privacy as captured by people's felt need for informational privacy, anonymity, and privacy in general.
 
@@
 
-On the other hand, however, privacy can also have negative aspects. 
+Privacy can also have negative aspects. 
 It is possible to have too much privacy.
-Human beings are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
+Humans are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
 The fact that privacy fosters self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010].
-Privacy can also help conceal power-asymmetries, wrongdoing, or crimes such as violence or theft.
+Privacy can also help conceal wrongdoing or crimes such as violence or theft.
 The dialectical tension between the positive and negative aspects of privacy thus might cause variability across individuals in their need for privacy.
@@
 And as there is no established theory connecting privacy and personality, it is difficult to formulate precise and well-informed a priori hypotheses.
-As a result, in this study we adopt a more _exploratory_ perspective.
+
+In terms of potential theoretical explanations as to why personality might relate to need for privacy, we could imagine that much depends on whether an entity is considered a threat or a resource. 
+If something is a threat, if it is negative, it seems more likely to withdraw and to desire more privacy; if something is a resource, however, it seems more plausible to open up, to approach, and to desire less privacy [@altmanPrivacyConceptualAnalysis1976].
+<!-- Our reasoning further was guided by another central theoretical tenet.  -->
+<!-- As suggested above, privacy can be either positive or negative.  -->
+<!-- Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_.  -->
+<!-- Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat.  -->
+<!-- It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976]. -->
+
+That said, in this study we nonetheless adopt a more _exploratory_ perspective. 
 We implement a large-scale operationalization on personality, in order not to miss potentially relevant personality factors and facets.
+To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
 
-To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
-The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999]
+The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
 <!-- and represents a broad understanding of personality-->
-.
 It measures overall six factors (see below), which have four specific facets each. 
-We include also the specific facets because we do not expect that the even more specific need for privacy dimensions will relate closely to overarching general personality factors.
-(For example, privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors; @bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008.)
+We include also the specific facets because we do not expect that the even more specific need for privacy dimensions will relate closely to the overarching general personality factors.
+For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].
 
 Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled honesty-humility, 
-plus another additional meta-facet labeled altruism,
-which seems promising to investigate the nothing-to-hide-argument.
+plus another additional meta-facet called altruism,
+which together seem promising to investigate the nothing-to-hide-argument.
 <!-- Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets. -->
@@
 
-<!-- Our reasoning further was guided by another central theoretical tenet.  -->
-<!-- As suggested above, privacy can be either positive or negative.  -->
-<!-- Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_.  -->
-<!-- Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat.  -->
-<!-- It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976]. -->
-
 ### Honesty-Humility & Altriusm
@@
 The meta-facet altruism measures benevolence toward others and consists of items such as "It wouldn’t bother me to harm someone I didn’t like."
-According to the nothing-to-hide argument, one could assume that people might need privacy because they have something to hide---that is, because they are hence less honest, sincere, fair or benevolent.
+According to the nothing-to-hide argument, one could assume that people might need privacy because they have something to hide---namely, because they are less honest, sincere, fair, or benevolent.
 <!-- Hence, a potential predictor of why people need privacy could be how honest, correct, sincere, or benign they are. -->
@@
 Logically, people who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would sanction their activities [@petronioCommunicationPrivacyManagement2010].
-Hence, the government and other people are more likely to be perceived as a threat, which should render privacy a resource. 
+Hence, the government and other people are more likely to be perceived as a threat. 
 As a consequence, once could argue that people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
@@
 Empirical studies have found that surveillance can indeed reduce cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
-@coveySelfmonitoringSurveillanceIncentive1989 for example asked students to solve an impossible maze. 
+@coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
 In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
-In the low surveillance condition, the experimenter remained behind the students where they could not see the students. 
-Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy, people show more honesty (i.e., fewer cheating behaviors). 
-When playing the ultimatum/dictator game, people share less if the game is double blind (Fähr & Gächter, 2000; Gaulin & McBurney, 2001).
+In the low surveillance condition, the experimenter could not see the students. 
+Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy people show are more honest. 
+<!-- When playing the ultimatum/dictator game, people share less if the game is double blind (Fähr & Gächter, 2000; Gaulin & McBurney, 2001). -->
 Next, in a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
@@
 
-In conclusion, it seems possible that lack of honesty may indeed relate to an increased felt need for privacy, especially when it comes to government surveillance.
+In conclusion, it seems possible that lack of honesty may indeed relate to an increased need for privacy, especially when it comes to government surveillance.
 <!-- , as governments have the legitimate power to prosecute illegal activities.  -->
@@
 With regard to interpersonal privacy, one could argue that people who are anxious are more likely to consider social interactions a risk or threat [especially with strangers or weak ties, @granovetterStrengthWeakTies1973], which is why anxious people might desire more privacy.
-Somewhat related, prior empirical research showed that people who are more concerned about their privacy are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
+Somewhat related, prior empirical research showed that people who are more concerned about their privacy (in other words, more anxious) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
 On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
@@
 Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy. 
-Despite the fact that only 18% of all Americans trust their government "to do what is right" [@pewresearchcenterPublicTrustGovernment2017], almost everyone agrees that "it's the government's job to keep the country safe," while most people are also satisfied with the government's job [@pewresearchcenterDistrustHowAmericans2015].
+Despite the fact that only 18% of all Americans trust their government "to do what is right" [@pewresearchcenterPublicTrustGovernment2017], almost everyone agrees that "it's the government's job to keep the country safe" [@pewresearchcenterDistrustHowAmericans2015].
 Hence, for anxious individuals, the government might be seen as a resource rather than a threat. 
@@
 Put differently, given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
-One could even make the case that need for (interpersonal) privacy and extraversion are conceptually the same, and that need for privacy is just a different label for the same underlying personality trait.
+One could even make the case that need for (interpersonal) privacy and sociability are conceptually the same, and that need for privacy is just a different label for the same underlying personality trait.
 That said, we are not aware of a personality inventory that explicitly refers to privacy,
-and besides, as we outline above privacy is multidimensional and aspects such as need for privacy from the government or anonymity appear to be different conceptually.
+and besides, as we outline above privacy is multidimensional and aspects such as need for privacy from the government or companies appear to be different conceptually.
 
-Several empirical studies support the relation.
+Several empirical studies support thhis relation.
 People who scored higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, desired less privacy [@mortonMeasuringInherentPrivacy2013]; people who described themselves as introverted thinkers were more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people were more likely to report invasions of privacy [@stoneRelationshipIntroversionExtraversion1986].
-@pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem (but note, general self-esteem, not social self-esteem): 
+@pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem (but note, _general_ self-esteem, not _social_ self-esteem): 
 Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
@@
 Potentially noteworthy is that people who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
-Because need for privacy and privacy concerns are closely related, it seems possible that more agreeable people desire less privacy.
+Thus, because need for privacy and privacy concerns are closely related, it seems possible that more agreeable people desire less privacy.
 
@@
 Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
-Arguably, all facets are more or less about being in control, about reducing potential risks, and avoiding future costs.
+Arguably, all facets are more or less about being in control, about reducing potential risks, or about avoiding future costs.
 And because privacy is much about control (see above), we could imagine that an individual's felt need for privacy relates to their general tendency to avoid risks, to deliberate, and to plan ahead carefully.
@@
 Openness to experience is also considered a measure of intellect and education.
-This is only a personal impression, but sometimes it feels that advocates of privacy seem to come from the higher educational echelons of society, that they are the intellectual elites, for example when citing Orwell's 1984.
+
+What follows is only a personal impression, but sometimes it feels that advocates of privacy seem to come from the higher educational echelons of society, that they are the intellectual elites, for example when citing Orwell's 1984.
 Potentially related to this, empirical studies showed that more educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
@@
 We are also curious how ethnicity might correspond to need for privacy, and could well imagine that non-white groups desire more privacy from the government---but not necessarily from other people.
-We additionally investigate wheter a person's relationship status corresponds to their expressed need for privacy.
-Last, we also investigate whether one's political position is related to the need for privacy.
+We will additionally investigate wheter a person's relationship status corresponds to their expressed need for privacy.
+Last, we will also investigate whether one's political position is related to the need for privacy.
 We could imagine that more right-leaning people desire more privacy from the government, but not necessarily from other people.
@@
 
-We ran a prestudy, which is published as preprint [@dienlinWhoNeedsPrivacy2019].
+We ran a prestudy, which is published as a preprint [@dienlinWhoNeedsPrivacy2019].
 This study was submitted initially, but rejected for several empirical and conceptual reasons (for example, insufficient statistical power).
@@
 We calculated that participation will take approximately 15 minutes. 
-We will pay participants \$ 2.56 for participation, which equals an hourly wage of \$ 9,81.
+We will pay participants \$ 2.56 for participation, which equals an hourly wage of \$ 10.24.
 
@@
 Note that the final analyses will be conducted using structural equation modeling, for which exact power analyses are difficult to obtain. 
-We hence conducted tentative power analyses using two-sided bivariate correlations. 
+We hence conducted preliminary power analyses using two-sided bivariate correlations. 
 Hence, the following power analyses are not exact but only a rough guide to get a better idea of the required minimum sample size.
@@
 Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%).
-We adopted an exploratory perspective, and aimed not to miss potentially existing effects (beta error).
+Because we adopted an exploratory perspective, we aimed not to miss potentially existing effects (beta error).
 We opted for an approach where alpha and beta error are balanced/equal, because we consider both errors to be equally relevant. 
@@
 As a "reality check", we will test items for potential ceiling and floor effects. 
-If means are below 0.5 or above 6.5, these items will be excluded.
+If means are below 1.5 or above 6.5, these items will be excluded.
 The factorial validity of the measures and the hypotheses will be tested with structural equation modeling (SEM). 
@@
 To avoid overfiting, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016].
+
 If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
 If these changes do not yield sufficient fit, we will drop malfunctioning items. 
-
 If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
@@
 First, we will predict need for privacy using the factors, and then using the facets. 
-To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model, which we will report in the companion website.
-Based on reviewer feedback, we will also test which items best predict need for privacy, and report these items in our companion website.
+To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model, which we will report on the companion website.
+Based on reviewer feedback, we will also test which items best predict need for privacy, and report these items on our companion website.
 
-Because both analyses require highly complex model (overall, 24 personality factors, 7 socio-demographic variables, and potentially 8 privacy dimensions), it might be that we need to simply the model.
+Because both analyses require highly complex model (overall, 24 personality facets, 7 socio-demographic variables, and potentially 8 privacy dimensions), it might be that we need to simply the model. 
 To this end, instead of a fully latent structural regression model we will then conduct a partially latent structural regression model, in which the predictor variables will be modeled as single indicators while controlling for measurement error [@klinePrinciplesPracticeStructural2016, p.
@@
 To get high-quality single indicators of the predictors, we will compute the average of the model predicted values / latent factor scores, which we can be extracted from the CFAs. 
-If the CFAs will show a unidimensional solution, we will use the model predicted values for this latent factor; if the CFAs will produce a multidimensional solution, we will use the model predicted values for the general latent factor.
+If the CFAs show a unidimensional solution, we will use the model predicted values for this latent factor; if the CFAs produce a multidimensional solution, we will use the model predicted values for the general latent factor.
 
@@
 We hence emphasize that we will adapt the models only to achieve satisfactory factorial validity, but not to cherry-pick significant results.
-We adopt this latent modeling approach because we consider it superior to regular analyses such as regression based models of manifest variables [@klinePrinciplesPracticeStructural2016]. 
+We adopt this latent modeling approach nonetheless because we consider it superior to regular analyses such as regression based models of manifest variables [@klinePrinciplesPracticeStructural2016]. 
 Combining several items into a latent factors helps reduce and condense information, while partialing out error and thereby reducing noise.
@@
 Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of an encompassing up-to-date scale.
-Hence, we use both extant scales and self-developed items, some of which were tested in our prestudy. 
-Ad-hoc scales were or will be (tentatively) validated using the following procedure:
-We (a) collected qualitative feedback from three different privacy experts; (b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and tested (and adapted) the items using four established readability indices [i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula]; (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations; (d) all items will be analyzed in confirmatory factor analyses as outline above.
+Hence, we use both extant scales and self-developed items, some of which were already tested in our prestudy. 
+Ad-hoc scales were or will be (preliminary) validated using the following procedure:
+We (a) collected qualitative feedback from three different privacy experts; (b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and tested (and adapted) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations; (d) all items will be analyzed in confirmatory factor analyses as outline above.
 
@@
 Three subdimensions build on Burgoon's @burgoonPrivacyCommunication1982 privacy theory and were adopted from @frenerDevelopmentValidationNeed2021---namely psychological, informational, and physiological privacy.
-Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, we also measured a social privacy dimension, which in the prestudy showed satisfactory fit.
-We then measured need for privacy on a societal level. 
-The first subdimension was government surveillance, which represents the extent to which people want the government to abstain from collecting information about them. 
-The second dimension was anonymity, which captures the extent to which people feel the need to avoid identification. 
-Both scales were pretested and showed good factorial validity. 
-Third, we measured need for privacy from companies using four self-designed items. 
-Finally, we self-developed also a general measure of need for privacy.
+Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, we will also measure a social privacy dimension, which in the prestudy showed satisfactory fit.
+Next, we will measure need for privacy on a societal level. 
+The first subdimension is government surveillance, which represents the extent to which people want the government to abstain from collecting information about them. 
+The second dimension is anonymity, which captures the extent to which people feel the need to avoid identification. 
+Both scales were already pretested and showed good factorial validity. 
+Third, we will measure need for privacy from companies using four self-designed items. 
+Finally, we will also collect a self-developed measure of general need for privacy.
 

### 2023-03-01 analyses.RmD
- major update - now set up as a registered report

@@
     code_folding: hide
+    df_print: paged
 bibliography      : 
@@
 
-```{r r-setup, include=F}
+Here you can find the results of our study.
+
+- At this point, we haven't yet collected data. 
+- The results below use simulated data. 
+- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
+- We'll later conduct additional analyses, for example model-alterations given misfit.
+
+# Set-Up
+
+```{r r-setup, include=T, echo=F}
 # install packages
@@
 ```{r data-wrangling}
-d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")
+d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
+d <- rename(d, COL = COL_, REL = REL_)
 
@@
                        "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
-                       "Social Self-Esteem", "Social Boldness", "Sociability", "Liveliness",
+                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
                        "Forgiveness", "Gentleness", "Flexibility", "Patience", 
                        "Organization", "Diligence", "Perfectionism", "Prudence", 
-                       "Aesthetic Appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
+                       "Aesthetic appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
                        "Altruism")
@@
 
-vars_pri <- c("NFP_INF", "NFP_PSY", "NFP_PHY", "NFP_CNC", "NFP_SPA", 
-              "NFP_GOV", "NFP_INT", "NFP_ANO", "NFP_COM", "NFP_GEN")
-vars_pri_txt <- c("Informational", "Psychological", "Physical", "Concealment", "Personal Space", 
-                  "Government", "Interpersonal", "Anonymity", "Companies", "General")
+vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
+              "NFP_GOV", "NFP_COM", 
+              "NFP_INF", "NFP_ANO", "NFP_GEN")
+vars_pri_txt <- c("Social", "Physical", "Psychological",
+                  "Companies", "Governnment",
+                  "Anonynmity", "Infornmational", "General")
+vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
+                  "Companies", "Govern-\nment",
+                  "Anony-\nmity", "Infor-\nmational", "General")
+vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
+                  "Comp.", "Gov.",
+                  "Anonym.", "Inform.", "General")
 
-vars_ses <- c("age", "gender", "ethnicity", "relationship", "college", "income", "conservatism")
-
+vars_ses <- c("AGE", "GEN", "ETH", "REL", "COL", "INC", "CON")
+vars_ses_txt <- c("Age", "Gender", "Ethnicity", "Relationship", "College", "Income", "Conservatism")
 ```
@@
 #### Dependence
+
  - When I suffer from a painful experience, I need someone to make me feel comfortable.
@@
 ## Need for privacy
+### Psychological
+
+ 1.	I don’t like to talk about personal issues with others unless they do it first.
+ 2.	There are a lot of things about me that I don’t like to talk about with others.
+ 3.	I prefer not to share my feelings and inner thoughts with others.
+ 4.	I don't like it when others talk to me about their private issues.
+
+```{r}
+model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
+```
+
+### Physical
+
+ 1.	I don’t like it when strangers come too close to me.
+ 2.	I don’t like to stand in a dense crowd of people.
+ 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
+ 4.	I hate it when people enter my personal space uninvited.
+
+```{r}
+model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
+```
+
+### Social
+
+ 1.	I don’t feel comfortable interacting with other people.
+ 2.	I often want to be alone.
+ 3.	I’m a fairly anti-social person.
+ 4.	I prefer to work independently in most situations.
+
+```{r}
+model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
+```
+
+### Privacy from Government
+
+ 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
+ 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
+ 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
+ 4.	I feel I need to protect my privacy from government agencies.
+
+```{r}
+model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
+```
+
+### Privacy from Companies
+
+ 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
+ 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
+ 3. I don’t want companies to collect data about me, even if that makes their services worse.
+ 4. I feel I need to protect my privacy from companies.
+
+```{r}
+model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
+```
+
 ### Informational
 
- - I would prefer that little is known about me. 
- - In general, I prefer to remain incognito. 
- - I don’t want my personal data to be publicly accessible. 
- - Not everyone has to know everything about me.
+ 1.	I would prefer that little is known about me.
+ 2.	I don’t want my personal data to be publicly accessible.
+ 3.	It is important to me that records pertaining to me remain confidential.
+ 4.	I prefer that others cannot easily find information about me on the Internet.
 
@@
 
-### Psychological
-
- - I don’t like to talk about personal issues unless others do it first.
- - There are a lot of things about me that I don’t like to talk about with others. 
- - I feel uncomfortable when others tell me private things about their lives. 
- - It is hard for me to talk about my feelings and inner thoughts.
-
-```{r}
-model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
-```
-
-### Physiological
-
- - I don’t like it when strangers come too close to me. 
- - I feel uncomfortable when others enter my flat or room unannounced. 
- - I don’t like to stand in a dense crowd of people. 
- - I don’t like to sit next to a stranger on the tram or bus.
-
-```{r}
-model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
-```
-
-### Privacy from other People
-
- - My need for privacy is so strong that it prevents me from using social media actively. 
- - I don’t feel I need to tell my friends all my secrets.
- - I feel I need to protect my privacy from other people.
- - I prefer it when others don’t know much about me.
-
-```{r}
-model <- "NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04"
-```
-
-#### Validation
-
-### Privacy from Government
-
- - I need government agencies to respect my privacy, even if that makes catching criminals harder.,
- - I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
- - I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
- - I feel I need to protect my privacy from government agencies.
-
-```{r}
-model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
-```
-
-#### Validation
-
 ### Privacy need anonymity
 
- - I need to be able to use a fake account on social network sites to preserve my privacy. 
- - I feel I need to avoid places with video surveillance.
- - I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
- - I need to be able to surf the Internet anonymously. (new)
+ 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
+ 2.	I feel I need to avoid places with video surveillance.
+ 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
+ 4.	I need to be able to surf the Internet anonymously.
 
@@
 
-#### Validation
-
-### Privacy from Companies
-
- - I’m willing to pay more for products or services so that companies don’t have to sell my data.
- - I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
- - I don’t want companies to gather information about me, even if that reduces the quality of their services.
- - I feel I need to protect my privacy from companies.
-
-```{r}
-model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
-```
-
-#### Validation
-
 ### General Need for privacy
 
- - I need a lot of privacy.
- - Privacy is very important to me.
- - I think a lot about how I can protect my privacy.
- - I need a lot of time for myself.
+ 1.	I need a lot of privacy.
+ 2.	Privacy is very important to me.
+ 3.	I think a lot about how I can protect my privacy.
+ 4.	I value privacy a lot.
 
@@
 ```
-
-#### Validation
 
@@
 # a priori power analyses
-pwr.r.test(r = sesoi, sig.level = .05, power = .95) ## too expensive
+pwr.r.test(r = sesoi, sig.level = .05, power = .95)
 power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
@@
 
-A 5% error rate would imply collecting 1.293 participants, which was outside of our budget.
+A 5% error rate would imply collecting 1.293 participants.
+
+# Results
+## SES
 
 ```{r}
-pwr.r.test(r = sesoi, sig.level = .1, power = .9)
-power_n_90 <- pwr.r.test(r = sesoi, sig.level = .1, power = .9)$n
+model_ses <- "
+# SES
+Age =~ AGE
+Gender =~ GEN
+Ethnicity =~ ETH
+Relationship =~ REL
+College =~ COL
+Income =~ INC
+Conservatism =~ CON
+
+# Privacy
+NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
+NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
+NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
+NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
+NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
+NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
+NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
+NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+"
+fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
+summary(fit_ses, standardized = TRUE)
+
+# get standardized data
+d_ses <- 
+  standardizedsolution(fit_ses)
 ```
 
-A 10% error rate would imply collecting 853 participants, which was within our budget.
-
-# Results
-## Facets
-
 ```{r}
-model_fac <- "
-HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
-HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
-HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
-HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
-HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
-HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
-HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
-HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
-HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
-HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
-HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
-HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
-HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
-HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
-HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
-HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
-HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
-HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
-HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
-HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
-HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
-HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
-HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
-NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
-NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
-NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-age =~ AGE
-gender =~ GEN
-ethnicity =~ ETH
-relationship =~ REL_
-college =~ COL_
-income =~ INC
-conservatism =~ CON
-"
-fit_fac <- sem(model_fac, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_fac, standardized = TRUE)
-
-d_fac <- 
-  standardizedsolution(fit_fac, ci = TRUE, level = .90) %>% 
+# make table
+tab_ses <- 
+  d_ses %>% 
   as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri)
-
-fig_fac <- ggplot(d_fac, aes(x = est.std, y = lhs)) +
-  geom_point() +
-  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
-  facet_wrap(vars(rhs), nrow = 1)
-
-# tab_results <- data.frame(
-#   tab_results_raw[1 : length(vars_pers_fac), ]$std.all,
-#   tab_results_raw[(1 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 2), ]$std.all,
-#   tab_results_raw[(2 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 3), ]$std.all,
-#   tab_results_raw[(3 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 4), ]$std.all,
-#   tab_results_raw[(4 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 5), ]$std.all,
-#   tab_results_raw[(5 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 6), ]$std.all,
-#   tab_results_raw[(6 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 7), ]$std.all,
-#   tab_results_raw[(7 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 8), ]$std.all,
-#   tab_results_raw[(8 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 9), ]$std.all,
-#   tab_results_raw[(9 * length(vars_pers_fac) + 1) : (length(vars_pers_fac) * 10), ]$std.all
-# )
-# names(tab_results) <- vars_pri
-# rownames(tab_results) <- vars_pers_fac
+  filter(op == "~~", lhs %in% vars_ses_txt, rhs %in% vars_pri) %>% 
+  select("Sociodemographics" = lhs, "Need for privacy" = rhs, est.std) %>% 
+  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
+  pivot_wider(id_cols = "Sociodemographics", names_from = "Need for privacy", values_from = "est.std") %>% 
+  as.data.frame()
+tab_ses
 ```
 
-## Factors
+## Dimensions
 
@@
 model_dim <- "
+# Personality Factors
 HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
@@
 
+# Privacy
+NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
+NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
+NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
+NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
+NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
+NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
 NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
-NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
 NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
@@
 
-# extract results
+# get standardized data
 d_dim <- 
-  standardizedsolution(fit_dim, ci = TRUE, level = .90) %>% 
-  as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri)
-
-fig_dim <- ggplot(d_dim, aes(x = est.std, y = lhs)) +
-  geom_point() +
-  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
-  facet_wrap(vars(rhs), nrow = 1)
-
-# tab_results <- data.frame(
-#   tab_results_raw[1 : length(vars_pers_dim), ]$std.all,
-#   tab_results_raw[(1 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 2), ]$std.all,
-#   tab_results_raw[(2 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 3), ]$std.all,
-#   tab_results_raw[(3 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 4), ]$std.all,
-#   tab_results_raw[(4 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 5), ]$std.all,
-#   tab_results_raw[(5 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 6), ]$std.all,
-#   tab_results_raw[(6 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 7), ]$std.all,
-#   tab_results_raw[(7 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 8), ]$std.all,
-#   tab_results_raw[(8 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 9), ]$std.all,
-#   tab_results_raw[(9 * length(vars_pers_dim) + 1) : (length(vars_pers_dim) * 10), ]$std.all
-# )
-# names(tab_results) <- vars_pri
-# rownames(tab_results) <- vars_pers_dim
+  standardizedsolution(fit_dim)
 ```
 
-## SES
+```{r}
+# make table
+tab_dim <- 
+  d_dim %>% 
+  as.data.frame() %>% 
+  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri) %>% 
+  select("Personality dimension" = lhs, "Need for privacy" = rhs, est.std) %>% 
+  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
+  pivot_wider(id_cols = "Personality dimension", names_from = "Need for privacy", values_from = "est.std") %>% 
+  mutate(`Personality dimension` = factor(`Personality dimension`, levels = vars_pers_dim, labels = vars_pers_dim_txt)) %>% 
+  as.data.frame()
+tab_dim
+```
+
+## Facets
 
 ```{r}
-model_ses <- "
-age =~ AGE
-gender =~ GEN
-ethnicity =~ ETH
-relationship =~ REL_
-college =~ COL_
-income =~ INC
-conservatism =~ CON
+model_fac <- "
+# Personality
+HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
+HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
+HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
+HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
+HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
+HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
+HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
+HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
+HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
+HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
+HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
+HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
+HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
+HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
+HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
+HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
+HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
+HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
+HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
+
+# Privacy
+NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
+NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
+NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
+NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
+NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
+NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
+NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
+NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+"
+fit_fac <- sem(model_fac, d, estimator = "ML", fixed.x = TRUE)
+summary(fit_fac, standardized = TRUE)
+
+# get standardized data
+d_fac <- 
+  standardizedsolution(fit_fac)
+```
+
+```{r}
+# make table
+tab_fac <- 
+  d_fac %>% 
+  as.data.frame() %>% 
+  filter(op == "~~", lhs %in% vars_pers_fac, rhs %in% vars_pri) %>% 
+  select("Personality facet" = lhs, "Need for privacy" = rhs, est.std) %>% 
+  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
+  pivot_wider(id_cols = "Personality facet", names_from = "Need for privacy", values_from = "est.std") %>% 
+  mutate(`Personality facet` = factor(`Personality facet`, levels = vars_pers_fac, labels = vars_pers_fac_txt)) %>% 
+  as.data.frame
+tab_fac
+```
+
+## Regression
+
+```{r}
+model_reg <- "
+# Personality Factors
+HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
+HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
+HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
+HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
+
+HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
+HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
+HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+
+HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
+HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
+HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
+HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
+HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+
+HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
+HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
+HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
+HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
+
+HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
+HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
+HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
+HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
+
+# Privacy
 NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
@@
 NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_CNC =~ NFP_CNC_01 + NFP_CNC_02 + NFP_CNC_03 + NFP_CNC_04
-NFP_SPA =~ NFP_SPA_01 + NFP_SPA_02 + NFP_SPA_03 + NFP_SPA_04
+NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
 NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04
+NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
 NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
 NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+
+NFP_INF + NFP_PSY + NFP_PHY + NFP_SOC + NFP_GOV + NFP_COM + NFP_ANO + NFP_GEN ~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD + HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN + HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV + HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT + HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU + HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC + AGE + GEN + ETH + REL + COL + INC + CON
 "
-fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_ses, standardized = TRUE)
+fit_reg <- sem(model_reg, d, estimator = "ML", fixed.x = TRUE)
+summary(fit_reg, standardized = TRUE)
 
-# extract results
-d_ses <- 
-  standardizedsolution(fit_ses, ci = TRUE, level = .90) %>% 
-  as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_ses, rhs %in% vars_pri)
-
-fig_ses <- ggplot(d_ses, aes(x = est.std, y = lhs)) +
-  geom_point() +
-  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper)) +
-  facet_wrap(vars(rhs), nrow = 1)
-
-# tab_results <- data.frame(
-#   tab_results_raw[1 : length(vars_ses), ]$std.all,
-#   tab_results_raw[(1 * length(vars_ses) + 1) : (length(vars_ses) * 2), ]$std.all,
-#   tab_results_raw[(2 * length(vars_ses) + 1) : (length(vars_ses) * 3), ]$std.all,
-#   tab_results_raw[(3 * length(vars_ses) + 1) : (length(vars_ses) * 4), ]$std.all,
-#   tab_results_raw[(4 * length(vars_ses) + 1) : (length(vars_ses) * 5), ]$std.all,
-#   tab_results_raw[(5 * length(vars_ses) + 1) : (length(vars_ses) * 6), ]$std.all,
-#   tab_results_raw[(6 * length(vars_ses) + 1) : (length(vars_ses) * 7), ]$std.all,
-#   tab_results_raw[(7 * length(vars_ses) + 1) : (length(vars_ses) * 8), ]$std.all,
-#   tab_results_raw[(8 * length(vars_ses) + 1) : (length(vars_ses) * 9), ]$std.all,
-#   tab_results_raw[(9 * length(vars_ses) + 1) : (length(vars_ses) * 10), ]$std.all
-# )
-# names(tab_results) <- vars_pri
-# rownames(tab_results) <- vars_ses
+# get standardized data
+d_reg <- 
+  standardizedsolution(fit_reg, ci = TRUE)
 ```
 
-```{r}
+```{r fig.width=10, fig.height=9}
+# make table
+tab_reg <- 
+  d_reg %>% 
+  as.data.frame() %>% 
+  filter(op == "~", lhs %in% vars_pri) %>% 
+  select("Need for privacy" = lhs, "Predictor" = rhs, Estimate = est.std, ci.lower, ci.upper) %>% 
+  mutate(Predictor = factor(Predictor, levels = c(vars_pers_fac, vars_ses), labels = c(vars_pers_fac_txt, vars_ses_txt)),
+         `Need for privacy` = factor(`Need for privacy`, levels = c(vars_pri), labels = c(vars_pri_txt)),
+         Predictor_cat = c(vars_pers_dim_txt %>% rep(each = 4), "Sociodemographics" %>% rep(7)) %>% rep(length(vars_pri_txt)))
+
+reg_fig <- ggplot(tab_reg, aes(x = Estimate, y = Predictor)) + 
+  coord_cartesian(xlim = c(-.5, .5)) +
+  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
+  geom_vline(xintercept = -.1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
+  geom_vline(xintercept = .1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
+  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper),
+                lwd = .75, height = .2, position = position_dodge(-.7)) +
+  geom_point(size = 1.5, position = position_dodge(-.7)) +
+  scale_x_continuous(breaks = c(-.3, 0, .3)) + 
+  theme(
+    axis.title.y = element_blank(),
+    plot.title = element_text(hjust = .5),
+    # panel.spacing = unit(.9, "lines"),
+    text = element_text(size = 12),
+    axis.text.y = element_text(hjust = 1),
+    legend.position = "none"
+    ) + 
+    facet_grid(Predictor_cat ~ `Need for privacy`, scales = "free_y")
+suppressWarnings(print(reg_fig, warning = F))
+
+ggsave("figures/fig_reg.png", width = 9, height = 10)
+```
+
+```{r cache=F}
 save.image("data/workspace.RData")

### 2023-03-01 analyses_additional.RmD
- major update - now set up as a registered report

--- 2021-08-25 analyses_readability.Rmd
@@
 ---
-title: "Readability analyses of items"
+title: "Who Needs Privacy? Exploring the relationship between personality and need for privacy"
+subtitle: "Additional Analyses"
 output:
@@
 lapply(packages, library, character.only = TRUE)
-
-# readability function
-readability = function(data){
-  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
-  textstat_readability(data, measure = reading_estimates) %>% 
-    as.data.frame %>% 
-    mutate(average = rowMeans(select(., -document)))
-}
 ```
 
-```{r data-wrangling}
-d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")
-```
-
-Below, we develop several new items for need for privacy.
-To validate items, we follow the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and calculate the following four reading scores: Flesch–Kincaid reading grade (FK), Gunning Fog Index (GFI), Coleman Liau Index (CLI), and the Powers-Sumner-Kearl Variation of the Dale and Chall Readability formula (DC).
-
-To have a benchmark, we calculated the readability of the HEXACO items. It was as follows:
-
-```{r}
-items_hexaco <- c(
-  "If I want something from a person I dislike, I will act very nicely toward that person in order to get it.", 
- "I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.", 
- "If I want something from someone, I will laugh at that person's worst jokes.", 
- "I wouldn't pretend to like someone just to get that person to do favors for me.", 
- "If I knew that I could never get caught, I would be willing to steal a million dollars.", 
- "I would be tempted to buy stolen property if I were financially tight.", 
- "I would never accept a bribe, even if it were very large.", 
- "I’d be tempted to use counterfeit money, if I were sure I could get away with it.", 
- "Having a lot of money is not especially important to me.", 
- "I would like to live in a very expensive, high-class neighborhood.", 
- "I would like to be seen driving around in a very expensive car.", 
- "I would get a lot of pleasure from owning expensive luxury goods.", 
- "I am an ordinary person who is no better than others.", 
- "I wouldn’t want people to treat me as though I were superior to them.", 
- "I think that I am entitled to more respect than the average person is.", 
- "I want people to know that I am an important person of high status.", 
- "I would feel afraid if I had to travel in bad weather conditions.", 
- "I don’t mind doing jobs that involve dangerous work.", 
- "When it comes to physical danger, I am very fearful.", 
- "Even in an emergency I wouldn't feel like panicking.", 
- "I sometimes can't help worrying about little things.", 
- "I worry a lot less than most people do.", 
- "I rarely, if ever, have trouble sleeping due to stress or anxiety.", 
- "I get very anxious when waiting to hear about an important decision.", 
- "When I suffer from a painful experience, I need someone to make me feel comfortable.", 
- "I can handle difficult situations without needing emotional support from anyone else.", 
- "Whenever I feel worried about something, I want to share my concern with another person.", 
- "I rarely discuss my problems with other people.", 
- "I feel like crying when I see other people crying.", 
- "When someone I know well is unhappy, I can almost feel that person's pain myself.", 
- "I feel strong emotions when someone close to me is going away for a long time.", 
- "I remain unemotional even in situations where most people get very sentimental.", 
- "I feel reasonably satisfied with myself overall.", 
- "I think that most people like some aspects of my personality.", 
- "I feel that I am an unpopular person.", 
- "Even in an emergency I wouldn't feel like panicking.", 
- "I rarely express my opinions in group meetings.", 
- "In social situations, I'm usually the one who makes the first move.", 
- "When I'm in a group of people, I'm often the one who speaks on behalf of the group.", 
- "I tend to feel quite self-conscious when speaking in front of a group of people.", 
- "I avoid making 'small talk' with people.", 
- "I enjoy having lots of people around to talk with.", 
- "I prefer jobs that involve active social interaction to those that involve working alone.", 
- "The first thing that I always do in a new place is to make friends.", 
- "I am energetic nearly all the time.", 
- "On most days, I feel cheerful and optimistic.", 
- "People often tell me that I should try to cheer up.", 
- "Most people are more upbeat and dynamic than I generally am.", 
- "I rarely hold a grudge, even against people who have badly wronged me.", 
- "My attitude toward people who have treated me badly is 'forgive and forget'.", 
- "If someone has cheated me once, I will always feel suspicious of that person.", 
- "I find it hard to fully forgive someone who has done something mean to me.", 
- "People sometimes tell me that I am too critical of others.", 
- "I generally accept people’s faults without complaining about them.", 
- "I tend to be lenient in judging other people.", 
- "Even when people make a lot of mistakes, I rarely say anything negative.", 
- "People sometimes tell me that I'm too stubborn.", 
- "I am usually quite flexible in my opinions when people disagree with me.", 
- "When people tell me that I’m wrong, my first reaction is to argue with them.", 
- "I find it hard to compromise with people when I really think I’m right.", 
- "People think of me as someone who has a quick temper.", 
- "I rarely feel anger, even when people treat me quite badly.", 
- "Most people tend to get angry more quickly than I do.", 
- "I find it hard to keep my temper when people insult me.", 
- "I clean my office or home quite frequently.", 
- "I plan ahead and organize things, to avoid scrambling at the last minute.", 
- "People often joke with me about the messiness of my room or desk.", 
- "When working, I sometimes have difficulties due to being disorganized.", 
- "When working, I often set ambitious goals for myself.", 
- "I often push myself very hard when trying to achieve a goal.", 
- "Often when I set a goal, I end up quitting without having reached it.", 
- "I do only the minimum amount of work needed to get by.", 
- "I often check my work over repeatedly to find any mistakes.", 
- "When working on something, I don't pay much attention to small details.", 
- "I always try to be accurate in my work, even at the expense of time.", 
- "People often call me a perfectionist.", 
- "I make decisions based on the feeling of the moment rather than on careful thought.", 
- "I make a lot of mistakes because I don't think before I act.", 
- "I don’t allow my impulses to govern my behavior.", 
- "I prefer to do whatever comes to mind, rather than stick to a plan.", 
- "I would be quite bored by a visit to an art gallery.", 
- "I wouldn't spend my time reading a book of poetry.", 
- "If I had the opportunity, I would like to attend a classical music concert.", 
- "Sometimes I like to just watch the wind as it blows through the trees.", 
- "I'm interested in learning about the history and politics of other countries.", 
- "I enjoy looking at maps of different places.", 
- "I would be very bored by a book about the history of science and technology.", 
- "I’ve never really enjoyed looking through an encyclopedia.", 
- "I would like a job that requires following a routine rather than being creative.", 
- "I would enjoy creating a work of art, such as a novel, a song, or a painting.", 
- "People have often told me that I have a good imagination.", 
- "I don't think of myself as the artistic or creative type.", 
- "I think that paying attention to radical ideas is a waste of time.", 
- "I like people who have unconventional views.", 
- "I think of myself as a somewhat eccentric person.", 
- "I find it boring to discuss philosophy.", 
- "I have sympathy for people who are less fortunate than I am.", 
- "I try to give generously to those in need.", 
- "It wouldn’t bother me to harm someone I didn’t like.", 
- "People see me as a hard-hearted person."
-)
-readability_hexaco <- readability(items_hexaco)
-readability_hexaco <- colMeans(select(readability_hexaco, -document))
-readability_hexaco <- data.frame(document = "HEXACO", as.list(readability_hexaco))
-readability_hexaco
-```
-
-Readability was good. The results means that, on average, understanding the items requires seven years of schooling.
-
-# Privacy from Government
-
- - I need government agencies to respect my privacy, even if that hinders a greater societal cause, such as catching criminals.
- - I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.
- - I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.
- - I feel I need to protect my privacy from government agencies.
-
-```{r}
-items_old <- c(
- "I need government agencies to respect my privacy, even if that hinders a greater societal cause, such as catching criminals.",
- "I don’t want the government to gather information about me, even if that makes it more difficult for them to spend tax income efficiently.",
- "I don’t want government agencies to monitor my personal communication, even if doing so prevents future terrorist attacks.",
- "I feel I need to protect my privacy from government agencies."
-)
-readability(items_old) %>% rbind(readability_hexaco)
-```
-
-Items 1, 2 and 3 show rather high scores. Try to formulate easier.
-
-New items:
-
- - I need government agencies to respect my privacy, even if that makes catching criminals harder.,
- - I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
- - I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
- - I feel I need to protect my privacy from government agencies.
-
-```{r}
-items_new <- c(
- "I need government agencies to respect my privacy, even if that makes catching criminals harder.",
- "I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.",
-  "I don’t want government agencies to track my communication, even if that stops terrorist attacks.",
-  "I feel I need to protect my privacy from government agencies."
-)
-readability(items_new) %>% rbind(readability_hexaco)
-```
-
-A bit better, but not much.
-
-```{r}
-model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
-```
-
-# Privacy from other People
-
- - My need for privacy is so strong that it prevents me from using social media actively. 
- - I don’t feel I need to tell my friends all my secrets.
- - I feel I need to protect my privacy from other people.
- - I prefer it when others don’t know much about me.
-
-```{r}
-items <- c(
- "My need for privacy is so strong that it prevents me from using social media actively.",
- "I don’t feel I need to tell my friends all my secrets.",
- "I feel I need to protect my privacy from other people.",
- "I prefer it when others don’t know much about me."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Readability looks good!
-
-```{r}
-model <- "NFP_INT =~ NFP_INT_01 + NFP_INT_02 + NFP_INT_03 + NFP_INT_04"
-```
-
-# Privacy need anonymity
-
- - I need to be able to use a fake account on social network sites to preserve my privacy. 
- - I feel I need to avoid places with video surveillance.
- - I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
- - I need to be able to surf the Internet anonymously. (new)
-
-```{r}
-items <- c(
- "I need to be able to use a fake account on social network sites to preserve my privacy.",
- "I feel I need to avoid places with video surveillance.",
- "I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.",
- "I need to be able to surf the Internet anonymously."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Readability looks good!
-
-```{r}
-model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
-```
-
-# Privacy from Companies
-
- - I’m willing to pay more for products or services so that companies don’t have to sell my data.
- - I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
- - I don’t want companies to gather information about me, even if that reduces the quality of their services.
- - I feel I need to protect my privacy from companies.
-
-```{r}
-items <- c(
- "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
- "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
- "I don’t want companies to collect data about me, even if that makes their services worse.",
- "I feel I need to protect my privacy from companies."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Items 3 seems to be a bit too difficult. Try to make easier.
-
-```{r}
-items <- c(
- "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
- "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
- "I don’t want companies to gather information about me, even if that lowers the quality of their services.",
- "I feel I need to protect my privacy from companies."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Readability now much better.
-
-```{r}
-model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
-```
-
-# General Need for privacy
-
- - I need a lot of privacy.
- - Privacy is very important to me.
- - I think a lot about how I can protect my privacy.
- - I need a lot of time for myself.
-
-```{r}
-items <- c(
-  "I need a lot of privacy.",
-  "Privacy is very important to me.",
-  "I think a lot about how I can protect my privacy.",
-  "I need a lot of time for myself."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Readability was good.
+Here you will be able to find additional analyses.

### 2023-03-01 index.Rmd
- updated for website
- major update - now set up as a registered report

@@
 
-On this website, you can find the companion material for the paper _Who needs privacy? Exploring the relation between personality and need for privacy_.
+On this website, you can find the companion material for the paper _Who needs privacy?
+Exploring the relations between need for privacy and personality_.
+The paper is currently submitted to the journal Collabra as registered report.
+The report is based on an [older paper](https://osf.io/m23bn) that was already submitted to Collabra but rejected.
+This paper now addresses the [feedback from the original submission](reviews.pdf) and considers the original paper a prestudy.
 
-You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf).
-You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper, as well as [additional analyses](analyses_additional.html) not reported in the paper.
+- You can either read the paper [in your browser](proposal.html) or download it as [pdf](proposal.pdf). 
+- You can also find the detailed code and summaries of the [planned analyses](analyses.html) reported in the paper
+- Once finished, you will also be able to find [additional analyses](analyses_additional.html) not reported in the paper.
 

### 2023-03-01 analysis_pipeline.Rmd
- major update - now set up as a registered report

---
title: "Analysis Pipeline"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---

Below we state how we plan to analyze the data. To achieve sufficient model fit, there'll likely be several adaptions.

# Model Fit

 - If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
 - If these changes do not yield sufficient fit, we will drop malfunctioning items. 
 - If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
 - EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
 - If more than one dimension is revealed, we will implement bifactor model solutions.[^1] 
 - Bifactor models retain a general measure of the variable, without introducing novel potentially overfitted subdimensions.
 - If no adequate bifactor model can be found, we will proceed by deleting items with low loadings on the general factor and/or the specific factors. 
 - If also after deletion of individual items no bifactor solution should emerge, we will use a subset of the items to extract a single factor with sufficient factorial validity.

[^1]: Bifactor models feature one factor that explains the variance in all items (the so-called general factor or g-factor). 
In addition, at least two additional factors are implemented that explain the variance in a subset of the items. The general factor and the specific factors are orthogonal. 
Bifactor models are nested within hierarchical models. 
For more information on bifactor models, see @klinePrinciplesPracticeStructural2016, p. 319. 
Note that we will not specify a bifactor model of all items measuring need for privacy, because we are explicitly interested in the relations between the personality facets and the respective dimensions of need for privacy.

# Analysis

Because the analyses are complex, it might be that we need to simplify the model. We will proceed as follows.

- Instead of a fully latent structural regression model, we will then conduct a partially latent structural regression model, in which the predictor variables will be modeled as single indicators while controlling for measurement error [@klinePrinciplesPracticeStructural2016, p. 214]. 
    - To get high-quality single indicators of the predictors, we will compute the average of the model predicted values/latent factor scores, which can be extracted from the CFAs. 
    - If the CFAs show a unidimensional solution, we will use the model predicted values for this latent factor; if the CFAs produce a multidimensional solution, we will use the model predicted values for the general latent factor.

### 2023-03-01 items.rmd
- major update - now set up as a registered report

@@
 title: "Items"
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-      toc_depth: 3
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#       toc_depth: 3
+output: pdf_document
+bibliography: 
+  - "bibliography/references.bib"
 ---
@@
 # Personality
+
+@leePsychometricPropertiesHEXACO1002018
+
 ## Honesty Humility
@@
 # Need for privacy
-## Informational
+## Horizontal privacy
+### Psychological
+
+@frenerDevelopmentValidationNeed2021
+
+ 1.	I don’t like to talk about personal issues with others unless they do it first.
+ 2.	There are a lot of things about me that I don’t like to talk about with others.
+ 3.	I prefer not to share my feelings and inner thoughts with others.
+ 4.	I don't like it when others talk to me about their private issues. (new)
+
+### Physical
+
+@frenerDevelopmentValidationNeed2021
+
+ 1.	I don’t like it when strangers come too close to me.
+ 2.	I don’t like to stand in a dense crowd of people.
+ 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
+ 4.	I hate it when people enter my personal space uninvited. (new)
+
+### Social
+
+@dienlinWhoNeedsPrivacy2019
+
+ 1.	I don’t feel comfortable interacting with other people. [@harrisonDevelopmentDesirePrivacy1993]
+ 2.	I often want to be alone. (new)
+ 3.	I’m a fairly anti-social person. (new)
+ 4.	I prefer to work independently in most situations. (new)
+
+## Vertical privacy
+### Privacy from Government
+
+@dienlinWhoNeedsPrivacy2019
+
+ 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
+ 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
+ 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
+ 4.	I feel I need to protect my privacy from government agencies.
+
+### Privacy from Companies
+
+New, self-designed.
+
+ 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
+ 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
+ 3. I don’t want companies to collect data about me, even if that makes their services worse.
+ 4. I feel I need to protect my privacy from companies.
+
+## General privacy
+### Informational
+
+@frenerDevelopmentValidationNeed2021
 
  1.	I would prefer that little is known about me.
- 1. In general, I prefer to remain incognito. 
- 1. I don’t want my personal data to be publicly accessible. 
- 1. Not everyone has to know everything about me.
+ 2.	I don’t want my personal data to be publicly accessible.
+ 3.	It is important to me that records pertaining to me remain confidential. [@harrisonDevelopmentDesirePrivacy1993]
+ 4.	I prefer that others cannot easily find information about me on the Internet. (new)
 
-## Psychological
+### Privacy need anonymity
 
- 1. I don’t like to talk about personal issues unless others do it first.
- 1. There are a lot of things about me that I don’t like to talk about with others. 
- 1. I feel uncomfortable when others tell me private things about their lives. 
- 1. It is hard for me to talk about my feelings and inner thoughts.
+@dienlinWhoNeedsPrivacy2019
 
-## Physiological
+ 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
+ 2.	I feel I need to avoid places with video surveillance.
+ 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
+ 4.	I need to be able to surf the Internet anonymously. (new)
 
- 1. I don’t like it when strangers come too close to me. 
- 1. I feel uncomfortable when others enter my flat or room unannounced. 
- 1. I don’t like to stand in a dense crowd of people. 
- 1. I don’t like to sit next to a stranger on the tram or bus.
+### General Need for privacy
 
-## Social
-
- 1. My need for privacy is so strong that it prevents me from using social media actively. 
- 1. I don’t feel I need to tell my friends all my secrets.
- 1. I feel I need to protect my privacy from other people.
- 1. I prefer it when others don’t know much about me.
-
-## Privacy from Government
-
- 1. I need government agencies to respect my privacy, even if that makes catching criminals harder.,
- 1. I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
- 1. I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
- 1. I feel I need to protect my privacy from government agencies.
-
-## Privacy need anonymity
-
- 1. I need to be able to use a fake account on social network sites to preserve my privacy. 
- 1. I feel I need to avoid places with video surveillance.
- 1. I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
- 1. I need to be able to surf the Internet anonymously. (new)
-
-## Privacy from Companies
-
- 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
- 1. I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
- 1. I don’t want companies to gather information about me, even if that reduces the quality of their services.
- 1. I feel I need to protect my privacy from companies.
-
-## General Need for privacy
+New, self-designed.
 
  1.	I need a lot of privacy.
- 1. Privacy is very important to me.
- 1. I think a lot about how I can protect my privacy.
- 1. I need a lot of time for myself.
+ 2.	Privacy is very important to me.
+ 3.	I think a lot about how I can protect my privacy.
+ 4.	I value privacy a lot.
+
+# Privacy other
+## Concerns
+
+I'm very much concerned about my privacy in general.
+
+## Behavior
+
+I often take safety measures to protect my privacy.
+
+# Sociodemographics
+
+## Age
+
+How old are you?
+
+## Gender
+
+How do you describe yourself?
+
+ 1. Man
+ 2. Woman
+ 3. Third gender / other
+
+## Ethnicity
+
+With what ethnicity do you identify with?
+
+ 1. White
+ 2. Other
+
+## Relationship status
+
+Are you currently in a partnership or relation with another person?
+
+ 1. No
+ 2. Yes
+
+## College
+
+Please indicate the highest degree you have completed
+
+ 1. No college degree
+ 2. College degree
+
+## Income
+
+About how much money do you have at your disposal each month?
+
+ 1. < \$1.000
+ 2. \$1.000 - \$4.000
+ 3. > \$4.000
+
+## Politics
+
+Where would you position yourself politically?
+
+ - Extremely liberal
+ - Liberal
+ - Somewhat liberal
+ - Neutral
+ - Somewhat conservative
+ - Conservative
+ - Extremely conservative
+
+## Literature

### 2023-03-01 items_need-for-privacy.Rmd
- major update - now set up as a registered report

--- 2023-03-01 items.rmd
@@
 ---
-title: "Items"
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#       toc_depth: 3
-output: pdf_document
-bibliography: 
-  - "bibliography/references.bib"
+title: 'Items: Need for Privacy'
+output:
+  pdf_document:
+    toc: yes
+  html_document:
+    toc: yes
+    toc_float:
+      collapsed: no
+      toc_depth: 3
+bibliography: bibliography/references.bib
 ---
@@
 (-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree
-
-# Personality
-
-@leePsychometricPropertiesHEXACO1002018
-
-## Honesty Humility
-### Sincerity
-
- 1. If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
- 1. I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
- 1. If I want something from someone, I will laugh at that person's worst jokes.
- 1. I wouldn't pretend to like someone just to get that person to do favors for me.
-
-### Fairness
-
- 1. If I knew that I could never get caught, I would be willing to steal a million dollars.
- 1. I would be tempted to buy stolen property if I were financially tight.
- 1. I would never accept a bribe, even if it were very large.
- 1. I’d be tempted to use counterfeit money, if I were sure I could get away with it.
-
-### Greed Avoidance
-
- 1. Having a lot of money is not especially important to me.
- 1. I would like to live in a very expensive, high-class neighborhood.
- 1. I would like to be seen driving around in a very expensive car.
- 1. I would get a lot of pleasure from owning expensive luxury goods.
-
-### Modesty
-
- 1. I am an ordinary person who is no better than others.
- 1. I wouldn’t want people to treat me as though I were superior to them.
- 1. I think that I am entitled to more respect than the average person is.
- 1. I want people to know that I am an important person of high status.
-
-## Emotionality
-### Fearfulness
-
- 1. I would feel afraid if I had to travel in bad weather conditions.
- 1. I don’t mind doing jobs that involve dangerous work.
- 1. When it comes to physical danger, I am very fearful.
- 1. Even in an emergency I wouldn't feel like panicking.
-
-### Anxiety
-
- 1. I sometimes can't help worrying about little things.
- 1. I worry a lot less than most people do.
- 1. I rarely, if ever, have trouble sleeping due to stress or anxiety.
- 1. I get very anxious when waiting to hear about an important decision.
-
-### Dependence
- 1. When I suffer from a painful experience, I need someone to make me feel comfortable.
- 1. I can handle difficult situations without needing emotional support from anyone else.
- 1. Whenever I feel worried about something, I want to share my concern with another person.
- 1. I rarely discuss my problems with other people.
-
-### Sentimentality
-
- 1. I feel like crying when I see other people crying.
- 1. When someone I know well is unhappy, I can almost feel that person's pain myself.
- 1. I feel strong emotions when someone close to me is going away for a long time.
- 1. I remain unemotional even in situations where most people get very sentimental.
-
-## Extraversion
-### Social Self-Esteem
-
- 1. I feel reasonably satisfied with myself overall.
- 1. I think that most people like some aspects of my personality.
- 1. I feel that I am an unpopular person.
- 1. Even in an emergency I wouldn't feel like panicking.
-
-### Social Boldness
-
- 1. I rarely express my opinions in group meetings.
- 1. In social situations, I'm usually the one who makes the first move.
- 1. When I'm in a group of people, I'm often the one who speaks on behalf of the group.
- 1. I tend to feel quite self-conscious when speaking in front of a group of people.
-
-### Sociability
-
- 1. I avoid making "small talk" with people.
- 1. I enjoy having lots of people around to talk with.
- 1. I prefer jobs that involve active social interaction to those that involve working alone.
- 1. The first thing that I always do in a new place is to make friends.
-
-### Liveliness
-
- 1. I am energetic nearly all the time.
- 1. On most days, I feel cheerful and optimistic.
- 1. People often tell me that I should try to cheer up.
- 1. Most people are more upbeat and dynamic than I generally am.
-
-## Agreeableness
-### Forgiveness
-
- 1. I rarely hold a grudge, even against people who have badly wronged me.
- 1. My attitude toward people who have treated me badly is "forgive and forget".
- 1. If someone has cheated me once, I will always feel suspicious of that person.
- 1. I find it hard to fully forgive someone who has done something mean to me.
-
-### Gentleness
-
- 1. People sometimes tell me that I am too critical of others.
- 1. I generally accept people’s faults without complaining about them.
- 1. I tend to be lenient in judging other people.
- 1. Even when people make a lot of mistakes, I rarely say anything negative.
-
-### Flexibility
-
- 1. People sometimes tell me that I'm too stubborn.
- 1. I am usually quite flexible in my opinions when people disagree with me.
- 1. When people tell me that I’m wrong, my first reaction is to argue with them.
- 1. I find it hard to compromise with people when I really think I’m right.
-
-### Patience
-
- 1. People think of me as someone who has a quick temper.
- 1. I rarely feel anger, even when people treat me quite badly.
- 1. Most people tend to get angry more quickly than I do.
- 1. I find it hard to keep my temper when people insult me.
-
-## Conscientiousness
-### Organization
-
- 1. I clean my office or home quite frequently.
- 1. I plan ahead and organize things, to avoid scrambling at the last minute.
- 1. People often joke with me about the messiness of my room or desk.
- 1. When working, I sometimes have difficulties due to being disorganized.
-
-### Diligence
-
- 1. When working, I often set ambitious goals for myself.
- 1. I often push myself very hard when trying to achieve a goal.
- 1. Often when I set a goal, I end up quitting without having reached it.
- 1. I do only the minimum amount of work needed to get by.
-
-### Perfectionism
-
- 1. I often check my work over repeatedly to find any mistakes.
- 1. When working on something, I don't pay much attention to small details.
- 1. I always try to be accurate in my work, even at the expense of time.
- 1. People often call me a perfectionist.
-
-### Prudence
-
- 1. I make decisions based on the feeling of the moment rather than on careful thought.
- 1. I make a lot of mistakes because I don't think before I act.
- 1. I don’t allow my impulses to govern my behavior.
- 1. I prefer to do whatever comes to mind, rather than stick to a plan.
-
-## Openness
-### Aesthetic Appreciation
-
- 1. I would be quite bored by a visit to an art gallery.
- 1. I wouldn't spend my time reading a book of poetry.
- 1. If I had the opportunity, I would like to attend a classical music concert.
- 1. Sometimes I like to just watch the wind as it blows through the trees.
-
-### Inquisitiveness
-
- 1. I'm interested in learning about the history and politics of other countries.
- 1. I enjoy looking at maps of different places.
- 1. I would be very bored by a book about the history of science and technology.
- 1. I’ve never really enjoyed looking through an encyclopedia.
-
-### Creativeness
-
- 1. I would like a job that requires following a routine rather than being creative.
- 1. I would enjoy creating a work of art, such as a novel, a song, or a painting.
- 1. People have often told me that I have a good imagination.
- 1. I don't think of myself as the artistic or creative type.
-
-### Unconventionality
-
- 1. I think that paying attention to radical ideas is a waste of time.
- 1. I like people who have unconventional views.
- 1. I think of myself as a somewhat eccentric person.
- 1. I find it boring to discuss philosophy.
-
-## Altruism
-
- 1. I have sympathy for people who are less fortunate than I am.
- 1. I try to give generously to those in need.
- 1. It wouldn’t bother me to harm someone I didn’t like.
- 1. People see me as a hard-hearted person.
 
@@
  3.	I prefer not to share my feelings and inner thoughts with others.
- 4.	I don't like it when others talk to me about their private issues. (new)
+ 4.	I do not like it when others talk to me about their private issues. (new)
 
@@
  2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
- 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
+ 3.	I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.
  4.	I feel I need to protect my privacy from government agencies.
@@
  2.	I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
- 3. I don’t want companies to collect data about me, even if that makes their services worse.
+ 3.	I don’t want companies to gather information about me, even if that reduces the quality of their services.
  4.	I feel I need to protect my privacy from companies.
@@
 
-# Privacy other
-## Concerns
-
-I'm very much concerned about my privacy in general.
-
-## Behavior
-
-I often take safety measures to protect my privacy.
-
-# Sociodemographics
-
-## Age
-
-How old are you?
-
-## Gender
-
-How do you describe yourself?
-
- 1. Man
- 2. Woman
- 3. Third gender / other
-
-## Ethnicity
-
-With what ethnicity do you identify with?
-
- 1. White
- 2. Other
-
-## Relationship status
-
-Are you currently in a partnership or relation with another person?
-
- 1. No
- 2. Yes
-
-## College
-
-Please indicate the highest degree you have completed
-
- 1. No college degree
- 2. College degree
-
-## Income
-
-About how much money do you have at your disposal each month?
-
- 1. < \$1.000
- 2. \$1.000 - \$4.000
- 3. > \$4.000
-
-## Politics
-
-Where would you position yourself politically?
-
- - Extremely liberal
- - Liberal
- - Somewhat liberal
- - Neutral
- - Somewhat conservative
- - Conservative
- - Extremely conservative
-
 ## Literature

### 2023-03-01 items_readability.Rmd
- major update - now set up as a registered report

--- 2021-08-25 analyses_readability.Rmd
@@
 To validate items, we follow the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and calculate the following four reading scores: Flesch–Kincaid reading grade (FK), Gunning Fog Index (GFI), Coleman Liau Index (CLI), and the Powers-Sumner-Kearl Variation of the Dale and Chall Readability formula (DC).
+
+# Personality
 
@@
 
-# Privacy from Government
+# Privacy
+## Horizontal
+### Psychological
+
+@frenerDevelopmentValidationNeed2021
+
+ 1.	I don’t like to talk about personal issues with others unless they do it first.
+ 2.	There are a lot of things about me that I don’t like to talk about with others.
+ 3.	I prefer not to share my feelings and inner thoughts with others.
+ 4.	I do not like it when others talk to me about their private issues. (new)
+
+```{r}
+items <- c(
+ "I don’t like to talk about personal issues with others unless they do it first.",
+ "There are a lot of things about me that I don’t like to talk about with others.",
+ "I prefer not to share my feelings and inner thoughts with others.",
+ "I do not like it when others talk to me about their private issues."
+)
+readability(items) %>% rbind(readability_hexaco)
+```
+
+Readability looks good!
+
+### Physical
+
+@frenerDevelopmentValidationNeed2021
+
+ 1.	I don’t like it when strangers come too close to me.
+ 2.	I don’t like to stand in a dense crowd of people.
+ 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
+ 4.	I hate it when people enter my personal space uninvited. (new)
+
+```{r}
+items <- c(
+ "I don’t like it when strangers come too close to me.",
+ "I don’t like to stand in a dense crowd of people.",
+ "I don’t like to sit next to a stranger on a tram, bus, or plane.",
+ "I hate it when people enter my personal space uninvited."
+)
+readability(items) %>% rbind(readability_hexaco)
+```
+
+Looks good. (Item 4 not perfect, but it should still work.)
+
+### Social Privacy
+
+@dienlinWhoNeedsPrivacy2019
+
+ 1.	I don’t feel comfortable interacting with other people. [@harrisonDevelopmentDesirePrivacy1993]
+ 2.	I often want to be alone. (new)
+ 3.	I’m a fairly anti-social person. (new)
+ 4.	I prefer to work independently in most situations. (new)
+
+```{r}
+items <- c(
+ "My need for privacy is so strong that it prevents me from using social media actively.",
+ "I don’t feel I need to tell my friends all my secrets.",
+ "I feel I need to protect my privacy from other people.",
+ "I prefer it when others don’t know much about me."
+)
+readability(items) %>% rbind(readability_hexaco)
+```
+
+Readability looks good. (Item 1 not perfect, but should still work and was already validated.)
+
+## Vertical
+### Privacy from Government
+
+@dienlinWhoNeedsPrivacy2019
 
@@
 
- - I need government agencies to respect my privacy, even if that makes catching criminals harder.,
- - I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.,
- - I don’t want government agencies to monitor my communication, even if that prevents terrorist attacks.,
- - I feel I need to protect my privacy from government agencies.
+ 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
+ 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
+ 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
+ 4.	I feel I need to protect my privacy from government agencies.
 
@@
  "I need government agencies to respect my privacy, even if that makes catching criminals harder.",
- "I don’t want the government to gather data about me, even if that makes it harder to spend tax income efficiently.",
-  "I don’t want government agencies to track my communication, even if that stops terrorist attacks.",
+ "I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.",
+ "I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.",
  "I feel I need to protect my privacy from government agencies."
@@
 
-A bit better, but not much.
-
-```{r}
-model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
-```
-
-# Privacy from other People
-
- - My need for privacy is so strong that it prevents me from using social media actively. 
- - I don’t feel I need to tell my friends all my secrets.
- - I feel I need to protect my privacy from other people.
- - I prefer it when others don’t know much about me.
-
-```{r}
-items <- c(
- "My need for privacy is so strong that it prevents me from using social media actively.",
- "I don’t feel I need to tell my friends all my secrets.",
- "I feel I need to protect my privacy from other people.",
- "I prefer it when others don’t know much about me."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Readability looks good!
+A bit better, but not much. But scale worked pretty well in original study, so should be okay.
 
@@
 
-# Privacy need anonymity
+### Privacy from Companies
 
- - I need to be able to use a fake account on social network sites to preserve my privacy. 
- - I feel I need to avoid places with video surveillance.
- - I prefer not to carry my drivers license or ID with me all the time to preserve my privacy.
- - I need to be able to surf the Internet anonymously. (new)
+New, self-designed.
+
+ 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
+ 2. I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
+ 3. I don’t want companies to gather information about me, even if that reduces the quality of their services.
+ 4. I feel I need to protect my privacy from companies.
 
@@
 items <- c(
- "I need to be able to use a fake account on social network sites to preserve my privacy.",
+ "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
+ "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
+ "I don’t want companies to gather information about me, even if that reduces the quality of their services.",
+ "I feel I need to protect my privacy from companies."
+)
+readability(items) %>% rbind(readability_hexaco)
+```
+
+Items 3 seems to be a bit too difficult. Try to make easier.
+
+ 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
+ 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
+ 3. I don’t want companies to collect data about me, even if that makes their services worse.
+ 4. I feel I need to protect my privacy from companies.
+
+```{r}
+items <- c(
+	"I’m willing to pay more for products or services so that companies don’t have to sell my data.",
+	"I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.",
+	"I don’t want companies to collect data about me, even if that makes their services worse.",
+	"I feel I need to protect my privacy from companies."
+)
+readability(items) %>% rbind(readability_hexaco)
+```
+
+Readability now much better.
+
+## General
+### Informational
+
+@frenerDevelopmentValidationNeed2021
+
+ 1.	I would prefer that little is known about me.
+ 2.	I don’t want my personal data to be publicly accessible.
+ 3.	It is important to me that records pertaining to me remain confidential. [@harrisonDevelopmentDesirePrivacy1993]
+ 4.	I prefer that others cannot easily find information about me on the Internet. (new)
+
+```{r}
+items <- c(
+	"I would prefer that little is known about me.",
+ 	"I don’t want my personal data to be publicly accessible.",
+ 	"It is important to me that records pertaining to me remain confidential.",
+  "I prefer that others cannot easily find information about me on the Internet."
+)
+readability(items) %>% rbind(readability_hexaco)
+```
+
+Readability looks good.
+
+### Privacy need anonymity
+
+@dienlinWhoNeedsPrivacy2019
+
+ 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
+ 2.	I feel I need to avoid places with video surveillance.
+ 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
+ 4.	I need to be able to surf the Internet anonymously. (new)
+
+```{r}
+items <- c(
+ "I would prefer to use a fake account on social network sites to preserve my privacy.",
  "I feel I need to avoid places with video surveillance.",
@@
 
-Readability looks good!
+Readability looks good.
 
-```{r}
-model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
-```
+### General Need for privacy
 
-# Privacy from Companies
+New, self-designed.
 
- - I’m willing to pay more for products or services so that companies don’t have to sell my data.
- - I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.
- - I don’t want companies to gather information about me, even if that reduces the quality of their services.
- - I feel I need to protect my privacy from companies.
-
-```{r}
-items <- c(
- "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
- "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
- "I don’t want companies to collect data about me, even if that makes their services worse.",
- "I feel I need to protect my privacy from companies."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Items 3 seems to be a bit too difficult. Try to make easier.
-
-```{r}
-items <- c(
- "I’m willing to pay more for products or services so that companies don’t have to sell my data.",
- "I’m happy to give up a little bit of privacy, so that I can use certain apps or services for free.",
- "I don’t want companies to gather information about me, even if that lowers the quality of their services.",
- "I feel I need to protect my privacy from companies."
-)
-readability(items) %>% rbind(readability_hexaco)
-```
-
-Readability now much better.
-
-```{r}
-model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
-```
-
-# General Need for privacy
-
- - I need a lot of privacy.
- - Privacy is very important to me.
- - I think a lot about how I can protect my privacy.
- - I need a lot of time for myself.
+ 1.	I need a lot of privacy.
+ 2.	Privacy is very important to me.
+ 3.	I think a lot about how I can protect my privacy.
+ 4.	I value privacy a lot.
 

### 2023-03-01 proposal.Rmd
- major update - now set up as a registered report

@@
 ---
-title             : "Who needs privacy? Exploring the relation between personality and need for privacy"
-shorttitle        : "Who Needs Privacy?"
+title             : "Who needs privacy? Exploring the relations between need for privacy and personality"
+shorttitle        : "Relations between need for privacy and personality"
 
@@
 authornote: |
-  Tobias Dienlin, Department of Communication, University of Vienna, Germany; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
+  Tobias Dienlin, Department of Communication, University of Vienna, Austria; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
 
-abstract          : "Privacy is an important societal topic.
-Living in an information age, people constantly have to decide what information to share, which service to use, when to communicate.
-All of these decisions are reflective of and determined by a person's need for privacy.
-We believe that it is relevant to understand who needs more and who needs less privacy, for example because desiring privacy often requires justification.
-The nothing-to-hide statement---'someone who has nothing to hide has nothing to fear'---implies that people who desire privacy are suspicious.
-Although such suspicions might be justified in some cases, there are many alternative legitimate explanations as to why people desire privacy.
-For example, they could be more introverted, hesitant, creative, or prudent.
-In this study we hence plan to explore the relation between personality and the need for privacy.
-Personality factors and facets will be operationalized using the HEXACO personality inventory.
-Need for privacy will be captured with a multidimensional approach, including informational and social privacy, need for privacy from government agencies, or need for privacy from companies.
-We will collect a sample of more than 800 respondents, which will be representative of the US in terms of age, gender, and ethnicity.
-The relations between personality and privacy will be explored using structural equation modeling."
-keywords          : "Privacy, need for privacy, personality, HEXACO, structural equation modeling"
+abstract          : "Privacy is defined as a voluntary withdrawal from society.
+Everyone needs privacy.
+Currently, however, we still know little about who needs more and how needs less privacy.
+In this study, we hence explore the relations between the need for privacy and personality.
+Personality will be operationalized using the HEXACO personality inventory.
+Need for privacy will be measured along the dimensions of (a) social, (b) psychological, and (c) physical privacy; need for privacy from (d) government agencies and (e) companies; as well as (f) informational privacy, (g) need for anonymity, and (h) general privacy.
+A sample of 1,293 respondents representative of the U.S.
+in terms of age, gender, and ethnicity will be collected.
+The correlations between privacy, personality, and sociodemographics will be analyzed using structural equation modeling."
+keywords          : "Privacy, need for privacy, personality, HEXACO"
 
@@
 classoption       : "man"
-# output            : papaja::apa6_pdf
-output            : papaja::apa6_word
+output            : papaja::apa6_pdf
+# output            : papaja::apa6_word
 header-includes:
@@
   - \note{\clearpage}
+  - \usepackage{float}
 ---
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
-                      fig.pos = 'h')
+                      fig.pos = 'h', echo = FALSE)
 ```
@@
 
-Amidst the increasing digitization of everyday life, 
+<!-- The increasing digitization of everyday life has catapulted  -->
 <!-- which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016],  -->
-privacy has become a major topic of public and academic interest. 
-Despite the topic's importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
-Why do some people feel they need more privacy than others, and how do these people differ from one another?
+Privacy is a major topic of public discourse and academic interest [@dienlinPrivacyDeadLong2022].
+Yet despite its importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155].
+<!-- Why do some people desire more and some people desire less privacy? -->
+What can we infer about a person if they desire more privacy?
+Are they more introverted, more risk-averse, or more traditional?
+<!-- Or do they have more to hide? -->
+Asking this question seems relevant, not least because people who desire more privacy are often confronted with suspicions, having to justify why they want to be left alone.
+Consider the nothing-to-hide argument [@soloveVeGotNothing2007].
+Accordingly, people who oppose state surveillance only do so because they have something to hide. 
+For if you who have nothing to hide, you would have nothing to fear.
+<!-- This may be due to the fact that privacy is most often analyzed from a situational or contextual perspective [@nissenbaumPrivacyContextTechnology2010]. -->
+<!-- However, privacy is also dispositional: Some need more and some need less privacy [@pedersenPersonalityCorrelatesPrivacy1982]. -->
+Is it true that people who desire more privacy are also more dishonest, greedy, or unfair? 
+Or are people simply less extroverted, more diligent, or more prudent?
+<!-- Analyzing these questions is relevant. -->
+With this paper, we hence seek to answer the following question: 
+What can we learn about a person's personality if they say they desire more privacy?
 
-We believe it is relevant to address this research question, because people who desire privacy are often asked to justify themselves. 
-For example, the so-called _nothing-to-hide argument_ states that “If you have nothing to hide, you have nothing to fear”. 
-<!-- As described by Solove, the nothing-to-hide argument says that -->
-It implies that people who desire privacy are suspicious. 
-For example, once can sometimes hear that data mining and surveillance by government entities “is not likely to be threatening to the privacy of law-abiding citizens. 
-Only those who are engaged in illegal activities have a reason to hide this information” [@soloveVeGotNothing2007, p. 753].
+<!-- This study therefore seeks to understand how the need for privacy is related to dimensions and facets of personality. -->
 
-And granted, it is only logical that people who commit crimes and who are insincere would in fact benefit from more privacy.
-However, there exist many other alternative reasons as to why people need privacy.
-For example, it could also be that people who need more privacy are just more introverted, hesitant, creative, or prudent. 
-We therefore believe that a better understanding of the relation between personality and privacy is relevant from a societal perspective.
+<!-- It states that data mining and surveillance by government entities poses no threat to the privacy of law-abiding citizens, and is only problematic for people who are engaged in illegal activities who want to hide their information [@soloveVeGotNothing2007, p.
+753].
+-->
+<!-- Summarized as “If you have nothing to hide, you have nothing to fear”, it implies that people who desire more privacy are also more likely to be involved in incriminating activities.  -->
+<!-- It is true that people who commit crimes and who are insincere would indeed benefit from greater privacy.  -->
+<!-- However, there exist many alternative reasons as to why people feel a greater or lesser need for privacy.  -->
+<!-- Among those reasons are dispositional explanations.  -->
+<!-- For example, people who need more privacy may be simply more introverted, hesitant, or prudent.  -->
 
-But also from an academic perspective, this research question is topical. 
-Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155]. 
-However, to date there is almost no empirical research that can be used to develop well-informed hypotheses.
+<!-- A better understanding of the relation between personality and privacy is thus useful to illuminate the full range of human motivation for desiring privacy, and thus understanding individual decision-making and behavior surrounding personal privacy.
+-->
+<!-- Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155].  -->
+<!-- However, to date there is almost no empirical research that can be used to develop well-informed hypotheses.  -->
 
-As a result, with this paper we would like to answer the following question:
-What personality factors and facets best explain peoples' felt need for privacy?
+## Privacy and Personality
 
-## The Need for Privacy
-
-We first outline our own understanding of privacy, because the theoretical concept of privacy is complicated and contested [@nissenbaumPrivacyContextTechnology2010, p. 71]. 
-First and foremost, privacy captures a _withdrawal_ from others, or from society in general [@westinPrivacyFreedom1967].
-This withdrawal (b) happens _voluntarily_ and is under a person's _control_ [@westinPrivacyFreedom1967]. 
-Several models suggest that privacy is multi-dimensional. 
-For example, in a theory-driven treatise @burgoonPrivacyCommunication1982 argued that privacy has four dimensions: informational, social, psychological, and physical privacy. 
-@pedersenDimensionsPrivacy1979 conducted an empirical factor analysis of overall 94 items and found six dimensions of privacy: 
+<!-- We first outline our own understanding of privacy, because the theoretical concept of privacy is multidisciplinary, complicated, and contested [@nissenbaumPrivacyContextTechnology2010, p.
+71].
+-->
+Privacy captures a _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967].
+This withdrawal happens _voluntarily_, and it is under a person's _control_ [@westinPrivacyFreedom1967]. 
+Privacy is multi-dimensional. 
+On the broadest level, we can differentiate the two dimensions of horizontal and vertical privacy [@schwartzSocialPsychologyPrivacy1968, @masurPrivatheitOnlineKommunikation2018].
+Whereas horizontal privacy captures withdrawal from other people or peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or businesses). 
+In her theoretical analysis, @burgoonPrivacyCommunication1982 argued that privacy has four more specific dimensions: informational, social, psychological, and physical privacy. 
+@pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
 reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. 
-@schwartzSocialPsychologyPrivacy1968 and @masurPrivatheitOnlineKommunikation2018 differentiated between horizontal and vertical privacy; whereas horizontal privacy captures withdrawal from peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or business companies).
-
 <!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
@@
 -->
+Building on this work, in this study we employ a multifaceted model of need for privacy. 
+We focus on vertical privacy with regard to people’s felt need for withdrawal from (a) government surveillance and (b) private companies; 
+horizontal privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
+and general privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
 
-For the purpose of this study, we will hence employ a multifaceted model of need for privacy.
-We fill focus on (a) vertical privacy with regard to people's felt need for withdrawal from government surveillance and private companies; (b) horizontal privacy in terms of the perceived need for withdrawal from other people, psychological privacy, and physical privacy; and (c) both horizontal and vertical privacy as captured by people's felt need for informational privacy, anonymity, and privacy in general.
-
-<!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->
-According to @trepteNeedPrivacy2017, the need for privacy is a secondary need---it is not an end in itself, but rather a means to satisfy other more fundamental needs such as safety, sexuality, recovery, or contemplation.
-Specifically, @westinPrivacyFreedom1967 defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
-Not least, privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], which is necessary for attaining social support, initiating relationships, and getting close to other people [@omarzuDisclosureDecisionModel2000].
-
-Privacy can also have negative aspects. 
-It is possible to have too much privacy.
-Humans are inherently social, and being overly cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
-The fact that privacy fosters self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information in other contexts [@petronioCommunicationPrivacyManagement2010].
-Privacy can also help conceal wrongdoing or crimes such as violence or theft.
-The dialectical tension between the positive and negative aspects of privacy thus might cause variability across individuals in their need for privacy.
-
-<!-- In this study we now ask, what role does personality play in determining individual-level variations in need for privacy? -->
+We understand and measure personality using the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018]. 
+The HEXACO is a large and comprehensive operationalization of personality. 
+Using the HEXACO will make it less likely to miss potentially relevant factors and facets.
+The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
+<!-- and represents a broad understanding of personality-->
+It includes overall six factors (discussed below), which have four specific facets each. 
+In predicting the dimensions of need for privacy, we will use the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to the more general personality factors
+<!-- For example, consider that privacy concern, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors  -->
+[@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].
+In addition to the Big Five, the HEXACO model includes a sixth factor labeled honesty-humility (plus a meta-facet called altruism), which together seem well-suited to investigate the nothing-to-hide-argument.
 
@@
 
-So far, not a lot of studies have analyzed the relation between personality and need for privacy explicitly.
-We are aware of only two studies that conducted an empirical analysis [@pedersenPersonalityCorrelatesPrivacy1982; @hosmanRelationshipsNeedPrivacy1991].
-And as there is no established theory connecting privacy and personality, it is difficult to formulate precise and well-informed a priori hypotheses.
+So far, only few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
+In addition, we are not aware of a viable theory specifically connecting privacy and personality.
+Due to the dearth of empirical studies and the lack of viable specific theories, in this study we hence adopt an exploratory perspective. 
+<!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->
 
-In terms of potential theoretical explanations as to why personality might relate to need for privacy, we could imagine that much depends on whether an entity is considered a threat or a resource. 
-If something is a threat, if it is negative, it seems more likely to withdraw and to desire more privacy; if something is a resource, however, it seems more plausible to open up, to approach, and to desire less privacy [@altmanPrivacyConceptualAnalysis1976].
+In order to understand how personality might relate to privacy, we can ask ourselves the following question. 
+Why do people desire privacy?
+Privacy is important.
+But according to @trepteNeedPrivacy2017, the need for privacy is only a secondary need---not an end in itself.
+Accordingly, privacy satisfies other more fundamental needs such as safety, sexuality, recovery, or contemplation.
+@westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
+Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014]. 
+It is hence important for social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
+But privacy can also have negative aspects. 
+It is possible to have too much privacy.
+Being cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
+<!-- The fact that privacy fosters self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information [@petronioCommunicationPrivacyManagement2010].
+-->
+And privacy can also help conceal wrongdoing or crime. 
+<!-- The dialectical tension between the positive and negative aspects of privacy might itself cause variability across individuals in their felt need for privacy both within and across contexts or situations.
+-->
+<!-- In this study we now ask, what role does personality play in determining individual-level variations in need for privacy? -->
 <!-- Our reasoning further was guided by another central theoretical tenet.  -->
@@
 <!-- It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976]. -->
-
-That said, in this study we nonetheless adopt a more _exploratory_ perspective. 
-We implement a large-scale operationalization on personality, in order not to miss potentially relevant personality factors and facets.
-To this end, we build on the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
-
-The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
-<!-- and represents a broad understanding of personality-->
-It measures overall six factors (see below), which have four specific facets each. 
-We include also the specific facets because we do not expect that the even more specific need for privacy dimensions will relate closely to the overarching general personality factors.
-For example, consider that privacy concerns, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].
-
-Another reason for choosing the HEXACO model was that in addition to the Big Five factors the HEXACO model includes a sixth one labeled honesty-humility, 
-plus another additional meta-facet called altruism,
-which together seem promising to investigate the nothing-to-hide-argument.
-<!-- Hence, in order to increase precision we follow Paunonen's [-@paunonenBigFiveFactors2001] advice and also include specific personality facets. -->
-<!-- To illustrate, instead of dwelling on the general factor of _Extraversion_, we instead focused on the facet _Gregariousness_, which we consider to be more pertinent.  -->
-In what follows, we briefly present all factors and provide some tentative thoughts on how they and several selected facets might relate to privacy.
-
-<!-- The rationales that we outline below should hence be considered tentative suggestions toward a theory of personality and privacy.
-Also, please note that we elaborate only on those dimensions of need for privacy for which plausible rationales could be formed.
--->
+As a general guiding principle based on an evolutionary perspective, 
+<!-- In terms of potential theoretical explanations as to why personality might relate to the need for privacy,  -->
+we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
+Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
+In what follows, we briefly present all factors and how they might relate to need for privacy.
 
@@
 Honesty-humility consists of the facets sincerity, fairness, greed avoidance, and modesty. 
-The meta-facet altruism measures benevolence toward others and consists of items such as "It wouldn’t bother me to harm someone I didn’t like."
-According to the nothing-to-hide argument, one could assume that people might need privacy because they have something to hide---namely, because they are less honest, sincere, fair, or benevolent.
-<!-- Hence, a potential predictor of why people need privacy could be how honest, correct, sincere, or benign they are. -->
-<!-- Because integrity is a delicate concept, let us first try to define it conceptually.  -->
-<!-- Although in terms of a scientific definition there is no consensus, most scholars seem to agree that integrity “incorporates a tendency to comply with social norms, avoid deviant behavior, and embrace a sense of justice, truthfulness, and fairness” [@Connelly.2006, p.
-82].
--->
-<!-- In order to sidestep the (very legitimate) philosophical debates about what constitutes integrity and what not, we hence follow @Paunonen.2002 and adopt a lowest common denominator definition, which means that we only consider participating in explicitly socially-sanctioned or illegal activities as a sign of lack of integrity.
--->
-<!-- It is possible to think of theoretical arguments for why lack of integrity might correlate positively with a person's felt need for privacy.  -->
-Logically, people who actually commit crimes may face even greater risk from self-disclosure compared to others, because government agencies and people would sanction their activities [@petronioCommunicationPrivacyManagement2010].
-Hence, the government and other people are more likely to be perceived as a threat. 
-As a consequence, once could argue that people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
-<!-- There are also a few empirical studies that imply---at least indirectly---a relation between privacy and integrity.  -->
+The meta-facet altruism measures benevolence toward others and consists of items such as “It wouldn’t bother me to harm someone I didn’t like.” 
+According to the nothing-to-hide argument, a person desiring more privacy might be less honest, sincere, fair, or benevolent. 
+People who commit crimes likely face greater risk from self-disclosure, because government agencies and people would enforce sanctions if their activities were revealed [@petronioCommunicationPrivacyManagement2010].
+Hence, in those cases the government and other people are likely perceived as a threat. 
+As a consequence, people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
 
-Empirical studies have found that surveillance can indeed reduce cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
+Empirical studies have indeed found that privacy can increase cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
 @coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
-In the high surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
-In the low surveillance condition, the experimenter could not see the students. 
-Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with less privacy people show are more honest. 
-<!-- When playing the ultimatum/dictator game, people share less if the game is double blind (Fähr & Gächter, 2000; Gaulin & McBurney, 2001). -->
-Next, in a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48) and less authentic in their personal relationships (_r_ = -.28).
-<!-- Given the argument that authenticity is a subset of integrity [@Sheldon.2004], one could hence also reason that the concept of integrity might relate to a person’s perceived need for privacy.
--->
+In the surveillance condition, the experimenter stood in front of the students and closely monitored their behavior. 
+In the privacy condition, the experimenter could not see the students. 
+Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with more privacy people are less honest. 
+In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
+People who needed more privacy were also less authentic in their personal relationships (_r_ = -.28). 
+<!-- Together, these studies suggest the possibility that lack of honesty may relate to an increased need for privacy, especially when it comes to government surveillance.    -->
 
-In conclusion, it seems possible that lack of honesty may indeed relate to an increased need for privacy, especially when it comes to government surveillance.
+In conclusion, it seems possible that lack of honesty may indeed relate to an increased need for privacy, especially when it comes to privacy from government agencies.
 <!-- , as governments have the legitimate power to prosecute illegal activities.  -->
@@
 
-Next, it seems possible that need for privacy is also related to a person's level of emotionality. 
+<!-- Need for privacy might relate to a person’s level of emotionality.  -->
 Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
-<!-- General anxiety measures for example whether people are afraid of negative events or whether they are easily frightened.  -->
-With regard to interpersonal privacy, one could argue that people who are anxious are more likely to consider social interactions a risk or threat [especially with strangers or weak ties, @granovetterStrengthWeakTies1973], which is why anxious people might desire more privacy.
-Somewhat related, prior empirical research showed that people who are more concerned about their privacy (in other words, more anxious) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
-On the other hand, one could argue in favor of the opposite: People who are more anxious may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
+People who are anxious may be more likely to consider social interactions a risk or threat  [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
+Anxious people might hence desire more privacy. 
+People who are more concerned about their privacy (in other words, more anxious) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
+On the other hand, the opposite may also be true: 
+People who are more anxious in general may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
 
-Concerning the need for privacy from government surveillance, we could imagine that people who are more anxious desire less privacy. 
-Despite the fact that only 18% of all Americans trust their government "to do what is right" [@pewresearchcenterPublicTrustGovernment2017], almost everyone agrees that "it's the government's job to keep the country safe" [@pewresearchcenterDistrustHowAmericans2015].
-Hence, for anxious individuals, the government might be seen as a resource rather than a threat. 
-It therefore seems plausible that people who are in general more anxious are also more likely to consent to government surveillance, given that such surveillance promises to prevent crime or to reduce the likelihood of terrorist attacks.
-That said, the relation could also be inverse, such that more anxious people desire more privacy.
-It is plausible that anxiety correlates with being in favor of government surveillance of _others_; however, this does not necessarily extend to someone’s _own_ data. 
-If the government is perceived as a threat, as often expressed by minority groups, than it would follow that they ask for more privacy for themselves.
-<!-- Therefore, people who are more anxious might desire less privacy from government surveillance and, for the same reasons, also less anonymity. -->
+People who are more anxious might also desire less privacy from government surveillance.
+Despite the fact that only 18% of all Americans trust their government “to do what is right,” almost everyone agrees that “it’s the government’s job to keep the country safe” [@pewresearchcenterPublicTrustGovernment2017; @pewresearchcenterDistrustHowAmericans2015].
+More anxious people might hence consider the government a resource rather than a threat. 
+They might more likely consent to government surveillance, given that such surveillance could prevent crime or terrorism. 
+On the other hand, it could also be that more anxious people desire more privacy from government agencies. 
+Although they even might be in favor of government surveillance of _others_, this does not necessarily include _themselves._
+Especially if the government is perceived as a threat, as often expressed by members of minority groups, then one might actually desire more personal privacy.
 
@@
 
-Extraversion comprises the facets social self-esteem, social boldness, sociability, and liveliness.
-Arguably, extraversion is the factor that should correspond most closely to the need for privacy.
-This especially pertains to the facet sociability, which captures whether people prefer to spend their time alone or in company. 
-It seems plausible that people who are more sociable are also more likely to think of other people as a resource, which is why they should generally desire less interpersonal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].
-Put differently, given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], we expect that people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
-One could even make the case that need for (interpersonal) privacy and sociability are conceptually the same, and that need for privacy is just a different label for the same underlying personality trait.
-That said, we are not aware of a personality inventory that explicitly refers to privacy,
-and besides, as we outline above privacy is multidimensional and aspects such as need for privacy from the government or companies appear to be different conceptually.
+Comprising the facets social self-esteem, social boldness, sociability, and liveliness, extraversion is arguably the factor that should correspond most closely to need for privacy. 
+<!-- This especially pertains to the sociability facet, which captures whether people prefer to spend their time alone or with company.  -->
+<!-- It is plausible that  -->
+Conceptually, interpersonal privacy and sociability are closely related.
+More sociable people are likely more inclined to think of other people as a resource, which is why they should desire less interpersonal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].
+Given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
 
-Several empirical studies support thhis relation.
-People who scored higher on the personality meta-factor _plasticity_, which is a composite of the two personality factors extraversion and openness, desired less privacy [@mortonMeasuringInherentPrivacy2013]; people who described themselves as introverted thinkers were more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982]; and introverted people were more likely to report invasions of privacy [@stoneRelationshipIntroversionExtraversion1986].
-@pedersenPersonalityCorrelatesPrivacy1982 showed that three dimensions of need for privacy relate to self-esteem (but note, _general_ self-esteem, not _social_ self-esteem): 
-Respondents who held a lower self-esteem were more reserved (_r_ = .29), needed more anonymity (_r_ = .21), and preferred solitude (_r_ = .24).
+This hypothesis is supported by several empirical studies. 
+People who scored higher on the personality meta-factor plasticity, which is a composite of the two personality factors extraversion and openness, desired less privacy [@mortonMeasuringInherentPrivacy2013].
+People who described themselves as introverted thinkers were more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982].
+Introverted people were more likely to feel their privacy was invaded [@stoneRelationshipIntroversionExtraversion1986].
+@pedersenPersonalityCorrelatesPrivacy1982 reported that the three dimensions of need for privacy related to general self-esteem (but not social self-esteem). 
+Respondents who held a lower general self-esteem were more reserved (_r_ = .29), and needed more anonymity (_r_ = .21) and solitude (_r_ = .24).
+Finally, @larsonNeedPrivacyIts1988 and @hosmanRelationshipsNeedPrivacy1991 suggested that people who are more shy also need more privacy.
 
-<!-- While self-esteem and integrity are distinct concepts, Pedersen’s specific operationalization of self-esteem integrated several aspects of integrity by using items such as moral, nice, fair, unselfish, good, honest, and reputable (p.
-12).
--->
+As a result, we hypothesize that people who are more extroverted also need less social privacy and less privacy in general.
+Regarding the other dimensions of privacy, such as privacy from governments or from companies, we do not pose specific hypotheses.
 
@@
 
-Agreeableness is captured by the facets forgiveness, gentleness, flexibility, and patience.
+Agreeableness has the four facets of forgiveness, gentleness, flexibility, and patience.
 It is not entirely clear whether or how agreeableness might relate to the need for privacy.
-Potentially noteworthy is that people who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
-Thus, because need for privacy and privacy concerns are closely related, it seems possible that more agreeable people desire less privacy.
+People who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+Thus, because need for privacy and privacy concern are closely related, more agreeable people might desire less privacy.
 
@@
 Conscientiousness consists of the facets organization, diligence, perfectionism, and prudence.
-Arguably, all facets are more or less about being in control, about reducing potential risks, or about avoiding future costs.
-And because privacy is much about control (see above), we could imagine that an individual's felt need for privacy relates to their general tendency to avoid risks, to deliberate, and to plan ahead carefully.
-<!-- Risk avoidance captures the degree to which people prefer to abstain from taking risks.  -->
-Especially if other people are considered a threat, people who are risk averse might desire more interpersonal privacy.
-<!-- , because they may feel greater risk associated with disclosure of personal information.  -->
-The most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private.
-
-Relatedly, empirical studies report that people who consider their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
-Moreover, conscientious people are slightly more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
-But as above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats. 
+Arguably, all facets are about being in control, about reducing relevant risks and future costs.
+Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully, might prefer to have more privacy.
+Especially if others are considered a threat, being risk averse might increase the desire for more interpersonal privacy. 
+Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for privacy. 
+In either case, the most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private.
+Empirical studies reported that people with a stronger control motive required slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
+People who considered their privacy at risk were less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
+Moreover, conscientious people were slightly more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+<!-- But as discussed above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats.
+-->
 <!-- In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study. -->
 
-### Openness to Experiences
+### Openness to experience
 
@@
 Openness to experience is also considered a measure of intellect and education. 
+In one study it was found that more educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
+In another study, openness to experience is positively related to privacy concern [@junglasPersonalityTraitsConcern2008]
 
-What follows is only a personal impression, but sometimes it feels that advocates of privacy seem to come from the higher educational echelons of society, that they are the intellectual elites, for example when citing Orwell's 1984.
-Potentially related to this, empirical studies showed that more educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
-Supporting this reasoning, @junglasPersonalityTraitsConcern2008 reported that openness to experience is positively related to privacy concern.
-
-On the other hand, openness is by definition the opposite of privacy, and people who are more open to experience new aspects might _not_ prioritize privacy, for example when it comes to testing a new social medium.
-Many new digital practices such as online interaction, purchases, or information seeking pose a risk to privacy, but offer many exciting new benefits.
-People who are more open to new experiences might not care so much about the potential downsides, but rather on what could be achieved.
-
-<!-- Next, it seems plausible that need for privacy is also related to traditionality [which is a subdimension of openness to experience, @Costa.1992b].  -->
-<!-- Traditionalism measures whether people prefer to stick with their usual routines.  -->
-<!-- Computers and the Internet have rendered the world increasingly knowable:  -->
-<!-- Social interactions, purchases, and medical treatments nowadays all produce digital traces, which can be combined into accurate latent user profiles.  -->
-<!-- Given that digital information is persistent, searchable, reproducible, and scalable [@boyd.2008c], this allows for unprecedented means and degrees of surveillance.  -->
-<!-- Mark Zuckerberg famously observed that privacy is no longer a social norm, rather the norm is that people share personal information [@Johnson.2010].  -->
-<!-- Hence, in order to be part of contemporary life, it seems necessary to give up some privacy.  -->
-<!-- However, people may not be equally willing to pay that price, and especially people who are more traditional might decide against giving up their privacy.  -->
-
-<!-- <!-- Empirical research does find that older people, who are generally less open and more traditional [@Donnellan.2008], are more concerned about their privacy [@Fife.2012].  -->
-<!-- Taken together, we still consider it plausible that people who are more traditional also desire more privacy in all three contexts measured in this study. -->
+On the other hand, openness is conceptually the opposite of privacy.
+People more open to new experiences might not prioritize privacy.
+Many new digital practices such as social media, online shopping, or online dating offer exciting new benefits, but pose a risk to privacy. 
+People who are more open to new experiences might focus on the benefits and not on the potential risks.
+<!-- An example might be that people with greater openness to experiences would be more likely to try a new online social network or medium of communication. -->
+Hence, different relations between need for privacy and openness seem possible.
 
@@
 
-Finally, it seems likely that the need for privacy is also related to sociodemographic variables, such as sex, age, education, and affluence. 
-For example, in a study with 3.072 people from Germany, it was found that women desired more informational and physical privacy, while man needed more psychological privacy [@frenerDevelopmentValidationNeed2021].
-In a nationally representative study of the US and Japan, in both countries people who were older and who had higher income levels reported more privacy concerns.
-As reported above, more educated people possess also more privacy knowledge [@parkDigitalLiteracyPrivacy2013], and it could be that they desire more privacy.
-We are also curious how ethnicity might correspond to need for privacy, and could well imagine that non-white groups desire more privacy from the government---but not necessarily from other people.
-We will additionally investigate wheter a person's relationship status corresponds to their expressed need for privacy.
-Last, we will also investigate whether one's political position is related to the need for privacy.
+The need for privacy should also be related to sociodemographic aspects, such as sex, age, education, and income. 
+For example, a study of 3,072 people from Germany found that women desired more informational and physical privacy than men, whereas men desired more psychological privacy [@frenerDevelopmentValidationNeed2021].
+In a nationally representative study of the U.S. and Japan, people who were older and who had higher income levels reported more privacy concern. 
+More educated people possess more privacy knowledge [@parkDigitalLiteracyPrivacy2013], and as a consequence they might desire more privacy. 
+Ethnicity might also correspond to the need for privacy, perhaps because members of minority groups desire more privacy from the government, but not necessarily from other people. 
+Some minorities groups (e.g., Black or Native Americans) often report lower levels of trust in white government representatives [@kochRacialMinoritiesTrust2019], which might increase the desire of privacy from government agencies.
+We will also explore whether a person’s romantic relationship status corresponds to their expressed need for privacy. 
+Last, we will examine whether one’s political position is related to the need for privacy. 
 We could imagine that more right-leaning people desire more privacy from the government, but not necessarily from other people.
+People who are more conservative tend to trust the government slightly less [@cookSkepticalAmericanRevisiting2005], which might be associated with an increased need for privacy.
 
@@
 
-We ran a prestudy, which is published as a preprint [@dienlinWhoNeedsPrivacy2019].
-This study was submitted initially, but rejected for several empirical and conceptual reasons (for example, insufficient statistical power).
-This proposal aims to remedy these shortcomings.
-In the prestudy, we tested several self-developed items, which are reported below.
+This study builds on a prior project in which we analyzed the same research question [@dienlinWhoNeedsPrivacy2019]. 
+This study was already submitted to Collabra, but rejected.
+The main reasons were that the sample was too small, that not one coherent personality inventory was used, that most privacy measures were designed ad-hoc, and that the inferences were too ambitious. 
+We hence decided to treat our prior project as a pilot study and to address the criticism by conducting a new study.
+In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together with other more established need for privacy measures, and overall adopt a more exploratory perspective.
+Being our central construct of interest, we also develop a small number of new items to have a more comprehensive measure of need for privacy.
 
@@
 The sample will be representative of the US in terms of age, gender, and ethnicity. 
-The study received IRB approval from University of Vienna. 
+The study received IRB approval from the University of Vienna (#20210805_067).
 We calculated that participation will take approximately 15 minutes. 
@@
 To determine sample size, we ran a priori power analyses. 
-Note that the final analyses will be conducted using structural equation modeling, for which exact power analyses are difficult to obtain. 
-We hence conducted preliminary power analyses using two-sided bivariate correlations. 
-Hence, the following power analyses are not exact but only a rough guide to get a better idea of the required minimum sample size.
+Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain. 
+We therefore conducted preliminary power analyses using two-sided bivariate correlations. 
+Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size.
+We based our power analysis on a smallest effect size of interest (SESOI).
+We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992]. 
+<!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
+Adopting an exploratory perspective, not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant. 
+We hence opted for balanced alpha and beta errors of 5%.
+A power analysis with an alpha and beta error of 5% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_n_95 %>% round(0)`.
+We obtained sufficient funding to collect a sample of this size.
+Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 5% and an effect size of at least _r_ = .10.
 
-We based our power analysis on a smallest effect size of interest (SESOI).
-We only considered effects at least as great as _r_ = .10 as sufficiently relevant to constitute support for an effect's existence [@cohenPowerPrimer1992]. 
-Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%).
-Because we adopted an exploratory perspective, we aimed not to miss potentially existing effects (beta error).
-We opted for an approach where alpha and beta error are balanced/equal, because we consider both errors to be equally relevant. 
-A power analysis with an alpha and beta error of 5% and an effect size of _r_ = .10 required a sample size of _N_ = `r power_n_95 %>% round(0)`, which was outside of our budget.
-If we slightly relaxed the error rate to 10%, power analyses showed that we would need a sample size of _N_ = `r power_n_90 %>% round(0)`, which was within our budget, and which will hence be the minimum sample size we plan to collect.
-Hence, we will use two inference criteria: Effects need to show a p-value below _p_ = 10% and an effect size of at least _r_ = .10.
+## Removing Participants, Imputation of Missing Data, and Planned Analyses
 
-We will individually check responses for patterns such as straight-lining or missing of inverted items, making sure to remove only clear cases. 
-We will automatically exclude participants who miss two attention checks. 
+We will individually check answers for response patterns such as straight-lining or missing of inverted items.
+We will conservatively remove participants with clear response patterns. 
+We will automatically exclude participants who miss the two attention checks we will implement.
 Participants who miss one attention check will be checked individually regarding response patterns. 
 We will remove participants below the minimum participation age of 18 years. 
-We will exclude respondents if they answer less than 50% of all questions. 
-The remaining missing responses will be imputed using predictive mean matching. 
-We will remove respondents with unrealistically fast responses, namely below three standard deviations of the medium response time.
+We will remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
+<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->
 
-## Data Analyses and Decision Pipeline
+Missing responses will be imputed using multiple imputation with predictive mean matching (five datasets, five iterations, using all variables). 
+The analyses will be run with all five datasets, and the pooled results will be reported.
 
-As a "reality check", we will test items for potential ceiling and floor effects. 
-If means are below 1.5 or above 6.5, these items will be excluded.
-The factorial validity of the measures and the hypotheses will be tested with structural equation modeling (SEM). 
+<!-- We will test items for potential ceiling and floor effects.  -->
+<!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
+The factorial validity of the measures and the hypotheses will be tested using structural equation modeling. 
 If Mardia’s test shows that the assumption of multivariate normality is violated, we will use the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator. 
 We will test each scale in a confirmatory factor analysis. 
-To avoid overfiting, we will use more liberal fit criteria (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016].
-
-If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
-If these changes do not yield sufficient fit, we will drop malfunctioning items. 
-If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
-EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
-If more than one dimension will be revealed, we will implement bifactor model solutions.[^1] 
-Bifactor models retain a general measure of the variable, and make it unneccesary to introduce novel (and potentially overfitted) subdimensions. 
-If no adequate bifactor model can be found, we will proceed by deleting items with low loadings on the general factor and/or the specific factors. 
-If also after deletion of individual items no bifactor solution should emerge, we will use a subset of the items to extract a single factor with sufficient factorial validity.
-
-[^1]: Bifactor models implement one factor that explains the variance in all items (the so-called general factor or g-factor). 
-In addition, at least two additional factors are implemented that explain the variance in a subset of the items. The general factor and the specific factors are orthogonal. 
-Bifactor models are nested within hierarchical models. 
-For more information on bifactor models, see @klinePrinciplesPracticeStructural2016, p. 319. 
-Note that we will not specify a bifactor model of need for privacy, because we are explicitly interested in the relations between the personality facets and the three dimensions of need for privacy.
+To assess model fit, we will use more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
+In cases of misfit, we will conservatively alter models using an a priori defined analysis pipeline (see online supplementary material).
 
 We want to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
-Hence, to answer our research question, we will analyze the variables' bivariate relations in a joint model combining all variables. 
-First, we will predict need for privacy using the factors, and then using the facets. 
-To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model, which we will report on the companion website.
-Based on reviewer feedback, we will also test which items best predict need for privacy, and report these items on our companion website.
+Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we will analyze the variables' bivariate relations. 
+To predict the need for privacy, we will first use the six personality factors.
+Afterward, we will predict privacy using the more specific facets. 
+To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model.
+<!-- We will also test which individual items best predict need for privacy. -->
 
-Because both analyses require highly complex model (overall, 24 personality facets, 7 socio-demographic variables, and potentially 8 privacy dimensions), it might be that we need to simply the model. 
-To this end, instead of a fully latent structural regression model we will then conduct a partially latent structural regression model, in which the predictor variables will be modeled as single indicators while controlling for measurement error [@klinePrinciplesPracticeStructural2016, p.
-214].
-To get high-quality single indicators of the predictors, we will compute the average of the model predicted values / latent factor scores, which we can be extracted from the CFAs. 
-If the CFAs show a unidimensional solution, we will use the model predicted values for this latent factor; if the CFAs produce a multidimensional solution, we will use the model predicted values for the general latent factor.
-
-Fully latent SEMs seldom work instantly and often require modifications to achieve satisfactory model fit.
-Although above we explicated our analysis pipeline, we are aware that this approach still maintains some researcher degrees of freedom. 
-We hence emphasize that we will adapt the models only to achieve satisfactory factorial validity, but not to cherry-pick significant results.
-We adopt this latent modeling approach nonetheless because we consider it superior to regular analyses such as regression based models of manifest variables [@klinePrinciplesPracticeStructural2016]. 
-Combining several items into a latent factors helps reduce and condense information, while partialing out error and thereby reducing noise.
-To provide the complete picture, in the online supplementary material (OSM) we will also share the results of the unaltered latent factors and of regular regression.
+Fully latent SEMs seldom work instantly, often requiring modifications to achieve satisfactory model fit.
+Although we explicate our analysis pipeline, there still remain several researcher degrees of freedom. 
+We still decided to use fully latent SEMs, because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
+Combining several items into a latent factors helps reduce error and condense information, thereby reducing noise.
+Together, this should provide a better measure of the latent variables, which will also reduce the beta error. 
+To provide context, in the online supplementary material (OSM) we will also share the results of alternative analyses, such as correlations of average scores.
 
@@
 
-All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
+All items will be answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
 A list of all the items that we will use are reported in the online supplementary material. 
@@
 [^2]: Note that the HEXACO inventory normally uses 5-point scales. 
-Because we were not interested in comparing absolute values across studies, we used 7-point scales to have a uniform answer format for all items, which in addition likely increase meaningful variance.
+Because we were not interested in comparing absolute values across studies, we used 7-point scales to have a uniform answer format across all items.
 
@@
 
-Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of an encompassing up-to-date scale.
-Hence, we use both extant scales and self-developed items, some of which were already tested in our prestudy. 
+Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of one encompassing, comprehensive, and up-to-date scale.
+Hence, we use both existing scales and self-developed items, some of which were tested in our pilot study. 
 Ad-hoc scales were or will be (preliminary) validated using the following procedure:
-We (a) collected qualitative feedback from three different privacy experts; (b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and tested (and adapted) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate relations; (d) all items will be analyzed in confirmatory factor analyses as outline above.
+We (a) collected qualitative feedback from three different privacy experts;[^experts]
+(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and tested (and adapted) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.
 
-Overall, we will collect 32 items measuring need for privacy, with eight subdimensions consisting of four items each. 
-Three subdimensions build on Burgoon's @burgoonPrivacyCommunication1982 privacy theory and were adopted from @frenerDevelopmentValidationNeed2021---namely psychological, informational, and physiological privacy.
-Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, we will also measure a social privacy dimension, which in the prestudy showed satisfactory fit.
-Next, we will measure need for privacy on a societal level. 
+[^experts]: The three experts who provided feedback were Moritz Büchi (University of Zurich), Regine Frener (University of Hohenheim), and Philipp Masur (VU Amsterdam).
+
+Overall, we will collect 32 items measuring need for privacy, with eight subdimensions that all consist of four items each. 
+Three subdimensions capture horizontal privacy---namely psychological, social, and physical privacy. 
+Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2021.
+Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, building on @burgoonPrivacyCommunication1982 we self-designed a new social privacy dimension, which in the prestudy showed satisfactory fit.
+Two subdimensions measure vertical privacy.
 The first subdimension is government surveillance, which represents the extent to which people want the government to abstain from collecting information about them. 
-The second dimension is anonymity, which captures the extent to which people feel the need to avoid identification. 
-Both scales were already pretested and showed good factorial validity. 
-Third, we will measure need for privacy from companies using four self-designed items. 
-Finally, we will also collect a self-developed measure of general need for privacy.
+The scale was pretested and showed good factorial validity. 
+The second subdimension is need for privacy from companies, which we will measure using four new self-designed items.
+Finally, three subdimensions capture general privacy. 
+The first subdimension is informational privacy, with items adopted from @frenerDevelopmentValidationNeed2021.
+The second subdimension is anonymity, which captures the extent to which people feel the need to avoid identification in general.
+The scale was pretested and showed good factorial validity; one new item was designed for this study.
+Third, we will also collect a new self-developed measure of general need for privacy.
 
@@
 Personality will be measured using the HEXACO personality inventory. 
-The inventory consists of six factors with four dimensions each, including the additional meta scale "altruism".
+The inventory consists of six factors with four dimensions each, including the additional meta scale of "altruism".
+
+# Results
+
+To visualize how results might look like, we have simulated some random data. Please note that these results are completely random and do not make sense from a theoretical perspective. 
+When calculating the multiple regressions, the models did not converge, which is why several estimates could not be computed (see below).
+
+In Table \@ref(tab:tab-ses), we report how sociodemographics predict need for privacy.
+
+```{r tab-ses, cache=F, warning=F, message=F, prompt=F}
+# tab_ses %<>% set_names(c("Sociodemographics", vars_pri_txt_brk))
+tab_ses %<>% set_names(c("Sociodemographics", vars_pri_txt_abr))
+
+apa_table(tab_ses,
+          # stub_indents = list("Sociodemographics" = c(1:6)),
+          col_spanners = list(`Need for privacy` = c(2, 9)),
+          caption = "Predicting the need for privacy dimensions using sociodemographic variables.",
+          font_size = "small",
+          escape = FALSE
+          )
+```
+
+In Table \@ref(tab:tab-dim), we report how personality factors predict need for privacy.
+
+```{r tab-dim, cache=F, warning=F, message=F, prompt=F}
+tab_dim %<>% set_names(c("Personality factors", vars_pri_txt_abr))
+
+apa_table(tab_dim,
+          # stub_indents = list("Sociodemographics" = c(1:6)),
+          col_spanners = list(`Need for privacy` = c(2, 9)),
+          caption = "Predicting the need for privacy dimensions using personality factors.",
+          font_size = "small",
+          escape = FALSE
+          )
+```
+
+In Table \@ref(tab:tab-fac), we report how personality facets predict need for privacy.
+
+```{r tab-fac, cache=F, warning=F, message=F, prompt=F}
+tab_fac %<>% set_names(c("Personality facets", vars_pri_txt_abr))
+
+apa_table(tab_fac,
+          stub_indents = list(
+            "Honesty humility" = c(1:4),
+            "Emotionality" = c(5:8),
+            "Extraversion" = c(9:12),
+            "Agreableness" = c(13:16),
+            "Conscientiousness" = c(17:20),
+            "Openness to experiences" = c(21:24)
+            ),
+          col_spanners = list(`Need for privacy` = c(2, 9)),
+          caption = "Predicting the need for privacy dimensions using personality facets.",
+          font_size = "scriptsize",
+          escape = FALSE
+          )
+```
+
+\newpage
+
+In Figure \@ref(fig:fig-reg), you can find how each personality factor---while holding constant for all other personality factors and sociodemographics---predicts need for privacy.
+
+```{r fig-reg, fig.cap="Results of multiple regressions, in which we predict all dimensions of need for privacy using all personality dimensions and sociodemgraphic factors simultaneously.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='H'}
+# fig_desc
+knitr::include_graphics("figures/fig_reg.png")
+```
 
@@
 The data will be shared on the open science framework (https://osf.io/e47yw/) and on github.
-
-<!-- In addition, we invite everyone to suggest changes and improvements to the manuscript via our github (https://github.com/tdienlin/need_for_privacy/). -->

### 2023-03-01 reviews.Rmd
- major update - now set up as a registered report

---
title: "Reviews of original submission"
# output:
#   html_document:
#     toc: TRUE
#     toc_float:
#       collapsed: FALSE
#       toc_depth: 3
output: pdf_document
---

Below you can find the reviews for the original submission

# Editor

Dear Dr Tobias Dienlin,

Thank you for trusting your manuscript “Who Needs Privacy" for review by Collabra: Psychology.  I sent the paper to two scholars who collectively have expertise concerning personality traits, cyber-psychology, and research methods. These individuals are extraordinarily well qualified to review this paper and I thank them for their service to this journal. I independently read the paper and then consulted the comments from the reviewers.

As you will read below, the reviewers thought the topic was interesting and worthy of study.  They also noted that the paper is well written.  However, the reviewers raised a number of significant questions and offered constructive suggestions for improvement, reconceptualization, and extension. The nature of the suggested improvements are substantial and seem to require additional samples. Indeed, I think a new and larger sample will be required to address the reviewer comments. Thus, I am sorry to say that my decision is to the submission for publication based on the peer review recommendations.  I would, however, be open to a new manuscript that includes a second larger sample (at least) that addresses the concerns of the reviewers with respect to evidence of replication, consideration of alternative analytic frameworks, and enhanced attention to measurement. I also think a sample with a wider age range might prove to be a useful compliment to the sample in the sample.  However, a large sample of college students might also work.

Regardless of this decision, I hope you find the reviews helpful as you decide on the next steps for this work. Below I outline some of the reasons that figured most prominently in my decision. I urge you to pay particular attention to reviewer feedback as I think their reactions are especially insightful.

1. I agree with concerns about re-labeling the NEO PI-R facets.  I actually think it might prove useful to use a long facet-based measure and keep labels consistent with those commonly used in the literature. The machine learning approach suggested by Reviewer B is intriguing.

2. I agree with the concerns of the reviewers about the need for additional studies to make sure there is adequate power and precision as well as evidence that the measures have acceptable levels of validity for the research purposes.  This is the major reason why I elected to reject the paper.  I think the current evidence is too preliminary to meet the rigor bar set for work published in this outlet.

3. Reviewer A raises an interesting conundrum about the overlap between a need for privacy and sociability.   This is something to consider when interpreting the results.

In the end, I am sorry to deliver unwelcome news. My decision boiled down to concerns about the strength of the current contribution in light of the expectations for rigor for papers at this outlet.  I think the idea of identifying personality correlates for privacy concerns is interesting.  The Reviewers and I simply concluded that additional study is needed to make a stronger case for the approach and ideas advanced in the paper.  Regardless of this decision, I wish you well as you pursue these topics.

Sincerely, 
Brent Donnellan
Senior Editor

# Reviewer A:

## General comments and summary of recommendation

Describe your overall impressions and your recommendation, including changes or revisions. Please note that you should pay attention to scientific, methodological, and ethical soundness only, not novelty, topicality, or scope. A checklist of things to you may want to consider is below:

 - Are the methodologies used appropriate?
 - Are any methodological weaknesses addressed?
 - Is all statistical analysis sound?
 - Does the conclusion (if present) reflect the argument, is it supported by data/facts?
 - Is the article logically structured, succinct, and does the argument flow coherently?
 - Are the references adequate and appropriate?:

This manuscript reports a cross-sectional correlational survey study on the link between privacy needs and various personality traits. The topic is interesting, and the manuscript is written in an accessible, transparent way, for which the authors should be applauded. However, I also thought there were several weaknesses, both conceptually (which may be addressed) and with regards to the empirical work. To this end, it may be reasonable to conduct a follow-up study (but this is a decision that should be made by the editor handling this manuscript).

BACKGROUND

The introduction and theoretical background is overall solid. The authors acknowledge that that the available evidence in this area is a) limited and b) results are rather mixed. As such, they carefully develop hypotheses but make it quite clear that the work is generally quite exploratory. I had a few thoughts that the authors might find helpful should they be given the opportunity to revise their manuscript:

p. 3, l. 34: „We think that a better understanding of the relation between personality and privacy is crucial”
Perhaps it is, but the authors do not really say why. Other than academic interest, why is a better understanding “crucial”? A paragraph laying out the relevance of research on the link between personality and privacy, either in the introduction or the discussion, would be helpful.

p. 8, l. 178: “Somewhat related, prior empirical research has shown that people who are more concerned about their privacy are also more likely to withdraw online, for example by deleting posts or untagging themselves from linked content (Dienlin & Metzger, 2016).”
Maybe I’m just not understanding the connection, but maybe the authors could explain how this is even “somewhat” related to the level of general anxiety.

p. 8, l. 184 to p. 9, l. 194: I found this entire paragraph on the link between anxiety and consent to government surveillance somewhat unconvincing. It is plausible that anxiety correlates with being in favor of government surveillance; however, this does not necessarily extend to someone’s own data. One can be in favor of government surveillance programmes and a high need for privacy. Maybe this paragraph just needs some slight editing to emphasize the point the authors are trying to make here (similar to p. 9, l. 207: one can desire privacy with regards to their own information or data and still be in favor of governmental surveillance measures to avert threats).

Maybe writing this will get me a ticket straight to personality psychology hell, but since the authors have already moved away from personality factors and instead consider facets (e.g. gregariousness instead of extraversion, p. 5), is it not conceivable that “need for privacy”, too, is another of those facets? Or maybe why it’s not! I’m not suggesting it actually is (I’m very much agnostic on that question) but maybe considering the idea would help the authors more clearly distinguish between the many constructs and also types of constructs they introduce and connect in their manuscript. In particular, I find it currently difficult to understand the meaningful difference between sociability (“whether people prefer to spend their time alone or with company”) and privacy (“a voluntary withdrawal from society”) as introduced in the manuscript.

DATA ANALYSIS

p. 11, l. 257: “Because all predictors were chosen on the basis of a-priori reasoning we did not control for alpha inflation.”
That is not a reason not to control for alpha inflation. If anything, in fact, one might even argue that it would be a good reason to do the opposite, i.e. apply some sort of inflation correction: Committing an alpha or Type I error means rejecting a true null hypothesis. When one is in “discovery mode”, or largely exploring, there could be an argument to set alpha relatively high (.1 or maybe even .2) in order to balance it with Type II errors and not miss potentially important relationships (at the cost of a greater number of false positives). However, when one is relatively sure that observed variables are indeed related, there is no good reason to do so because p-values will tend to 0 and should not be “just below .05” anyway (I will return to this point later in my review). Here, it is more important that they survive “stricter” thresholds (as there should not be many false negatives). This is not to say I am asking the authors to definitely apply some correction method (although they reasonably might), but to reconsider the argument they present to have alpha fixed at .05.

MEASURES

Quite a few items from validated scales were dropped. I am not a big fan of this practice, and the authors note that it is certainly not ideal, but mention that it did not make a huge difference. Maybe they could expand a little what this means in practice (e.g. whether the bivariate correlations change meaningfully, etc).

I found it striking that the correlation between privacy need government and privacy need anonymity was > .8, which seems to suggest these two factors treated separately are massively overlapping. Maybe it would be good if the authors expanded a little on this.

RESULTS

Currently, I see the greatest issues with the results of the statistical analyses, or rather, their interpretation, in the context of the observed sample size and predefined SESOI. To me it seems that with the exception of the link between Sociability and Privacy need Interpersonal, all hypotheses should be rejected. This is greatly visualized in Figure 2, where a number of interesting observations can be made

 1. all but one of the 95% CIs overlap with the equivalence region
 2. all but the age CIs are actually wider than the equivalence region, which means that for most variables, the precision was too low to perform meaningful equivalence tests.

From what I understand, the authors did not actually conduct equivalence tests (otherwise they would have used 90% CIs instead of 95%), but use the thresholds descriptively (i.e. without testing “against” them). Still, taking into account the standard errors makes sense, but also implies that almost all of the coefficients are not larger than the authors’ defined smallest effect size of interest. This is further corroborated by the observed p-values reported in Table 3 (in increasing order, < .05 only): < .001, .004, .008, .011, .025, .027, .031, .036, .037, .042. Under the assumption of true alternative hypotheses, this distribution of p-values should be quite rare, as they seem to tend away from rather than to 0. Even a very relaxed alpha inflation correction (e.g., fixed alpha/2, would have rendered 50% of these p-values nonsignificant). This, of course, would change the interpretation and discussion substantially, and I am happy to see counterarguments by the authors.

Notably, I am wholly unconvinced by the last paragraph in the results section (p. 19, l. 397 an onwards), purportedly presenting arguments why the results cannot be explained by chance alone. Although the authors seem to be very careful in their statistical inference (defining SESOIs, discussing power, etc), this paragraph seems to reintroduce several common misconceptions about p-values that they elsewhere carefully avoid, the most important being that P-values are conditional probabilities and as such cannot be used to infer that the results could not have been explained by chance alone (this is why we define a priori error rates). This entire paragraph is built on the comparison of the observations with a hypothetical “null hypotheses”. However, as far as I can tell, the study tested a very large number of hypotheses (at least 24), and as such, speaking of one uniform null would be the most extreme case (24 out of 24 hypotheses are false). But just consider that, say 20 out or 24 tested hypotheses are actually false. Would observing 11 significant tests be so unusual? What about under 19 out of 24, or 17? These comparisons are meaningless as they do not tell us which of the 11 significant tests represent true hypotheses, and which are false positives.

DISCUSSION

I will limit my comments on the discussion for now as, depending on the revision of the manuscript, it might look very different from what is currently reported (see above).

CONCLUSION

Overall, the research topic is interesting, and the authors wrote up a transparent, accessible report. However, I wonder, given the concerns identified, the potentially insufficient precision, and the fact that the authors failed to meet their own sample target (300), whether it might not be the best route to conduct a follow-up study to substantiate many of these initial findings. This would also put a suggestion to the test the authors make on p. 19, l. 395: that a larger study, which yields smaller standard errors, would find additional effects. This is certainly possible, but it is also entirely conceivable that some of the initially observed effects would be smaller (regression to the mean).

## Figures/tables/data availability:

Please comment on the author’s use of tables, charts, figures, ifrelevant. Please acknowledge that adequate underlying data is available to ensure reproducibility (see open data policies per discipline of Collabra here).:

Figures and tables are used appropriately, and data are available.

## Ethical approval:

If humans or animals have been used as research subjects, and/or tissue or field sampling, are the necessary statements of ethical approval by a relevant authority present? Where humans have participated in research, informed consent should also be declared. If not, please detail where you think a further ethics approval/statement/follow-up is required.:

It is not reported whether consent was obtained (the study does have IRB approval though)

## Language

Is the text well written and jargon free? Please comment on the quality of English and any need for improvement beyond the scope of this process.:

The quality of English is fine; some slight editing might be good, but not necessary

# Reviewer B:

1) General comments and summary of recommendation

Describe your overall impressions and your recommendation, including changes or revisions. Please note that you should pay attention to scientific, methodological, and ethical soundness only, not novelty, topicality, or scope. A checklist of things to you may want to consider is below:

 - Are the methodologies used appropriate?
 - Are any methodological weaknesses addressed?
 - Is all statistical analysis sound?
 - Does the conclusion (if present) reflect the argument, is it supported by data/facts?
 - Is the article logically structured, succinct, and does the argument flow coherently?
 - Are the references adequate and appropriate?:

I am glad to have the opportunity to review this manuscript. By evaluating the individual characteristics that relate to the perceived need for privacy, it addresses a topic of increasing social relevance and I think there is a need for more research along these lines. I also applaud the authors' use of advanced analytic methods and their efforts to address issues important to open science.

That said, I feel the impact of this work is limited by their methodological approach. Specifically, I find myself unable to endorse their approach to measurement due to two concerns.

The first and more straight-forward concern relates to their measures of privacy. The standards for new measures that are derived through rational methods (the approach taken here) increasingly require more extensive procedures than those that are described in this manuscript. For example, it is becoming standard practice to attain expert input via qualitative data collection for concept elicitation (not mentioned here) in addition to an exhaustive literature review (conducted, at least in part, for this manuscript though it would be helpful to more directly explain how the prior research described in the introduction ties to procedures used to develop this measure of privacy). Ideally, when budgets allow, one would also co-administer extant measures of the construct before choosing content for preliminary/potential inclusion in the new measure, as this allows for more informed understanding of the overlapping and unique features of prior operationalizations. It is also important that the preliminary content is evaluated across a range of qualitative attributes (e.g., literacy levels, readability, avoidance of colloquialisms, etc.) prior to large scale data collection. I should note that the final items (in Table 2) look pretty good with respect to these qualitative attributes but little detail is given about the procedures used to write the new content. Then, the overly-inclusive pool of preliminary items would be administered to one or more large and representative sample(s) -- EFAs and CFAs would not be used on the same data. Optimally, EFA results would be replicated before moving to confirmatory evaluations of fit. Finally, once a final set of items has been identified on the basis of these structural analyses, reports on their psychometric properties should be made. The authors did a nice job of addressing questions about dimensionality and reliability but validation evidence was lacking. It is most common for these procedures to be detailed in a stand-alone project/publication, and sometimes more than one. Of course, validation is an on-going endeavor and I think this paper would constitute a nice example of a validation project if the measure had previously been introduced in prior work (using something like the steps described above).

My second concern is more subtle than the first, but not less important. It relates to the authors' approach to measuring the other facets of personality. After reading the abstract, I was immediately curious to know which measurement framework the authors had used for personality assessment, as it was clear that they had deviated from using one of the mainstream assessment models -- not necessarily a problem on its own merits, but this does introduce some challenges in terms of situating the findings relative to other personality research. As I proceeded through the introduction, I began to understand that they endorsed a Big Five approach but were measuring unfamiliar facet-level constructs. Only when reviewing the Measures section of the Methods did I understand that they were using facets of the NEO-PI-R with different names than the constructs being measured. While I am sympathetic to the notion that there are many plausible features of personality that *may* be covered by unnamed nooks and crannies of the NEO and various other measurement frameworks (more technically, "homogenous item clusters"), it is not valid to use -- for example -- the reversed scores of the Actions facet of Openness to Experiences as a measure of Traditionalism in the absence of empirical evidence confirming that this measures what the authors claim it measures. Though cold comfort for the authors, I understand the temptation to do this and I think stems from a real weakness for our field -- the fact that we do not have a strong working knowledge of the nomological relations among empirically-identified personality traits that are less abstract than the Big Five.

I have a possible suggestion but it would require a substantial overhaul to the text. If the authors happened to collect data on all 30 facets of the NEO (not clear) in addition to the privacy items, an informative analysis would be to use machine learning methods capable of showing the NEO items that are most predictive of the privacy variables (whether scales or items). Some would argue that this constitutes baseless data mining. To counter that argument (a little), a nice addition might be pre-registration and analysis by someone who is not familiar with the data/findings and/or the use of a training and test sub-samples (given the size of this sample, I would recommend using it as the training sample and then collecting a new sample as the test set).

In addition to the comments provided here, I have attached a marked-up copy of the manuscript with several more minor comments and questions.

## Figures/tables/data availability

Please comment on the author’s use of tables, charts, figures, ifrelevant. Please acknowledge that adequate underlying data is available to ensure reproducibility (see open data policies per discipline of Collabra here).:

I have not attempted to reproduce these findings nor is it clear to me whether the data and code needed to do so are available. If so, I must have missed it. Given the comments provided in my review, reproduction of the results did not seem like an immediate concern.

## Ethical approval:

If humans or animals have been used as research subjects, and/or tissue or field sampling, are the necessary statements of ethical approval by a relevant authority present? Where humans have participated in research, informed consent should also be declared. If not, please detail where you think a further ethics approval/statement/follow-up is required.:

The study was subject to IRB approval.

## Language:

Is the text well written and jargon free? Please comment on the quality of English and any need for improvement beyond the scope of this process.:

Yes, I think it is well-written

### 2023-03-01 analyses.RmD
- added results to CFAs

@@
 - The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
-- We'll later conduct additional analyses, for example model-alterations given misfit.
+- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit.
 
@@
 
-```{r r-setup, include=T, echo=F}
+```{r r-setup, include=T, echo=T, results='hide'}
 # install packages
@@
 ```{r}
+name <- "HEX_HOH_SIN"
 model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_HOH_FAI"
 model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEY_HOH_GRE"
 model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_HOH_MOD"
 model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EMO_FEA"
 model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EMO_ANX"
 model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EMO_DEP"
 model <- "HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EMO_SEN"
 model <- "HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EXT_SSE"
 model <- "HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EXT_BOL"
 model <- "HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EXT_SOC"
 model <- "HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_EXT_LIV"
 model <- "HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_AGR_FOR"
 model <- "HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_AGR_GEN"
 model <- "HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_AGR_FLX"
 model <- "HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_AGR_PAT"
 model <- "HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_CNS_ORG"
 model <- "HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_CNS_DIL"
 model <- "HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_CNS_PER"
 model <- "HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_CNS_PRU"
 model <- "HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_OPN_AEX"
 model <- "HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_OPN_INQ"
 model <- "HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_OPN_CRE"
 model <- "HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_OPN_UNC"
 model <- "HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "HEX_ALT"
 model <- "HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_PSY"
 model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_PHY"
 model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_SOC"
 model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_GOV"
 model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_COM"
 model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_INF"
 model <- "NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_ANO"
 model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 ```{r}
+name <- "NFP_GEN"
 model <- "NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04"
+assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
 ```
@@
 
-A 5% error rate would imply collecting 1.293 participants.
+A 5% error rate would imply collecting `r power_n_95` participants.
 

### 2023-03-01 items.rmd
- added toc to items

@@
 title: "Items"
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#       toc_depth: 3
-output: pdf_document
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+      toc_depth: 3
+# output: pdf_document
 bibliography: 

### 2023-03-01 proposal.Rmd
- last updates before sending to Miriam

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+      toc_depth: 2
+# output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 
-## Removing Participants, Imputation of Missing Data, and Planned Analyses
+## Planned Analyses
 
@@
 In cases of misfit, we will conservatively alter models using an a priori defined analysis pipeline (see online supplementary material).
+As a “reality check,” we will test items for potential ceiling and floor effects. If means are below 1.5 or above 6.5, these items will be excluded.
 
@@
 To provide context, in the online supplementary material (OSM) we will also share the results of alternative analyses, such as correlations of average scores.
+
+We anticipate to finish the project three months after our registration was accepted.
 

### 2023-03-07 items.rmd
- updates before submission

@@
  1. I would never accept a bribe, even if it were very large.
- 1. I’d be tempted to use counterfeit money, if I were sure I could get away with it.
+ 1. I’d be tempted to use counterfeit money if I were sure I could get away with it.
 
@@
  1. I feel that I am an unpopular person.
- 1. Even in an emergency I wouldn't feel like panicking.
+ 1. I sometimes feel that I am a worthless person.
 
@@
  2.	I don’t like to stand in a dense crowd of people.
- 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
+ 3.	I don’t like to sit next to a stranger on a subway, bus, or plane.
  4.	I hate it when people enter my personal space uninvited. (new)
@@
 
-Are you currently in a partnership or relation with another person?
+Are you currently in a romantic partnership or relation with another person?
 

### 2023-03-07 proposal.Rmd
- updates before submission

@@
 abstract          : "Privacy is defined as a voluntary withdrawal from society.
-Everyone needs privacy.
-Currently, however, we still know little about who needs more and how needs less privacy.
-In this study, we hence explore the relations between the need for privacy and personality.
+While everyone needs some degree of privacy, we currently know little about people’s privacy needs..
+In this study, we explore the relations between the need for privacy and personality.
 Personality will be operationalized using the HEXACO personality inventory.
-Need for privacy will be measured along the dimensions of (a) social, (b) psychological, and (c) physical privacy; need for privacy from (d) government agencies and (e) companies; as well as (f) informational privacy, (g) need for anonymity, and (h) general privacy.
+Need for privacy will be measured in relation to (a) social, (b) psychological, and (c) physical privacy from other individuals (horizontal privacy); need for privacy from (d) government agencies and (e) companies (vertical privacy); as well as need for (f) informational privacy, (g) anonymity, and (h) general privacy (both horizontal and vertical privacy).
 A sample of 1,293 respondents representative of the U.S.
@@
 classoption       : "man"
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-      toc_depth: 2
-# output            : papaja::apa6_pdf
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#       toc_depth: 2
+output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 <!-- Or do they have more to hide? -->
-Asking this question seems relevant, not least because people who desire more privacy are often confronted with suspicions, having to justify why they want to be left alone.
-Consider the nothing-to-hide argument [@soloveVeGotNothing2007].
-Accordingly, people who oppose state surveillance only do so because they have something to hide. 
-For if you who have nothing to hide, you would have nothing to fear.
-<!-- This may be due to the fact that privacy is most often analyzed from a situational or contextual perspective [@nissenbaumPrivacyContextTechnology2010]. -->
-<!-- However, privacy is also dispositional: Some need more and some need less privacy [@pedersenPersonalityCorrelatesPrivacy1982]. -->
+Asking this question seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
+Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007]: People who oppose state surveillance only do so because they have something to hide, because if you have nothing to hide, you would have nothing to fear.
 Is it true that people who desire more privacy are also more dishonest, greedy, or unfair? 
 Or are people simply less extroverted, more diligent, or more prudent? 
-<!-- Analyzing these questions is relevant. -->
-With this paper, we hence seek to answer the following question: 
-What can we learn about a person's personality if they say they desire more privacy?
+With this paper, we seek to answer the following question: What can we learn about a person’s personality if they say they desire more privacy?
 
@@
 This withdrawal happens _voluntarily_, and it is under a person's _control_ [@westinPrivacyFreedom1967]. 
-Privacy is multi-dimensional. 
-On the broadest level, we can differentiate the two dimensions of horizontal and vertical privacy [@schwartzSocialPsychologyPrivacy1968, @masurPrivatheitOnlineKommunikation2018].
+Privacy is also multi-dimensional. 
+On the broadest level, we can differentiate the two dimensions of horizontal and vertical privacy [@schwartzSocialPsychologyPrivacy1968; @masurPrivatheitOnlineKommunikation2018].
 Whereas horizontal privacy captures withdrawal from other people or peers, vertical privacy addresses withdrawal from superiors or institutions (e.g., government agencies or businesses). 
@@
 @pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
-reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity. 
+reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity: 
 <!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
@@
 Building on this work, in this study we employ a multifaceted model of need for privacy. 
-We focus on vertical privacy with regard to people’s felt need for withdrawal from (a) government surveillance and (b) private companies; 
-horizontal privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
-and general privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
+We focus on _vertical_ privacy with regard to people’s felt need for withdrawal from (a) government surveillance and (b) private companies; 
+_horizontal_ privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
+and _general_ privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
 
 We understand and measure personality using the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018]. 
-The HEXACO is a large and comprehensive operationalization of personality. 
-Using the HEXACO will make it less likely to miss potentially relevant factors and facets.
+HEXACO is a large and comprehensive operationalization of personality, and thus is less likely to miss potentially relevant factors and facets than other personality constructs. 
 The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
 <!-- and represents a broad understanding of personality-->
-It includes overall six factors (discussed below), which have four specific facets each. 
-In predicting the dimensions of need for privacy, we will use the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to the more general personality factors
+It includes six factors (discussed below), which have four specific facets each. 
+In addition, the HEXACO model includes a sixth factor not present in the Big Five labeled honesty-humility (plus a meta-facet called altruism), which seem particularly well-suited to investigate the nothing-to-hide-argument.
+
+In predicting the need for privacy, we will primarily focus on the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to more general personality factors
 <!-- For example, consider that privacy concern, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors  -->
 [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008]. 
-In addition to the Big Five, the HEXACO model includes a sixth factor labeled honesty-humility (plus a meta-facet called altruism), which together seem well-suited to investigate the nothing-to-hide-argument.
+And for reasons of scope, below we cannot discuss all four facets for all six factors. Instead, we focus on those we consider most relevant. However, all we be analyzed empirically.
 
@@
 
-So far, only few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
-In addition, we are not aware of a viable theory specifically connecting privacy and personality.
-Due to the dearth of empirical studies and the lack of viable specific theories, in this study we hence adopt an exploratory perspective. 
+So far, very few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
+Moreover, we are not aware of a viable theory specifically connecting privacy and personality.
+Due to the dearth of empirical studies and the lack of theory, in this study we hence adopt an exploratory perspective. 
 <!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->
 
-In order to understand how personality might relate to privacy, we can ask ourselves the following question. 
+In order to understand how personality might relate to privacy, we can ask ourselves the following question:  
 Why do people desire privacy?
@@
 @westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
-Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014]. 
-It is hence important for social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
+Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], and so it is hence important for social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
 But privacy can also have negative aspects. 
@@
 And privacy can also help conceal wrongdoing or crime. 
-<!-- The dialectical tension between the positive and negative aspects of privacy might itself cause variability across individuals in their felt need for privacy both within and across contexts or situations.
--->
-<!-- In this study we now ask, what role does personality play in determining individual-level variations in need for privacy? -->
-<!-- Our reasoning further was guided by another central theoretical tenet.  -->
-<!-- As suggested above, privacy can be either positive or negative.  -->
-<!-- Similarly, other people, the government, and anonymity can be considered either a _resource_ or a _threat_.  -->
-<!-- Having information about a person's personality can inform us whether he or she is more likely to think of others as a resource or a threat.  -->
-<!-- It follows that if other people are considered a threat it seems to be more likely that a person will desire more privacy from others, and vice versa [@altmanPrivacyConceptualAnalysis1976]. -->
-As a general guiding principle based on an evolutionary perspective, 
-<!-- In terms of potential theoretical explanations as to why personality might relate to the need for privacy,  -->
-we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
+As a general guiding principle based on an evolutionary perspective, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
 Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
-In what follows, we briefly present all factors and how they might relate to need for privacy.
+In what follows, we briefly present each HEXACO factor and how it might relate to need for privacy.
 
@@
 According to the nothing-to-hide argument, a person desiring more privacy might be less honest, sincere, fair, or benevolent. 
-People who commit crimes likely face greater risk from self-disclosure, because government agencies and people would enforce sanctions if their activities were revealed [@petronioCommunicationPrivacyManagement2010].
-Hence, in those cases the government and other people are likely perceived as a threat. 
+People who commit crimes likely face greater risk from some types of self-disclosure, because government agencies and people would enforce sanctions if their activities were revealed [@petronioCommunicationPrivacyManagement2010].
+Hence, in those cases the government and other people may be perceived as a threat. 
 As a consequence, people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
 
-Empirical studies have indeed found that privacy can increase cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
+Empirical studies have linked privacy to increased cheating behaviors [@corcoranMoralityconscienceGuiltScale1987; @coveySelfmonitoringSurveillanceIncentive1989]. 
 @coveySelfmonitoringSurveillanceIncentive1989 asked students to solve an impossible maze. 
@@
 In the privacy condition, the experimenter could not see the students. 
-Results showed greater cheating among students in the low surveillance condition, suggesting that in situations with more privacy people are less honest. 
+Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
+While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty.
 In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
@@
 
-In conclusion, it seems possible that lack of honesty may indeed relate to an increased need for privacy, especially when it comes to privacy from government agencies.
+In conclusion, it seems possible that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies. 
 <!-- , as governments have the legitimate power to prosecute illegal activities.  -->
@@
 Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
-People who are anxious may be more likely to consider social interactions a risk or threat  [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
+People who are anxious may be more likely to view social interactions as risky or threatening [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
 Anxious people might hence desire more privacy. 
-People who are more concerned about their privacy (in other words, more anxious) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content [@dienlinExtendedPrivacyCalculus2016a].
+People who are more concerned about their privacy (in other words, more anxious about privacy) may be more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016a].
 On the other hand, the opposite may also be true: 
-People who are more anxious in general may desire _less_ privacy from others (especially their strong ties), as a means to cope better with their daily challenges.
+People who are more anxious in general may desire less privacy from others (especially their strong ties), as a means to cope better with their daily challenges or to seek social approval to either verify or dispel their social anxiety.
 
@@
 They might more likely consent to government surveillance, given that such surveillance could prevent crime or terrorism. 
-On the other hand, it could also be that more anxious people desire more privacy from government agencies. 
-Although they even might be in favor of government surveillance of _others_, this does not necessarily include _themselves._
-Especially if the government is perceived as a threat, as often expressed by members of minority groups, then one might actually desire more personal privacy.
+On the other hand, it could also be that more anxious people desire more privacy from government agencies, at least on a personal level. 
+For example, while they might favor government surveillance of _others_, this does not necessarily include _themselves_. 
+Especially if the government is perceived as a threat, as often expressed by members of minority groups, then anxiety might lead one to actually desire more personal privacy.
 
@@
 <!-- It is plausible that  -->
-Conceptually, interpersonal privacy and sociability are closely related.
-More sociable people are likely more inclined to think of other people as a resource, which is why they should desire less interpersonal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].
+Conceptually, social privacy and sociability are closely related.
+More sociable people are likely more inclined to think of other people as a resource, and thus they should desire less horizontal privacy and less anonymity [e.g., @bussPsychologicalDimensionsSelf2001].
 Given that privacy is a voluntary withdrawal from society [@westinPrivacyFreedom1967], people who are less sociable, more reserved, or more shy should have a greater need for privacy from others.
@@
 This hypothesis is supported by several empirical studies. 
-People who scored higher on the personality meta-factor plasticity, which is a composite of the two personality factors extraversion and openness, desired less privacy [@mortonMeasuringInherentPrivacy2013].
+People who scored higher on the personality meta-factor plasticity, which is a composite of the two personality factors extraversion and openness, were found to desire less privacy [@mortonMeasuringInherentPrivacy2013].
 People who described themselves as introverted thinkers were more likely to prefer social isolation [@pedersenPersonalityCorrelatesPrivacy1982].
-Introverted people were more likely to feel their privacy was invaded [@stoneRelationshipIntroversionExtraversion1986].
-@pedersenPersonalityCorrelatesPrivacy1982 reported that the three dimensions of need for privacy related to general self-esteem (but not social self-esteem). 
-Respondents who held a lower general self-esteem were more reserved (_r_ = .29), and needed more anonymity (_r_ = .21) and solitude (_r_ = .24).
+Introverted people were more likely to feel their privacy was invaded when they were asked to answer very personal questions [@stoneRelationshipIntroversionExtraversion1986].
+@pedersenPersonalityCorrelatesPrivacy1982 reported that the need for privacy related to general self-esteem (but not social self-esteem), which in turn is a defining part of extraversion [@leePsychometricPropertiesHEXACO1002018].
+Specifically, he found respondents who held a lower general self-esteem were more reserved (_r_ = .29), and needed more anonymity (_r_ = .21) and solitude (_r_ = .24).
 Finally, @larsonNeedPrivacyIts1988 and @hosmanRelationshipsNeedPrivacy1991 suggested that people who are more shy also need more privacy.
@@
 Agreeableness has the four facets of forgiveness, gentleness, flexibility, and patience.
-It is not entirely clear whether or how agreeableness might relate to the need for privacy.
-People who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+It is not entirely clear whether or how agreeableness might relate to the need for privacy, although people who are more agreeable are also moderately less concerned about their privacy [@junglasPersonalityTraitsConcern2008].
 Thus, because need for privacy and privacy concern are closely related, more agreeable people might desire less privacy. 
+It is also possible that people higher in agreeableness hold more generous attitudes toward others and are less suspicious that others have malicious motives, and consequently perceive less risk from interacting with others.
 
@@
 Arguably, all facets are about being in control, about reducing relevant risks and future costs.
-Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully, might prefer to have more privacy.
-Especially if others are considered a threat, being risk averse might increase the desire for more interpersonal privacy. 
-Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for privacy. 
+Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully, might prefer to have more privacy because it affords them greater control.
+Especially if others are considered a threat, being risk averse might increase the desire for more horizontal privacy. 
+Similarly, if government agencies or private companies are considered a threat, risk averse people might have a stronger desire for vertical privacy. 
 In either case, the most cautious strategy to minimize risks of information disclosure would be to keep as much information as possible private. 
-Empirical studies reported that people with a stronger control motive required slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
-People who considered their privacy at risk were less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
-Moreover, conscientious people were slightly more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
+Empirical studies have found that people with a stronger control motive require slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
+People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
+Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
 <!-- But as discussed above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats.
@@
 People more open to new experiences might not prioritize privacy. 
-Many new digital practices such as social media, online shopping, or online dating offer exciting new benefits, but pose a risk to privacy. 
-People who are more open to new experiences might focus on the benefits and not on the potential risks.
-<!-- An example might be that people with greater openness to experiences would be more likely to try a new online social network or medium of communication. -->
-Hence, different relations between need for privacy and openness seem possible.
+Many digital practices such as social media, online shopping, or online dating offer exciting benefits and new experiences, but pose a risk to privacy. 
+People who are more open to new experiences might focus on the benefits rather than the potential risks. 
+Hence, either a positive or negative relationship between need for privacy and openness is possible.
 
@@
 For example, a study of 3,072 people from Germany found that women desired more informational and physical privacy than men, whereas men desired more psychological privacy [@frenerDevelopmentValidationNeed2021].
-In a nationally representative study of the U.S. and Japan, people who were older and who had higher income levels reported more privacy concern. 
+In a nationally representative study of the U.S. and Japan, people who were older and who had higher income reported more privacy concern. 
 More educated people possess more privacy knowledge [@parkDigitalLiteracyPrivacy2013], and as a consequence they might desire more privacy. 
-Ethnicity might also correspond to the need for privacy, perhaps because members of minority groups desire more privacy from the government, but not necessarily from other people. 
+Ethnicity might also correspond to the need for privacy, perhaps because members of minority groups desire more privacy from the government, although not necessarily from other people. 
 Some minorities groups (e.g., Black or Native Americans) often report lower levels of trust in white government representatives [@kochRacialMinoritiesTrust2019], which might increase the desire of privacy from government agencies.
-We will also explore whether a person’s romantic relationship status corresponds to their expressed need for privacy. 
 Last, we will examine whether one’s political position is related to the need for privacy. 
@@
 People who are more conservative tend to trust the government slightly less [@cookSkepticalAmericanRevisiting2005], which might be associated with an increased need for privacy.
+We will also explore whether a person’s romantic relationship status corresponds to their expressed need for privacy.
 
@@
 We hence decided to treat our prior project as a pilot study and to address the criticism by conducting a new study.
-In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together with other more established need for privacy measures, and overall adopt a more exploratory perspective.
+In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together and established need for privacy measures, and overall adopt a more exploratory perspective.
 Being our central construct of interest, we also develop a small number of new items to have a more comprehensive measure of need for privacy.
@@
 We calculated that participation will take approximately 15 minutes. 
-We will pay participants \$ 2.56 for participation, which equals an hourly wage of \$ 10.24.
+We will pay participants \$2.00 for participation, which equals an hourly wage of \$8.00.
 
@@
 Although we explicate our analysis pipeline, there still remain several researcher degrees of freedom. 
-We still decided to use fully latent SEMs, because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
+We decided to use fully latent SEMs because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
 Combining several items into a latent factors helps reduce error and condense information, thereby reducing noise.
@@
 Hence, we use both existing scales and self-developed items, some of which were tested in our pilot study. 
-Ad-hoc scales were or will be (preliminary) validated using the following procedure:
+Ad-hoc scales were or will be (preliminarily) validated using the following procedure:
 We (a) collected qualitative feedback from three different privacy experts;[^experts]
-(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 and tested (and adapted) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.
+(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.
 
@@
 Overall, we will collect 32 items measuring need for privacy, with eight subdimensions that all consist of four items each. 
-Three subdimensions capture horizontal privacy---namely psychological, social, and physical privacy. 
+Three subdimensions capture horizontal privacy---namely psychological, social, and physical privacy from other individuals. 
 Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2021.

### 2023-03-07 analyses.RmD
- last updates before sending to Miriam
- updates before submission

@@
 ---
-title: "Who Needs Privacy? Exploring the relationship between personality and need for privacy"
+title: "Who needs privacy? Exploring the relations between need for privacy and personality"
 subtitle: "Analyses"
@@
   - "bibliography/references.bib"
-  # pdf_document:
-  #   toc: TRUE
 ---
@@
 - The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
-- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit.
+- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit or imputation of missing data.
 
@@
  - I feel that I am an unpopular person.
- - Even in an emergency I wouldn't feel like panicking.
+ - I sometimes feel that I am a worthless person.
 

### 2023-03-07 proposal.Rmd
- small changes to abstract

@@
 Personality will be operationalized using the HEXACO personality inventory.
-Need for privacy will be measured in relation to (a) social, (b) psychological, and (c) physical privacy from other individuals (horizontal privacy); need for privacy from (d) government agencies and (e) companies (vertical privacy); as well as need for (f) informational privacy, (g) anonymity, and (h) general privacy (both horizontal and vertical privacy).
+Need for privacy will be measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy).
 A sample of 1,293 respondents representative of the U.S.
@@
 classoption       : "man"
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#       toc_depth: 2
-output            : papaja::apa6_pdf
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+      toc_depth: 2
+# output            : papaja::apa6_pdf
 # output            : papaja::apa6_word

### 2023-03-07 proposal.Rmd
- added link

@@
 This section describes how we determine the sample size, data exclusions, the analyses, and all measures in the study.
+The Study will be conducted as an online questionnaire, programmed with Qualtrics.
+A preview of the survey can be found [here](https://compcommlab.eu.qualtrics.com/jfe/preview/previewId/5c6193c9-12a4-424f-9808-a7c6e74247c1/SV_9ppRmr32VrmeAnA?Q_CHL=preview&Q_SurveyVersionID=current).
 
@@
 A list of all the items that we will use are reported in the online supplementary material. 
+The personality and privacy items will be presented in random order, and the sociodemographic questions will be asked at the end.
 We will later report also the results of the CFAs/EFAs, as well as item statistics and their distribution plots.

### 2023-03-07 proposal.Rmd
- minor formatting changes

@@
 
-In predicting the need for privacy, we will primarily focus on the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to more general personality factors
-<!-- For example, consider that privacy concern, a variable conceptually close to need for privacy, shows only small relations to the Big Five factors  -->
-[@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008]. 
+In predicting the need for privacy, we will primarily focus on the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to more general personality factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].
 And for reasons of scope, below we cannot discuss all four facets for all six factors. Instead, we focus on those we consider most relevant. However, all we be analyzed empirically.
@@
 We will test each scale in a confirmatory factor analysis. 
-To assess model fit, we will use more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA <. .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
+To assess model fit, we will use more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
 In cases of misfit, we will conservatively alter models using an a priori defined analysis pipeline (see online supplementary material).

### 2023-03-07 proposal.Rmd
- fixed typo in abstract
- edited COI

@@
 abstract          : "Privacy is defined as a voluntary withdrawal from society.
-While everyone needs some degree of privacy, we currently know little about people’s privacy needs..
+While everyone needs some degree of privacy, we currently know little about people’s privacy needs.
 In this study, we explore the relations between the need for privacy and personality.
@@
 documentclass     : "apa6"
-classoption       : "man"
+# classoption       : "man"
 output:
@@
 
-# Competing Interests
+# Conflict of Interests
 
-Both authors declare no competing interests.
+Both authors declare no conflict of interests.
 

### 2023-11-16 analyses.RmD
- fixed one item
- implemented feedback from reviewers

@@
               "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
-              "pwr", "semPlot", "semTools", "tidyverse", "td")
+              "pwr", "semPlot", "simsem", "semTools", "tidyverse", "td")
 
@@
                   "Companies", "Governnment",
-                  "Anonynmity", "Infornmational", "General")
+                  "Anonynmity", "Informational", "General")
 vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
@@
  2.	I don’t like to stand in a dense crowd of people.
- 3.	I don’t like to sit next to a stranger on a tram, bus, or plane.
+ 3.	I don’t like to sit next to a stranger on a train, bus, or plane.
  4.	I hate it when people enter my personal space uninvited.
@@
 # Power Analyses
+## Rudimentary
 
@@
 A 5% error rate would imply collecting `r power_n_95` participants.
+
+## Detailed: Simple
+
+```{r}
+population <- 
+  "
+  # Fix means to 0
+  HEX_HOH_SIN_01 ~ 0*1
+  HEX_HOH_SIN_02 ~ 0*1
+  HEX_HOH_SIN_03 ~ 0*1
+  HEX_HOH_SIN_04 ~ 0*1
+  NFP_PHY_01 ~ 0*1
+  NFP_PHY_02 ~ 0*1
+  NFP_PHY_03 ~ 0*1
+  NFP_PHY_04 ~ 0*1
+
+  # Fix variances
+  HEX_HOH_SIN_01 ~~ 1 * HEX_HOH_SIN_01
+  HEX_HOH_SIN_02 ~~ 1 * HEX_HOH_SIN_02
+  HEX_HOH_SIN_03 ~~ 1 * HEX_HOH_SIN_03
+  HEX_HOH_SIN_04 ~~ 1 * HEX_HOH_SIN_04
+  NFP_PHY_01 ~~ 1 * NFP_PHY_01
+  NFP_PHY_02 ~~ 1 * NFP_PHY_02
+  NFP_PHY_03 ~~ 1 * NFP_PHY_03
+  NFP_PHY_04 ~~ 1 * NFP_PHY_04
+
+  # Define latent vars
+  HEX_HOH_SIN =~ .9*HEX_HOH_SIN_01 + .9*HEX_HOH_SIN_02 + .9*HEX_HOH_SIN_03 + .9*HEX_HOH_SIN_04
+  NFP_PHY =~ .9*NFP_PHY_01 + .9*NFP_PHY_02 + .9*NFP_PHY_03 + .9*NFP_PHY_04
+
+  # Covariances
+  HEX_HOH_SIN ~~ .1*NFP_PHY
+  "
+sample <- "
+  HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
+  NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
+"
+
+reliability <- sim(
+  # nRep = NULL, 
+  model = sample, 
+#  n = 500,
+  n = seq(500, 5000, 50), 
+  generate = population, 
+  # std.lv = TRUE, 
+  lavaanfun = "sem"
+  )
+
+summary(reliability)
+power_tab <- getPower(reliability)
+power_80 <- findPower(power_tab, "N", 0.90)
+power_80["HEX_HOH_SIN~~NFP_PHY"]
+```
 
@@
 
+# make figure
 reg_fig <- ggplot(tab_reg, aes(x = Estimate, y = Predictor)) + 

### 2023-11-16 analysis_pipeline.Rmd
- implemented feedback from reviewers

@@
 
-# Model Fit
+# Factorial validity
 
- - If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariance or cross-loadings if theoretically plausible. 
- - If these changes do not yield sufficient fit, we will drop malfunctioning items. 
- - If fit is still subpar, we will conduct exploratory factor analyses (EFA) to asssess the underlying factor structure. 
+We will inspect the factorial validity of the privacy and personality variables as follows.
+
+ - We run a model with all personality and privacy variables as we originally configured them in a confirmatory factor analysis.
+ - If model fit is below the criteria, we will first inspect modification indices, potentially allowing covariances or cross-loadings if theoretically plausible. 
+ - If these changes do not yield sufficient fit, we will drop malfunctioning items, while having at least three items per dimension/facet.
+ - If this should not work out, we will run Exploratory Structural Equation Modelling using oblimin rotation, allowing all personality items to load on the same factors, while allowing all privacy items to load on the same factors.
+ - If fit is still subpar, we will conduct in-depth exploratory factor analyses (EFA) to asssess the underlying factor structure. 
  - EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 

### 2023-11-16 proposal.Rmd
- implemented feedback from reviewers

@@
 Need for privacy will be measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy).
-A sample of 1,293 respondents representative of the U.S.
+A sample of 1,576 respondents representative of the U.S.
 in terms of age, gender, and ethnicity will be collected.
@@
 # classoption       : "man"
-output:
-  html_document:
-    toc: TRUE
-    toc_float:
-      collapsed: FALSE
-      toc_depth: 2
+output: html_document
+
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#       toc_depth: 2
 # output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
+
 header-includes:
@@
 packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
-              "magrittr", "papaja", "semPlot", "td", "tidyverse")
+              "magrittr", "papaja", "semPlot", "simsem", "td", "tidyverse")
 lapply(packages, library, character.only = TRUE)
@@
 <!-- which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016],  -->
-Privacy is a major topic of public discourse and academic interest [@dienlinPrivacyDeadLong2022].
+Privacy is a major topic of public discourse and academic interest [@dienlinPrivacyDeadLong2023].
 Yet despite its importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155].
@@
 <!-- Or do they have more to hide? -->
-Asking this question seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
-Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007]: People who oppose state surveillance only do so because they have something to hide, because if you have nothing to hide, you would have nothing to fear.
+Asking **these questions** seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
+Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007]: 
+Accordingly, people who oppose state surveillance only do so because they have something to hide---because if you have nothing to hide, you would have nothing to fear. 
 Is it true that people who desire more privacy are also more dishonest, greedy, or unfair? 
-Or are people simply less extroverted, more diligent, or more prudent? 
-With this paper, we seek to answer the following question: What can we learn about a person’s personality if they say they desire more privacy?
+Or are people simply less extraverted, more diligent, or more prudent? 
+With this paper, we seek to answer the following question: 
+What can we learn about a person’s personality if they say they desire more privacy?
 
@@
 @pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
-reserve, isolation, solitude, intimacy with friends, intimacy with family, and anonymity: 
+**reserve ("unwillingness to be with and talk with others, especially strangers", p.
+1293); isolation ("desire to be alone and away from others", p.
+1293), solitude ("being alone by oneself and free from observation by others", p.
+1293), intimacy with friends ("being alone with friends", p.
+1293), intimacy with family ("being alone with members of one's own family", p.
+1293), and anonymity ("wanting to go unnoticed in a crowd and not wishing to be the center of group attention", p.
+1293).**
 <!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
@@
 -->
-Building on this work, in this study we employ a multifaceted model of need for privacy. 
-We focus on _vertical_ privacy with regard to people’s felt need for withdrawal from (a) government surveillance and (b) private companies; 
+**Building on these understandings of privacy,** in this study we employ a multifaceted model of need for privacy. 
+We focus on _vertical_ privacy with regard to people’s felt need for **withdrawal from surveillance by a) the government and b) private companies;** 
 _horizontal_ privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
 and _general_ privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
+**Although all of these dimensions were defined and established in prior research, combining these dimensions into one single comprehensive measure of privacy represents a novel approach.**
 
-We understand and measure personality using the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018]. 
-HEXACO is a large and comprehensive operationalization of personality, and thus is less likely to miss potentially relevant factors and facets than other personality constructs. 
+**Acknowledging that various understandings of personality exist, we operationalize personality using the factors and facets of the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].**
+HEXACO is a large and comprehensive operationalization of personality, and thus is less likely to miss potentially relevant aspects than other operationalizations. 
 The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
@@
 
-So far, very few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
+So far, only few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
 Moreover, we are not aware of a viable theory specifically connecting privacy and personality.
@@
 @westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
-Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], and so it is hence important for social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
+Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], and thereby social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
 But privacy can also have negative aspects. 
@@
 And privacy can also help conceal wrongdoing or crime.
-As a general guiding principle based on an evolutionary perspective, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
-Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
+
+<!-- **To understand why people desire privacy, we can also adopt an evolutionary perspective.** -->
+**Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].**
+**Confronted with a threat---for example, the prototypical a tiger---people are inclined to withdraw.**
+**In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.**
+**Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.**
+**Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].**
+
 In what follows, we briefly present each HEXACO factor and how it might relate to need for privacy.
@@
 Honesty-humility consists of the facets sincerity, fairness, greed avoidance, and modesty. 
-The meta-facet altruism measures benevolence toward others and consists of items such as “It wouldn’t bother me to harm someone I didn’t like.” 
+The meta-facet altruism measures benevolence toward others and consists of items such as “It wouldn't bother me to harm someone I didn’t like” (reversed).  
 According to the nothing-to-hide argument, a person desiring more privacy might be less honest, sincere, fair, or benevolent. 
 People who commit crimes likely face greater risk from some types of self-disclosure, because government agencies and people would enforce sanctions if their activities were revealed [@petronioCommunicationPrivacyManagement2010].
-Hence, in those cases the government and other people may be perceived as a threat. 
+In those cases, the government and other people may be perceived as a threat. 
 As a consequence, people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
@@
 
-In conclusion, it seems possible that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies. 
+**On the other hand, the nothing-to-hide argument has often been criticized, arguing that everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].**
+**A recent study confirmed this notion, finding that also those people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].**
+
+Taken together, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies.
 <!-- , as governments have the legitimate power to prosecute illegal activities.  -->
@@
 Anxious people might hence desire more privacy. 
-People who are more concerned about their privacy (in other words, more anxious about privacy) may be more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016a].
+People who are more concerned about their privacy (in other words, more anxious about privacy) may be more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
 On the other hand, the opposite may also be true: 
@@
 
-This hypothesis is supported by several empirical studies. 
+This **assumption** is supported by several empirical studies. 
 People who scored higher on the personality meta-factor plasticity, which is a composite of the two personality factors extraversion and openness, were found to desire less privacy [@mortonMeasuringInherentPrivacy2013].
@@
 
-As a result, we hypothesize that people who are more extroverted also need less social privacy and less privacy in general.
-Regarding the other dimensions of privacy, such as privacy from governments or from companies, we do not pose specific hypotheses.
+As a result, we **expect** that people who are more extraverted also need less social privacy and less privacy in general.
+Regarding the other dimensions of privacy, such as privacy from governments or from companies, we do not expect specific effects.
 
@@
 Thus, because need for privacy and privacy concern are closely related, more agreeable people might desire less privacy. 
-It is also possible that people higher in agreeableness hold more generous attitudes toward others and are less suspicious that others have malicious motives, and consequently perceive less risk from interacting with others.
+To explain, more agreeable people might hold more generous attitudes toward others and are less suspicious that others have malicious motives, and consequently perceive less risk from interacting with others.
 
@@
 Empirical studies have found that people with a stronger control motive require slightly more seclusion (_r_ = .12) and anonymity (_r_ = .15) [@hosmanRelationshipsNeedPrivacy1991].
-People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018b]. 
+People who considered their privacy at risk are less likely to disclose information online [e.g., @bolUnderstandingEffectsPersonalization2018]. 
 Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008]. 
@@
 In one study it was found that more educated people have more knowledge about how to protect their privacy [@parkDigitalLiteracyPrivacy2013], which could be the result of an increased need for privacy.
-In another study, openness to experience is positively related to privacy concern [@junglasPersonalityTraitsConcern2008]
+Similarly, openness to experience is positively related to privacy concern [@junglasPersonalityTraitsConcern2008].
 
@@
 The need for privacy should also be related to sociodemographic aspects, such as sex, age, education, and income. 
-For example, a study of 3,072 people from Germany found that women desired more informational and physical privacy than men, whereas men desired more psychological privacy [@frenerDevelopmentValidationNeed2021].
+For example, a study of 3,072 people from Germany found that women desired more informational and physical privacy than men, whereas men desired more psychological privacy [@frenerDevelopmentValidationNeed2023].
 In a nationally representative study of the U.S. and Japan, people who were older and who had higher income reported more privacy concern. 
@@
 We will also explore whether a person’s romantic relationship status corresponds to their expressed need for privacy.
+
+### Overview of expectations
+
+**In what follows, we summarize the aforementioned points. **
+**We will order our expectations, beginning with those relationships where we have higher certainty in identifying significant effects.**
+**First, we strongly assume that people more extraverted will desire less privacy, especially less social privacy.**
+**We also expect that people who are less honest will need more privacy.**
+**Females likely need more informational and physical privacy, while males will likely report needing more psychological privacy.**
+**Older people are also expected to need more privacy, as do more affluent people.**
+**We assume that more conscientious people will desire more privacy.**
+**We could imagine that more agreeable people might desire less privacy.**
+**It seems largely unclear how privacy needs relate to openness to experiences and emotionality.**
 
@@
 We hence decided to treat our prior project as a pilot study and to address the criticism by conducting a new study.
-In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together and established need for privacy measures, and overall adopt a more exploratory perspective.
+In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together with established need for privacy measures, and overall adopt a more exploratory perspective.
 Being our central construct of interest, we also develop a small number of new items to have a more comprehensive measure of need for privacy.
@@
 
-To determine sample size, we ran a priori power analyses. 
-Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain. 
-We therefore conducted preliminary power analyses using two-sided bivariate correlations. 
-Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size.
-We based our power analysis on a smallest effect size of interest (SESOI).
+**To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].**
+We based our power analysis on a smallest effect size of interest (SESOI; see also below).
 We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992].
+<!-- Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain.
+-->
+<!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
+**We simulated data, set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10, and the latent factor loadings to be $\lambda$ = .85 (the SESOI)**
+<!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
 <!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
-Adopting an exploratory perspective, not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant. 
-We hence opted for balanced alpha and beta errors of 5%.
-A power analysis with an alpha and beta error of 5% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_n_95 %>% round(0)`.
+**Adopting an exploratory perspective, not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].**
+**Because balanced alpha and beta errors of 5% were outside of our budget, we opted for balanced alpha and beta errors of 10%.**
+**A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.**
+**To account for potential attrition (see below), we will oversample by five percent, leading to a final sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.**
 We obtained sufficient funding to collect a sample of this size.
-Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 5% and an effect size of at least _r_ = .10.
+<!-- Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 10% and an effect size of at least _r_ = .10.  -->
+
+## Exclusions and Imputation
+
+**We will individually check answers for response patterns such as straight-lining or missing of inverted items.**
+**We will conservatively remove participants with clear response patterns.**
+**We will automatically exclude participants who miss the two attention checks we will implement.**
+**Participants who miss one attention check will be checked individually regarding response patterns.**
+**We will remove participants below the minimum participation age of 18 years.**
+**We will remove respondents with unrealistically fast responses (three standard deviations below the median response time).** 
+<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->
+
+**Missing responses will be imputed using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10).** 
+**The analyses will be run with all ten datasets, and the pooled results will be reported.**
 
@@
 
-We will individually check answers for response patterns such as straight-lining or missing of inverted items.
-We will conservatively remove participants with clear response patterns. 
-We will automatically exclude participants who miss the two attention checks we will implement.
-Participants who miss one attention check will be checked individually regarding response patterns. 
-We will remove participants below the minimum participation age of 18 years. 
-We will remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
-<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->
-
-Missing responses will be imputed using multiple imputation with predictive mean matching (five datasets, five iterations, using all variables). 
-The analyses will be run with all five datasets, and the pooled results will be reported.
-
 <!-- We will test items for potential ceiling and floor effects.  -->
 <!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
-The factorial validity of the measures and the hypotheses will be tested using structural equation modeling. 
+The factorial validity of the measures and the relations will be tested using structural equation modeling. 
 If Mardia’s test shows that the assumption of multivariate normality is violated, we will use the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator. 
@@
 
+**We will use two measures as inference criterion: statistical significance and effect size.** 
+**Regarding statistical significance, we will use an alpha value of 10%.**
+**Regarding effect size, we will define a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.**
+**As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25).**
+**We will consider effects irrelevant if the confidence interval falls completely within the null region (e.g., .02 to .08).**
+**And we will suspend judgement if the confidence intervals partially include the null region (e.g., .05 to .15).**
+
 Fully latent SEMs seldom work instantly, often requiring modifications to achieve satisfactory model fit.
@@
 We decided to use fully latent SEMs because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
-Combining several items into a latent factors helps reduce error and condense information, thereby reducing noise.
-Together, this should provide a better measure of the latent variables, which will also reduce the beta error. 
+Combining several items into latent factors helps reduce noise and thereby the beta error. 
 To provide context, in the online supplementary material (OSM) we will also share the results of alternative analyses, such as correlations of average scores.
@@
 
-Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2021; @marshallDimensionsPrivacyPreferences1974], we are not aware of one encompassing, comprehensive, and up-to-date scale.
+Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2023; @marshallDimensionsPrivacyPreferences1974], we are not aware of one encompassing, comprehensive, and up-to-date scale.
 Hence, we use both existing scales and self-developed items, some of which were tested in our pilot study. 
@@
 We (a) collected qualitative feedback from three different privacy experts;[^experts]
-(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2021, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.
+(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.
 
@@
 Overall, we will collect 32 items measuring need for privacy, with eight subdimensions that all consist of four items each. 
-Three subdimensions capture horizontal privacy---namely psychological, social, and physical privacy from other individuals. 
-Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2021.
-Because @frenerDevelopmentValidationNeed2021 could not successfully operationalize the dimension of social privacy, building on @burgoonPrivacyCommunication1982 we self-designed a new social privacy dimension, which in the prestudy showed satisfactory fit.
+Three subdimensions capture horizontal privacy---namely _psychological_, _social_, and _physical_ privacy from other individuals. 
+Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2023.
+Because @frenerDevelopmentValidationNeed2023 could not successfully operationalize the dimension of social privacy, building on @burgoonPrivacyCommunication1982 we self-designed a new social privacy dimension, which in the prestudy showed satisfactory fit.
 Two subdimensions measure vertical privacy.
-The first subdimension is government surveillance, which represents the extent to which people want the government to abstain from collecting information about them. 
+The first subdimension is _government surveillance_, which represents the extent to which people want the government to abstain from collecting information about them. 
 The scale was pretested and showed good factorial validity. 
-The second subdimension is need for privacy from companies, which we will measure using four new self-designed items.
+The second subdimension is need for privacy from _companies_, which we will measure using four new self-designed items.
 Finally, three subdimensions capture general privacy. 
-The first subdimension is informational privacy, with items adopted from @frenerDevelopmentValidationNeed2021.
-The second subdimension is anonymity, which captures the extent to which people feel the need to avoid identification in general.
+The first subdimension is _informational_ privacy, with items adopted from @frenerDevelopmentValidationNeed2023.
+The second subdimension is _anonymity_, which captures the extent to which people feel the need to avoid identification in general.
 The scale was pretested and showed good factorial validity; one new item was designed for this study.
-Third, we will also collect a new self-developed measure of general need for privacy.
+Third, we will also collect a new self-developed measure of _general_ need for privacy.
 
@@
 Personality will be measured using the HEXACO personality inventory. 
-The inventory consists of six factors with four dimensions each, including the additional meta scale of "altruism".
+The inventory consists of six factors with four facets each, including the additional meta scale of "altruism".
 
@@
 
-In Figure \@ref(fig:fig-reg), you can find how each personality factor---while holding constant for all other personality factors and sociodemographics---predicts need for privacy.
+In Figure \@ref(fig:fig-reg), you can find how each personality factor---while holding constant all other personality factors and sociodemographics---predicts need for privacy.
 
-```{r fig-reg, fig.cap="Results of multiple regressions, in which we predict all dimensions of need for privacy using all personality dimensions and sociodemgraphic factors simultaneously.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='H'}
+```{r fig-reg, fig.cap="Results of multiple regressions, in which we predict all dimensions of need for privacy using all personality facets and sociodemgraphic factors simultaneously.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='H'}
 # fig_desc

### 2023-11-20 proposal.Rmd
- Implemented Miriam's feedback

@@
 # classoption       : "man"
-output: html_document
-
-# output:
-#   html_document:
-#     toc: TRUE
-#     toc_float:
-#       collapsed: FALSE
-#       toc_depth: 2
-# output            : papaja::apa6_pdf
+# output: html_document
+output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 Asking **these questions** seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
-Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007]: 
-Accordingly, people who oppose state surveillance only do so because they have something to hide---because if you have nothing to hide, you would have nothing to fear. 
+Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007], which is that people who oppose state surveillance only do so because they have something to hide---because if you have nothing to hide, you would have nothing to fear.
 Is it true that people who desire more privacy are also more dishonest, greedy, or unfair? 
@@
 @pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
-**reserve ("unwillingness to be with and talk with others, especially strangers", p.
-1293); isolation ("desire to be alone and away from others", p.
-1293), solitude ("being alone by oneself and free from observation by others", p.
-1293), intimacy with friends ("being alone with friends", p.
-1293), intimacy with family ("being alone with members of one's own family", p.
-1293), and anonymity ("wanting to go unnoticed in a crowd and not wishing to be the center of group attention", p.
+**reserve ("unwillingness to be with and talk with others, especially strangers," p.
+1293); isolation ("desire to be alone and away from others," p.
+1293), solitude ("being alone by oneself and free from observation by others," p.
+1293), intimacy with friends ("being alone with friends," p.
+1293), intimacy with family ("being alone with members of one's own family," p.
+1293), and anonymity ("wanting to go unnoticed in a crowd and not wishing to be the center of group attention," p.
 1293).**
@@
 
-In order to understand how personality might relate to privacy, we can ask ourselves the following question: 
+In order to understand how personality might relate to privacy, we can ask the following question: 
 Why do people desire privacy?
@@
 <!-- **To understand why people desire privacy, we can also adopt an evolutionary perspective.** -->
-**Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].**
+**Privacy also has strong evolutionary roots [@acquistiHowPrivacyMay2022].**
 **Confronted with a threat---for example, the prototypical a tiger---people are inclined to withdraw.**
@@
 **Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].**
+**Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities.**
+**Indeed, the need for privacy may have evolved precisely because it offers such advantages.**
 
@@
 According to the nothing-to-hide argument, a person desiring more privacy might be less honest, sincere, fair, or benevolent. 
-People who commit crimes likely face greater risk from some types of self-disclosure, because government agencies and people would enforce sanctions if their activities were revealed [@petronioCommunicationPrivacyManagement2010].
+People who commit crimes likely face greater risk from some types of self-disclosure because government agencies and people would enforce sanctions if their activities were revealed [@petronioCommunicationPrivacyManagement2010].
 In those cases, the government and other people may be perceived as a threat. 
-As a consequence, people with lower honesty and humility might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
+As a consequence, people with lower honesty and sincerity might desire more privacy as a means to mitigate their felt risk [@altmanPrivacyConceptualAnalysis1976].
 
@@
 
-**On the other hand, the nothing-to-hide argument has often been criticized, arguing that everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].**
+**We do not mean to suggest that it is only dishonest people who feel a need for privacy.**
+**Everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].**
 **A recent study confirmed this notion, finding that also those people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].**
-
-Taken together, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies.
+**Our argument is rather that people lower on the honesty HEXACO factor may feel a greater need for privacy.**
+Considering all the evidence, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies.
 <!-- , as governments have the legitimate power to prosecute illegal activities.  -->
@@
 
-**In what follows, we summarize the aforementioned points. **
-**We will order our expectations, beginning with those relationships where we have higher certainty in identifying significant effects.**
-**First, we strongly assume that people more extraverted will desire less privacy, especially less social privacy.**
-**We also expect that people who are less honest will need more privacy.**
-**Females likely need more informational and physical privacy, while males will likely report needing more psychological privacy.**
-**Older people are also expected to need more privacy, as do more affluent people.**
-**We assume that more conscientious people will desire more privacy.**
-**We could imagine that more agreeable people might desire less privacy.**
-**It seems largely unclear how privacy needs relate to openness to experiences and emotionality.**
+**The arguments discussed above lead to a number of expectations for our data which we delineate below, in order from most to least confidence in terms of identifying significant effects.**
+**First, we strongly assume that more extraverted people will desire less privacy, especially less social privacy.**
+**We also expect that people who are less honest will express greater need for privacy.**
+**We further assume that more conscientious people will desire more privacy and that more agreeable people may desire less privacy.**
+**Yet it is largely unclear how privacy needs relate to openness to experience and emotionality.**
+**In terms of the sociodemographic variables, we expect females likely need more informational and physical privacy, while males will likely report needing more psychological privacy.**
+**Older, more highly educated, and affluent people are also expected to need more privacy, and we anticipate that people who are ethnic minorities or are politically conservative will express greater need for privacy from the government than from other people.**
 
@@
 <!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
-**We simulated data, set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10, and the latent factor loadings to be $\lambda$ = .85 (the SESOI)**
+**To estimate power, we simulated data."
+**We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10.**
+**We, furthermore, set the latent factor loadings to be $\lambda$ = .85 (the SESOI)**
 <!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
 <!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
-**Adopting an exploratory perspective, not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].**
-**Because balanced alpha and beta errors of 5% were outside of our budget, we opted for balanced alpha and beta errors of 10%.**
+**Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].**
+**Because balanced alpha and beta errors of 5% are outside of our budget, we opted for balanced alpha and beta errors of 10%.**
 **A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.**
@@
 
-**We will use two measures as inference criterion: statistical significance and effect size.** 
+**We will use two measures as inference criteria: statistical significance and effect size.** 
 **Regarding statistical significance, we will use an alpha value of 10%.**
 **Regarding effect size, we will define a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.**
-**As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25).**
+**As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25 or -.15 to -.25).**
 **We will consider effects irrelevant if the confidence interval falls completely within the null region (e.g., .02 to .08).**

### 2024-02-07 analyses.RmD
- Collected and analzed data - Wrote results and discussion section

--- 2023-03-07 analyses.RmD
@@
 set.seed(170819)
-knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
-                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
-options(digits = 3, width = 90)
+
+knitr::opts_chunk$set(
+  warning=F, 
+  echo=F, 
+  error=F, 
+  message=F, 
+  cache = T, 
+  tidy=T, 
+  dev = 'pdf', 
+  cache.extra = knitr::rand_seed
+  )
+
+options(
+  digits = 3, 
+  width = 150,
+  max.print = 100000000
+  )
 ```
@@
 
-- At this point, we haven't yet collected data. 
-- The results below use simulated data. 
-- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
-- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit or imputation of missing data.
-
 # Set-Up
+## Packages
 
@@
 
-# define packages
-packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
-              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
-              "pwr", "semPlot", "semTools", "tidyverse", "td")
-
-# load packages
-lapply(packages, library, character.only = TRUE)
-
-# readability function
-readability = function(data){
-  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
-  textstat_readability(data, measure = reading_estimates) %>% 
-    as.data.frame %>% 
-    mutate(average = rowMeans(select(., -document)))
-}
+library(confintr)
+library(corrplot)
+library(devtools)
+library(easystats)
+library(GGally)
+library(ggplot2)
+library(haven)
+library(kableExtra)
+library(knitr)
+library(lavaan)
+library(magrittr)
+library(mice)
+library(MVN)
+library(naniar)
+library(PerFit)
+library(psych)
+library(quanteda.textstats)
+library(pwr)
+library(semPlot)
+library(sjlabelled)
+library(simsem)
+library(semTools)
+library(tidyverse)
+library(td)
+
+load("data/workspace_1.RData")
+source("custom_functions.R")
 ```
@@
 ```{r data-wrangling}
-d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
-d <- rename(d, COL = COL_, REL = REL_)
-
+# d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
+d_raw <- sjlabelled::read_spss(
+  "data/Need+for+Privacy_February+6%2C+2024_15.56.sav",
+  convert.factors = FALSE
+  )
+```
+
+### Data-Wrangling
+
+```{r data-inverting}
+vars_invert <- c(
+  "HEX_HOH_SIN_01", "HEX_HOH_SIN_03",
+  "HEX_HOH_FAI_01", "HEX_HOH_FAI_02", "HEX_HOH_FAI_04",
+  "HEX_HOH_GRE_02", "HEX_HOH_GRE_03", "HEX_HOH_GRE_04",
+  "HEX_HOH_MOD_03", "HEX_HOH_MOD_04",
+  "HEX_EMO_FEA_02", "HEX_EMO_FEA_04",
+  "HEX_EMO_ANX_02", "HEX_EMO_ANX_03",
+  "HEX_EMO_DEP_02", "HEX_EMO_DEP_04",
+  "HEX_EMO_SEN_04",
+  "HEX_EXT_SSE_03", "HEX_EXT_SSE_04",
+  "HEX_EXT_BOL_01", "HEX_EXT_BOL_04",
+  "HEX_EXT_SOC_01",
+  "HEX_EXT_LIV_03", "HEX_EXT_LIV_04",
+  "HEX_AGR_FOR_03", "HEX_AGR_FOR_04",
+  "HEX_AGR_GEN_01",
+  "HEX_AGR_FLX_01", "HEX_AGR_FLX_03", "HEX_AGR_FLX_04",
+  "HEX_AGR_PAT_01", "HEX_AGR_PAT_04",
+  "HEX_CNS_ORG_03", "HEX_CNS_ORG_04",
+  "HEX_CNS_DIL_03", "HEX_CNS_DIL_04",
+  "HEX_CNS_PER_02",
+  "HEX_CNS_PRU_01", "HEX_CNS_PRU_02", "HEX_CNS_PRU_04",
+  "HEX_OPN_AES_01", "HEX_OPN_AES_02",
+  "HEX_OPN_INQ_03", "HEX_OPN_INQ_04",
+  "HEX_OPN_CRE_01", "HEX_OPN_CRE_04",
+  "HEX_OPN_UNC_01", "HEX_OPN_UNC_04",
+  "HEX_ALT_03", "HEX_ALT_04",
+  "NFP_COM_02"
+)
+
+d <-
+  d_raw %>% 
+  rename(
+    COL = COL_,
+    REL = REL_
+    ) %>%
+  mutate(
+    across(all_of(vars_invert),
+    ~ 8 - .x
+         ),
+    male = case_match(
+      GEN,
+      c(2, 3) ~ 0,
+      1 ~ 1),
+    age = case_match(
+      AGE,
+      1 ~ 1,
+      2 ~ 2,
+      3 ~ 3,
+      4 ~ 4,
+      5 ~ 7,
+      6 ~ 5,
+      7 ~ 6),
+    white = case_match(
+      ETH,
+      2 ~ 0,
+      1 ~ 1),
+    relation = case_match(
+      REL,
+      2 ~ 1,
+      1 ~ 0),
+    college = case_match(
+      COL,
+      2 ~ 1,
+      1 ~ 0),
+    conserv = CON,
+    income = INC
+  ) 
+```
+
+### Labels
+
+```{r data-labels}
 # define vars and labels
+vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")
+vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")
+
 vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
+                   "HEX_ALT",
                    "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
@@
                    "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
-                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC", 
-                   "HEX_ALT")
+                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
 vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
+                       "Altruism",
                        "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
@@
                        "Organization", "Diligence", "Perfectionism", "Prudence", 
-                       "Aesthetic appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
-                       "Altruism")
+                       "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality")
+
+vars_pers_hoh <- 
+  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")
+vars_pers_emo <- 
+  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")
+vars_pers_ext <- 
+  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")
+vars_pers_agr <- 
+  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")
+vars_pers_cns <- 
+  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")
+vars_pers_opn <- 
+  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
+
+vars_pers_all <- 
+  c(
+    vars_pers_hoh, 
+    vars_pers_emo, 
+    vars_pers_ext, 
+    vars_pers_agr, 
+    vars_pers_cns,
+    vars_pers_opn
+    )
+
+vars_pers_all_txt <- 
+  c("Honesty humility", 
+      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
+    "Emotionality", 
+      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
+    "Extraversion",
+      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
+    "Agreeableness",
+      "Forgiveness", "Gentleness", "Flexibility", "Patience",
+    "Conscientiousness",
+      "Organization", "Diligence", "Perfectionism", "Prudence", 
+    "Openness",
+      "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
+    )
+
+vars_pred_all_txt <- 
+  c(
+    vars_pers_all_txt,
+    vars_ses_txt
+    )
 
@@
 
-vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
+vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
               "NFP_GOV", "NFP_COM", 
               "NFP_INF", "NFP_ANO", "NFP_GEN")
-vars_pri_txt <- c("Social", "Physical", "Psychological",
-                  "Companies", "Governnment",
-                  "Anonynmity", "Infornmational", "General")
-vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
-                  "Companies", "Govern-\nment",
-                  "Anony-\nmity", "Infor-\nmational", "General")
-vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
-                  "Comp.", "Gov.",
-                  "Anonym.", "Inform.", "General")
-
-vars_ses <- c("AGE", "GEN", "ETH", "REL", "COL", "INC", "CON")
-vars_ses_txt <- c("Age", "Gender", "Ethnicity", "Relationship", "College", "Income", "Conservatism")
-```
+vars_pri_txt <- c("Psychological", "Social", "Physical", 
+                  "Government", "Companies", 
+                  "Informational", "Anonymity", "General")
+vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
+                  "Govern-\nment", "Companies", 
+                  "Infor-\nmational", "Anony-\nmity", "General")
+vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
+                  "Gov.", "Comp.", 
+                  "Inform.", "Anonym.", "General")
+
+vars_pers_pri <- c(vars_pers_fac, vars_pri)
+```
+
+## Means
+
+```{r}
+# Person means per facet
+
+d %<>%
+  mutate(
+    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
+    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
+    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
+    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
+    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
+    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
+    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
+    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
+    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
+    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
+    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
+    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
+    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
+    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
+    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
+    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
+    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
+    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
+    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
+    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
+    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
+    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
+    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
+    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
+    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
+    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
+    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
+    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
+    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
+    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
+    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
+    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
+    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
+    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
+    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
+    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
+    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
+    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
+    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
+  )
+
+# item means
+c_m <- 
+  c(
+    HEX_ALT_m     = mean(d$HEX_ALT_M, na.rm = T),
+    HEX_AGR_FLX_m = mean(d$HEX_AGR_FLX_M, na.rm = T),
+    HEX_AGR_FOR_m = mean(d$HEX_AGR_FOR_M, na.rm = T),
+    HEX_AGR_GEN_m = mean(d$HEX_AGR_GEN_M, na.rm = T),
+    HEX_AGR_PAT_m = mean(d$HEX_AGR_PAT_M, na.rm = T),
+    HEX_CNS_DIL_m = mean(d$HEX_CNS_DIL_M, na.rm = T),
+    HEX_CNS_ORG_m = mean(d$HEX_CNS_ORG_M, na.rm = T),
+    HEX_CNS_PER_m = mean(d$HEX_CNS_PER_M, na.rm = T),
+    HEX_CNS_PRU_m = mean(d$HEX_CNS_PRU_M, na.rm = T),
+    HEX_EMO_ANX_m = mean(d$HEX_EMO_ANX_M, na.rm = T),
+    HEX_EMO_DEP_m = mean(d$HEX_EMO_DEP_M, na.rm = T),
+    HEX_EMO_FEA_m = mean(d$HEX_EMO_FEA_M, na.rm = T),
+    HEX_EMO_SEN_m = mean(d$HEX_EMO_SEN_M, na.rm = T),
+    HEX_EXT_BOL_m = mean(d$HEX_EXT_BOL_M, na.rm = T),
+    HEX_EXT_LIV_m = mean(d$HEX_EXT_LIV_M, na.rm = T),
+    HEX_EXT_SOC_m = mean(d$HEX_EXT_SOC_M, na.rm = T),
+    HEX_EXT_SSE_m = mean(d$HEX_EXT_SSE_M, na.rm = T),
+    HEX_HOH_FAI_m = mean(d$HEX_HOH_FAI_M, na.rm = T),
+    HEX_HOH_GRE_m = mean(d$HEX_HOH_GRE_M, na.rm = T),
+    HEX_HOH_MOD_m = mean(d$HEX_HOH_MOD_M, na.rm = T),
+    HEX_HOH_SIN_m = mean(d$HEX_HOH_SIN_M, na.rm = T),
+    HEX_OPN_AES_m = mean(d$HEX_OPN_AES_M, na.rm = T),
+    HEX_OPN_CRE_m = mean(d$HEX_OPN_CRE_M, na.rm = T),
+    HEX_OPN_INQ_m = mean(d$HEX_OPN_INQ_M, na.rm = T),
+    HEX_OPN_UNC_m = mean(d$HEX_OPN_UNC_M, na.rm = T),
+    NFP_ANO_m     = mean(d$NFP_ANO_M, na.rm = T),
+    NFP_COM_m     = mean(d$NFP_COM_M, na.rm = T),
+    NFP_GEN_m     = mean(d$NFP_GEN_M, na.rm = T),
+    NFP_GOV_m     = mean(d$NFP_GOV_M, na.rm = T),
+    NFP_INF_m     = mean(d$NFP_INF_M, na.rm = T),
+    NFP_PHY_m     = mean(d$NFP_PHY_M, na.rm = T),
+    NFP_PSY_m     = mean(d$NFP_PSY_M, na.rm = T),
+    NFP_SOC_m     = mean(d$NFP_SOC_M, na.rm = T),
+    HEX_HOH_m     = mean(d$HEX_HOH_M, na.rm = T),
+    HEX_EMO_m     = mean(d$HEX_EMO_M, na.rm = T),
+    HEX_EXT_m     = mean(d$HEX_EXT_M, na.rm = T),
+    HEX_AGR_m     = mean(d$HEX_AGR_M, na.rm = T),
+    HEX_CNS_m     = mean(d$HEX_CNS_M, na.rm = T),
+    HEX_OPN_m     = mean(d$HEX_OPN_M, na.rm = T)
+  )
+
+# item standard deviation
+c_sd <- 
+  c(
+    HEX_ALT_sd     = sd(d$HEX_ALT_M, na.rm = T),
+    HEX_AGR_FLX_sd = sd(d$HEX_AGR_FLX_M, na.rm = T),
+    HEX_AGR_FOR_sd = sd(d$HEX_AGR_FOR_M, na.rm = T),
+    HEX_AGR_GEN_sd = sd(d$HEX_AGR_GEN_M, na.rm = T),
+    HEX_AGR_PAT_sd = sd(d$HEX_AGR_PAT_M, na.rm = T),
+    HEX_CNS_DIL_sd = sd(d$HEX_CNS_DIL_M, na.rm = T),
+    HEX_CNS_ORG_sd = sd(d$HEX_CNS_ORG_M, na.rm = T),
+    HEX_CNS_PER_sd = sd(d$HEX_CNS_PER_M, na.rm = T),
+    HEX_CNS_PRU_sd = sd(d$HEX_CNS_PRU_M, na.rm = T),
+    HEX_EMO_ANX_sd = sd(d$HEX_EMO_ANX_M, na.rm = T),
+    HEX_EMO_DEP_sd = sd(d$HEX_EMO_DEP_M, na.rm = T),
+    HEX_EMO_FEA_sd = sd(d$HEX_EMO_FEA_M, na.rm = T),
+    HEX_EMO_SEN_sd = sd(d$HEX_EMO_SEN_M, na.rm = T),
+    HEX_EXT_BOL_sd = sd(d$HEX_EXT_BOL_M, na.rm = T),
+    HEX_EXT_LIV_sd = sd(d$HEX_EXT_LIV_M, na.rm = T),
+    HEX_EXT_SOC_sd = sd(d$HEX_EXT_SOC_M, na.rm = T),
+    HEX_EXT_SSE_sd = sd(d$HEX_EXT_SSE_M, na.rm = T),
+    HEX_HOH_FAI_sd = sd(d$HEX_HOH_FAI_M, na.rm = T),
+    HEX_HOH_GRE_sd = sd(d$HEX_HOH_GRE_M, na.rm = T),
+    HEX_HOH_MOD_sd = sd(d$HEX_HOH_MOD_M, na.rm = T),
+    HEX_HOH_SIN_sd = sd(d$HEX_HOH_SIN_M, na.rm = T),
+    HEX_OPN_AES_sd = sd(d$HEX_OPN_AES_M, na.rm = T),
+    HEX_OPN_CRE_sd = sd(d$HEX_OPN_CRE_M, na.rm = T),
+    HEX_OPN_INQ_sd = sd(d$HEX_OPN_INQ_M, na.rm = T),
+    HEX_OPN_UNC_sd = sd(d$HEX_OPN_UNC_M, na.rm = T),
+    NFP_ANO_sd     = sd(d$NFP_ANO_M, na.rm = T),
+    NFP_COM_sd     = sd(d$NFP_COM_M, na.rm = T),
+    NFP_GEN_sd     = sd(d$NFP_GEN_M, na.rm = T),
+    NFP_GOV_sd     = sd(d$NFP_GOV_M, na.rm = T),
+    NFP_INF_sd     = sd(d$NFP_INF_M, na.rm = T),
+    NFP_PHY_sd     = sd(d$NFP_PHY_M, na.rm = T),
+    NFP_PSY_sd     = sd(d$NFP_PSY_M, na.rm = T),
+    NFP_SOC_sd     = sd(d$NFP_SOC_M, na.rm = T),
+    HEX_HOH_sd     = sd(d$HEX_HOH_M, na.rm = T),
+    HEX_EMO_sd     = sd(d$HEX_EMO_M, na.rm = T),
+    HEX_EXT_sd     = sd(d$HEX_EXT_M, na.rm = T),
+    HEX_AGR_sd     = sd(d$HEX_AGR_M, na.rm = T),
+    HEX_CNS_sd     = sd(d$HEX_CNS_M, na.rm = T),
+    HEX_OPN_sd     = sd(d$HEX_OPN_M, na.rm = T)
+  )
+```
+
+# Missing data
+
+First filter those who didn't finish the questionnaire.
+
+```{r}
+d %<>%
+  filter(
+    Progress == 100
+  )
+
+n_finished <- nrow(d)
+```
+
+Let's first inspect missing data.
+
+How many missing do we have?
+
+```{r}
+n_miss(d)
+prop_miss(d)
+```
+
+Only 23 cells are missing -- which is very little. To be precise, 0.00006 percent only.
+
+Which variables are affected?
+
+```{r}
+miss_var_summary(d) %>% 
+  head(19)
+```
+
+Missing answers vary randomly across variables.
+
+How about participants?
+
+```{r}
+miss_case_summary(d)
+```
+
+Only six participants with missing data, and even then, not much. We hence decided to keep everyone.
+
+# Quality checks
+
+We preregistered to remove participants faster than 3 standard deviations than the median response time.
+
+```{r cache=F}
+# Median response time
+time_med <- median(d$Duration__in_seconds_)
+
+# Average response time
+time_m <- mean(d$Duration__in_seconds_) / 60
+
+# Standard deviation
+time_sd <- sd(d$Duration__in_seconds_)
+
+# filter speeders
+time_crit_init <- time_med - (3 * time_sd) # minimum time on survey
+```
+
+However, this made little sense. The median response time was `r time_med` and the standard deviation `r time_sd`. Hence, three SDs below median was `r time_crit_init`, hence not informative.
+
+Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
+
+```{r cache=F}
+time_crit <- 5 * 60
+
+# count number of speeders
+n_speeding <- 
+  nrow(
+    filter(
+      d, 
+      Duration__in_seconds_ < time_crit
+      )
+    )
+
+# Deletion of fast respondents
+d <- 
+  filter(
+    d, 
+    Duration__in_seconds_ >= time_crit
+    )
+
+n_used <- nrow(d)
+```
+
+Average response time was `r time_m %>% round(0)` minutes. We removed `r n_speeding` because they answered the survey unreasonably fast.
+
+Let's inspect for potential response patterns.
+
+# Sociodemographics
+
+To improve privacy, we didn't collect exact but binned measures of sociodemographics.
+
+Let's first inspect age. Here, the age categories were as follows:
+
+1: Under 18 years old
+2: 18-24 years old 
+3: 25-34 years old 
+4: 35-44 years old 
+5: 45-54 years old 
+6: 55-64 years old 
+7: 65+ years old
+
+```{r}
+table(d$AGE)
+```
+
+No person indicated being younger than 18 years old. Hence, everybody could be included.
+
+```{r}
+age_m <- 
+  mean(d$AGE)
+```
+
+The mean age was 45 to 54 years of age.
+
+Let's next inspect gender. Categories were:
+
+1: "Man" 
+2: "Woman" 
+3: "Third gender / Other"
+
+```{r}
+table(d$GEN) %>% 
+  prop.table() %>% 
+  round(2)
+```
+
+48 percent were male, 50 female, and 1 percent indicated third/other gender.
+
+Let's next inspect education. Categories were:
+
+1: "No college degree" 
+2: "College degree"
+
+```{r}
+table(d$COL) %>% 
+  prop.table() %>% 
+  round(2)
+```
+
+69% reported having a college degree.
+
+Let's next inspect ethnicity. Answer categories were as follows:
+
+1: "White"
+2: "Other"
+
+```{r}
+table(d$ETH) %>%
+  prop.table() %>% 
+  round(2)
+```
+
+78 % percent were white, 22 % not white.
 
@@
 (-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree
+
+## Ceiling/Floor effects
+
+Let's first check for ceiling and floor effects.
+
+```{r}
+d %>%
+  select(
+    paste0(rep(vars_pers_pri, each = 4), "_0", 1:4)
+  ) %>% 
+  apply(
+    2,  mean, na.rm = T
+  )
+```
+
+No item below floor (1.5) or ceiling (6.5) thresholds.
 
@@
 name <- "HEX_HOH_SIN"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
 model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is okay, but RMSEA is significantly above .10. Let's hence inspect modification indices to see if there are potential fixes.
+
+```{r}
+modindices(fit_HEX_HOH_SIN)
+```
+
+Suggests that item 1 & 3, and item 2 & 4 build subdimensions. Let's allow covariances.
+
+```{r}
+model <- 
+  "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
+  HEX_HOH_SIN_01 ~~ a*HEX_HOH_SIN_03
+  HEX_HOH_SIN_02 ~~ a*HEX_HOH_SIN_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now great.
 
@@
 name <- "HEX_HOH_FAI"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+
 model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
 
@@
 ```{r}
-name <- "HEY_HOH_GRE"
+name <- "HEX_HOH_GRE"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+
 model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is okaish, but RMSEA above .10. Let's inspect modification indices.
+
+```{r}
+modindices(fit_HEX_HOH_GRE)
+```
+
+Item 1 & 2, and item 3 & 4 form subdimensions.
+
+```{r}
+model <- "
+  HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
+  HEX_HOH_GRE_01 ~~ a*HEX_HOH_GRE_02
+  HEX_HOH_GRE_03 ~~ a*HEX_HOH_GRE_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now great.
 
@@
 name <- "HEX_HOH_MOD"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
 model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
+
+#### Honesty Humility
+
+Let's also look at the dimension itself.
+
+```{r}
+model_hex_hoh <- "
+# Personality Factors
+HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
+HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
+HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
+HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
+HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
+
+# Covariances
+HEX_HOH_SIN_01 ~~ HEX_HOH_SIN_03
+HEX_HOH_SIN_02 ~~ HEX_HOH_SIN_04
+HEX_HOH_GRE_01 ~~ HEX_HOH_GRE_02
+HEX_HOH_GRE_03 ~~ HEX_HOH_GRE_04
+"
+fit_hex_hoh <- sem(model_hex_hoh, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_hoh, standardized = TRUE, fit = TRUE)
 ```
@@
 name <- "HEX_EMO_FEA"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
 model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is great.
 
@@
 name <- "HEX_EMO_ANX"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+
 model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is great.
 
@@
 name <- "HEX_EMO_DEP"
-model <- "HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is bad; TLI and RMSEA outside thresholds.
+
+```{r}
+modindices(fit_HEX_EMO_DEP)
+```
+
+Not entirely clear. Let's allow items 1 & 4 to correlate, and items 2 & 3.
+
+```{r}
+model <- "
+HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+HEX_EMO_DEP_01 ~~ a*HEX_EMO_DEP_04
+HEX_EMO_DEP_02 ~~ a*HEX_EMO_DEP_03
+"
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit not great, but okay.
 
@@
 name <- "HEX_EMO_SEN"
-model <- "HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+
+model <- "
+HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit not terrible, but TLI and RSMEA outside of thresholds.
+
+```{r}
+modindices(fit_HEX_EMO_SEN)
+```
+
+Items 1 & 3, and items 2 & 4 want to covary.
+
+```{r}
+model <- "
+  HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+  HEX_EMO_SEN_01 ~~ a*HEX_EMO_SEN_03
+  HEX_EMO_SEN_02 ~~ a*HEX_EMO_SEN_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now good.
+
+#### Emotionality
+
+Let's look at overall dimension.
+
+```{r}
+model_hex_emo <- "
+HEX_EMO =~ HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN
+HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
+HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
+HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+HEX_EMO_DEP_01 ~~ HEX_EMO_DEP_04
+HEX_EMO_DEP_02 ~~ HEX_EMO_DEP_03
+HEX_EMO_SEN_01 ~~ HEX_EMO_SEN_03
+HEX_EMO_SEN_02 ~~ HEX_EMO_SEN_04
+"
+fit_hex_emo <- sem(model_hex_emo, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_emo, standardized = TRUE, fit = TRUE)
+```
+
+Fit is subpar. Let's inspect.
+
+```{r}
+modindices(fit_hex_emo, minimum.value = 40)
+```
+
+Suggests one major cross-loading:
+
+ - HEX_EMO with	HEX_EMO_FEA_04
+
+```{r}
+model_hex_emo <- "
+HEX_EMO =~ HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN
+HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
+HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04 + HEX_EMO_FEA_04
+HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+
+HEX_EMO_DEP_01 ~~ HEX_EMO_DEP_04
+HEX_EMO_DEP_02 ~~ HEX_EMO_DEP_03
+HEX_EMO_SEN_01 ~~ HEX_EMO_SEN_03
+HEX_EMO_SEN_02 ~~ HEX_EMO_SEN_04
+"
+fit_hex_emo <- sem(model_hex_emo, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_emo, standardized = TRUE, fit = TRUE)
+```
+
+Still not great. Let's reinspect.
+
+```{r}
+modindices(fit_hex_emo, minimum.value = 50)
+```
+
+No clear candidate emerges. Will keep it that way.
 
@@
 name <- "HEX_EXT_SSE"
-model <- "HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+
+model <- "
+  HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is not good. Let's inspect.
+
+```{r}
+modindices(fit_HEX_EXT_SSE)
+```
+
+Items 1 & 4 and 2 & 3 want to covary.
+
+```{r}
+model <- "
+  HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+  HEX_EXT_SSE_01 ~~ a*HEX_EXT_SSE_04
+  HEX_EXT_SSE_02 ~~ a*HEX_EXT_SSE_03
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now okay.
 
@@
 name <- "HEX_EXT_BOL"
-model <- "HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+
+model <- "
+  HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+RMSEA significantly larger than .10, will hence check modification indices.
+
+```{r}
+modindices(fit_HEX_EXT_BOL)
+```
+
+Let's allow 1 & 4, and 2 & 3 to covary.
+
+```{r}
+model <- "
+  HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+  HEX_EXT_BOL_01 ~~ a*HEX_EXT_BOL_04
+  HEX_EXT_BOL_02 ~~ a*HEX_EXT_BOL_03
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
 
@@
 name <- "HEX_EXT_SOC"
-model <- "HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
 
@@
 name <- "HEX_EXT_LIV"
-model <- "HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is supar, let's inspect.
+
+```{r}
+modindices(fit_HEX_EXT_LIV)
+```
+
+```{r}
+model <- "
+  HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+  HEX_EXT_LIV_01 ~~ a*HEX_EXT_LIV_03
+  HEX_EXT_LIV_02 ~~ a*HEX_EXT_LIV_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Again, fit is not really good --> but it seems preferable to stick to this more parsimoneous solution.
+
+#### Extraversion
+
+Let's analyze main model.
+
+```{r}
+model_hex_ext <- "
+HEX_EXT =~ HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV
+HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
+HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+
+HEX_EXT_SSE_01 ~~ HEX_EXT_SSE_04
+HEX_EXT_SSE_02 ~~ HEX_EXT_SSE_03
+HEX_EXT_BOL_01 ~~ HEX_EXT_BOL_04
+HEX_EXT_BOL_02 ~~ HEX_EXT_BOL_03
+HEX_EXT_LIV_01 ~~ HEX_EXT_LIV_03
+HEX_EXT_LIV_02 ~~ HEX_EXT_LIV_04
+"
+fit_hex_ext <- sem(model_hex_ext, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_ext, standardized = TRUE, fit = TRUE)
+```
+
+Fit is subpar. Let's inspect.
+
+```{r}
+modindices(fit_hex_ext, minimum.value = 50)
+```
+
+One clear cross-loading emerges plus one covariance.
+
+- 	HEX_EXT_SOC	=~	HEX_EXT_BOL_02
+-   HEX_EXT_SSE_01	~~	HEX_EXT_LIV_02
+
+```{r}
+model_hex_ext <- "
+HEX_EXT =~ HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV
+HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04 + HEX_EXT_BOL_02
+HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+
+HEX_EXT_SSE_01 ~~ HEX_EXT_SSE_04
+HEX_EXT_SSE_02 ~~ HEX_EXT_SSE_03
+HEX_EXT_BOL_01 ~~ HEX_EXT_BOL_04
+HEX_EXT_BOL_02 ~~ HEX_EXT_BOL_03
+HEX_EXT_LIV_01 ~~ HEX_EXT_LIV_03
+HEX_EXT_LIV_02 ~~ HEX_EXT_LIV_04
+HEX_EXT_SSE_01 ~~	HEX_EXT_LIV_02
+"
+fit_hex_ext <- sem(model_hex_ext, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_ext, standardized = TRUE, fit = TRUE)
+```
+
+Fit not great, but improved.
 
@@
 name <- "HEX_AGR_FOR"
-model <- "HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
 
@@
 name <- "HEX_AGR_GEN"
-model <- "HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is okay.
 
@@
 name <- "HEX_AGR_FLX"
-model <- "HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is okay.
 
@@
 name <- "HEX_AGR_PAT"
-model <- "HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is subpar. Let's check for potential improvements.
+
+```{r}
+modindices(fit_HEX_AGR_PAT)
+```
+
+Items 1 & 2 and Items 3 & 4 want to covary.
+
+```{r}
+model <- "
+HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+HEX_AGR_PAT_01 ~~ a*HEX_AGR_PAT_02
+HEX_AGR_PAT_03 ~~ a*HEX_AGR_PAT_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
+
+#### Agreeableness
+
+Let's analyze main model.
+
+```{r}
+model_hex_agr <- "
+HEX_AGR =~ HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
+HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
+HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
+HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+
+HEX_AGR_PAT_01 ~~ HEX_AGR_PAT_02
+HEX_AGR_PAT_03 ~~ HEX_AGR_PAT_04
+"
+fit_hex_agr <- sem(model_hex_agr, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_agr, standardized = TRUE, fit = TRUE)
+```
+
+Fit subpar, let's inspect.
+
+```{r}
+modindices(fit_hex_agr, minimum.value = 50)
+```
+
+One cross-loading and one covariance emerges.
+
+- 	HEX_AGR_FOR	=~	HEX_AGR_PAT_02
+-   HEX_AGR_GEN_01	~~	HEX_AGR_FLX_01
+
+```{r}
+model_hex_agr <- "
+HEX_AGR =~ HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04 + HEX_AGR_PAT_02
+HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
+HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
+HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+
+HEX_AGR_PAT_01 ~~ HEX_AGR_PAT_02
+HEX_AGR_PAT_03 ~~ HEX_AGR_PAT_04
+HEX_AGR_GEN_01	~~	HEX_AGR_FLX_01
+"
+fit_hex_agr <- sem(model_hex_agr, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_agr, standardized = TRUE, fit = TRUE)
+```
+
+Fit is now quite good.
 
@@
 name <- "HEX_CNS_ORG"
-model <- "HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit only "just" above thresholds. 
 #### Diligence
@@
 name <- "HEX_CNS_DIL"
-model <- "HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated.
+Hence we should use the robust estimator.
+However, if we do so, one participant will be excluded, because MLM doesn't allow imputation.
+Will hence use ML but with FIML imputation.
+
+```{r}
+model <- "
+  HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is bad. Let's inspect.
+
+```{r}
+modindices(fit_HEX_CNS_DIL)
+```
+
+Items 1 & 2, and items 3 & 4 want to covary.
+
+```{r}
+model <- "
+  HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
+  HEX_CNS_DIL_01 ~~ a*HEX_CNS_DIL_02
+  HEX_CNS_DIL_03 ~~ a*HEX_CNS_DIL_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now good.
 
@@
 name <- "HEX_CNS_PER"
-model <- "HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit subpar, needs to be improved.
+
+```{r}
+modindices(fit_HEX_CNS_PER)
+```
+
+Items 1 & 4 and items 2 & 3 want to covary.
+
+```{r}
+model <- "
+  HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
+  HEX_CNS_PER_01 ~~ a*HEX_CNS_PER_04
+  HEX_CNS_PER_02 ~~ a*HEX_CNS_PER_03
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now great.
 
@@
 name <- "HEX_CNS_PRU"
-model <- "HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Although not great, fit is within of thresholds.
+
+#### Conscientiousness
+
+Let's analyze main model as well.
+
+```{r}
+model_hex_cns <- "
+HEX_CNS =~ HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU
+HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
+HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
+HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
+HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
+
+HEX_CNS_ORG_01 ~~ HEX_CNS_ORG_04
+HEX_CNS_ORG_02 ~~ HEX_CNS_ORG_03
+HEX_CNS_DIL_01 ~~ HEX_CNS_DIL_02
+HEX_CNS_DIL_03 ~~ HEX_CNS_DIL_04
+HEX_CNS_PER_01 ~~ HEX_CNS_PER_04
+HEX_CNS_PER_02 ~~ HEX_CNS_PER_03
+HEX_CNS_PRU_01 ~~ HEX_CNS_PRU_04
+HEX_CNS_PRU_02 ~~ HEX_CNS_PRU_03
+"
+fit_hex_cns <- sem(model_hex_cns, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_cns, standardized = TRUE, fit = TRUE)
+```
+
+Fit is slightly below thresholds, let's inspect.
+
+```{r}
+modindices(fit_hex_cns, minimum.value = 50)
+```
+
+No real candidate emerges. Will keep that way.
 
@@
 ```{r}
-name <- "HEX_OPN_AEX"
-model <- "HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+name <- "HEX_OPN_AES"
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
 
@@
 name <- "HEX_OPN_INQ"
-model <- "HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is just within thresholds.
 
@@
 name <- "HEX_OPN_CRE"
-model <- "HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is great.
 
@@
 name <- "HEX_OPN_UNC"
-model <- "HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is subpar. Let's inspect.
+
+```{r}
+modindices(fit_HEX_OPN_UNC)
+```
+
+Items 1 & 4 and items 2 & 3 want to covary.
+
+```{r}
+model <- "
+  HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
+  HEX_OPN_UNC_01 ~~ a*HEX_OPN_UNC_04
+  HEX_OPN_UNC_02 ~~ a*HEX_OPN_UNC_03
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now great.
+
+#### Openness
+
+Let's analyze main model as well.
+
+```{r}
+model_hex_opn <- "
+HEX_OPN =~ HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC
+HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
+HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
+HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
+HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
+
+HEX_OPN_INQ_01 ~~ HEX_OPN_INQ_04
+HEX_OPN_INQ_02 ~~ HEX_OPN_INQ_03
+HEX_OPN_UNC_01 ~~ HEX_OPN_UNC_04
+HEX_OPN_UNC_02 ~~ HEX_OPN_UNC_03
+"
+fit_hex_opn <- sem(model_hex_opn, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex_opn, standardized = TRUE, fit = TRUE)
 ```
@@
 name <- "HEX_ALT"
-model <- "HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is subpar. Let's inspect.
+
+```{r}
+modindices(fit_HEX_ALT)
+```
+
+Items 1 & 2 and items 3 & 4 want to covary.
+
+```{r}
+model <- "
+  HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
+  HEX_ALT_01 ~~ a*HEX_ALT_02
+  HEX_ALT_03 ~~ a*HEX_ALT_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now good.
+
+### Hexaco Model
+
+```{r}
+model_hex <- "
+HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
+HEX_EMO =~ HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN
+HEX_EXT =~ HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV
+HEX_AGR =~ HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT
+HEX_CNS =~ HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU
+HEX_OPN =~ HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC
+
+HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
+HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
+HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
+HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
+
+HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
+HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04 + HEX_EMO_FEA_04
+HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
+HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
+
+HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
+HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04 + HEX_EXT_BOL_02
+HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
+
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04 + HEX_AGR_PAT_02
+HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
+HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
+HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
+
+HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
+HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
+HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
+HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
+
+HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
+HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
+HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
+HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
+
+# Covariances
+HEX_HOH_SIN_01 ~~ HEX_HOH_SIN_03
+HEX_HOH_SIN_02 ~~ HEX_HOH_SIN_04
+HEX_HOH_GRE_01 ~~ HEX_HOH_GRE_02
+HEX_HOH_GRE_03 ~~ HEX_HOH_GRE_04
+HEX_EMO_DEP_01 ~~ HEX_EMO_DEP_04
+HEX_EMO_DEP_02 ~~ HEX_EMO_DEP_03
+HEX_EMO_SEN_01 ~~ HEX_EMO_SEN_03
+HEX_EMO_SEN_02 ~~ HEX_EMO_SEN_04
+HEX_EXT_SSE_01 ~~ HEX_EXT_SSE_04
+HEX_EXT_SSE_02 ~~ HEX_EXT_SSE_03
+HEX_EXT_BOL_01 ~~ HEX_EXT_BOL_04
+HEX_EXT_BOL_02 ~~ HEX_EXT_BOL_03
+HEX_EXT_LIV_01 ~~ HEX_EXT_LIV_03
+HEX_EXT_LIV_02 ~~ HEX_EXT_LIV_04
+HEX_AGR_PAT_01 ~~ HEX_AGR_PAT_02
+HEX_AGR_PAT_03 ~~ HEX_AGR_PAT_04
+HEX_CNS_PER_01 ~~ HEX_CNS_PER_04
+HEX_CNS_PER_02 ~~ HEX_CNS_PER_03
+HEX_CNS_DIL_01 ~~ HEX_CNS_DIL_02
+HEX_CNS_DIL_03 ~~ HEX_CNS_DIL_04
+HEX_OPN_UNC_01 ~~ HEX_OPN_UNC_04
+HEX_OPN_UNC_02 ~~ HEX_OPN_UNC_03
+HEX_AGR_GEN_01	~~	HEX_AGR_FLX_01
+"
+fit_hex <- sem(model_hex, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_hex, standardized = TRUE, fit = TRUE)
+```
+
+Model throws a warning: Negative variance. Also several Heywood cases included. Shows that latent is not working.
+
+Hence, let's not extract the factor scores for the personality dimensions, but rather calculate mean scores.
 
@@
 name <- "NFP_PSY"
-model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is great.
 
@@
 name <- "NFP_PHY"
-model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is great.
 
@@
 name <- "NFP_SOC"
-model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit isn't that good. Let's inspect.
+
+```{r}
+modindices(fit_NFP_SOC)
+```
+
+Items 1 & 3 and items 2 & 4 want to covary.
+
+```{r}
+model <- "
+  NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
+  NFP_SOC_01 ~~ p1*NFP_SOC_03
+  NFP_SOC_02 ~~ p1*NFP_SOC_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is great.
 
@@
 name <- "NFP_GOV"
-model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is not optimal, but within thresholds.
 
@@
 name <- "NFP_COM"
-model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is not great but sufficiently okay.
 
@@
 name <- "NFP_INF"
-model <- "NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is suboptimal. Let's inspect.
+
+```{r}
+modindices(fit_NFP_INF)
+```
+
+Items 1 & 4 and items 2 & 3 want to covary.
+
+```{r}
+model <- "
+  NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
+  NFP_INF_01 ~~ a*NFP_INF_04
+  NFP_INF_02 ~~ a*NFP_INF_03
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
 
@@
 name <- "NFP_ANO"
-model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is really bad. Let's inspect.
+
+```{r}
+modindices(fit_NFP_ANO)
+```
+
+Items 1 & 4 and items 2 & 3 want to covary.
+
+```{r}
+model <- "
+  NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
+  NFP_ANO_01 ~~ a*NFP_ANO_04
+  NFP_ANO_02 ~~ a*NFP_ANO_03
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLM")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is now good.
 
@@
 name <- "NFP_GEN"
-model <- "NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-# Power Analyses
-
-To estimate sample size, we conducted a rudimentary power analysis.
-That is, we planned for a two-sided correlation of _r_ = .1.
-We adopted a balanced alpha and beta error approach.
-Because we were in "exploration mode", we aimed for a high statistical power and hence relaxed alpha.
-Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget.
-Instead, we opted for an error rate of 10%.
-
-```{r}
-sesoi <- .1
-
-# a priori power analyses
-pwr.r.test(r = sesoi, sig.level = .05, power = .95)
-power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
-```
-
-A 5% error rate would imply collecting `r power_n_95` participants.
-
-# Results
-## SES
-
-```{r}
-model_ses <- "
-# SES
-Age =~ AGE
-Gender =~ GEN
-Ethnicity =~ ETH
-Relationship =~ REL
-College =~ COL
-Income =~ INC
-Conservatism =~ CON
-
-# Privacy
+
+plot_hist(name)
+
+mardia(
+  select(
+    d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+  )
+)
+```
+
+Assumption of multivariate normality violated. Hence we'll use the robust estimator.
+
+```{r}
+model <- "
+  NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+"
+
+assign(
+  paste("fit", name, sep = "_"), 
+  cfa(model, d, estimator = "MLR", missing = "FIML")
+  )
+
+summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+```
+
+Fit is good.
+
+### Need for Privacy model
+
+```{r}
+model_pri <- "
 NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
@@
 NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-"
-fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_ses, standardized = TRUE)
-
-# get standardized data
-d_ses <- 
-  standardizedsolution(fit_ses)
-```
-
-```{r}
-# make table
-tab_ses <- 
-  d_ses %>% 
-  as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_ses_txt, rhs %in% vars_pri) %>% 
-  select("Sociodemographics" = lhs, "Need for privacy" = rhs, est.std) %>% 
-  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
-  pivot_wider(id_cols = "Sociodemographics", names_from = "Need for privacy", values_from = "est.std") %>% 
-  as.data.frame()
-tab_ses
-```
-
+
+# Covariances
+NFP_SOC_01 ~~ NFP_SOC_03
+NFP_SOC_02 ~~ NFP_SOC_04
+NFP_GOV_01 ~~ NFP_GOV_03
+NFP_GOV_02 ~~ NFP_GOV_04
+NFP_INF_01 ~~ NFP_INF_04
+NFP_INF_02 ~~ NFP_INF_03
+NFP_ANO_01 ~~ NFP_ANO_04
+NFP_ANO_02 ~~ NFP_ANO_03
+"
+fit_pri <- sem(model_pri, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_pri, standardized = TRUE, fit = TRUE)
+```
+
+Fit is actually quite good and only marginally below thresholds. Will inspect.
+
+```{r}
+modindices(fit_pri, minimum.value = 50)
+```
+
+Suggests several cross-loadings. Will integrate.
+
+- NFP_PHY	=~	NFP_GEN_01
+- NFP_PSY	=~	NFP_INF_01
+- NFP_PSY	=~	NFP_GEN_01
+- NFP_SOC	=~	NFP_INF_01
+- NFP_SOC	=~	NFP_GEN_01
+
+```{r}
+model_pri <- "
+NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04 + NFP_GEN_01
+NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04 + NFP_GEN_01 + NFP_INF_01
+NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04 + NFP_GEN_01 + NFP_INF_01
+NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
+NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
+NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
+NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
+NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+
+# Covariances
+NFP_SOC_01 ~~ NFP_SOC_03
+NFP_SOC_02 ~~ NFP_SOC_04
+NFP_GOV_01 ~~ NFP_GOV_03
+NFP_GOV_02 ~~ NFP_GOV_04
+NFP_INF_01 ~~ NFP_INF_04
+NFP_INF_02 ~~ NFP_INF_03
+NFP_ANO_01 ~~ NFP_ANO_04
+NFP_ANO_02 ~~ NFP_ANO_03
+"
+fit_pri <- sem(model_pri, d, estimator = "MLM", fixed.x = TRUE)
+summary(fit_pri, standardized = TRUE, fit = TRUE)
+```
+
+Fit is now great.
+
+## Convergent validity
+
+To assess convergent validity, let's correlate measures with privacy concerns and privacy behavior.
+
+```{r}
+tab_conval <- 
+  d %>% 
+  select(
+    all_of(paste0(vars_pri, "_M")), PRI_CON, PRI_BEH
+  ) %>% 
+  cor(use = "pairwise") %>% 
+  round(2) %>% 
+  as.data.frame
+tab_conval
+```
+
+Almost all variables showed high convergent validity.
+
+# Export factor scores
+
+```{r cache=F}
+d <- 
+  d %>% 
+  mutate(
+    HEX_ALT_FS = lavPredict(fit_HEX_ALT),
+    HEX_AGR_FLX_FS = lavPredict(fit_HEX_AGR_FLX),
+    HEX_AGR_FOR_FS = lavPredict(fit_HEX_AGR_FOR),
+    HEX_AGR_GEN_FS = lavPredict(fit_HEX_AGR_GEN),
+    HEX_AGR_PAT_FS = lavPredict(fit_HEX_AGR_PAT),
+    HEX_CNS_DIL_FS = lavPredict(fit_HEX_CNS_DIL),
+    HEX_CNS_ORG_FS = lavPredict(fit_HEX_CNS_ORG),
+    HEX_CNS_PER_FS = lavPredict(fit_HEX_CNS_PER),
+    HEX_CNS_PRU_FS = lavPredict(fit_HEX_CNS_PRU),
+    HEX_EMO_ANX_FS = lavPredict(fit_HEX_EMO_ANX),
+    HEX_EMO_DEP_FS = lavPredict(fit_HEX_EMO_DEP),
+    HEX_EMO_FEA_FS = lavPredict(fit_HEX_EMO_FEA),
+    HEX_EMO_SEN_FS = lavPredict(fit_HEX_EMO_SEN),
+    HEX_EXT_BOL_FS = lavPredict(fit_HEX_EXT_BOL),
+    HEX_EXT_LIV_FS = lavPredict(fit_HEX_EXT_LIV),
+    HEX_EXT_SOC_FS = lavPredict(fit_HEX_EXT_SOC),
+    HEX_EXT_SSE_FS = lavPredict(fit_HEX_EXT_SSE),
+    HEX_HOH_FAI_FS = lavPredict(fit_HEX_HOH_FAI),
+    HEX_HOH_GRE_FS = lavPredict(fit_HEX_HOH_GRE),
+    HEX_HOH_MOD_FS = lavPredict(fit_HEX_HOH_MOD),
+    HEX_HOH_SIN_FS = lavPredict(fit_HEX_HOH_SIN),
+    HEX_OPN_AES_FS = lavPredict(fit_HEX_OPN_AES),
+    HEX_OPN_CRE_FS = lavPredict(fit_HEX_OPN_CRE),
+    HEX_OPN_INQ_FS = lavPredict(fit_HEX_OPN_INQ),
+    HEX_OPN_UNC_FS = lavPredict(fit_HEX_OPN_UNC),
+    NFP_ANO_FS = lavPredict(fit_NFP_ANO),
+    NFP_COM_FS = lavPredict(fit_NFP_COM),
+    NFP_GEN_FS = lavPredict(fit_NFP_GEN),
+    NFP_GOV_FS = lavPredict(fit_NFP_GOV),
+    NFP_INF_FS = lavPredict(fit_NFP_INF),
+    NFP_PHY_FS = lavPredict(fit_NFP_PHY),
+    NFP_PSY_FS = lavPredict(fit_NFP_PSY),
+    NFP_SOC_FS = lavPredict(fit_NFP_SOC)
+  )
+```
+
+# Item errors
+
+```{r}
+# Extract variance
+HEX_ALT_var <- var(d$HEX_ALT_M, na.rm = T)
+HEX_AGR_FLX_var <- var(d$HEX_AGR_FLX_M, na.rm = T)
+HEX_AGR_FOR_var <- var(d$HEX_AGR_FOR_M, na.rm = T)
+HEX_AGR_GEN_var <- var(d$HEX_AGR_GEN_M, na.rm = T)
+HEX_AGR_PAT_var <- var(d$HEX_AGR_PAT_M, na.rm = T)
+HEX_CNS_DIL_var <- var(d$HEX_CNS_DIL_M, na.rm = T)
+HEX_CNS_ORG_var <- var(d$HEX_CNS_ORG_M, na.rm = T)
+HEX_CNS_PER_var <- var(d$HEX_CNS_PER_M, na.rm = T)
+HEX_CNS_PRU_var <- var(d$HEX_CNS_PRU_M, na.rm = T)
+HEX_EMO_ANX_var <- var(d$HEX_EMO_ANX_M, na.rm = T)
+HEX_EMO_DEP_var <- var(d$HEX_EMO_DEP_M, na.rm = T)
+HEX_EMO_FEA_var <- var(d$HEX_EMO_FEA_M, na.rm = T)
+HEX_EMO_SEN_var <- var(d$HEX_EMO_SEN_M, na.rm = T)
+HEX_EXT_BOL_var <- var(d$HEX_EXT_BOL_M, na.rm = T)
+HEX_EXT_LIV_var <- var(d$HEX_EXT_LIV_M, na.rm = T)
+HEX_EXT_SOC_var <- var(d$HEX_EXT_SOC_M, na.rm = T)
+HEX_EXT_SSE_var <- var(d$HEX_EXT_SSE_M, na.rm = T)
+HEX_HOH_FAI_var <- var(d$HEX_HOH_FAI_M, na.rm = T)
+HEX_HOH_GRE_var <- var(d$HEX_HOH_GRE_M, na.rm = T)
+HEX_HOH_MOD_var <- var(d$HEX_HOH_MOD_M, na.rm = T)
+HEX_HOH_SIN_var <- var(d$HEX_HOH_SIN_M, na.rm = T)
+HEX_OPN_AES_var <- var(d$HEX_OPN_AES_M, na.rm = T)
+HEX_OPN_CRE_var <- var(d$HEX_OPN_CRE_M, na.rm = T)
+HEX_OPN_INQ_var <- var(d$HEX_OPN_INQ_M, na.rm = T)
+HEX_OPN_UNC_var <- var(d$HEX_OPN_UNC_M, na.rm = T)
+
+NFP_ANO_var <- var(d$NFP_ANO_M, na.rm = T)
+NFP_COM_var <- var(d$NFP_COM_M, na.rm = T)
+NFP_GEN_var <- var(d$NFP_GEN_M, na.rm = T)
+NFP_GOV_var <- var(d$NFP_GOV_M, na.rm = T)
+NFP_INF_var <- var(d$NFP_INF_M, na.rm = T)
+NFP_PHY_var <- var(d$NFP_PHY_M, na.rm = T)
+NFP_PSY_var <- var(d$NFP_PSY_M, na.rm = T)
+NFP_SOC_var <- var(d$NFP_SOC_M, na.rm = T)
+
+HEX_AGR_var <- var(d$HEX_AGR_M, na.rm = T)
+HEX_CNS_var <- var(d$HEX_CNS_M, na.rm = T)
+HEX_EMO_var <- var(d$HEX_EMO_M, na.rm = T)
+HEX_EXT_var <- var(d$HEX_EXT_M, na.rm = T)
+HEX_HOH_var <- var(d$HEX_HOH_M, na.rm = T)
+HEX_OPN_var <- var(d$HEX_OPN_M, na.rm = T)
+
+# Get reliability
+c_rel <- 
+  c(
+    HEX_ALT_rel     = reliability(fit_HEX_ALT)["omega", "HEX_ALT"],
+    HEX_AGR_FLX_rel = reliability(fit_HEX_AGR_FLX)["omega", "HEX_AGR_FLX"],
+    HEX_AGR_FOR_rel = reliability(fit_HEX_AGR_FOR)["omega", "HEX_AGR_FOR"],
+    HEX_AGR_GEN_rel = reliability(fit_HEX_AGR_GEN)["omega", "HEX_AGR_GEN"],
+    HEX_AGR_PAT_rel = reliability(fit_HEX_AGR_PAT)["omega", "HEX_AGR_PAT"],
+    HEX_CNS_DIL_rel = reliability(fit_HEX_CNS_DIL)["omega", "HEX_CNS_DIL"],
+    HEX_CNS_ORG_rel = reliability(fit_HEX_CNS_ORG)["omega", "HEX_CNS_ORG"],
+    HEX_CNS_PER_rel = reliability(fit_HEX_CNS_PER)["omega", "HEX_CNS_PER"],
+    HEX_CNS_PRU_rel = reliability(fit_HEX_CNS_PRU)["omega", "HEX_CNS_PRU"],
+    HEX_EMO_ANX_rel = reliability(fit_HEX_EMO_ANX)["omega", "HEX_EMO_ANX"],
+    HEX_EMO_DEP_rel = reliability(fit_HEX_EMO_DEP)["omega", "HEX_EMO_DEP"],
+    HEX_EMO_FEA_rel = reliability(fit_HEX_EMO_FEA)["omega", "HEX_EMO_FEA"],
+    HEX_EMO_SEN_rel = reliability(fit_HEX_EMO_SEN)["omega", "HEX_EMO_SEN"],
+    HEX_EXT_BOL_rel = reliability(fit_HEX_EXT_BOL)["omega", "HEX_EXT_BOL"],
+    HEX_EXT_LIV_rel = reliability(fit_HEX_EXT_LIV)["omega", "HEX_EXT_LIV"],
+    HEX_EXT_SOC_rel = reliability(fit_HEX_EXT_SOC)["omega", "HEX_EXT_SOC"],
+    HEX_EXT_SSE_rel = reliability(fit_HEX_EXT_SSE)["omega", "HEX_EXT_SSE"],
+    HEX_HOH_FAI_rel = reliability(fit_HEX_HOH_FAI)["omega", "HEX_HOH_FAI"],
+    HEX_HOH_GRE_rel = reliability(fit_HEX_HOH_GRE)["omega", "HEX_HOH_GRE"],
+    HEX_HOH_MOD_rel = reliability(fit_HEX_HOH_MOD)["omega", "HEX_HOH_MOD"],
+    HEX_HOH_SIN_rel = reliability(fit_HEX_HOH_SIN)["omega", "HEX_HOH_SIN"],
+    HEX_OPN_AES_rel = reliability(fit_HEX_OPN_AES)["omega", "HEX_OPN_AES"],
+    HEX_OPN_CRE_rel = reliability(fit_HEX_OPN_CRE)["omega", "HEX_OPN_CRE"],
+    HEX_OPN_INQ_rel = reliability(fit_HEX_OPN_INQ)["omega", "HEX_OPN_INQ"],
+    HEX_OPN_UNC_rel = reliability(fit_HEX_OPN_UNC)["omega", "HEX_OPN_UNC"],
+
+    NFP_ANO_rel     = reliability(fit_NFP_ANO)["omega", "NFP_ANO"],
+    NFP_COM_rel     = reliability(fit_NFP_COM)["omega", "NFP_COM"],
+    NFP_GEN_rel     = reliability(fit_NFP_GEN)["omega", "NFP_GEN"],
+    NFP_GOV_rel     = reliability(fit_NFP_GOV)["omega", "NFP_GOV"],
+    NFP_INF_rel     = reliability(fit_NFP_INF)["omega", "NFP_INF"],
+    NFP_PHY_rel     = reliability(fit_NFP_PHY)["omega", "NFP_PHY"],
+    NFP_PSY_rel     = reliability(fit_NFP_PSY)["omega", "NFP_PSY"],
+    NFP_SOC_rel     = reliability(fit_NFP_SOC)["omega", "NFP_SOC"],
+
+    HEX_HOH_rel     = reliability(fit_hex_hoh, return.total = T)["omega", "total"],
+    HEX_EMO_rel     = reliability(fit_hex_emo, return.total = T)["omega", "total"],
+    HEX_EXT_rel     = reliability(fit_hex_ext, return.total = T)["omega", "total"],
+    HEX_AGR_rel     = reliability(fit_hex_agr, return.total = T)["omega", "total"],
+    HEX_CNS_rel     = reliability(fit_hex_cns, return.total = T)["omega", "total"],
+    HEX_OPN_rel     = reliability(fit_hex_opn, return.total = T)["omega", "total"]
+  )
+
+# Define error
+HEX_ALT_err     <- (1 - c_rel["HEX_ALT_rel"]) * HEX_ALT_var
+HEX_AGR_FLX_err <- (1 - c_rel["HEX_AGR_FLX_rel"]) * HEX_AGR_FLX_var
+HEX_AGR_FOR_err <- (1 - c_rel["HEX_AGR_FOR_rel"]) * HEX_AGR_FOR_var
+HEX_AGR_GEN_err <- (1 - c_rel["HEX_AGR_GEN_rel"]) * HEX_AGR_GEN_var
+HEX_AGR_PAT_err <- (1 - c_rel["HEX_AGR_PAT_rel"]) * HEX_AGR_PAT_var
+HEX_CNS_DIL_err <- (1 - c_rel["HEX_CNS_DIL_rel"]) * HEX_CNS_DIL_var
+HEX_CNS_ORG_err <- (1 - c_rel["HEX_CNS_ORG_rel"]) * HEX_CNS_ORG_var
+HEX_CNS_PER_err <- (1 - c_rel["HEX_CNS_PER_rel"]) * HEX_CNS_PER_var
+HEX_CNS_PRU_err <- (1 - c_rel["HEX_CNS_PRU_rel"]) * HEX_CNS_PRU_var
+HEX_EMO_ANX_err <- (1 - c_rel["HEX_EMO_ANX_rel"]) * HEX_EMO_ANX_var
+HEX_EMO_DEP_err <- (1 - c_rel["HEX_EMO_DEP_rel"]) * HEX_EMO_DEP_var
+HEX_EMO_FEA_err <- (1 - c_rel["HEX_EMO_FEA_rel"]) * HEX_EMO_FEA_var
+HEX_EMO_SEN_err <- (1 - c_rel["HEX_EMO_SEN_rel"]) * HEX_EMO_SEN_var
+HEX_EXT_BOL_err <- (1 - c_rel["HEX_EXT_BOL_rel"]) * HEX_EXT_BOL_var
+HEX_EXT_LIV_err <- (1 - c_rel["HEX_EXT_LIV_rel"]) * HEX_EXT_LIV_var
+HEX_EXT_SOC_err <- (1 - c_rel["HEX_EXT_SOC_rel"]) * HEX_EXT_SOC_var
+HEX_EXT_SSE_err <- (1 - c_rel["HEX_EXT_SSE_rel"]) * HEX_EXT_SSE_var
+HEX_HOH_FAI_err <- (1 - c_rel["HEX_HOH_FAI_rel"]) * HEX_HOH_FAI_var
+HEX_HOH_GRE_err <- (1 - c_rel["HEX_HOH_GRE_rel"]) * HEX_HOH_GRE_var
+HEX_HOH_MOD_err <- (1 - c_rel["HEX_HOH_MOD_rel"]) * HEX_HOH_MOD_var
+HEX_HOH_SIN_err <- (1 - c_rel["HEX_HOH_SIN_rel"]) * HEX_HOH_SIN_var
+HEX_OPN_AES_err <- (1 - c_rel["HEX_OPN_AES_rel"]) * HEX_OPN_AES_var
+HEX_OPN_CRE_err <- (1 - c_rel["HEX_OPN_CRE_rel"]) * HEX_OPN_CRE_var
+HEX_OPN_INQ_err <- (1 - c_rel["HEX_OPN_INQ_rel"]) * HEX_OPN_INQ_var
+HEX_OPN_UNC_err <- (1 - c_rel["HEX_OPN_UNC_rel"]) * HEX_OPN_UNC_var
+
+NFP_ANO_err     <- (1 - c_rel["NFP_ANO_rel"]) * NFP_ANO_var
+NFP_COM_err     <- (1 - c_rel["NFP_COM_rel"]) * NFP_COM_var
+NFP_GEN_err     <- (1 - c_rel["NFP_GEN_rel"]) * NFP_GEN_var
+NFP_GOV_err     <- (1 - c_rel["NFP_GOV_rel"]) * NFP_GOV_var
+NFP_INF_err     <- (1 - c_rel["NFP_INF_rel"]) * NFP_INF_var
+NFP_PHY_err     <- (1 - c_rel["NFP_PHY_rel"]) * NFP_PHY_var
+NFP_PSY_err     <- (1 - c_rel["NFP_PSY_rel"]) * NFP_PSY_var
+NFP_SOC_err     <- (1 - c_rel["NFP_SOC_rel"]) * NFP_SOC_var
+
+HEX_AGR_err <- (1 - c_rel["HEX_AGR_rel"]) * HEX_AGR_var
+HEX_CNS_err <- (1 - c_rel["HEX_CNS_rel"]) * HEX_CNS_var
+HEX_EMO_err <- (1 - c_rel["HEX_EMO_rel"]) * HEX_EMO_var
+HEX_EXT_err <- (1 - c_rel["HEX_EXT_rel"]) * HEX_EXT_var
+HEX_HOH_err <- (1 - c_rel["HEX_HOH_rel"]) * HEX_HOH_var
+HEX_OPN_err <- (1 - c_rel["HEX_OPN_rel"]) * HEX_OPN_var
+
+HEX_err <- data.frame(
+  err = 
+    c(HEX_HOH_err, 
+      HEX_EMO_err, 
+      HEX_EXT_err, 
+      HEX_AGR_err, 
+      HEX_CNS_err,
+      HEX_OPN_err
+      )
+  ) %>% 
+  round(3)
+
+NFP_err <- data.frame(
+  err = 
+    c(NFP_PSY_err, 
+      NFP_SOC_err, 
+      NFP_PHY_err, 
+      NFP_GOV_err, 
+      NFP_COM_err,
+      NFP_INF_err,
+      NFP_ANO_err,
+      NFP_GEN_err
+      )
+  ) %>% 
+  round(3)
+
+HEX_NFP_err <- rbind(HEX_err, NFP_err)
+```
+
+# Results
 ## Dimensions
 
-Factor or dimensions.
-
-```{r}
+Let's first look at relations between need for privacy and personality factors.
+
+```{r results-dims}
 model_dim <- "
@@
 HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
-HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
+HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04 + HEX_EMO_FEA_04
 HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
@@
 HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04 + HEX_EXT_BOL_02
 HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
@@
 HEX_AGR =~ HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04 + HEX_AGR_PAT_02
 HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
@@
 # Privacy
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
+NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04 + NFP_GEN_01
+NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04 + NFP_GEN_01 + NFP_INF_01
+NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04 + NFP_GEN_01 + NFP_INF_01
 NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
@@
 NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+
+# Covariances
+HEX_HOH_SIN_01 ~~ HEX_HOH_SIN_03
+HEX_HOH_SIN_02 ~~ HEX_HOH_SIN_04
+HEX_HOH_GRE_01 ~~ HEX_HOH_GRE_02
+HEX_HOH_GRE_03 ~~ HEX_HOH_GRE_04
+HEX_EMO_DEP_01 ~~ HEX_EMO_DEP_04
+HEX_EMO_DEP_02 ~~ HEX_EMO_DEP_03
+HEX_EMO_SEN_01 ~~ HEX_EMO_SEN_03
+HEX_EMO_SEN_02 ~~ HEX_EMO_SEN_04
+HEX_EXT_SSE_01 ~~ HEX_EXT_SSE_04
+HEX_EXT_SSE_02 ~~ HEX_EXT_SSE_03
+HEX_EXT_BOL_01 ~~ HEX_EXT_BOL_04
+HEX_EXT_BOL_02 ~~ HEX_EXT_BOL_03
+HEX_EXT_LIV_01 ~~ HEX_EXT_LIV_03
+HEX_EXT_LIV_02 ~~ HEX_EXT_LIV_04
+HEX_AGR_PAT_01 ~~ HEX_AGR_PAT_02
+HEX_AGR_PAT_03 ~~ HEX_AGR_PAT_04
+HEX_CNS_ORG_01 ~~ HEX_CNS_ORG_04
+HEX_CNS_ORG_02 ~~ HEX_CNS_ORG_03
+HEX_CNS_DIL_01 ~~ HEX_CNS_DIL_02
+HEX_CNS_DIL_03 ~~ HEX_CNS_DIL_04
+HEX_CNS_PER_01 ~~ HEX_CNS_PER_04
+HEX_CNS_PER_02 ~~ HEX_CNS_PER_03
+HEX_CNS_PRU_01 ~~ HEX_CNS_PRU_04
+HEX_CNS_PRU_02 ~~ HEX_CNS_PRU_03
+HEX_OPN_INQ_01 ~~ HEX_OPN_INQ_04
+HEX_OPN_INQ_02 ~~ HEX_OPN_INQ_03
+HEX_OPN_UNC_01 ~~ HEX_OPN_UNC_04
+HEX_OPN_UNC_02 ~~ HEX_OPN_UNC_03
+HEX_ALT_01 ~~ HEX_ALT_02
+HEX_ALT_03 ~~ HEX_ALT_04
+HEX_AGR_GEN_01	~~	HEX_AGR_FLX_01
+
+NFP_SOC_01 ~~ NFP_SOC_03
+NFP_SOC_02 ~~ NFP_SOC_04
+NFP_GOV_01 ~~ NFP_GOV_03
+NFP_GOV_02 ~~ NFP_GOV_04
+NFP_INF_01 ~~ NFP_INF_04
+NFP_INF_02 ~~ NFP_INF_03
+NFP_ANO_01 ~~ NFP_ANO_04
+NFP_ANO_02 ~~ NFP_ANO_03
 "
 fit_dim <- sem(model_dim, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_dim, standardized = TRUE)
+summary(fit_dim, standardized = TRUE, fit = TRUE)
 
@@
 
+Doesn't converge. Hence let's use means of observed values for personality and for privacy. Let's specify errors as preregistered.
+
+```{r}
+model_dim_err <- "
+# Personality Factors
+HEX_HOH =~ HEX_HOH_M
+HEX_EMO =~ HEX_EMO_M
+HEX_EXT =~ HEX_EXT_M
+HEX_AGR =~ HEX_AGR_M
+HEX_CNS =~ HEX_CNS_M
+HEX_OPN =~ HEX_OPN_M
+
+# Privacy
+NFP_PHY =~ NFP_PHY_M
+NFP_PSY =~ NFP_PSY_M
+NFP_SOC =~ NFP_SOC_M
+NFP_GOV =~ NFP_GOV_M
+NFP_COM =~ NFP_COM_M
+NFP_INF =~ NFP_INF_M
+NFP_ANO =~ NFP_ANO_M
+NFP_GEN =~ NFP_GEN_M
+
+# Define Error
+HEX_HOH_M ~~ 0.104 * HEX_HOH_M
+HEX_EMO_M ~~ 0.087 * HEX_EMO_M
+HEX_EXT_M ~~ 0.099 * HEX_EXT_M
+HEX_AGR_M ~~ 0.079 * HEX_AGR_M
+HEX_CNS_M ~~ 0.085 * HEX_CNS_M
+HEX_OPN_M ~~ 0.108 * HEX_OPN_M
+NFP_PHY_M ~~ 0.353 * NFP_PHY_M
+NFP_PSY_M ~~ 0.457 * NFP_PSY_M
+NFP_SOC_M ~~ 0.328 * NFP_SOC_M
+NFP_GOV_M ~~ 0.261 * NFP_GOV_M
+NFP_COM_M ~~ 0.331 * NFP_COM_M
+NFP_INF_M ~~ 0.284 * NFP_INF_M
+NFP_ANO_M ~~ 0.603 * NFP_ANO_M
+NFP_GEN_M ~~ 0.207 * NFP_GEN_M
+"
+fit_dim_err <- sem(model_dim_err, d, estimator = "ML", fixed.x = TRUE)
+summary(fit_dim_err, standardized = TRUE, fit = TRUE)
+```
+Throws a warning: "covariance matrix of latent variables is not positive definite." Let's hence look at correlations of observed mean scores.
+Also do in subsequent analyses (i.e., facets and SES), to maintain comparability.
+
 ```{r}
 # make table
-tab_dim <- 
-  d_dim %>% 
+tab_cor_dim_m <- 
+  d %>% 
+  select(
+    paste0(vars_pers_dim, "_M"),
+    paste0(vars_pri, "_M")
+    ) %>% 
+  cor(use = "pairwise") %>% 
+  round(2) %>% 
   as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri) %>% 
-  select("Personality dimension" = lhs, "Need for privacy" = rhs, est.std) %>% 
-  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
-  pivot_wider(id_cols = "Personality dimension", names_from = "Need for privacy", values_from = "est.std") %>% 
-  mutate(`Personality dimension` = factor(`Personality dimension`, levels = vars_pers_dim, labels = vars_pers_dim_txt)) %>% 
-  as.data.frame()
-tab_dim
+  select(starts_with("NFP")) %>% 
+  head(6) %>% 
+  cbind(
+    `Personality dimension` = factor(
+      vars_pers_dim, 
+      levels = vars_pers_dim, 
+      labels = vars_pers_dim_txt
+      ),
+    .
+    ) %>% 
+  remove_rownames() %>% 
+  set_names(c("Personality factors", vars_pri_txt_abr))
+
+tab_cor_dim_m
 ```
@@
 
-```{r}
+Let's first look at latent model to confirm it's also not converging.
+
+```{r results-facets}
 model_fac <- "
@@
 HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
+HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04 + HEX_EXT_BOL_02
 HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
+HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04 + HEX_AGR_PAT_02
 HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
@@
 NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
+
+# Covariances
+HEX_HOH_SIN_01 ~~ HEX_HOH_SIN_03
+HEX_HOH_SIN_02 ~~ HEX_HOH_SIN_04
+HEX_HOH_GRE_01 ~~ HEX_HOH_GRE_02
+HEX_HOH_GRE_03 ~~ HEX_HOH_GRE_04
+HEX_EMO_DEP_01 ~~ HEX_EMO_DEP_04
+HEX_EMO_DEP_02 ~~ HEX_EMO_DEP_03
+HEX_EMO_SEN_01 ~~ HEX_EMO_SEN_03
+HEX_EMO_SEN_02 ~~ HEX_EMO_SEN_04
+HEX_EXT_SSE_01 ~~ HEX_EXT_SSE_04
+HEX_EXT_SSE_02 ~~ HEX_EXT_SSE_03
+HEX_EXT_BOL_01 ~~ HEX_EXT_BOL_04
+HEX_EXT_BOL_02 ~~ HEX_EXT_BOL_03
+HEX_EXT_LIV_01 ~~ HEX_EXT_LIV_03
+HEX_EXT_LIV_02 ~~ HEX_EXT_LIV_04
+HEX_AGR_PAT_01 ~~ HEX_AGR_PAT_02
+HEX_AGR_PAT_03 ~~ HEX_AGR_PAT_04
+HEX_CNS_ORG_01 ~~ HEX_CNS_ORG_04
+HEX_CNS_ORG_02 ~~ HEX_CNS_ORG_03
+HEX_CNS_DIL_01 ~~ HEX_CNS_DIL_02
+HEX_CNS_DIL_03 ~~ HEX_CNS_DIL_04
+HEX_CNS_PER_01 ~~ HEX_CNS_PER_04
+HEX_CNS_PER_02 ~~ HEX_CNS_PER_03
+HEX_CNS_PRU_01 ~~ HEX_CNS_PRU_04
+HEX_CNS_PRU_02 ~~ HEX_CNS_PRU_03
+HEX_OPN_INQ_01 ~~ HEX_OPN_INQ_04
+HEX_OPN_INQ_02 ~~ HEX_OPN_INQ_03
+HEX_OPN_UNC_01 ~~ HEX_OPN_UNC_04
+HEX_OPN_UNC_02 ~~ HEX_OPN_UNC_03
+HEX_AGR_GEN_01	~~	HEX_AGR_FLX_01
+
+HEX_ALT_01 ~~ HEX_ALT_02
+HEX_ALT_03 ~~ HEX_ALT_04
+NFP_SOC_01 ~~ NFP_SOC_03
+NFP_SOC_02 ~~ NFP_SOC_04
+NFP_GOV_01 ~~ NFP_GOV_03
+NFP_GOV_02 ~~ NFP_GOV_04
+NFP_INF_01 ~~ NFP_INF_04
+NFP_INF_02 ~~ NFP_INF_03
+NFP_ANO_01 ~~ NFP_ANO_04
+NFP_ANO_02 ~~ NFP_ANO_03
 "
 fit_fac <- sem(model_fac, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_fac, standardized = TRUE)
+summary(fit_fac, standardized = TRUE, fit = TRUE)
 
@@
 
+As expected, throws the same warning. Let's hence again use correlations of observed mean values.
+
+```{r}
+tab_cor_fac_m <- 
+  d %>% 
+  select(
+    paste0(vars_pers_fac, "_M"),
+    paste0(vars_pri, "_M")
+    ) %>% 
+  cor(use = "pairwise") %>% 
+  round(2) %>% 
+  as.data.frame() %>% 
+  select(starts_with("NFP")) %>% 
+  head(25) %>% 
+  relocate(paste0(vars_pri, "_M")) %>% 
+  rownames_to_column("Facets") %>% 
+  mutate(
+    Facets = factor(
+      x = Facets,
+      levels = paste0(vars_pers_fac, "_M"),
+      labels = vars_pers_fac_txt
+    )
+      ) %>% 
+  arrange(Facets) %>% 
+  set_names(c("Personality factors", vars_pri_txt_abr))
+tab_cor_fac_m
+```
+
+## SES
+
+Let's directly inspect results of correlations between means of observed scores.
+
 ```{r}
 # make table
-tab_fac <- 
-  d_fac %>% 
+tab_cor_ses_m <- 
+  d %>% 
+  select(
+    vars_ses,
+    paste0(vars_pri, "_M")
+    ) %>%
+  cor(use = "pairwise") %>% 
+  round(2) %>% 
   as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_pers_fac, rhs %in% vars_pri) %>% 
-  select("Personality facet" = lhs, "Need for privacy" = rhs, est.std) %>% 
-  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
-  pivot_wider(id_cols = "Personality facet", names_from = "Need for privacy", values_from = "est.std") %>% 
-  mutate(`Personality facet` = factor(`Personality facet`, levels = vars_pers_fac, labels = vars_pers_fac_txt)) %>% 
-  as.data.frame
-tab_fac
+  select(starts_with("NFP")) %>% 
+  head(7) %>% 
+  cbind(
+    `Sociodemographics` = factor(
+      vars_ses, 
+      levels = vars_ses, 
+      labels = vars_ses_txt
+      ),
+    .
+    ) %>% 
+  remove_rownames() %>% 
+  set_names(c("Sociodemographics", vars_pri_txt_abr))
+
+tab_cor_ses_m
 ```
@@
 
+As preregistered, also look at multiple regression. Directly begin with means of observed values. Let's analyze in one single path-model.
+
+Let's also look only at dimensions, as facets are strongly correlated with one another, leading to problems of multicollinearity.
+
 ```{r}
 model_reg <- "
-# Personality Factors
-HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
-HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
-HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
-HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
-
-HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
-HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
-HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
-HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
-
-HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
-HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
-HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
-
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
-HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
-HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
-HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
-
-HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
-HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
-HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
-HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
-
-HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
-HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
-HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
-HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
-
-# Privacy
-NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-
-NFP_INF + NFP_PSY + NFP_PHY + NFP_SOC + NFP_GOV + NFP_COM + NFP_ANO + NFP_GEN ~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD + HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN + HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV + HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT + HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU + HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC + AGE + GEN + ETH + REL + COL + INC + CON
+NFP_INF_M + NFP_PSY_M + NFP_PHY_M + NFP_SOC_M + NFP_GOV_M + NFP_COM_M + NFP_ANO_M + NFP_GEN_M ~ HEX_HOH_M + HEX_EMO_M + HEX_EXT_M + HEX_AGR_M + HEX_CNS_M + HEX_OPN_M +  + age + male + white + relation + college + income + conserv
 "
 fit_reg <- sem(model_reg, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_reg, standardized = TRUE)
-
-# get standardized data
-d_reg <- 
-  standardizedsolution(fit_reg, ci = TRUE)
-```
-
-```{r fig.width=10, fig.height=9}
-# make table
-tab_reg <- 
-  d_reg %>% 
+summary(fit_reg, standardized = TRUE, fit = TRUE)
+```
+
+# Tables
+## Descriptives
+
+Let's first make a descriptive table with means and model fit.
+
+```{r cache=F}
+# Extract model fit indices: CFI, TLI, RMSEA, SRMR
+c_cfi <- 
+  c(
+    HEX_ALT_cfi     = fitmeasures(fit_HEX_ALT)["cfi.scaled"],
+    HEX_AGR_FLX_cfi = fitmeasures(fit_HEX_AGR_FLX)["cfi.scaled"],
+    HEX_AGR_FOR_cfi = fitmeasures(fit_HEX_AGR_FOR)["cfi.scaled"],
+    HEX_AGR_GEN_cfi = fitmeasures(fit_HEX_AGR_GEN)["cfi.scaled"],
+    HEX_AGR_PAT_cfi = fitmeasures(fit_HEX_AGR_PAT)["cfi.scaled"],
+    HEX_CNS_DIL_cfi = fitmeasures(fit_HEX_CNS_DIL)["cfi.scaled"],
+    HEX_CNS_ORG_cfi = fitmeasures(fit_HEX_CNS_ORG)["cfi.scaled"],
+    HEX_CNS_PER_cfi = fitmeasures(fit_HEX_CNS_PER)["cfi.scaled"],
+    HEX_CNS_PRU_cfi = fitmeasures(fit_HEX_CNS_PRU)["cfi.scaled"],
+    HEX_EMO_ANX_cfi = fitmeasures(fit_HEX_EMO_ANX)["cfi.scaled"],
+    HEX_EMO_DEP_cfi = fitmeasures(fit_HEX_EMO_DEP)["cfi.scaled"],
+    HEX_EMO_FEA_cfi = fitmeasures(fit_HEX_EMO_FEA)["cfi.scaled"],
+    HEX_EMO_SEN_cfi = fitmeasures(fit_HEX_EMO_SEN)["cfi.scaled"],
+    HEX_EXT_BOL_cfi = fitmeasures(fit_HEX_EXT_BOL)["cfi.scaled"],
+    HEX_EXT_LIV_cfi = fitmeasures(fit_HEX_EXT_LIV)["cfi.scaled"],
+    HEX_EXT_SOC_cfi = fitmeasures(fit_HEX_EXT_SOC)["cfi.scaled"],
+    HEX_EXT_SSE_cfi = fitmeasures(fit_HEX_EXT_SSE)["cfi.scaled"],
+    HEX_HOH_FAI_cfi = fitmeasures(fit_HEX_HOH_FAI)["cfi.scaled"],
+    HEX_HOH_GRE_cfi = fitmeasures(fit_HEX_HOH_GRE)["cfi.scaled"],
+    HEX_HOH_MOD_cfi = fitmeasures(fit_HEX_HOH_MOD)["cfi.scaled"],
+    HEX_HOH_SIN_cfi = fitmeasures(fit_HEX_HOH_SIN)["cfi.scaled"],
+    HEX_OPN_AES_cfi = fitmeasures(fit_HEX_OPN_AES)["cfi.scaled"],
+    HEX_OPN_CRE_cfi = fitmeasures(fit_HEX_OPN_CRE)["cfi.scaled"],
+    HEX_OPN_INQ_cfi = fitmeasures(fit_HEX_OPN_INQ)["cfi.scaled"],
+    HEX_OPN_UNC_cfi = fitmeasures(fit_HEX_OPN_UNC)["cfi.scaled"],
+    NFP_ANO_cfi     = fitmeasures(fit_NFP_ANO)["cfi.scaled"],
+    NFP_COM_cfi     = fitmeasures(fit_NFP_COM)["cfi.scaled"],
+    NFP_GEN_cfi     = fitmeasures(fit_NFP_GEN)["cfi.scaled"],
+    NFP_GOV_cfi     = fitmeasures(fit_NFP_GOV)["cfi.scaled"],
+    NFP_INF_cfi     = fitmeasures(fit_NFP_INF)["cfi.scaled"],
+    NFP_PHY_cfi     = fitmeasures(fit_NFP_PHY)["cfi.scaled"],
+    NFP_PSY_cfi     = fitmeasures(fit_NFP_PSY)["cfi.scaled"],
+    NFP_SOC_cfi     = fitmeasures(fit_NFP_SOC)["cfi.scaled"],
+    HEX_HOH_srmr     = fitmeasures(fit_hex_hoh)["cfi.scaled"],
+    HEX_EMO_srmr     = fitmeasures(fit_hex_emo)["cfi.scaled"],
+    HEX_EXT_srmr     = fitmeasures(fit_hex_ext)["cfi.scaled"],
+    HEX_AGR_srmr     = fitmeasures(fit_hex_agr)["cfi.scaled"],
+    HEX_CNS_srmr     = fitmeasures(fit_hex_cns)["cfi.scaled"],
+    HEX_OPN_srmr     = fitmeasures(fit_hex_opn)["cfi.scaled"]
+  )
+
+c_tli <- 
+  c(
+    HEX_ALT_tli     = fitmeasures(fit_HEX_ALT)["tli.scaled"],
+    HEX_AGR_FLX_tli = fitmeasures(fit_HEX_AGR_FLX)["tli.scaled"],
+    HEX_AGR_FOR_tli = fitmeasures(fit_HEX_AGR_FOR)["tli.scaled"],
+    HEX_AGR_GEN_tli = fitmeasures(fit_HEX_AGR_GEN)["tli.scaled"],
+    HEX_AGR_PAT_tli = fitmeasures(fit_HEX_AGR_PAT)["tli.scaled"],
+    HEX_CNS_DIL_tli = fitmeasures(fit_HEX_CNS_DIL)["tli.scaled"],
+    HEX_CNS_ORG_tli = fitmeasures(fit_HEX_CNS_ORG)["tli.scaled"],
+    HEX_CNS_PER_tli = fitmeasures(fit_HEX_CNS_PER)["tli.scaled"],
+    HEX_CNS_PRU_tli = fitmeasures(fit_HEX_CNS_PRU)["tli.scaled"],
+    HEX_EMO_ANX_tli = fitmeasures(fit_HEX_EMO_ANX)["tli.scaled"],
+    HEX_EMO_DEP_tli = fitmeasures(fit_HEX_EMO_DEP)["tli.scaled"],
+    HEX_EMO_FEA_tli = fitmeasures(fit_HEX_EMO_FEA)["tli.scaled"],
+    HEX_EMO_SEN_tli = fitmeasures(fit_HEX_EMO_SEN)["tli.scaled"],
+    HEX_EXT_BOL_tli = fitmeasures(fit_HEX_EXT_BOL)["tli.scaled"],
+    HEX_EXT_LIV_tli = fitmeasures(fit_HEX_EXT_LIV)["tli.scaled"],
+    HEX_EXT_SOC_tli = fitmeasures(fit_HEX_EXT_SOC)["tli.scaled"],
+    HEX_EXT_SSE_tli = fitmeasures(fit_HEX_EXT_SSE)["tli.scaled"],
+    HEX_HOH_FAI_tli = fitmeasures(fit_HEX_HOH_FAI)["tli.scaled"],
+    HEX_HOH_GRE_tli = fitmeasures(fit_HEX_HOH_GRE)["tli.scaled"],
+    HEX_HOH_MOD_tli = fitmeasures(fit_HEX_HOH_MOD)["tli.scaled"],
+    HEX_HOH_SIN_tli = fitmeasures(fit_HEX_HOH_SIN)["tli.scaled"],
+    HEX_OPN_AES_tli = fitmeasures(fit_HEX_OPN_AES)["tli.scaled"],
+    HEX_OPN_CRE_tli = fitmeasures(fit_HEX_OPN_CRE)["tli.scaled"],
+    HEX_OPN_INQ_tli = fitmeasures(fit_HEX_OPN_INQ)["tli.scaled"],
+    HEX_OPN_UNC_tli = fitmeasures(fit_HEX_OPN_UNC)["tli.scaled"],
+    NFP_ANO_tli     = fitmeasures(fit_NFP_ANO)["tli.scaled"],
+    NFP_COM_tli     = fitmeasures(fit_NFP_COM)["tli.scaled"],
+    NFP_GEN_tli     = fitmeasures(fit_NFP_GEN)["tli.scaled"],
+    NFP_GOV_tli     = fitmeasures(fit_NFP_GOV)["tli.scaled"],
+    NFP_INF_tli     = fitmeasures(fit_NFP_INF)["tli.scaled"],
+    NFP_PHY_tli     = fitmeasures(fit_NFP_PHY)["tli.scaled"],
+    NFP_PSY_tli     = fitmeasures(fit_NFP_PSY)["tli.scaled"],
+    NFP_SOC_tli     = fitmeasures(fit_NFP_SOC)["tli.scaled"],
+    HEX_HOH_srmr     = fitmeasures(fit_hex_hoh)["tli.scaled"],
+    HEX_EMO_srmr     = fitmeasures(fit_hex_emo)["tli.scaled"],
+    HEX_EXT_srmr     = fitmeasures(fit_hex_ext)["tli.scaled"],
+    HEX_AGR_srmr     = fitmeasures(fit_hex_agr)["tli.scaled"],
+    HEX_CNS_srmr     = fitmeasures(fit_hex_cns)["tli.scaled"],
+    HEX_OPN_srmr     = fitmeasures(fit_hex_opn)["tli.scaled"]
+  )
+
+c_rmsea <- 
+  c(
+    HEX_ALT_rmsea     = fitmeasures(fit_HEX_ALT)["rmsea.scaled"],
+    HEX_AGR_FLX_rmsea = fitmeasures(fit_HEX_AGR_FLX)["rmsea.scaled"],
+    HEX_AGR_FOR_rmsea = fitmeasures(fit_HEX_AGR_FOR)["rmsea.scaled"],
+    HEX_AGR_GEN_rmsea = fitmeasures(fit_HEX_AGR_GEN)["rmsea.scaled"],
+    HEX_AGR_PAT_rmsea = fitmeasures(fit_HEX_AGR_PAT)["rmsea.scaled"],
+    HEX_CNS_DIL_rmsea = fitmeasures(fit_HEX_CNS_DIL)["rmsea.scaled"],
+    HEX_CNS_ORG_rmsea = fitmeasures(fit_HEX_CNS_ORG)["rmsea.scaled"],
+    HEX_CNS_PER_rmsea = fitmeasures(fit_HEX_CNS_PER)["rmsea.scaled"],
+    HEX_CNS_PRU_rmsea = fitmeasures(fit_HEX_CNS_PRU)["rmsea.scaled"],
+    HEX_EMO_ANX_rmsea = fitmeasures(fit_HEX_EMO_ANX)["rmsea.scaled"],
+    HEX_EMO_DEP_rmsea = fitmeasures(fit_HEX_EMO_DEP)["rmsea.scaled"],
+    HEX_EMO_FEA_rmsea = fitmeasures(fit_HEX_EMO_FEA)["rmsea.scaled"],
+    HEX_EMO_SEN_rmsea = fitmeasures(fit_HEX_EMO_SEN)["rmsea.scaled"],
+    HEX_EXT_BOL_rmsea = fitmeasures(fit_HEX_EXT_BOL)["rmsea.scaled"],
+    HEX_EXT_LIV_rmsea = fitmeasures(fit_HEX_EXT_LIV)["rmsea.scaled"],
+    HEX_EXT_SOC_rmsea = fitmeasures(fit_HEX_EXT_SOC)["rmsea.scaled"],
+    HEX_EXT_SSE_rmsea = fitmeasures(fit_HEX_EXT_SSE)["rmsea.scaled"],
+    HEX_HOH_FAI_rmsea = fitmeasures(fit_HEX_HOH_FAI)["rmsea.scaled"],
+    HEX_HOH_GRE_rmsea = fitmeasures(fit_HEX_HOH_GRE)["rmsea.scaled"],
+    HEX_HOH_MOD_rmsea = fitmeasures(fit_HEX_HOH_MOD)["rmsea.scaled"],
+    HEX_HOH_SIN_rmsea = fitmeasures(fit_HEX_HOH_SIN)["rmsea.scaled"],
+    HEX_OPN_AES_rmsea = fitmeasures(fit_HEX_OPN_AES)["rmsea.scaled"],
+    HEX_OPN_CRE_rmsea = fitmeasures(fit_HEX_OPN_CRE)["rmsea.scaled"],
+    HEX_OPN_INQ_rmsea = fitmeasures(fit_HEX_OPN_INQ)["rmsea.scaled"],
+    HEX_OPN_UNC_rmsea = fitmeasures(fit_HEX_OPN_UNC)["rmsea.scaled"],
+    NFP_ANO_rmsea     = fitmeasures(fit_NFP_ANO)["rmsea.scaled"],
+    NFP_COM_rmsea     = fitmeasures(fit_NFP_COM)["rmsea.scaled"],
+    NFP_GEN_rmsea     = fitmeasures(fit_NFP_GEN)["rmsea.scaled"],
+    NFP_GOV_rmsea     = fitmeasures(fit_NFP_GOV)["rmsea.scaled"],
+    NFP_INF_rmsea     = fitmeasures(fit_NFP_INF)["rmsea.scaled"],
+    NFP_PHY_rmsea     = fitmeasures(fit_NFP_PHY)["rmsea.scaled"],
+    NFP_PSY_rmsea     = fitmeasures(fit_NFP_PSY)["rmsea.scaled"],
+    NFP_SOC_rmsea     = fitmeasures(fit_NFP_SOC)["rmsea.scaled"],
+    HEX_HOH_srmr     = fitmeasures(fit_hex_hoh)["rmsea.scaled"],
+    HEX_EMO_srmr     = fitmeasures(fit_hex_emo)["rmsea.scaled"],
+    HEX_EXT_srmr     = fitmeasures(fit_hex_ext)["rmsea.scaled"],
+    HEX_AGR_srmr     = fitmeasures(fit_hex_agr)["rmsea.scaled"],
+    HEX_CNS_srmr     = fitmeasures(fit_hex_cns)["rmsea.scaled"],
+    HEX_OPN_srmr     = fitmeasures(fit_hex_opn)["rmsea.scaled"]
+  )
+
+c_srmr <- 
+  c(
+    HEX_ALT_srmr     = fitmeasures(fit_HEX_ALT)["srmr"],
+    HEX_AGR_FLX_srmr = fitmeasures(fit_HEX_AGR_FLX)["srmr"],
+    HEX_AGR_FOR_srmr = fitmeasures(fit_HEX_AGR_FOR)["srmr"],
+    HEX_AGR_GEN_srmr = fitmeasures(fit_HEX_AGR_GEN)["srmr"],
+    HEX_AGR_PAT_srmr = fitmeasures(fit_HEX_AGR_PAT)["srmr"],
+    HEX_CNS_DIL_srmr = fitmeasures(fit_HEX_CNS_DIL)["srmr"],
+    HEX_CNS_ORG_srmr = fitmeasures(fit_HEX_CNS_ORG)["srmr"],
+    HEX_CNS_PER_srmr = fitmeasures(fit_HEX_CNS_PER)["srmr"],
+    HEX_CNS_PRU_srmr = fitmeasures(fit_HEX_CNS_PRU)["srmr"],
+    HEX_EMO_ANX_srmr = fitmeasures(fit_HEX_EMO_ANX)["srmr"],
+    HEX_EMO_DEP_srmr = fitmeasures(fit_HEX_EMO_DEP)["srmr"],
+    HEX_EMO_FEA_srmr = fitmeasures(fit_HEX_EMO_FEA)["srmr"],
+    HEX_EMO_SEN_srmr = fitmeasures(fit_HEX_EMO_SEN)["srmr"],
+    HEX_EXT_BOL_srmr = fitmeasures(fit_HEX_EXT_BOL)["srmr"],
+    HEX_EXT_LIV_srmr = fitmeasures(fit_HEX_EXT_LIV)["srmr"],
+    HEX_EXT_SOC_srmr = fitmeasures(fit_HEX_EXT_SOC)["srmr"],
+    HEX_EXT_SSE_srmr = fitmeasures(fit_HEX_EXT_SSE)["srmr"],
+    HEX_HOH_FAI_srmr = fitmeasures(fit_HEX_HOH_FAI)["srmr"],
+    HEX_HOH_GRE_srmr = fitmeasures(fit_HEX_HOH_GRE)["srmr"],
+    HEX_HOH_MOD_srmr = fitmeasures(fit_HEX_HOH_MOD)["srmr"],
+    HEX_HOH_SIN_srmr = fitmeasures(fit_HEX_HOH_SIN)["srmr"],
+    HEX_OPN_AES_srmr = fitmeasures(fit_HEX_OPN_AES)["srmr"],
+    HEX_OPN_CRE_srmr = fitmeasures(fit_HEX_OPN_CRE)["srmr"],
+    HEX_OPN_INQ_srmr = fitmeasures(fit_HEX_OPN_INQ)["srmr"],
+    HEX_OPN_UNC_srmr = fitmeasures(fit_HEX_OPN_UNC)["srmr"],
+    NFP_ANO_srmr     = fitmeasures(fit_NFP_ANO)["srmr"],
+    NFP_COM_srmr     = fitmeasures(fit_NFP_COM)["srmr"],
+    NFP_GEN_srmr     = fitmeasures(fit_NFP_GEN)["srmr"],
+    NFP_GOV_srmr     = fitmeasures(fit_NFP_GOV)["srmr"],
+    NFP_INF_srmr     = fitmeasures(fit_NFP_INF)["srmr"],
+    NFP_PHY_srmr     = fitmeasures(fit_NFP_PHY)["srmr"],
+    NFP_PSY_srmr     = fitmeasures(fit_NFP_PSY)["srmr"],
+    NFP_SOC_srmr     = fitmeasures(fit_NFP_SOC)["srmr"],
+    HEX_HOH_srmr     = fitmeasures(fit_hex_hoh)["srmr"],
+    HEX_EMO_srmr     = fitmeasures(fit_hex_emo)["srmr"],
+    HEX_EXT_srmr     = fitmeasures(fit_hex_ext)["srmr"],
+    HEX_AGR_srmr     = fitmeasures(fit_hex_agr)["srmr"],
+    HEX_CNS_srmr     = fitmeasures(fit_hex_cns)["srmr"],
+    HEX_OPN_srmr     = fitmeasures(fit_hex_opn)["srmr"]
+  )
+
+tab_des <- 
+  data.frame(
+    Variable = factor(
+      gsub('.{2}$', '', names(c_m)), 
+      levels = c(vars_pers_all, vars_pri),
+      labels = c(vars_pers_all_txt, vars_pri_txt)),
+    M = c_m,
+    SD = c_sd,
+    REL = c_rel,
+    CFI = c_cfi,
+    TLI = c_tli,
+    SRMS = c_srmr,
+    RMSEA = c_rmsea
+  ) %>% 
+  arrange(Variable) %>% 
+  mutate(
+    across(
+      -Variable,
+      ~ round(.x, 2)
+    )
+  ) %>% 
+  remove_rownames()
+tab_des
+```
+
+# Figures
+## Correlation
+
+```{r cache=F, fig.height=6, fig.width=12}
+# First extract data
+tab_cor <- 
+  d %>% 
+  correlation(
+    select = 
+      c(
+        vars_ses, 
+        paste0(
+          c(vars_pers_dim, vars_pers_fac), 
+        "_M"
+        )
+      ),
+    select2 = paste0(vars_pri, "_M"),
+    ci = .90) %>% 
   as.data.frame() %>% 
-  filter(op == "~", lhs %in% vars_pri) %>% 
-  select("Need for privacy" = lhs, "Predictor" = rhs, Estimate = est.std, ci.lower, ci.upper) %>% 
-  mutate(Predictor = factor(Predictor, levels = c(vars_pers_fac, vars_ses), labels = c(vars_pers_fac_txt, vars_ses_txt)),
-         `Need for privacy` = factor(`Need for privacy`, levels = c(vars_pri), labels = c(vars_pri_txt)),
-         Predictor_cat = c(vars_pers_dim_txt %>% rep(each = 4), "Sociodemographics" %>% rep(7)) %>% rep(length(vars_pri_txt)))
-
-reg_fig <- ggplot(tab_reg, aes(x = Estimate, y = Predictor)) + 
-  coord_cartesian(xlim = c(-.5, .5)) +
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_vline(xintercept = -.1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
-  geom_vline(xintercept = .1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
-  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper),
-                lwd = .75, height = .2, position = position_dodge(-.7)) +
-  geom_point(size = 1.5, position = position_dodge(-.7)) +
-  scale_x_continuous(breaks = c(-.3, 0, .3)) + 
+  mutate(
+    across(
+      c(r, CI_low, CI_high),
+      ~ round(.x, 2)
+    )
+  ) %>% 
+  rename(
+    "Need for privacy" = Parameter2,
+    "Predictor" = Parameter1,
+    "Estimate" = r
+  ) %>% 
+  mutate(
+    category = case_when(
+      Predictor %in% vars_ses ~ "Sociodemographics",
+      Predictor %in% paste0(vars_pers_hoh, "_M") ~ "Honesty humility",
+      Predictor %in% paste0(vars_pers_emo, "_M") ~ "Emotionality", 
+      Predictor %in% paste0(vars_pers_ext, "_M") ~ "Extraversion",
+      Predictor %in% paste0(vars_pers_agr, "_M") ~ "Agreeableness", 
+      Predictor %in% paste0(vars_pers_cns, "_M") ~ "Conscientiousness",
+      Predictor %in% paste0(vars_pers_opn, "_M") ~ "Openness",
+      .default = "missing"
+    ),
+    "Need for privacy" = factor(
+      `Need for privacy`,
+      levels = paste0(vars_pri, "_M"),
+      labels = vars_pri_txt
+    ),
+    category = factor(
+      category,
+      levels = c(vars_pers_dim_txt, "Sociodemographics")
+    ), 
+    relevant = case_when(
+      CI_low <= -.1 & CI_high <= -.1 | CI_low >= .1 & CI_high >= .1 ~ "yes",
+      .default = "no"
+    ),
+    Predictor = factor(
+      x = Predictor,
+      levels = c(
+        paste0(vars_pers_all, "_M"),
+        vars_ses),
+      labels = vars_pred_all_txt
+    )
+  ) %>% 
+  select(
+    -Method, -p, -df_error, -t, -CI
+  )
+
+fig_reg <- ggplot(
+  tab_reg, aes(x = Estimate, y = Predictor, color = relevant)
+  ) + 
+  coord_cartesian(xlim = c(-.7, .3)) +
+  geom_vline(xintercept = 0, lwd = .5, colour = "darkgrey") + 
+  geom_vline(xintercept = -.1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
+  geom_vline(xintercept = .1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
+  geom_errorbarh(
+    aes(xmin = CI_low, xmax = CI_high),
+    lwd = .5, height = .4, position = position_dodge(-.7)
+    ) +
+  geom_point(size = 1, position = position_dodge(-.7)) +
+#   geom_pointrange(aes(xmin = CI_low, xmax = CI_high), size = .2) + 
+  scale_x_continuous(
+    breaks = c(-.6, -.4, -.2, 0, .2, .4),
+    labels = c("-.6", "-.4", "-.2", "0", ".2", ".4")
+    ) + 
+  scale_y_discrete(limits=rev) +
+  scale_color_manual(values = c("grey", "black")) +
+  labs(
+    title = "Predicting the need for privacy",
+    x = "Correlation coefficient"
+    ) +
+  # theme_minimal() +
   theme(
@@
     plot.title = element_text(hjust = .5),
-    # panel.spacing = unit(.9, "lines"),
-    text = element_text(size = 12),
+    text = element_text(size = 14),
     axis.text.y = element_text(hjust = 1),
+    axis.text.x = element_text(size = 10),
     legend.position = "none"
     ) + 
-    facet_grid(Predictor_cat ~ `Need for privacy`, scales = "free_y")
-suppressWarnings(print(reg_fig, warning = F))
-
-ggsave("figures/fig_reg.png", width = 9, height = 10)
-```
+  facet_grid(category ~ `Need for privacy`, scales = "free_y")
+
+suppressWarnings(print(fig_cor, warning = F))
+
+ggsave("figures/fig_cor.png", width = 10, height = 12)
+```
+
+## Regression
+
+```{r fig.height=6, fig.width=12}
+tab_reg <- 
+  standardizedsolution(fit_reg, ci = TRUE) %>% 
+  as.data.frame() %>% 
+  filter(
+    op == "~", 
+    lhs %in% paste0(vars_pri, "_M")
+    ) %>% 
+  select(
+    "Need for privacy" = lhs, 
+    "Predictor" = rhs, 
+    Estimate = est.std, 
+    CI_low = ci.lower, 
+    CI_high = ci.upper
+    ) %>% 
+  mutate(
+    Predictor = factor(
+      Predictor, 
+      levels = c(paste0(vars_pers_dim, "_M"), vars_ses), 
+      labels = c(vars_pers_dim_txt, vars_ses_txt)
+      ),
+    `Need for privacy` = factor(
+      `Need for privacy`, 
+      levels = paste0(vars_pri, "_M"), 
+      labels = c(vars_pri_txt)
+      ),
+    category = c(
+      rep("Personality", 6),
+      "Sociodemographics" %>% 
+        rep(7)) %>% 
+      rep(length(vars_pri_txt)),
+    relevant = case_when(
+      CI_low <= -.1 & CI_high <= -.1 | CI_low >= .1 & CI_high >= .1 ~ "yes",
+      .default = "no"
+      )
+    )
+
+fig_reg <- ggplot(
+  tab_reg, aes(x = Estimate, y = Predictor, color = relevant)
+  ) + 
+  coord_cartesian(xlim = c(-.8, .3)) +
+  geom_vline(xintercept = 0, lwd = .5, colour = "darkgrey") + 
+  geom_vline(xintercept = -.1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
+  geom_vline(xintercept = .1, lwd = .5, colour = "darkgrey", linetype = "dashed") + 
+  geom_errorbarh(
+    aes(xmin = CI_low, xmax = CI_high),
+    lwd = .5, height = .4, position = position_dodge(-.7)
+    ) +
+  geom_point(size = 1, position = position_dodge(-.7)) +
+  scale_x_continuous(
+    breaks = c(-.8, -.6, -.4, -.2, 0, .2, .4),
+    labels = c("-.8", "-.6", "-.4", "-.2", "0", ".2", ".4")
+    ) + 
+  scale_y_discrete(limits=rev) +
+  scale_color_manual(values = c("grey", "black")) +
+  labs(
+    title = "Explaining the need for privacy",
+    x = "Regression coefficient"
+    ) +
+  # theme_minimal() +
+  theme(
+    axis.title.y = element_blank(),
+    plot.title = element_text(hjust = .5),
+    text = element_text(size = 14),
+    axis.text.y = element_text(hjust = 1),
+    axis.text.x = element_text(size = 10),
+    legend.position = "none"
+    ) + 
+  facet_grid(category ~ `Need for privacy`, scales = "free_y")
+
+suppressWarnings(print(fig_reg, warning = F))
+
+ggsave("figures/fig_reg.png", width = 10, height = 5)
+```
+
+# Save Workspace
 
 ```{r cache=F}
-save.image("data/workspace.RData")
-```
+save.image("data/workspace_2.RData")
+```

### 2024-02-07 proposal.Rmd
- Collected and analzed data - Wrote results and discussion section

@@
   Tobias Dienlin, Department of Communication, University of Vienna, Austria; Miriam Metzger, Department of Communication, University of California, Santa Barbara, United States of America.
+
+note: |
+  This paper is in-principle-accepted at as a Stage 1 Registered Report at Collabra.
 
@@
 <!-- Or do they have more to hide? -->
-Asking **these questions** seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
+Asking these questions seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
 Consider the “nothing-to-hide” argument [@soloveVeGotNothing2007], which is that people who oppose state surveillance only do so because they have something to hide---because if you have nothing to hide, you would have nothing to fear.
@@
 @pedersenDimensionsPrivacy1979  conducted an empirical factor analysis of 94 privacy-related items, finding six dimensions of privacy: 
-**reserve ("unwillingness to be with and talk with others, especially strangers," p.
+reserve ("unwillingness to be with and talk with others, especially strangers," p.
 1293); isolation ("desire to be alone and away from others," p.
@@
 1293), and anonymity ("wanting to go unnoticed in a crowd and not wishing to be the center of group attention," p.
-1293).**
+1293).
 <!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
@@
 -->
-**Building on these understandings of privacy,** in this study we employ a multifaceted model of need for privacy. 
-We focus on _vertical_ privacy with regard to people’s felt need for **withdrawal from surveillance by a) the government and b) private companies;** 
+Building on these understandings of privacy, in this study we employ a multifaceted model of need for privacy. 
+We focus on _vertical_ privacy with regard to people’s felt need for withdrawal from surveillance by a) the government and b) private companies; 
 _horizontal_ privacy in terms of the perceived need for (c) psychological, (d) social and/or (e) physical withdrawal from other people; 
 and _general_ privacy as captured by people’s felt need for (f) informational privacy, (g) anonymity, and (h) privacy in general.
-**Although all of these dimensions were defined and established in prior research, combining these dimensions into one single comprehensive measure of privacy represents a novel approach.**
+Although all of these dimensions were defined and established in prior research, combining these dimensions into one single comprehensive measure of privacy represents a novel approach.
 
-**Acknowledging that various understandings of personality exist, we operationalize personality using the factors and facets of the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].**
+Acknowledging that various understandings of personality exist, we operationalize personality using the factors and facets of the HEXACO inventory of personality [@leePsychometricPropertiesHEXACO1002018].
 HEXACO is a large and comprehensive operationalization of personality, and thus is less likely to miss potentially relevant aspects than other operationalizations. 
@@
 
-<!-- **To understand why people desire privacy, we can also adopt an evolutionary perspective.** -->
-**Privacy also has strong evolutionary roots [@acquistiHowPrivacyMay2022].**
-**Confronted with a threat---for example, the prototypical a tiger---people are inclined to withdraw.**
-**In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.**
-**Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.**
-**Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].**
-**Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities.**
-**Indeed, the need for privacy may have evolved precisely because it offers such advantages.**
+<!-- To understand why people desire privacy, we can also adopt an evolutionary perspective. -->
+Privacy also has strong evolutionary roots [@acquistiHowPrivacyMay2022].
+Confronted with a threat---for example, the prototypical a tiger---people are inclined to withdraw.
+In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.
+Transferred to privacy, we could imagine that if other people, the government, or companies are considered a threat, people are more likely to withdraw and to desire more privacy.
+Conversely, if something is considered a resource, people might open up, approach others, and desire less privacy [@altmanPrivacyConceptualAnalysis1976].
+Privacy also affords the opportunity to hide less socially desirable aspects of the self from others, which may bestow evolutionary advantages in terms of sexual selection or other social benefits and opportunities.
+Indeed, the need for privacy may have evolved precisely because it offers such advantages.
 
@@
 
-**We do not mean to suggest that it is only dishonest people who feel a need for privacy.**
-**Everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].**
-**A recent study confirmed this notion, finding that also those people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].**
-**Our argument is rather that people lower on the honesty HEXACO factor may feel a greater need for privacy.**
+We do not mean to suggest that it is only dishonest people who feel a need for privacy.
+Everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].
+A recent study confirmed this notion, finding that also those people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].
+Our argument is rather that people lower on the honesty HEXACO factor may feel a greater need for privacy.
 Considering all the evidence, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies.
@@
 
-This **assumption** is supported by several empirical studies. 
+This assumption is supported by several empirical studies. 
 People who scored higher on the personality meta-factor plasticity, which is a composite of the two personality factors extraversion and openness, were found to desire less privacy [@mortonMeasuringInherentPrivacy2013].
@@
 
-As a result, we **expect** that people who are more extraverted also need less social privacy and less privacy in general.
+As a result, we expect that people who are more extraverted also need less social privacy and less privacy in general.
 Regarding the other dimensions of privacy, such as privacy from governments or from companies, we do not expect specific effects.
@@
 
-**The arguments discussed above lead to a number of expectations for our data which we delineate below, in order from most to least confidence in terms of identifying significant effects.**
-**First, we strongly assume that more extraverted people will desire less privacy, especially less social privacy.**
-**We also expect that people who are less honest will express greater need for privacy.**
-**We further assume that more conscientious people will desire more privacy and that more agreeable people may desire less privacy.**
-**Yet it is largely unclear how privacy needs relate to openness to experience and emotionality.**
-**In terms of the sociodemographic variables, we expect females likely need more informational and physical privacy, while males will likely report needing more psychological privacy.**
-**Older, more highly educated, and affluent people are also expected to need more privacy, and we anticipate that people who are ethnic minorities or are politically conservative will express greater need for privacy from the government than from other people.**
+The arguments discussed above lead to a number of expectations for our data which we delineate below, in order from most to least confidence in terms of identifying significant effects.
+First, we strongly assume that more extraverted people will desire less privacy, especially less social privacy.
+We also expect that people who are less honest will express greater need for privacy.
+We further assume that more conscientious people will desire more privacy and that more agreeable people may desire less privacy.
+Yet it is largely unclear how privacy needs relate to openness to experience and emotionality.
+In terms of the sociodemographic variables, we expect females likely need more informational and physical privacy, while males will likely report needing more psychological privacy.
+Older, more highly educated, and affluent people are also expected to need more privacy, and we anticipate that people who are ethnic minorities or are politically conservative will express greater need for privacy from the government than from other people.
 
@@
 
-**To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].**
+To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].
 We based our power analysis on a smallest effect size of interest (SESOI; see also below).
@@
 <!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
-**To estimate power, we simulated data."
-**We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10.**
-**We, furthermore, set the latent factor loadings to be $\lambda$ = .85 (the SESOI)**
+To estimate power, we simulated data."
+We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10.
+We, furthermore, set the latent factor loadings to be $\lambda$ = .85 (the SESOI)
 <!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
 <!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
-**Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].**
-**Because balanced alpha and beta errors of 5% are outside of our budget, we opted for balanced alpha and beta errors of 10%.**
-**A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.**
-**To account for potential attrition (see below), we will oversample by five percent, leading to a final sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.**
+Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
+Because balanced alpha and beta errors of 5% are outside of our budget, we opted for balanced alpha and beta errors of 10%.
+A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
+To account for potential attrition (see below), we will oversample by five percent, leading to a final sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
 We obtained sufficient funding to collect a sample of this size.
@@
 
-**We will individually check answers for response patterns such as straight-lining or missing of inverted items.**
-**We will conservatively remove participants with clear response patterns.**
-**We will automatically exclude participants who miss the two attention checks we will implement.**
-**Participants who miss one attention check will be checked individually regarding response patterns.**
-**We will remove participants below the minimum participation age of 18 years.**
-**We will remove respondents with unrealistically fast responses (three standard deviations below the median response time).** 
+We will individually check answers for response patterns such as straight-lining or missing of inverted items.
+We will conservatively remove participants with clear response patterns.
+We will automatically exclude participants who miss the two attention checks we will implement.
+Participants who miss one attention check will be checked individually regarding response patterns.
+We will remove participants below the minimum participation age of 18 years.
+We will remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
 <!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->
 
-**Missing responses will be imputed using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10).** 
-**The analyses will be run with all ten datasets, and the pooled results will be reported.**
+Missing responses will be imputed using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
+The analyses will be run with all ten datasets, and the pooled results will be reported.
 
@@
 
-**We will use two measures as inference criteria: statistical significance and effect size.** 
-**Regarding statistical significance, we will use an alpha value of 10%.**
-**Regarding effect size, we will define a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.**
-**As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25 or -.15 to -.25).**
-**We will consider effects irrelevant if the confidence interval falls completely within the null region (e.g., .02 to .08).**
-**And we will suspend judgement if the confidence intervals partially include the null region (e.g., .05 to .15).**
+We will use two measures as inference criteria: statistical significance and effect size. 
+Regarding statistical significance, we will use an alpha value of 10%.
+Regarding effect size, we will define a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.
+As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25 or -.15 to -.25).
+We will consider effects irrelevant if the confidence interval falls completely within the null region (e.g., .02 to .08).
+And we will suspend judgement if the confidence intervals partially include the null region (e.g., .05 to .15).
 

### 2024-02-07 manuscript.Rmd
- Collected and analzed data - Wrote results and discussion section

--- 2024-02-07 proposal.Rmd
@@
 abstract          : "Privacy is defined as a voluntary withdrawal from society.
-While everyone needs some degree of privacy, we currently know little about people’s privacy needs.
-In this study, we explore the relations between the need for privacy and personality.
-Personality will be operationalized using the HEXACO personality inventory.
-Need for privacy will be measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy).
+While everyone needs some degree of privacy, we currently know little about who needs how much.
+In this study, we explored the relations between the need for privacy and personality.
+Personality was operationalized using the HEXACO personality inventory.
+Need for privacy was measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy).
 A sample of 1,576 respondents representative of the U.S.
-in terms of age, gender, and ethnicity will be collected.
-The correlations between privacy, personality, and sociodemographics will be analyzed using structural equation modeling."
+in terms of age, gender, and ethnicity was collected.
+The results showed several substantial relationships: More extraverted people needed substantially more privacy.
+People less honest, less fair, and less altruistic needed more privacy, lending some support to the nothing to hide-argument.
+More conservative respondents needed more privacy from the government."
 keywords          : "Privacy, need for privacy, personality, HEXACO"
@@
   - \usepackage{float}
+  - \usepackage{setspace}
+  - \AtBeginEnvironment{tabular}{\singlespacing}
+  - \AtBeginEnvironment{lltable}{\singlespacing}
+  - \AtBeginEnvironment{tablenotes}{\doublespacing}
+  - \captionsetup[table]{font={stretch=1.5}}
+  - \captionsetup[figure]{font={stretch=1.5}}
 ---
@@
 # devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
-packages <- c("devtools", "english", "ggplot2", "kableExtra", "lavaan", 
-              "magrittr", "papaja", "semPlot", "simsem", "td", "tidyverse")
-lapply(packages, library, character.only = TRUE)
-load("data/workspace.RData")
+library(devtools)
+library(english)
+library(ggplot2)
+library(kableExtra)
+library(lavaan)
+library(magrittr)
+library(naniar)
+library(papaja)
+library(semPlot)
+library(simsem)
+library(td)
+library(tidyverse)
+
+load("data/workspace_2.RData")
+
+source("custom_functions.R")
 
@@
 In predicting the need for privacy, we will primarily focus on the facets, because it is unlikely that the very specific need for privacy dimensions will relate closely to more general personality factors [@bansalImpactPersonalDispositions2010; @junglasPersonalityTraitsConcern2008].
-And for reasons of scope, below we cannot discuss all four facets for all six factors. Instead, we focus on those we consider most relevant. However, all we be analyzed empirically.
+And for reasons of scope, below we cannot discuss all four facets for all six factors. Instead, we focus on those we consider most relevant. However, all will be analyzed empirically.
 
@@
 <!-- To understand why people desire privacy, we can also adopt an evolutionary perspective. -->
-Privacy also has strong evolutionary roots [@acquistiHowPrivacyMay2022].
-Confronted with a threat---for example, the prototypical a tiger---people are inclined to withdraw.
+Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].
+Confronted with a threat---for example, the prototypical tiger---people are inclined to withdraw.
 In the presences of opportunities---for example, the unexpected sharing of resources---people open up and approach one another.
@@
 Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
-While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty.
+<!-- While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty. -->
 In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
@@
 Anxious people might hence desire more privacy. 
-People who are more concerned about their privacy (in other words, more anxious about privacy) may be more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
+People who are more concerned about their privacy (in other words, more anxious about privacy) are more likely to self-withdraw online, for example by deleting posts or untagging themselves from linked content to minimize risk [@dienlinExtendedPrivacyCalculus2016].
 On the other hand, the opposite may also be true: 
@@
 Arguably, all facets are about being in control, about reducing relevant risks and future costs.
-Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully, might prefer to have more privacy because it affords them greater control.
+Because control is a central part of privacy [@westinPrivacyFreedom1967], people who avoid risks, who deliberate, and who plan ahead carefully might prefer to have more privacy because it affords them greater control.
 Especially if others are considered a threat, being risk averse might increase the desire for more horizontal privacy. 
@@
 
-This section describes how we determine the sample size, data exclusions, the analyses, and all measures in the study.
-The Study will be conducted as an online questionnaire, programmed with Qualtrics.
-A preview of the survey can be found [here](https://compcommlab.eu.qualtrics.com/jfe/preview/previewId/5c6193c9-12a4-424f-9808-a7c6e74247c1/SV_9ppRmr32VrmeAnA?Q_CHL=preview&Q_SurveyVersionID=current).
+This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
+The Study was conducted as an online questionnaire, programmed with Qualtrics.
+The survey can be found in the [online supplementary material](https://osf.io/e47yw/files/osfstorage/65c363e69b32ca0b4397f002).
 
@@
 This study builds on a prior project in which we analyzed the same research question [@dienlinWhoNeedsPrivacy2019]. 
-This study was already submitted to Collabra, but rejected.
+This study was already submitted to Collabra but rejected.
 The main reasons were that the sample was too small, that not one coherent personality inventory was used, that most privacy measures were designed ad-hoc, and that the inferences were too ambitious. 
 We hence decided to treat our prior project as a pilot study and to address the criticism by conducting a new study.
-In this new study, we redevelop our study design, we collect a larger sample, implement the HEXACO inventory together with established need for privacy measures, and overall adopt a more exploratory perspective.
-Being our central construct of interest, we also develop a small number of new items to have a more comprehensive measure of need for privacy.
+In this new study, we redeveloped our study design, collected a larger sample, implemented the HEXACO inventory together with established need for privacy measures, and overall adopted a more exploratory perspective.
+Being our central construct of interest, we also developed a small number of new items to have a more comprehensive measure of need for privacy.
 
@@
 
-Participants will be collected from the professional online survey panel Prolific. 
-The sample will be representative of the US in terms of age, gender, and ethnicity. 
+Participants were collected from the professional online survey panel Prolific. 
+The sample was representative of the US in terms of age, gender, and ethnicity. 
 The study received IRB approval from the University of Vienna (#20210805_067).
-We calculated that participation will take approximately 15 minutes. 
-We will pay participants \$2.00 for participation, which equals an hourly wage of \$8.00.
+Participation took on average `r round(time_m, 0) ` minutes. 
+We paid participants \$2.00 for participation, which equals an hourly wage of \$8.00.
 
 To determine sample size, we ran a priori power analyses using the R package _simsem_ [@R-simsem].
-We based our power analysis on a smallest effect size of interest (SESOI; see also below).
+We based our power analysis on a smallest effect size of interest (SESOI; see below).
 We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992].
@@
 <!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
-To estimate power, we simulated data."
-We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10.
-We, furthermore, set the latent factor loadings to be $\lambda$ = .85 (the SESOI)
+To estimate power, we simulated data.
+We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10 (the SESOI).
+We, furthermore, set the latent factor loadings to be $\lambda$ = .85.
 <!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
@@
 Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
-Because balanced alpha and beta errors of 5% are outside of our budget, we opted for balanced alpha and beta errors of 10%.
+Because balanced alpha and beta errors of 5% were outside of our budget, we opted for balanced alpha and beta errors of 10%.
 A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
-To account for potential attrition (see below), we will oversample by five percent, leading to a final sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
-We obtained sufficient funding to collect a sample of this size.
+To account for potential attrition (see below), we oversampled by five percent, leading to a planned sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
 <!-- Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 10% and an effect size of at least _r_ = .10.  -->
+In the end, `r n_finished` respondents successfully finished our study, slightly exceeding our plans.
 
@@
 
-We will individually check answers for response patterns such as straight-lining or missing of inverted items.
-We will conservatively remove participants with clear response patterns.
-We will automatically exclude participants who miss the two attention checks we will implement.
-Participants who miss one attention check will be checked individually regarding response patterns.
-We will remove participants below the minimum participation age of 18 years.
-We will remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
+We individually checked answers for response patterns such as straight-lining or missing of inverted items.
+We planned to conservatively remove participants with clear response patterns.
+However, as no clear patterns emerged we maintained all participants.
+We automatically excluded participants who missed the two attention checks we implemented.
+Overall, 30 participants were filtered out automatically by Prolific, not counting toward our quota.
+Participants who missed one attention check were checked individually regarding response patterns.
+Again, no clear patterns emerged.
+We planned to remove participants below the minimum participation age of 18 years.
+As no minors took part in our study we did not exclude any participant for this reason.
+We planned to remove respondents with unrealistically fast responses (three standard deviations below the median response time). 
+The median response time was `r round(time_med / 60, 0)` minutes and the standard deviation `r round(time_sd / 60, 0)` minutes. 
+Hence, three SDs below median was `r round(time_crit_init / 60, 0)` minutes, hence not informative. 
+Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
+We removed `r n_speeding %>% english::english()` participants for this reason.
 <!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->
 
-Missing responses will be imputed using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
-The analyses will be run with all ten datasets, and the pooled results will be reported.
+We planned to impute missing responses using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
+However, as there were only `r n_miss(d)` answers missing in total (`r round(prop_miss(d) * 100, 3)` percent), we decided not to impute any data.
+The final sample size was _N_ = `r nrow(d)`.
 
-## Planned Analyses
+## Analyses
 
@@
 <!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
-The factorial validity of the measures and the relations will be tested using structural equation modeling. 
-If Mardia’s test shows that the assumption of multivariate normality is violated, we will use the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator. 
-We will test each scale in a confirmatory factor analysis. 
-To assess model fit, we will use more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
-In cases of misfit, we will conservatively alter models using an a priori defined analysis pipeline (see online supplementary material).
-As a “reality check,” we will test items for potential ceiling and floor effects. If means are below 1.5 or above 6.5, these items will be excluded.
+The factorial validity of the measures and the relations were tested using structural equation modeling. 
+If Mardia’s test showed that the assumption of multivariate normality was violated, we used the more robust Satorra-Bentler scaled and mean-adjusted test statistic (MLM) as estimator (or, in the few cases of missing data MLR plus FIML estimation).
+We tested each scale in a confirmatory factor analysis. 
+To assess model fit, we used more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
+In cases of misfit, we conservatively altered models using an a priori defined analysis pipeline (see online supplementary material).
+As a “reality check,” we tested items for potential ceiling and floor effects. 
+If means were below 1.5 or above 6.5, we preregistered to exclude these items.
+However, as no item was outside these threshold, no items were excluded.
 
-We want to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
-Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we will analyze the variables' bivariate relations. 
-To predict the need for privacy, we will first use the six personality factors.
-Afterward, we will predict privacy using the more specific facets. 
-To get a first idea of the variables' potential causal relations, we will also run a multiple structural regression model.
+We wanted to find out _who_ needs privacy, and not so much _what causes_ the need for privacy.
+Hence, to answer our research question, in a joint model combining all variables (including sociodemographic variables) we analyzed the variables' bivariate relations. 
+To predict the need for privacy, we first used the six personality factors.
+Afterward, we predicted privacy using the more specific facets. 
+To get a first idea of the variables' potential causal relations, we also planned to run latent structural regression models.
+However, because model fit was not acceptable we analyzed the potential effects in a multiple regression using the mean values of the observed scores. 
 <!-- We will also test which individual items best predict need for privacy. -->
 
-We will use two measures as inference criteria: statistical significance and effect size. 
-Regarding statistical significance, we will use an alpha value of 10%.
-Regarding effect size, we will define a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.
-As proposed by @dienesUsingBayesGet2014, we will consider effects to be meaningful if the confidence interval falls outside of the null region (e.g., .15 to .25 or -.15 to -.25).
-We will consider effects irrelevant if the confidence interval falls completely within the null region (e.g., .02 to .08).
-And we will suspend judgement if the confidence intervals partially include the null region (e.g., .05 to .15).
+We used two measures as inference criteria: statistical significance and effect size. 
+Regarding statistical significance, we used an alpha value of 10%.
+Regarding effect size, we defined a SESOI of _r_ = .10, and thereby a null-region ranging from -.10 to .10.
+As proposed by @dienesUsingBayesGet2014, we considered effects to be meaningful if the confidence interval fell outside of the null region (e.g., .15 to .25 or -.15 to -.25).
+We considered effects irrelevant if the confidence interval fell completely within the null region (e.g., .02 to .08).
+And we suspended judgement if the confidence intervals partially included the null region (e.g., .05 to .15).
 
 Fully latent SEMs seldom work instantly, often requiring modifications to achieve satisfactory model fit.
-Although we explicate our analysis pipeline, there still remain several researcher degrees of freedom. 
-We decided to use fully latent SEMs because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
-Combining several items into latent factors helps reduce noise and thereby the beta error. 
-To provide context, in the online supplementary material (OSM) we will also share the results of alternative analyses, such as correlations of average scores.
-
-We anticipate to finish the project three months after our registration was accepted.
+Although we explicated our analysis pipeline, there still remained several researcher degrees of freedom. 
+We planned to use fully latent SEM because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
+However, as several of the scales showed suboptimal fit, we decided to report the more conservative correlations of average scores.
+In the online supplementary material (OSM) we also share the results of alternative analyses, such as fully latent SEMs.
 
@@
 
-All items will be answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
-A list of all the items that we will use are reported in the online supplementary material. 
-The personality and privacy items will be presented in random order, and the sociodemographic questions will be asked at the end.
-We will later report also the results of the CFAs/EFAs, as well as item statistics and their distribution plots.
+All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
+A list of all the items that we were used are reported in the online supplementary material. 
+The personality and privacy items were presented in random order, and the sociodemographic questions were asked at the end.
+Online we also report all item statistics and their distribution plots.
 
@@
 Although there exist several operationalizations of need for privacy [@bussPsychologicalDimensionsSelf2001; @pedersenDimensionsPrivacy1979; @frenerDevelopmentValidationNeed2023; @marshallDimensionsPrivacyPreferences1974], we are not aware of one encompassing, comprehensive, and up-to-date scale.
-Hence, we use both existing scales and self-developed items, some of which were tested in our pilot study. 
-Ad-hoc scales were or will be (preliminarily) validated using the following procedure:
+Hence, we used both existing scales and self-developed items, some of which were tested in our pilot study. 
+Ad-hoc scales were validated using the following procedure:
 We (a) collected qualitative feedback from three different privacy experts;[^experts]
-(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, we will assess convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) all items will be analyzed in confirmatory factor analyses as outlined above.
+(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, assessed convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) analyzed all items in confirmatory factor analyses as outlined above.
 
@@
 
-Overall, we will collect 32 items measuring need for privacy, with eight subdimensions that all consist of four items each. 
-Three subdimensions capture horizontal privacy---namely _psychological_, _social_, and _physical_ privacy from other individuals. 
+Overall, we collected 32 items measuring need for privacy, with eight subdimensions that all consisted of four items each. 
+Three subdimensions captured horizontal privacy---namely _psychological_, _social_, and _physical_ privacy from other individuals. 
 Psychological and physical privacy were adopted from @frenerDevelopmentValidationNeed2023.
 Because @frenerDevelopmentValidationNeed2023 could not successfully operationalize the dimension of social privacy, building on @burgoonPrivacyCommunication1982 we self-designed a new social privacy dimension, which in the prestudy showed satisfactory fit.
-Two subdimensions measure vertical privacy.
-The first subdimension is _government surveillance_, which represents the extent to which people want the government to abstain from collecting information about them. 
+Two subdimensions measured vertical privacy.
+The first subdimension was _government surveillance_, which represents the extent to which people want the government to abstain from collecting information about them. 
 The scale was pretested and showed good factorial validity. 
-The second subdimension is need for privacy from _companies_, which we will measure using four new self-designed items.
-Finally, three subdimensions capture general privacy. 
-The first subdimension is _informational_ privacy, with items adopted from @frenerDevelopmentValidationNeed2023.
-The second subdimension is _anonymity_, which captures the extent to which people feel the need to avoid identification in general.
+The second subdimension was need for privacy from _companies_, which we measured using four new self-designed items.
+Finally, three subdimensions captured general privacy. 
+The first subdimension was _informational_ privacy, with items adopted from @frenerDevelopmentValidationNeed2023.
+The second subdimension was _anonymity_, which captured the extent to which people feel the need to avoid identification in general.
 The scale was pretested and showed good factorial validity; one new item was designed for this study.
-Third, we will also collect a new self-developed measure of _general_ need for privacy.
+Third, we also collected a new self-developed measure of _general_ need for privacy.
 
@@
 
-Personality will be measured using the HEXACO personality inventory. 
+Personality were measured using the HEXACO personality inventory. 
 The inventory consists of six factors with four facets each, including the additional meta scale of "altruism".
@@
 
-To visualize how results might look like, we have simulated some random data. Please note that these results are completely random and do not make sense from a theoretical perspective. 
-When calculating the multiple regressions, the models did not converge, which is why several estimates could not be computed (see below).
+We first tested the factorial validity of all measures.
+When analyzed individually, most measures showed satisfactory model fit, not requiring any changes.
+Some measures showed satisfactory model fit after small adaptions, such as allowing items to covary.
+In terms of reliability, most measures showed satisfactory results.
+However, some measures such as altruism, unconventionality, or anonymity showed insufficient reliability.
+Instead of strongly adapting measures, we decided to maintain the initial factor structure and did not delete any items or did not introduce substantial changes to the factors.
+For an overview of all measures, their descriptives and factorial validity, see Table \@ref(tab:tab-des).
+Although individually most of the measures showed good fit, when analyzed together fit decreased substantially, below acceptable levels. 
+As a result, we conservatively decided to analyze our data using the variables' observed mean scores.
 
-In Table \@ref(tab:tab-ses), we report how sociodemographics predict need for privacy.
+```{r tab-des, cache=F, warning=F, message=F, prompt=F}
+apa_table(
+  tab_des, 
+  stub_indents = list(
+    "Personality" = c(1:31),
+    "Need for Privacy" = c(32:39)
+    ),
+  align = c("l", rep("r", 8)),
+  caption = "Factorial validity of all measures.",
+  font_size = "small",
+  escape = FALSE
+  )
+```
+
+The need for privacy measures showed good convergent validity.
+If respondents reported higher needs for privacy they were also more concerned about their privacy, with coefficients ranging from _r_ = .21 to _r_ = .73.
+The only exception was the relation between privacy concerns and the need for social privacy, which was very small (_r_ = .09).
+Similarly, if respondents reported higher needs of privacy they also engaged in more privacy behaviors, with coefficients ranging from _r_ = .20 to _r_ = .71
+The only exception was the relation between privacy behavior and the need for social privacy, which was virtually nonexistent (_r_ = .01), and the need for physical privacy, which was very small (_r_ = .09).
+See online supplementary material for all results.
+
+People who reported being less honest and humble needed more anonymity (`r get_res("Honesty humility", "Anonymity")`).
+Looking at facets, more anonymity was needed by people who reported being less fair (`r get_res("Fairness", "Anonymity")`), less modest (`r get_res("Modesty", "Anonymity")`), and less altruistic (`r get_res("Altruism", "Anonymity")`).
+However, less sincere people needed less privacy from companies (`r get_res("Sincerity", "Companies")`) and less privacy in general (`r get_res("Sincerity", "General")`).
+Effects were small or small-to-medium sized.
+
+Several relations between emotionality and need for privacy were found.
+More emotional people needed less psychological privacy (`r get_res("Emotionality", "Psychological")`), less privacy from the government (`r get_res("Emotionality", "Government")`), less anonymity (`r get_res("Emotionality", "Anonymity")`)---but also more physical privacy (`r get_res("Emotionality", "Physical")`).
+More anxious respondents needed substantially more social (`r get_res("Anxiety", "Social")`) and physical privacy (`r get_res("Anxiety", "Physical")`).
+Similarly, more fearful respondents needed more social (`r get_res("Fearfulness", "Social")`) and physical privacy (`r get_res("Fearfulness", "Physical")`).
+More dependent participants generally needed less privacy, including less psychological (`r get_res("Dependence", "Psychological")`) and social privacy (`r get_res("Dependence", "Social")`), less privacy from the government (`r get_res("Dependence", "Government")`), and less informational (`r get_res("Dependence", "Informational")`) and general privacy (`r get_res("Dependence", "General")`).
+A similar picture for more sentimental participants emerged, who needed less psychological (`r get_res("Sentimentality", "Psychological")`) and social privacy (`r get_res("Sentimentality", "Social")`) and less anonymity (`r get_res("Sentimentality", "Anonymity")`).
+
+More extraverted people reported they needed a lot less privacy.
+They wanted less psychological privacy (`r get_res("Extraversion", "Psychological")`), social privacy (`r get_res("Extraversion", "Social")`), and physical privacy (`r get_res("Extraversion", "Physical")`), less informational privacy (`r get_res("Extraversion", "Informational")`) and less anonymity (`r get_res("Extraversion", "Anonymity")`).
+Effect sizes were oftentimes large.
+All facets showed virtually the same relations, with small differences in effect sizes.
+
+More agreeable participants showed a similar pattern, needing less psychological (`r get_res("Agreeableness", "Psychological")`), social privacy (`r get_res("Agreeableness", "Social")`), and physical privacy (`r get_res("Agreeableness", "Physical")`).
+The facets showed virtually the same pattern.
+Effect sizes were substantial, but on the whole smaller than those for extraversion.
+
+Although more conscientious respondents generally needed less privacy, the pattern was varied.
+More conscientious respondents needed less psychological (`r get_res("Conscientiousness", "Psychological")`) and less social privacy (`r get_res("Conscientiousness", "Social")`), as well as less anonymity (`r get_res("Conscientiousness", "Anonymity")`).
+However, when asked about privacy in general more conscientious people responded to need more (`r get_res("Conscientiousness", "General")`).
+Looking at facets of conscientiousness, more organized people needed less social privacy (`r get_res("Organization", "Social")`) and less anonymity (`r get_res("Organization", "Anonymity")`). 
+More prudent participants needed less anonymity (`r get_res("Prudence", "Anonymity")`).
+More diligent people needed less psychological (`r get_res("Diligence", "Psychological")`), social (`r get_res("Diligence", "Social")`), and physical privacy (`r get_res("Diligence", "Physical")`) as well as less anonymity (`r get_res("Diligence", "Anonymity")`).
+At the same time, more perfectionist respondents reported needing more informational (`r get_res("Perfectionism", "Informational")`) and more general privacy (`r get_res("Perfectionism", "General")`).
+
+Whether or not respondents were open to new experiences was largely unrelated to how much privacy they needed.
+Only three facets showed relevant but still small relations. 
+Respondents who reported being more creative needed less psychological (`r get_res("Creativeness", "Psychological", "tab_cor")`) and less social privacy (`r get_res("Creativeness", "Social")`). 
+More inquisitive respondents needed less physical privacy (`r get_res("Inquisitiveness", "Physical")`).
+
+```{r tab-dim, cache=F, warning=F, message=F, prompt=F}
+apa_table(
+  tab_cor_dim_m, 
+  # tab_dim,
+  # stub_indents = list("Sociodemographics" = c(1:6)),
+  col_spanners = list(`Need for privacy` = c(2, 9)),
+  align = c("l", rep("r", 8)),
+  caption = "Predicting the need for privacy dimensions using personality factors.",
+  font_size = "small",
+  escape = FALSE
+  )
+```
+
+```{r tab-fac, cache=F, warning=F, message=F, prompt=F}
+apa_table(
+  # tab_fac,
+  tab_cor_fac_m, 
+  stub_indents = list(
+    "Honesty humility" = c(1:5),
+    "Emotionality" = c(6:9),
+    "Extraversion" = c(10:13),
+    "Agreeableness" = c(14:17),
+    "Conscientiousness" = c(18:21),
+    "Openness to experiences" = c(22:25)
+    ),
+  col_spanners = list(`Need for privacy` = c(2, 9)),
+  align = c("l", rep("r", 8)),
+  caption = "Predicting the need for privacy dimensions using personality facets.",
+  font_size = "small",
+  escape = FALSE
+  )
+```
+
+Not many meaningful relations between sociodemographic variables and need for privacy were found.
+Older participants needed less social (`r get_res("Age", "Social")`) and less physical privacy (`r get_res("Age", "Physical")`). 
+Male participants needed more anonymity (`r get_res("Male", "Anonymity")`). 
+Less social privacy was needed by people in a relationship (`r get_res("Relationship", "Social")`), with a college degree (`r get_res("College", "Social")`), and with higher income (`r get_res("Income", "Social")`).
+People with higher income also reported needing less physical privacy (`r get_res("Income", "Physical")`). 
+More politically conservative respondents reported needing more privacy from the government (`r get_res("Conservatism", "Government")`).
+
+In Table \@ref(tab:tab-dim), we report how the personality dimensions predicted need for privacy.
+In Table \@ref(tab:tab-fac), we report how the personality facets predicted need for privacy.
+In Table \@ref(tab:tab-ses), we report how sociodemographics predicted need for privacy.
+In Figure \@ref(fig:fig-cor), you can find how all variables---dimensions, facets, and sociodemographics---predicted the need for privacy.
 
@@
 # tab_ses %<>% set_names(c("Sociodemographics", vars_pri_txt_brk))
-tab_ses %<>% set_names(c("Sociodemographics", vars_pri_txt_abr))
+tab_cor_ses_m %<>% 
+  set_names(c("Sociodemographics", vars_pri_txt_abr))
 
-apa_table(tab_ses,
+apa_table(tab_cor_ses_m,
           # stub_indents = list("Sociodemographics" = c(1:6)),
+          align = c("l", rep("r", 8)),
           col_spanners = list(`Need for privacy` = c(2, 9)),
@@
 
-In Table \@ref(tab:tab-dim), we report how personality factors predict need for privacy.
+In exploratory analyses we analyzed how personality facets might have potentially caused need for privacy.
+We found that the psychological need for privacy was explained by two variables.
+The need for psychological privacy was potentially reduced by extraversion (`r get_res("Extraversion", "Psychological", "tab_reg")`) and by emotionality (`r get_res("Emotionality", "Psychological", "tab_reg")`).
+The need for informational privacy was also potentially affected by extraversion and emotionality.
+Being more extraverted substantially decreased the need for psychological privacy (`r get_res("Extraversion", "Social", "tab_reg")`), as did being more emotional (`r get_res("Emotionality", "Social", "tab_reg")`).
+Physical privacy was determined by again extraversion, but also by agreeableness and conscientiousness.
+Being more extraverted potentially decreased the need for physical privacy (`r get_res("Extraversion", "Physical", "tab_reg")`); 
+being more agreeable likewise decreased the need for physical privacy (`r get_res("Agreeableness", "Physical", "tab_reg")`);
+however, being more conscientious increased the need for physical privacy (`r get_res("Conscientiousness", "Physical", "tab_reg")`).
+The need for privacy from the government was potentially affected by the two factors of openness and conservatism.
+Being more open to new experiences potentially increased the need for privacy from the government (`r get_res("Openness", "Government", "tab_reg")`), as did being more politically conservative (`r get_res("Conservatism", "Government", "tab_reg")`).
+The need for privacy from companies was potentially affected by the same two factors.
+Being more open to new experiences potentially increased the need for privacy from companies (`r get_res("Openness", "Companies", "tab_reg")`), as did being more politically conservative (`r get_res("Conservatism", "Companies", "tab_reg")`).
+Being extraverted and conscientious potentially affected the need for informational privacy.
 
-```{r tab-dim, cache=F, warning=F, message=F, prompt=F}
-tab_dim %<>% set_names(c("Personality factors", vars_pri_txt_abr))
-
-apa_table(tab_dim,
-          # stub_indents = list("Sociodemographics" = c(1:6)),
-          col_spanners = list(`Need for privacy` = c(2, 9)),
-          caption = "Predicting the need for privacy dimensions using personality factors.",
-          font_size = "small",
-          escape = FALSE
-          )
+```{r fig-cor, fig.cap="Results of bivariate correlations between personality and need for privacy.
+Bold: Effects that are statistically significant and larger than \\textit{r} = .10 / -.10.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='H'}
+# fig_desc
+knitr::include_graphics("figures/fig_cor.png")
 ```
 
-In Table \@ref(tab:tab-fac), we report how personality facets predict need for privacy.
+Whereas being more extraverted likely decreased the need for informational privacy (`r get_res("Extraversion", "Informational", "tab_reg")`), being more conscientious likely increased the need for informational privacy (`r get_res("Conscientiousness", "Informational", "tab_reg")`).
+The need for anonymity was potentially affected by extraversion.
+More extraverted people need less anonymity (`r get_res("Extraversion", "Anonymity", "tab_reg")`).
+Finally, the general need for privacy was potentially affected by four variables.
+Being extraverted again likely decreased the general need for privacy (`r get_res("Conservatism", "Companies", "tab_reg")`).
+However, the general need for privacy was potentially increased by being more conscientious (`r get_res("Conscientiousness", "General", "tab_reg")`), more conservative (`r get_res("Conservatism", "General", "tab_reg")`), and more open to experiences (`r get_res("Openness", "General", "tab_reg")`).
 
-```{r tab-fac, cache=F, warning=F, message=F, prompt=F}
-tab_fac %<>% set_names(c("Personality facets", vars_pri_txt_abr))
+In Figure \@ref(fig:fig-reg), you can find how privacy dimensions and sociodemographics potentially affected the need for privacy.
 
-apa_table(tab_fac,
-          stub_indents = list(
-            "Honesty humility" = c(1:4),
-            "Emotionality" = c(5:8),
-            "Extraversion" = c(9:12),
-            "Agreableness" = c(13:16),
-            "Conscientiousness" = c(17:20),
-            "Openness to experiences" = c(21:24)
-            ),
-          col_spanners = list(`Need for privacy` = c(2, 9)),
-          caption = "Predicting the need for privacy dimensions using personality facets.",
-          font_size = "scriptsize",
-          escape = FALSE
-          )
-```
-
-\newpage
-
-In Figure \@ref(fig:fig-reg), you can find how each personality factor---while holding constant all other personality factors and sociodemographics---predicts need for privacy.
-
-```{r fig-reg, fig.cap="Results of multiple regressions, in which we predict all dimensions of need for privacy using all personality facets and sociodemgraphic factors simultaneously.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='H'}
+```{r fig-reg, fig.cap="Results of multiple regression.
+Bold: Effects that are statistically significant and larger than \\textit{$\\beta$} = .10 / -.10.", out.width = "\\textwidth", cache=F, warning=F, message=F, prompt=F, fig.pos='h'}
 # fig_desc
@@
 ```
+
+# Discussion
+
+In this study we analyzed the relation between personality and need for privacy.
+The data came from _N_ = `r n_used` respondents from the US, representative in terms of age, gender, and ethnicity. 
+The results showed several meaningful relations between personality and need for privacy that were statistically significant (_p_ < 10%) and not trivial in size (i.e., 90% CI _r_ $\geq$ .10).
+In a multiple regression with all personality dimensions and sociodemographic variables, we also explored potential causal effects.
+
+As expected, the need for privacy was most closely related to extraversion.
+Participants who were more extraverted generally needed substantially less privacy. 
+The relation between extraversion and social privacy was particularly large, suggesting that social privacy and extraversion overlap conceptually.
+In addition, almost all subscales of extraversion showed similar patterns: 
+People with greater social boldness, self-esteem, or liveliness all needed substantially less privacy from other people and less physical, psychological, and informational privacy.
+Extraverted people reach out to others, share their inner lives, are confident around others---which reflects in a reduced need for privacy.
+
+The personality factor next closely related to need for privacy was agreeableness. 
+Although this finding aligned with our prior expectation, we were surprised by the strength of the relations.
+More agreeable respondents needed less privacy in general.
+In particular, more agreeable respondents needed substantially less psychological, social, and physical privacy.
+More agreeable people have fewer conflicts with others, are more easy to get along with.
+They likely see others less as a threat, and hence have a reduced need for privacy.
+No relevant relations with need for privacy from government and companies exist, suggesting that agreeableness---a personality trait mostly relevant in interpersonal contexts---might not extend to the need for privacy in these public domains.
+
+In analyzing how the honesty humility factor relates to need for privacy, we analyzed the nothing-to-hide argument.
+As expected, our results provided support for the nothing-to-hide argument, especially with regard to the need for anonymity.
+Respondents who needed more anonymity were less honest, less fair, less modest, and less altruistic.
+Respondents who were less fair and less altruistic also needed more psychological, social, and physical privacy.
+Less honest participants required more anonymity and privacy from other people, be it psychologically, socially, or physically.
+However, honesty was unrelated to the need for privacy from government and companies or informational and general privacy.
+If anything, people who were more sincere actually desired more privacy from companies and more privacy in general.
+So although less honest people needed more privacy in several dimensions, this pattern is not general but varied and nuanced.
+
+Emotionality showed mixed relations with need for privacy, which confirmed our ambivalent a priori expectations.
+More emotional people desired less psychological privacy, less privacy from the government, and less anonymity. 
+At the same time, they needed more physical privacy. 
+Whereas they want closer bonds to people close to them, they are wary of strangers entering their personal spaces.
+Fearful and anxious people wanted more social and more physical privacy, while dependent and sensitive people wanted less.
+It seems that more emotional people have subtle and varied approach- versus avoidance preferences.
+
+Contrary to our expectations, conscientiousness showed a varied relation with need for privacy.
+More conscientious people needed less psychological and social privacy and less anonymity.
+Asked about privacy in general, however, they answered they needed more.
+This relations was driven by the subscale perfectionism.
+More perfectionist people preferred both more informational privacy and more privacy in general---perhaps to have more options and leeway to adapt plans. 
+More diligent people needed less privacy from other people, less psychological privacy, and less physical privacy. 
+Speculating about a potential explanation, we could imagine that similar to the nothing-to-hide argument more diligent people might have less to be afraid of.
+
+Although openness might be the opposite of privacy semantically, empirically next to no meaningful relations with need for privacy were found.
+The main dimension showed no relevant relationships.
+The facet creativity was meaningfully related to psychological and social privacy, such that more creative people needed less psychological and social privacy.
+It might be that more creative people generally think of others as resources, thriving from their inputs and exchanges. 
+More inquisitive people needed less physical privacy from others.
+They might see others as a resource, valuing closer exchanges with people unknown to them.
+
+In addition, we looked at relations between need for privacy and various sociodemographic variables.
+Contrary to our expectations, older participants desired less privacy from others, both socially and physically. 
+It is an open question as to whether this relation represents a developmental mechanism or a difference between cohorts.
+With increasing age social relations become more sparse, and perhaps to compensate older people prefer more contact with others.
+But it could also be a difference between cohorts. 
+Younger people nowadays have fewer social contacts than before, often attributed to increases in time spent online.
+Hence, it could also be that younger generations prefer more solitude than the generations beforehand.
+
+We expected that males would desire more psychological privacy but less social and physical privacy than females.
+Although in our data these relations were statistically significant as well, the effects sizes were too small to be considered meaningful.
+The only meaningful gender effect we found was with regard to anonymity.
+Males needed more anonymity than females.
+
+People in relationships needed less social privacy.
+This makes sense as being in a relationship implies a minimum openness to committing to others. 
+Contrary to our expectations, respondents with a college degree and with greater income all reported lower levels of need for social privacy.
+Having fewer educational and financial resources might result in fewer social opportunities, reflecting in an increased need for social privacy. 
+More politically conservative respondents needed more privacy from the government---which we expected given the general political tendencies of conservatives to prefer fewer state regulations and interferences.
+Finally, no meaningful relations with ethnicity were found.
+For example, contrary to what we expected we did not find that minority groups desired more privacy from the government.
+
+Finally, we also looked at the potential impact of personality on need for privacy.
+Results were comparable, in that extraversion turned out to be the major cause of need for privacy.
+However, there were also some changes.
+Most notably, when controlling for other personality dimensions and sociodemographics, results implied that being more conscientious increases the need for physical, informational, and general privacy.
+Similarly, being more open to new experiences might increase the need for privacy from the government, from companies, and for privacy in general.
+Finally, multiple regression results suggested that being conservative does not only increase the need for privacy from the government, but also from companies and for privacy in general.
+All other sociodemographic variables ceased to be significant.
+
+Looking at the results more broadly, we make four general observations.
+First, it makes sense to differentiate different levels of need for privacy.
+Many personality traits showed meaningful relations with some dimension, but no or even opposite relations with others.
+To illustrate, whereas more conscientious people desired less psychological privacy and less privacy from other, when asked about privacy in general they needed more. 
+General need for privacy rather represents a cognitive appraisal, whereas social or psychological privacy might be more experienced and psychological.
+
+Second, the need for privacy from companies and the government, both vertical forms of privacy, showed next to no meaningful relations with personality.
+Most relations were found on the horizontal level, suggesting that personality shows more strongly in these more social and interpersonal aspects of privacy.
+
+Third, although we found support for the nothing-to-hide-argument, our results also support the reasoning of the argument's critics.
+Although desiring more anonymity was related to less honesty, fairness, and altruism, these relations were not particularly large.
+Next, needing anonymity is insufficient to assume reduced honesty.
+Our results underscore that many other personality aspects related to an increased need of anonymity.
+Less emotional, less extraverted, and more conscientious people also needed more anonymity.
+Finally, when analyzed together with the other predictors, honesty and humility ceased to be a relevant predictor.
+
+This leads to our fourth general observation.
+Our main interest was to determine what predicts the need for privacy.
+What can we learn about a person given their need for privacy?
+We analyzed these questions in correlation analyses.
+In addition, we also explored the potential causal effects in a multiple regression.
+Here, a somewhat different picture emerged.
+Several correlations we found might not be the results of a causal processes.
+At the same time, some causal effects might also be surpressed in correlation analyses.
+
+## Limitations
+
+Not all personality and privacy measures showed good fit. 
+Especially when analyzed together, fit was not satisfactory. 
+Likewise, some measures such as altruism, unconventionality, or anonymity showed low reliability. 
+The results of these variables need to be interpreted more cautiously.
+Instead of deleting items or changing the factor structure, to avoid overfitting we decided to maintain the measures' original factor structure.
+
+For this reason, instead of reporting the results from latent structural equation modelling, we reported the results of the correlations of the observed variables' means. 
+We report the results of the latent analyses online.
+The results are highly comparable, with the major difference that effect sizes in the latent models tended to be larger.
+The results reported here are hence more conservative and likely underestimate the true effect sizes.
 
@@
 
-All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found or will be shared as online supplementary material on the open science framework (https://osf.io/e47yw/).
+All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on the open science framework (https://osf.io/e47yw/).
 The paper also has a companion website where all materials can be accessed (https://tdienlin.github.io/Who_Needs_Privacy_RR/proposal.html).
@@
 
-The data will be shared on the open science framework (https://osf.io/e47yw/) and on github.
+The data are shared on the open science framework (https://osf.io/e47yw/) and on github.

### 2024-02-07 power_analyses.Rmd
- Collected and analzed data - Wrote results and discussion section

---
title: "power_analyses"
author: "Tobias Dienlin"
date: "2024-01-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lavaan)
library(semTools)
library(simsem)
library(pwr)
```

# Power Analyses
## Rudimentary

To estimate sample size, we conducted a rudimentary power analysis. That is, we planned for a two-sided correlation of _r_ = .1. We adopted a balanced alpha and beta error approach. Because we were in "exploration mode", we aimed for a high statistical power and hence relaxed alpha. Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget. Instead, we opted for an error rate of 10%.

```{r}
sesoi <- .1

# a priori power analyses
pwr.r.test(r = sesoi, sig.level = .05, power = .95)
power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
```

A 5% error rate would imply collecting `r power_n_95` participants.

## Detailed: Simple

```{r}
population <- 
  "
  # Fix means to 0
  HEX_HOH_SIN_01 ~ 0*1
  HEX_HOH_SIN_02 ~ 0*1
  HEX_HOH_SIN_03 ~ 0*1
  HEX_HOH_SIN_04 ~ 0*1
  NFP_PHY_01 ~ 0*1
  NFP_PHY_02 ~ 0*1
  NFP_PHY_03 ~ 0*1
  NFP_PHY_04 ~ 0*1

  # Fix variances
  HEX_HOH_SIN_01 ~~ 1 * HEX_HOH_SIN_01
  HEX_HOH_SIN_02 ~~ 1 * HEX_HOH_SIN_02
  HEX_HOH_SIN_03 ~~ 1 * HEX_HOH_SIN_03
  HEX_HOH_SIN_04 ~~ 1 * HEX_HOH_SIN_04
  NFP_PHY_01 ~~ 1 * NFP_PHY_01
  NFP_PHY_02 ~~ 1 * NFP_PHY_02
  NFP_PHY_03 ~~ 1 * NFP_PHY_03
  NFP_PHY_04 ~~ 1 * NFP_PHY_04

  # Define latent vars
  HEX_HOH_SIN =~ .9*HEX_HOH_SIN_01 + .9*HEX_HOH_SIN_02 + .9*HEX_HOH_SIN_03 + .9*HEX_HOH_SIN_04
  NFP_PHY =~ .9*NFP_PHY_01 + .9*NFP_PHY_02 + .9*NFP_PHY_03 + .9*NFP_PHY_04

  # Covariances
  HEX_HOH_SIN ~~ .1*NFP_PHY
  "
sample <- "
  HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
  NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
"

reliability <- simsem::sim(
  # nRep = NULL, 
  model = sample, 
#  n = 500,
  n = seq(500, 5000, 50), 
  generate = population, 
  # std.lv = TRUE, 
  lavaanfun = "sem"
  )

summary(reliability)
power_tab <- getPower(reliability)
power_80 <- findPower(power_tab, "N", 0.90)
power_80["HEX_HOH_SIN~~NFP_PHY"]
```

```{r}
save.image("data/workspace_1.RData")
```

### 2024-02-07 custom_functions.R

@@ -1,0 +1,56 @@
+# readability function
+readability <- function(data){
+  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
+  textstat_readability(data, measure = reading_estimates) %>% 
+    as.data.frame %>% 
+    mutate(average = rowMeans(select(., -document)))
+}
+
+# plot distributions
+
+plot_hist <- function(name){
+  
+  dat <- 
+    select(
+      d, paste0(rep(paste0(name, "_0"), 4), 1:4)
+    ) %>% 
+    pivot_longer(
+      cols = everything(),
+      names_to = "item"
+    )
+  
+  ggplot(dat, aes(value)) +
+    geom_bar() +
+    scale_x_binned() +
+    facet_wrap(facets = "item")
+}
+
+# extracting results.
+get_res <- function(predictor_var, privacy_var, object = "tab_cor"){
+  
+    if(object == "tab_reg") {
+      dat <- 
+        tab_reg %>% 
+        filter(`Need for privacy` == privacy_var & Predictor == predictor_var) %>%
+        select(Estimate, CI_low, CI_high)
+    } else {
+      dat <- 
+        tab_cor %>% 
+        filter(`Need for privacy` == privacy_var & Predictor == predictor_var) %>%
+        select(Estimate, CI_low, CI_high)
+    }
+  
+  paste0(
+    if(object == "tab_reg") {
+      "_$\\beta$_ = "
+    } else {
+      "_r_ = "  
+    },
+    my_round(dat$Estimate, "std"),
+    ", 90% CI ",
+    my_round(dat$CI_low, "std"),
+    ", ",
+    my_round(dat$CI_high, "std"),
+    ""
+  )
+}

### 2024-02-08 analyses.RmD
- Rendered website

@@
 
-fig_reg <- ggplot(
-  tab_reg, aes(x = Estimate, y = Predictor, color = relevant)
+fig_cor <- ggplot(
+  tab_cor, aes(x = Estimate, y = Predictor, color = relevant)
   ) + 

### 2024-02-08 index.Rmd
- Rendered website

@@
 - You can either read the paper [in your browser](proposal.html) or download it as [pdf](proposal.pdf). 
-- You can also find the detailed code and summaries of the [planned analyses](analyses.html) reported in the paper
-- Once finished, you will also be able to find [additional analyses](analyses_additional.html) not reported in the paper.
+- You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper
 

### 2024-02-08 proposal.Rmd
- Rendered website

@@
 # classoption       : "man"
-# output: html_document
-output            : papaja::apa6_pdf
+output: html_document
+# output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 lapply(packages, library, character.only = TRUE)
-load("data/workspace.RData")
+load("data/workspace_2.RData")
 

### 2024-04-12 analysis_pipeline.Rmd
- Collected and analzed data - Wrote results and discussion section
deleting large files

@@
 ---
-title: "Analysis Pipeline"
+title: "Preregistered Analysis Pipeline"
 output:
@@
 
-Below we state how we plan to analyze the data. To achieve sufficient model fit, there'll likely be several adaptions.
+Below we state how we planned and preregistered to analyze the data in more detail.
 
 # Factorial validity
+## Preregistered procedure
 
@@
  - If this should not work out, we will run Exploratory Structural Equation Modelling using oblimin rotation, allowing all personality items to load on the same factors, while allowing all privacy items to load on the same factors.
- - If fit is still subpar, we will conduct in-depth exploratory factor analyses (EFA) to asssess the underlying factor structure. 
+ - If fit is still subpar, we will conduct in-depth exploratory factor analyses (EFA) to assess the underlying factor structure. 
  - EFAs will be run using maximum likelihood estimation and oblimin rotation [@osborneSampleSizeSubject2004, p. 7]. 
@@
 
+## Implementation and Deviation
+
+When analyzed individually, most measures showed satisfactory model fit, not requiring any changes.
+Some measures showed satisfactory model fit after small adaptions, such as allowing items to covary.
+Half a dozen measures were then still marginally outside of the preregistered thresholds (e.g., liveliness with a RMSEA of .12).
+We could've now substantially altered the factor structure to see if this leads to sufficient model fit.
+However, we considered it more cogent to rather accept this then to fundamentally alter scales.
+
+We did not explicate a minimum thresholf of reliability.
+Most measures showed satisfactory results (i.e., reliability above .70).
+However, some measures such as altruism, unconventionality, or anonymity showed insufficient reliability.
+Again, instead of strongly adapting measures (as suggested above), we decided to maintain the initial factor structure and did not delete any items and we did not introduce substantial changes to the factors.
+
 # Analysis
+## Preregistered Procedure
 
@@
     - If the CFAs show a unidimensional solution, we will use the model predicted values for this latent factor; if the CFAs produce a multidimensional solution, we will use the model predicted values for the general latent factor.
+
+## Implementation and Deviation
+
+Although individually most of the measures showed good fit, when analyzed together fit decreased substantially, below acceptable levels. 
+This problem maintained when trying to model the results using single indicator of the predictors with factor scores. 
+As a result, we conservatively decided to analyze our data using the variables' observed mean scores.

### 2024-04-12 data_prep.Rmd
deleting large files

--- 2023-11-16 analyses.RmD
@@
 ---
-title: "Who needs privacy? Exploring the relations between need for privacy and personality"
-subtitle: "Analyses"
+title: "Data Preparation"
 output:
@@
     toc_depth: 2
-    code_folding: hide
+    code_folding: show
     df_print: paged
@@
 set.seed(170819)
-knitr::opts_chunk$set(warning=F, echo=F, error=F, message=F, cache = T, 
-                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
-options(digits = 3, width = 90)
+
+knitr::opts_chunk$set(
+  warning=F, 
+  echo=T, 
+  error=F, 
+  message=F, 
+  cache = T, 
+  tidy=T, 
+  dev = 'pdf', 
+  cache.extra = knitr::rand_seed,
+  fig.height = 6,
+  fig.width = 8
+  )
+
+options(
+  digits = 3, 
+  width = 150,
+  max.print = 100000000
+  )
 ```
 
-Here you can find the results of our study.
+Here we outline how we prepared the data for our analyses, including quality checks.
 
-- At this point, we haven't yet collected data. 
-- The results below use simulated data. 
-- The data are random and don't make sense, but help to illustrate the overall approach and planned analyses.
-- We'll later conduct further analyses not yet reported here, for example model-alterations given misfit or imputation of missing data.
+# Data
 
-# Set-Up
+Please first download the data from [AUSSDA](https://data.aussda.at/dataset.xhtml?persistentId=doi:10.11587/IC66GC) and put it into the folder "data".
 
-```{r r-setup, include=T, echo=T, results='hide'}
+# Set-up
+
+We load the packages.
+
+```{r r-setup, include=T, echo=T, results='hide', cache=F}
 # install packages
@@
 
-# define packages
-packages <- c("corrplot", "devtools", "GGally", "ggplot2", "haven", "kableExtra", "knitr", 
-              "lavaan", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
-              "pwr", "semPlot", "simsem", "semTools", "tidyverse", "td")
+library(confintr)
+library(corrplot)
+library(easystats)
+library(ggplot2)
+library(kableExtra)
+library(knitr)
+library(lavaan)
+library(magrittr)
+library(MVN)
+library(naniar)
+library(PerFit)
+library(psych)
+library(sjlabelled)
+library(semTools)
+library(tidyverse)
+library(td)
 
-# load packages
-lapply(packages, library, character.only = TRUE)
-
-# readability function
-readability = function(data){
-  reading_estimates <- c("Flesch.Kincaid", "FOG", "Coleman.Liau.short", "Dale.Chall.PSK")
-  textstat_readability(data, measure = reading_estimates) %>% 
-    as.data.frame %>% 
-    mutate(average = rowMeans(select(., -document)))
-}
+load("data/workspace_1.RData")
+source("custom_functions.R")
 ```
 
+We next load the data.
+
 ```{r data-wrangling}
-d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
-d <- rename(d, COL = COL_, REL = REL_)
+d_raw <- sjlabelled::read_spss(
+  "data/10849_da_en_v1_0.zsav",
+  convert.factors = FALSE
+  )
+```
 
+# Data Preparation
+
+## Recoding
+
+We need to recode inverted items, rename variables, and recode variables (Age was coded wrongly).
+
+```{r data-inverting}
+vars_invert <- c(
+  "HEX_HOH_SIN_01", "HEX_HOH_SIN_03",
+  "HEX_HOH_FAI_01", "HEX_HOH_FAI_02", "HEX_HOH_FAI_04",
+  "HEX_HOH_GRE_02", "HEX_HOH_GRE_03", "HEX_HOH_GRE_04",
+  "HEX_HOH_MOD_03", "HEX_HOH_MOD_04",
+  "HEX_EMO_FEA_02", "HEX_EMO_FEA_04",
+  "HEX_EMO_ANX_02", "HEX_EMO_ANX_03",
+  "HEX_EMO_DEP_02", "HEX_EMO_DEP_04",
+  "HEX_EMO_SEN_04",
+  "HEX_EXT_SSE_03", "HEX_EXT_SSE_04",
+  "HEX_EXT_BOL_01", "HEX_EXT_BOL_04",
+  "HEX_EXT_SOC_01",
+  "HEX_EXT_LIV_03", "HEX_EXT_LIV_04",
+  "HEX_AGR_FOR_03", "HEX_AGR_FOR_04",
+  "HEX_AGR_GEN_01",
+  "HEX_AGR_FLX_01", "HEX_AGR_FLX_03", "HEX_AGR_FLX_04",
+  "HEX_AGR_PAT_01", "HEX_AGR_PAT_04",
+  "HEX_CNS_ORG_03", "HEX_CNS_ORG_04",
+  "HEX_CNS_DIL_03", "HEX_CNS_DIL_04",
+  "HEX_CNS_PER_02",
+  "HEX_CNS_PRU_01", "HEX_CNS_PRU_02", "HEX_CNS_PRU_04",
+  "HEX_OPN_AES_01", "HEX_OPN_AES_02",
+  "HEX_OPN_INQ_03", "HEX_OPN_INQ_04",
+  "HEX_OPN_CRE_01", "HEX_OPN_CRE_04",
+  "HEX_OPN_UNC_01", "HEX_OPN_UNC_04",
+  "HEX_ALT_03", "HEX_ALT_04",
+  "NFP_COM_02"
+)
+
+d <-
+  d_raw %>% 
+  rename(
+    COL = COL_,
+    REL = REL_
+    ) %>%
+  mutate(
+    across(all_of(vars_invert),
+    ~ 8 - .x
+         ),
+    male = case_match(
+      GEN,
+      c(2, 3) ~ 0,
+      1 ~ 1),
+    # note that age was coded wrongly; needs to be corrected
+    age = case_match(
+      AGE,
+      1 ~ 1,
+      2 ~ 2,
+      3 ~ 3,
+      4 ~ 4,
+      5 ~ 6,
+      6 ~ 7,
+      7 ~ 5),
+    age = set_labels(
+      age, 
+      labels = c(
+        "18-24 years old", 
+        "25-34 years old", 
+        "35-44 years old", 
+        "45-54 years old",
+        "55-64 years old", 
+        "65+ years old"
+      )
+    ),
+    white = case_match(
+      ETH,
+      2 ~ 0,
+      1 ~ 1),
+    relation = case_match(
+      REL,
+      2 ~ 1,
+      1 ~ 0),
+    college = case_match(
+      COL,
+      2 ~ 1,
+      1 ~ 0),
+    conserv = CON,
+    income = INC
+  ) 
+```
+
+## Labels
+
+We define names and labels for categories of variables, so that we can use them later.
+
+```{r data-labels}
 # define vars and labels
+vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")
+
+vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")
+
 vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
+                   "HEX_ALT",
                    "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
@@
                    "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
-                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC", 
-                   "HEX_ALT")
+                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
+
 vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
+                       "Altruism",
                        "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
@@
                        "Organization", "Diligence", "Perfectionism", "Prudence", 
-                       "Aesthetic appreciation", "Inquisitiveness", "Creativeness", "Unconventionality", 
-                       "Altruism")
+                       "Aesth. appreciation", "Inquisitiveness", "Creativeness", "Unconventionality")
+
+vars_pers_hoh <- 
+  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")
+
+vars_pers_emo <- 
+  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")
+
+vars_pers_ext <- 
+  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")
+
+vars_pers_agr <- 
+  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")
+
+vars_pers_cns <- 
+  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")
+
+vars_pers_opn <- 
+  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
+
+vars_pers_all <- 
+  c(
+    vars_pers_hoh, 
+    vars_pers_emo, 
+    vars_pers_ext, 
+    vars_pers_agr, 
+    vars_pers_cns,
+    vars_pers_opn
+    )
+
+vars_pers_all_txt <- 
+  c("Honesty humility", 
+      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
+    "Emotionality", 
+      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
+    "Extraversion",
+      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
+    "Agreeableness",
+      "Forgiveness", "Gentleness", "Flexibility", "Patience",
+    "Conscientiousness",
+      "Organization", "Diligence", "Perfectionism", "Prudence", 
+    "Openness",
+      "Aesth. appreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
+    )
+
+vars_pred_all_txt <- 
+  c(
+    vars_pers_all_txt,
+    vars_ses_txt
+    )
 
 vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")
+
 vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
@@
 
-vars_pri <- c("NFP_SOC", "NFP_PHY", "NFP_PSY",
+vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
               "NFP_GOV", "NFP_COM", 
               "NFP_INF", "NFP_ANO", "NFP_GEN")
-vars_pri_txt <- c("Social", "Physical", "Psychological",
-                  "Companies", "Governnment",
-                  "Anonynmity", "Informational", "General")
-vars_pri_txt_brk <- c("Social", "Physical", "Psycho-\nlogical",
-                  "Companies", "Govern-\nment",
-                  "Anony-\nmity", "Infor-\nmational", "General")
-vars_pri_txt_abr <- c("Social", "Phys.", "Psych.",
-                  "Comp.", "Gov.",
-                  "Anonym.", "Inform.", "General")
 
-vars_ses <- c("AGE", "GEN", "ETH", "REL", "COL", "INC", "CON")
-vars_ses_txt <- c("Age", "Gender", "Ethnicity", "Relationship", "College", "Income", "Conservatism")
+vars_pri_txt <- c("Psychological", "Social", "Physical", 
+                  "Government", "Companies", 
+                  "Informational", "Anonymity", "General")
+
+vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
+                  "Govern-\nment", "Companies", 
+                  "Infor-\nmational", "Anony-\nmity", "General")
+
+vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
+                  "Gov.", "Comp.", 
+                  "Inform.", "Anonym.", "General")
+
+vars_pers_pri <- c(vars_pers_fac, vars_pri)
+
+vars_all <- c(
+  vars_pers_all, 
+  vars_pri,
+  vars_ses
+)
 ```
 
-# Items
+## Means
 
-All items were answered on a 7-point scale with the following options:
-
-"To what extent do you agree or disagree with the following statements?"
-
-(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree
-
-## Personality
-### Honesty Humility
-#### Sincerity
-
- - If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
- - I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
- - If I want something from someone, I will laugh at that person's worst jokes.
- - I wouldn't pretend to like someone just to get that person to do favors for me.
+Below we compute the means for scales and items.
 
 ```{r}
-name <- "HEX_HOH_SIN"
-model <- "HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+# Person means per facet
+d %<>%
+  mutate(
+    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
+    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
+    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
+    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
+    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
+    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
+    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
+    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
+    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
+    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
+    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
+    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
+    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
+    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
+    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
+    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
+    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
+    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
+    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
+    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
+    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
+    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
+    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
+    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
+    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
+    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
+    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
+    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
+    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
+    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
+    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
+    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
+    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
+    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
+    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
+    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
+    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
+    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
+    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
+  )
+
+# item means
+c_m <- 
+  c(
+    HEX_ALT_m     = mean(d$HEX_ALT_M, na.rm = T),
+    HEX_AGR_FLX_m = mean(d$HEX_AGR_FLX_M, na.rm = T),
+    HEX_AGR_FOR_m = mean(d$HEX_AGR_FOR_M, na.rm = T),
+    HEX_AGR_GEN_m = mean(d$HEX_AGR_GEN_M, na.rm = T),
+    HEX_AGR_PAT_m = mean(d$HEX_AGR_PAT_M, na.rm = T),
+    HEX_CNS_DIL_m = mean(d$HEX_CNS_DIL_M, na.rm = T),
+    HEX_CNS_ORG_m = mean(d$HEX_CNS_ORG_M, na.rm = T),
+    HEX_CNS_PER_m = mean(d$HEX_CNS_PER_M, na.rm = T),
+    HEX_CNS_PRU_m = mean(d$HEX_CNS_PRU_M, na.rm = T),
+    HEX_EMO_ANX_m = mean(d$HEX_EMO_ANX_M, na.rm = T),
+    HEX_EMO_DEP_m = mean(d$HEX_EMO_DEP_M, na.rm = T),
+    HEX_EMO_FEA_m = mean(d$HEX_EMO_FEA_M, na.rm = T),
+    HEX_EMO_SEN_m = mean(d$HEX_EMO_SEN_M, na.rm = T),
+    HEX_EXT_BOL_m = mean(d$HEX_EXT_BOL_M, na.rm = T),
+    HEX_EXT_LIV_m = mean(d$HEX_EXT_LIV_M, na.rm = T),
+    HEX_EXT_SOC_m = mean(d$HEX_EXT_SOC_M, na.rm = T),
+    HEX_EXT_SSE_m = mean(d$HEX_EXT_SSE_M, na.rm = T),
+    HEX_HOH_FAI_m = mean(d$HEX_HOH_FAI_M, na.rm = T),
+    HEX_HOH_GRE_m = mean(d$HEX_HOH_GRE_M, na.rm = T),
+    HEX_HOH_MOD_m = mean(d$HEX_HOH_MOD_M, na.rm = T),
+    HEX_HOH_SIN_m = mean(d$HEX_HOH_SIN_M, na.rm = T),
+    HEX_OPN_AES_m = mean(d$HEX_OPN_AES_M, na.rm = T),
+    HEX_OPN_CRE_m = mean(d$HEX_OPN_CRE_M, na.rm = T),
+    HEX_OPN_INQ_m = mean(d$HEX_OPN_INQ_M, na.rm = T),
+    HEX_OPN_UNC_m = mean(d$HEX_OPN_UNC_M, na.rm = T),
+    NFP_ANO_m     = mean(d$NFP_ANO_M, na.rm = T),
+    NFP_COM_m     = mean(d$NFP_COM_M, na.rm = T),
+    NFP_GEN_m     = mean(d$NFP_GEN_M, na.rm = T),
+    NFP_GOV_m     = mean(d$NFP_GOV_M, na.rm = T),
+    NFP_INF_m     = mean(d$NFP_INF_M, na.rm = T),
+    NFP_PHY_m     = mean(d$NFP_PHY_M, na.rm = T),
+    NFP_PSY_m     = mean(d$NFP_PSY_M, na.rm = T),
+    NFP_SOC_m     = mean(d$NFP_SOC_M, na.rm = T),
+    HEX_HOH_m     = mean(d$HEX_HOH_M, na.rm = T),
+    HEX_EMO_m     = mean(d$HEX_EMO_M, na.rm = T),
+    HEX_EXT_m     = mean(d$HEX_EXT_M, na.rm = T),
+    HEX_AGR_m     = mean(d$HEX_AGR_M, na.rm = T),
+    HEX_CNS_m     = mean(d$HEX_CNS_M, na.rm = T),
+    HEX_OPN_m     = mean(d$HEX_OPN_M, na.rm = T)
+  )
+
+# item standard deviation
+c_sd <- 
+  c(
+    HEX_ALT_sd     = sd(d$HEX_ALT_M, na.rm = T),
+    HEX_AGR_FLX_sd = sd(d$HEX_AGR_FLX_M, na.rm = T),
+    HEX_AGR_FOR_sd = sd(d$HEX_AGR_FOR_M, na.rm = T),
+    HEX_AGR_GEN_sd = sd(d$HEX_AGR_GEN_M, na.rm = T),
+    HEX_AGR_PAT_sd = sd(d$HEX_AGR_PAT_M, na.rm = T),
+    HEX_CNS_DIL_sd = sd(d$HEX_CNS_DIL_M, na.rm = T),
+    HEX_CNS_ORG_sd = sd(d$HEX_CNS_ORG_M, na.rm = T),
+    HEX_CNS_PER_sd = sd(d$HEX_CNS_PER_M, na.rm = T),
+    HEX_CNS_PRU_sd = sd(d$HEX_CNS_PRU_M, na.rm = T),
+    HEX_EMO_ANX_sd = sd(d$HEX_EMO_ANX_M, na.rm = T),
+    HEX_EMO_DEP_sd = sd(d$HEX_EMO_DEP_M, na.rm = T),
+    HEX_EMO_FEA_sd = sd(d$HEX_EMO_FEA_M, na.rm = T),
+    HEX_EMO_SEN_sd = sd(d$HEX_EMO_SEN_M, na.rm = T),
+    HEX_EXT_BOL_sd = sd(d$HEX_EXT_BOL_M, na.rm = T),
+    HEX_EXT_LIV_sd = sd(d$HEX_EXT_LIV_M, na.rm = T),
+    HEX_EXT_SOC_sd = sd(d$HEX_EXT_SOC_M, na.rm = T),
+    HEX_EXT_SSE_sd = sd(d$HEX_EXT_SSE_M, na.rm = T),
+    HEX_HOH_FAI_sd = sd(d$HEX_HOH_FAI_M, na.rm = T),
+    HEX_HOH_GRE_sd = sd(d$HEX_HOH_GRE_M, na.rm = T),
+    HEX_HOH_MOD_sd = sd(d$HEX_HOH_MOD_M, na.rm = T),
+    HEX_HOH_SIN_sd = sd(d$HEX_HOH_SIN_M, na.rm = T),
+    HEX_OPN_AES_sd = sd(d$HEX_OPN_AES_M, na.rm = T),
+    HEX_OPN_CRE_sd = sd(d$HEX_OPN_CRE_M, na.rm = T),
+    HEX_OPN_INQ_sd = sd(d$HEX_OPN_INQ_M, na.rm = T),
+    HEX_OPN_UNC_sd = sd(d$HEX_OPN_UNC_M, na.rm = T),
+    NFP_ANO_sd     = sd(d$NFP_ANO_M, na.rm = T),
+    NFP_COM_sd     = sd(d$NFP_COM_M, na.rm = T),
+    NFP_GEN_sd     = sd(d$NFP_GEN_M, na.rm = T),
+    NFP_GOV_sd     = sd(d$NFP_GOV_M, na.rm = T),
+    NFP_INF_sd     = sd(d$NFP_INF_M, na.rm = T),
+    NFP_PHY_sd     = sd(d$NFP_PHY_M, na.rm = T),
+    NFP_PSY_sd     = sd(d$NFP_PSY_M, na.rm = T),
+    NFP_SOC_sd     = sd(d$NFP_SOC_M, na.rm = T),
+    HEX_HOH_sd     = sd(d$HEX_HOH_M, na.rm = T),
+    HEX_EMO_sd     = sd(d$HEX_EMO_M, na.rm = T),
+    HEX_EXT_sd     = sd(d$HEX_EXT_M, na.rm = T),
+    HEX_AGR_sd     = sd(d$HEX_AGR_M, na.rm = T),
+    HEX_CNS_sd     = sd(d$HEX_CNS_M, na.rm = T),
+    HEX_OPN_sd     = sd(d$HEX_OPN_M, na.rm = T)
+  )
 ```
 
-#### Fairness
+# Quality checks
+## Missing data
 
- - If I knew that I could never get caught, I would be willing to steal a million dollars.
- - I would be tempted to buy stolen property if I were financially tight.
- - I would never accept a bribe, even if it were very large.
- - I’d be tempted to use counterfeit money, if I were sure I could get away with it.
+First we filter those who didn't finish the questionnaire.
 
 ```{r}
-name <- "HEX_HOH_FAI"
-model <- "HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+d %<>%
+  filter(
+    Progress == 100
+  )
+
+n_finished <- nrow(d)
 ```
 
-#### Greed Avoidance
+Let's first inspect missing data.
 
- - Having a lot of money is not especially important to me.
- - I would like to live in a very expensive, high-class neighborhood.
- - I would like to be seen driving around in a very expensive car.
- - I would get a lot of pleasure from owning expensive luxury goods.
+How many missing do we have?
 
 ```{r}
-name <- "HEY_HOH_GRE"
-model <- "HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+missing_n <- 
+  d %>% 
+  select(HEX_HOH_SIN_01:CON) %>% 
+  n_miss()
+
+missing_per <- 
+  d %>% 
+  select(HEX_HOH_SIN_01:CON) %>%
+  prop_miss() %>% 
+  as.numeric() * 100
 ```
 
-#### Modesty
+Only `r missing_n` cells are missing -- which is very little. To be precise, `r missing_per %>% round(4)` percent only.
 
- - I am an ordinary person who is no better than others.
- - I wouldn’t want people to treat me as though I were superior to them.
- - I think that I am entitled to more respect than the average person is.
- - I want people to know that I am an important person of high status.
+Which variables are affected?
 
 ```{r}
-name <- "HEX_HOH_MOD"
-model <- "HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+d %>% 
+  select(HEX_HOH_SIN_01:CON) %>% 
+  miss_var_summary() %>% 
+  head(19)
 ```
 
-### Emotionality
-#### Fearfulness
+Missing answers vary randomly across variables.
 
- - I would feel afraid if I had to travel in bad weather conditions.
- - I don’t mind doing jobs that involve dangerous work.
- - When it comes to physical danger, I am very fearful.
- - Even in an emergency I wouldn't feel like panicking.
+How about participants?
 
 ```{r}
-name <- "HEX_EMO_FEA"
-model <- "HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+d %>% 
+  select(HEX_HOH_SIN_01:CON) %>% 
+  miss_case_summary()
 ```
 
-#### Anxiety
+Only six participants with missing data, and even then, not much. We hence decided to keep everyone.
 
- - I sometimes can't help worrying about little things.
- - I worry a lot less than most people do.
- - I rarely, if ever, have trouble sleeping due to stress or anxiety.
- - I get very anxious when waiting to hear about an important decision.
+## Speeders
+
+We preregistered to remove participants faster than 3 standard deviations than the median response time.
+
+```{r cache=F}
+# Median response time
+time_med <- median(d$Duration__in_seconds_)
+
+# Average response time
+time_m <- mean(d$Duration__in_seconds_) / 60
+
+# Standard deviation
+time_sd <- sd(d$Duration__in_seconds_)
+
+# filter speeders
+time_crit_init <- time_med - (3 * time_sd) # minimum time on survey
+```
+
+However, this made little sense.
+The median response time was `r time_med` seconds and the standard deviation `r time_sd %>% round(0)` seconds.
+Hence, three SDs below median was `r time_crit_init %>% round(0)` seconds, hence not informative.
+
+Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
+
+```{r cache=F}
+time_crit <- 5 * 60
+
+# count number of speeders
+n_speeding <- 
+  nrow(
+    filter(
+      d, 
+      Duration__in_seconds_ < time_crit
+      )
+    )
+
+# Deletion of fast respondents
+d <- 
+  filter(
+    d, 
+    Duration__in_seconds_ >= time_crit
+    )
+
+n_used <- nrow(d)
+```
+
+Average response time was `r time_m %>% round(0)` minutes. We removed `r n_speeding` because they answered the survey unreasonably fast.
+
+## Response patterns
+
+Let's inspect for potential response patterns. We'll do so looking at influential cases, which we'll then inspect manually.
+
+We'll use raw data, so that inverted items aren't recoded and patterns become more visible. (Note that this data set isn't yet filtered for speeders).
 
 ```{r}
-name <- "HEX_EMO_ANX"
-model <- "HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+options(mc.cores = 8)
+
+# analyses require complete cases only
+d_raw_compl <- d_raw %>% 
+  select(ID, Duration__in_seconds_, HEX_HOH_SIN_01:PRI_BEH) %>% 
+  .[complete.cases(.), ]
+
+outliers <- 
+  check_outliers(
+    d_raw_compl, 
+    method = "all", 
+    verbose = FALSE
+  )
+
+summary(outliers)
 ```
 
-#### Dependence
-
- - When I suffer from a painful experience, I need someone to make me feel comfortable.
- - I can handle difficult situations without needing emotional support from anyone else.
- - Whenever I feel worried about something, I want to share my concern with another person.
- - I rarely discuss my problems with other people.
+194 outliers were detected. We'll now inspect these outliers manually.
 
 ```{r}
-name <- "HEX_EMO_DEP"
-model <- "HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+d_outliers_stats <- as.data.frame(outliers)
+
+d_outliers <- 
+  d_raw_compl[d_outliers_stats$Outlier >= 0.5, ] %>%
+  as.data.frame()
+
+d_outliers
+
+patterns <- c(
+  449      # "R_72Kshi80pwPq9Gy"
+  , 6      # "R_5OrhZQwvj9wfJWp"
+  , 705    # "R_5QSPlArm0BtfIrE"
+  , 1422   # "R_3Cv1Tmj5HX4ghJU"
+  , 1401   # "R_5Pld7hbh1ay8sb7"
+  , 1355   # "R_4DuqyujkQ7Hjapj"
+  , 273    # "R_6MqzefRkB3aQdPj"
+  , 747    # "R_7QSq0FbgZfcnJIt"
+  , 1406   # "R_1MrHTg5CZpBLeYw"
+  )
 ```
 
-#### Sentimentality
-
- - I feel like crying when I see other people crying.
- - When someone I know well is unhappy, I can almost feel that person's pain myself.
- - I feel strong emotions when someone close to me is going away for a long time.
- - I remain unemotional even in situations where most people get very sentimental.
+The following `r length(patterns) %>% english::english()` cases show clear patterns and will be removed.
 
 ```{r}
-name <- "HEX_EMO_SEN"
-model <- "HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
+d_filtered <- filter(d, ID %in% patterns)
+d_filtered
+
+d <- filter(d, !ID %in% patterns)
+n_final <- nrow(d)
 ```
 
-### Extraversion
-#### Social Self-Esteem
-
- - I feel reasonably satisfied with myself overall.
- - I think that most people like some aspects of my personality.
- - I feel that I am an unpopular person.
- - I sometimes feel that I am a worthless person.
-
-```{r}
-name <- "HEX_EXT_SSE"
-model <- "HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Social Boldness
-
- - I rarely express my opinions in group meetings.
- - In social situations, I'm usually the one who makes the first move.
- - When I'm in a group of people, I'm often the one who speaks on behalf of the group.
- - I tend to feel quite self-conscious when speaking in front of a group of people.
-
-```{r}
-name <- "HEX_EXT_BOL"
-model <- "HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Sociability
-
- - I avoid making "small talk" with people.
- - I enjoy having lots of people around to talk with.
- - I prefer jobs that involve active social interaction to those that involve working alone.
- - The first thing that I always do in a new place is to make friends.
-
-```{r}
-name <- "HEX_EXT_SOC"
-model <- "HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Liveliness
-
- - I am energetic nearly all the time.
- - On most days, I feel cheerful and optimistic.
- - People often tell me that I should try to cheer up.
- - Most people are more upbeat and dynamic than I generally am.
-
-```{r}
-name <- "HEX_EXT_LIV"
-model <- "HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Agreeableness
-#### Forgiveness
-
- - I rarely hold a grudge, even against people who have badly wronged me.
- - My attitude toward people who have treated me badly is "forgive and forget".
- - If someone has cheated me once, I will always feel suspicious of that person.
- - I find it hard to fully forgive someone who has done something mean to me.
-
-```{r}
-name <- "HEX_AGR_FOR"
-model <- "HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Gentleness
-
- - People sometimes tell me that I am too critical of others.
- - I generally accept people’s faults without complaining about them.
- - I tend to be lenient in judging other people.
- - Even when people make a lot of mistakes, I rarely say anything negative.
-
-```{r}
-name <- "HEX_AGR_GEN"
-model <- "HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Flexibility
-
- - People sometimes tell me that I'm too stubborn.
- - I am usually quite flexible in my opinions when people disagree with me.
- - When people tell me that I’m wrong, my first reaction is to argue with them.
- - I find it hard to compromise with people when I really think I’m right.
-
-```{r}
-name <- "HEX_AGR_FLX"
-model <- "HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Patience
-
- - People think of me as someone who has a quick temper.
- - I rarely feel anger, even when people treat me quite badly.
- - Most people tend to get angry more quickly than I do.
- - I find it hard to keep my temper when people insult me.
-
-```{r}
-name <- "HEX_AGR_PAT"
-model <- "HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Conscientiousness
-#### Organization
-
- - I clean my office or home quite frequently.
- - I plan ahead and organize things, to avoid scrambling at the last minute.
- - People often joke with me about the messiness of my room or desk.
- - When working, I sometimes have difficulties due to being disorganized.
-
-```{r}
-name <- "HEX_CNS_ORG"
-model <- "HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Diligence
-
- - When working, I often set ambitious goals for myself.
- - I often push myself very hard when trying to achieve a goal.
- - Often when I set a goal, I end up quitting without having reached it.
- - I do only the minimum amount of work needed to get by.
-
-```{r}
-name <- "HEX_CNS_DIL"
-model <- "HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Perfectionism
-
- - I often check my work over repeatedly to find any mistakes.
- - When working on something, I don't pay much attention to small details.
- - I always try to be accurate in my work, even at the expense of time.
- - People often call me a perfectionist.
-
-```{r}
-name <- "HEX_CNS_PER"
-model <- "HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Prudence
-
- - I make decisions based on the feeling of the moment rather than on careful thought.
- - I make a lot of mistakes because I don't think before I act.
- - I don’t allow my impulses to govern my behavior.
- - I prefer to do whatever comes to mind, rather than stick to a plan.
-
-```{r}
-name <- "HEX_CNS_PRU"
-model <- "HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Openness
-#### Aesthetic Appreciation
-
- - I would be quite bored by a visit to an art gallery.
- - I wouldn't spend my time reading a book of poetry.
- - If I had the opportunity, I would like to attend a classical music concert.
- - Sometimes I like to just watch the wind as it blows through the trees.
-
-```{r}
-name <- "HEX_OPN_AEX"
-model <- "HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Inquisitiveness
-
- - I'm interested in learning about the history and politics of other countries.
- - I enjoy looking at maps of different places.
- - I would be very bored by a book about the history of science and technology.
- - I’ve never really enjoyed looking through an encyclopedia.
-
-```{r}
-name <- "HEX_OPN_INQ"
-model <- "HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Creativeness
-
- - I would like a job that requires following a routine rather than being creative.
- - I would enjoy creating a work of art, such as a novel, a song, or a painting.
- - People have often told me that I have a good imagination.
- - I don't think of myself as the artistic or creative type.
-
-```{r}
-name <- "HEX_OPN_CRE"
-model <- "HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-#### Unconventionality
-
- - I think that paying attention to radical ideas is a waste of time.
- - I like people who have unconventional views.
- - I think of myself as a somewhat eccentric person.
- - I find it boring to discuss philosophy.
-
-```{r}
-name <- "HEX_OPN_UNC"
-model <- "HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Altruism
-
- - I have sympathy for people who are less fortunate than I am.
- - I try to give generously to those in need.
- - It wouldn’t bother me to harm someone I didn’t like.
- - People see me as a hard-hearted person.
-
-```{r}
-name <- "HEX_ALT"
-model <- "HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-## Need for privacy
-### Psychological
-
- 1.	I don’t like to talk about personal issues with others unless they do it first.
- 2.	There are a lot of things about me that I don’t like to talk about with others.
- 3.	I prefer not to share my feelings and inner thoughts with others.
- 4.	I don't like it when others talk to me about their private issues.
-
-```{r}
-name <- "NFP_PSY"
-model <- "NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Physical
-
- 1.	I don’t like it when strangers come too close to me.
- 2.	I don’t like to stand in a dense crowd of people.
- 3.	I don’t like to sit next to a stranger on a train, bus, or plane.
- 4.	I hate it when people enter my personal space uninvited.
-
-```{r}
-name <- "NFP_PHY"
-model <- "NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Social
-
- 1.	I don’t feel comfortable interacting with other people.
- 2.	I often want to be alone.
- 3.	I’m a fairly anti-social person.
- 4.	I prefer to work independently in most situations.
-
-```{r}
-name <- "NFP_SOC"
-model <- "NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Privacy from Government
-
- 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
- 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
- 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
- 4.	I feel I need to protect my privacy from government agencies.
-
-```{r}
-name <- "NFP_GOV"
-model <- "NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Privacy from Companies
-
- 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
- 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
- 3. I don’t want companies to collect data about me, even if that makes their services worse.
- 4. I feel I need to protect my privacy from companies.
-
-```{r}
-name <- "NFP_COM"
-model <- "NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Informational
-
- 1.	I would prefer that little is known about me.
- 2.	I don’t want my personal data to be publicly accessible.
- 3.	It is important to me that records pertaining to me remain confidential.
- 4.	I prefer that others cannot easily find information about me on the Internet.
-
-```{r}
-name <- "NFP_INF"
-model <- "NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### Privacy need anonymity
-
- 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
- 2.	I feel I need to avoid places with video surveillance.
- 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
- 4.	I need to be able to surf the Internet anonymously.
-
-```{r}
-name <- "NFP_ANO"
-model <- "NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-### General Need for privacy
-
- 1.	I need a lot of privacy.
- 2.	Privacy is very important to me.
- 3.	I think a lot about how I can protect my privacy.
- 4.	I value privacy a lot.
-
-```{r}
-name <- "NFP_GEN"
-model <- "NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04"
-assign(paste("fit", name, sep = "_"), cfa(model, d, missing = "FIML"))
-summary(get(paste0("fit_", name)), fit = TRUE, standardized = TRUE)
-```
-
-# Power Analyses
-## Rudimentary
-
-To estimate sample size, we conducted a rudimentary power analysis.
-That is, we planned for a two-sided correlation of _r_ = .1.
-We adopted a balanced alpha and beta error approach.
-Because we were in "exploration mode", we aimed for a high statistical power and hence relaxed alpha.
-Ideally, we would have wanted to set an error rate of 5%; however, this was outside of our budget.
-Instead, we opted for an error rate of 10%.
-
-```{r}
-sesoi <- .1
-
-# a priori power analyses
-pwr.r.test(r = sesoi, sig.level = .05, power = .95)
-power_n_95 <- pwr.r.test(r = sesoi, sig.level = .05, power = .95)$n
-```
-
-A 5% error rate would imply collecting `r power_n_95` participants.
-
-## Detailed: Simple
-
-```{r}
-population <- 
-  "
-  # Fix means to 0
-  HEX_HOH_SIN_01 ~ 0*1
-  HEX_HOH_SIN_02 ~ 0*1
-  HEX_HOH_SIN_03 ~ 0*1
-  HEX_HOH_SIN_04 ~ 0*1
-  NFP_PHY_01 ~ 0*1
-  NFP_PHY_02 ~ 0*1
-  NFP_PHY_03 ~ 0*1
-  NFP_PHY_04 ~ 0*1
-
-  # Fix variances
-  HEX_HOH_SIN_01 ~~ 1 * HEX_HOH_SIN_01
-  HEX_HOH_SIN_02 ~~ 1 * HEX_HOH_SIN_02
-  HEX_HOH_SIN_03 ~~ 1 * HEX_HOH_SIN_03
-  HEX_HOH_SIN_04 ~~ 1 * HEX_HOH_SIN_04
-  NFP_PHY_01 ~~ 1 * NFP_PHY_01
-  NFP_PHY_02 ~~ 1 * NFP_PHY_02
-  NFP_PHY_03 ~~ 1 * NFP_PHY_03
-  NFP_PHY_04 ~~ 1 * NFP_PHY_04
-
-  # Define latent vars
-  HEX_HOH_SIN =~ .9*HEX_HOH_SIN_01 + .9*HEX_HOH_SIN_02 + .9*HEX_HOH_SIN_03 + .9*HEX_HOH_SIN_04
-  NFP_PHY =~ .9*NFP_PHY_01 + .9*NFP_PHY_02 + .9*NFP_PHY_03 + .9*NFP_PHY_04
-
-  # Covariances
-  HEX_HOH_SIN ~~ .1*NFP_PHY
-  "
-sample <- "
-  HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
-  NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-"
-
-reliability <- sim(
-  # nRep = NULL, 
-  model = sample, 
-#  n = 500,
-  n = seq(500, 5000, 50), 
-  generate = population, 
-  # std.lv = TRUE, 
-  lavaanfun = "sem"
-  )
-
-summary(reliability)
-power_tab <- getPower(reliability)
-power_80 <- findPower(power_tab, "N", 0.90)
-power_80["HEX_HOH_SIN~~NFP_PHY"]
-```
-
-# Results
-## SES
-
-```{r}
-model_ses <- "
-# SES
-Age =~ AGE
-Gender =~ GEN
-Ethnicity =~ ETH
-Relationship =~ REL
-College =~ COL
-Income =~ INC
-Conservatism =~ CON
-
-# Privacy
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-"
-fit_ses <- sem(model_ses, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_ses, standardized = TRUE)
-
-# get standardized data
-d_ses <- 
-  standardizedsolution(fit_ses)
-```
-
-```{r}
-# make table
-tab_ses <- 
-  d_ses %>% 
-  as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_ses_txt, rhs %in% vars_pri) %>% 
-  select("Sociodemographics" = lhs, "Need for privacy" = rhs, est.std) %>% 
-  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
-  pivot_wider(id_cols = "Sociodemographics", names_from = "Need for privacy", values_from = "est.std") %>% 
-  as.data.frame()
-tab_ses
-```
-
-## Dimensions
-
-Factor or dimensions.
-
-```{r}
-model_dim <- "
-# Personality Factors
-HEX_HOH =~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD
-HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
-HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
-HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
-HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
-
-HEX_EMO =~ HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN
-HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
-HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
-HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
-HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
-
-HEX_EXT =~ HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV
-HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
-HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
-HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
-
-HEX_AGR =~ HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
-HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
-HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
-HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
-
-HEX_CNS =~ HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU
-HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
-HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
-HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
-HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
-
-HEX_OPN =~ HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC
-HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
-HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
-HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
-HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
-
-# Privacy
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-"
-fit_dim <- sem(model_dim, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_dim, standardized = TRUE)
-
-# get standardized data
-d_dim <- 
-  standardizedsolution(fit_dim)
-```
-
-```{r}
-# make table
-tab_dim <- 
-  d_dim %>% 
-  as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_pers_dim, rhs %in% vars_pri) %>% 
-  select("Personality dimension" = lhs, "Need for privacy" = rhs, est.std) %>% 
-  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
-  pivot_wider(id_cols = "Personality dimension", names_from = "Need for privacy", values_from = "est.std") %>% 
-  mutate(`Personality dimension` = factor(`Personality dimension`, levels = vars_pers_dim, labels = vars_pers_dim_txt)) %>% 
-  as.data.frame()
-tab_dim
-```
-
-## Facets
-
-```{r}
-model_fac <- "
-# Personality
-HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
-HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
-HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
-HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
-HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
-HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
-HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
-HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
-HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
-HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
-HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
-HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
-HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
-HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
-HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
-HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
-HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
-HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
-HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
-HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
-HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
-HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
-HEX_ALT =~ HEX_ALT_01 + HEX_ALT_02 + HEX_ALT_03 + HEX_ALT_04
-
-# Privacy
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-"
-fit_fac <- sem(model_fac, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_fac, standardized = TRUE)
-
-# get standardized data
-d_fac <- 
-  standardizedsolution(fit_fac)
-```
-
-```{r}
-# make table
-tab_fac <- 
-  d_fac %>% 
-  as.data.frame() %>% 
-  filter(op == "~~", lhs %in% vars_pers_fac, rhs %in% vars_pri) %>% 
-  select("Personality facet" = lhs, "Need for privacy" = rhs, est.std) %>% 
-  mutate(`Need for privacy` = factor(`Need for privacy`, levels = vars_pri, labels = vars_pri_txt)) %>% 
-  pivot_wider(id_cols = "Personality facet", names_from = "Need for privacy", values_from = "est.std") %>% 
-  mutate(`Personality facet` = factor(`Personality facet`, levels = vars_pers_fac, labels = vars_pers_fac_txt)) %>% 
-  as.data.frame
-tab_fac
-```
-
-## Regression
-
-```{r}
-model_reg <- "
-# Personality Factors
-HEX_HOH_SIN =~ HEX_HOH_SIN_01 + HEX_HOH_SIN_02 + HEX_HOH_SIN_03 + HEX_HOH_SIN_04
-HEX_HOH_FAI =~ HEX_HOH_FAI_01 + HEX_HOH_FAI_02 + HEX_HOH_FAI_03 + HEX_HOH_FAI_04
-HEX_HOH_GRE =~ HEX_HOH_GRE_01 + HEX_HOH_GRE_02 + HEX_HOH_GRE_03 + HEX_HOH_GRE_04
-HEX_HOH_MOD =~ HEX_HOH_MOD_01 + HEX_HOH_MOD_02 + HEX_HOH_MOD_03 + HEX_HOH_MOD_04
-
-HEX_EMO_FEA =~ HEX_EMO_FEA_01 + HEX_EMO_FEA_02 + HEX_EMO_FEA_03 + HEX_EMO_FEA_04
-HEX_EMO_ANX =~ HEX_EMO_ANX_01 + HEX_EMO_ANX_02 + HEX_EMO_ANX_03 + HEX_EMO_ANX_04
-HEX_EMO_DEP =~ HEX_EMO_DEP_01 + HEX_EMO_DEP_02 + HEX_EMO_DEP_03 + HEX_EMO_DEP_04
-HEX_EMO_SEN =~ HEX_EMO_SEN_01 + HEX_EMO_SEN_02 + HEX_EMO_SEN_03 + HEX_EMO_SEN_04
-
-HEX_EXT_SSE =~ HEX_EXT_SSE_01 + HEX_EXT_SSE_02 + HEX_EXT_SSE_03 + HEX_EXT_SSE_04
-HEX_EXT_BOL =~ HEX_EXT_BOL_01 + HEX_EXT_BOL_02 + HEX_EXT_BOL_03 + HEX_EXT_BOL_04
-HEX_EXT_SOC =~ HEX_EXT_SOC_01 + HEX_EXT_SOC_02 + HEX_EXT_SOC_03 + HEX_EXT_SOC_04
-HEX_EXT_LIV =~ HEX_EXT_LIV_01 + HEX_EXT_LIV_02 + HEX_EXT_LIV_03 + HEX_EXT_LIV_04
-
-HEX_AGR_FOR =~ HEX_AGR_FOR_01 + HEX_AGR_FOR_02 + HEX_AGR_FOR_03 + HEX_AGR_FOR_04
-HEX_AGR_GEN =~ HEX_AGR_GEN_01 + HEX_AGR_GEN_02 + HEX_AGR_GEN_03 + HEX_AGR_GEN_04
-HEX_AGR_FLX =~ HEX_AGR_FLX_01 + HEX_AGR_FLX_02 + HEX_AGR_FLX_03 + HEX_AGR_FLX_04
-HEX_AGR_PAT =~ HEX_AGR_PAT_01 + HEX_AGR_PAT_02 + HEX_AGR_PAT_03 + HEX_AGR_PAT_04
-
-HEX_CNS_ORG =~ HEX_CNS_ORG_01 + HEX_CNS_ORG_02 + HEX_CNS_ORG_03 + HEX_CNS_ORG_04
-HEX_CNS_DIL =~ HEX_CNS_DIL_01 + HEX_CNS_DIL_02 + HEX_CNS_DIL_03 + HEX_CNS_DIL_04
-HEX_CNS_PER =~ HEX_CNS_PER_01 + HEX_CNS_PER_02 + HEX_CNS_PER_03 + HEX_CNS_PER_04
-HEX_CNS_PRU =~ HEX_CNS_PRU_01 + HEX_CNS_PRU_02 + HEX_CNS_PRU_03 + HEX_CNS_PRU_04
-
-HEX_OPN_AES =~ HEX_OPN_AES_01 + HEX_OPN_AES_02 + HEX_OPN_AES_03 + HEX_OPN_AES_04
-HEX_OPN_INQ =~ HEX_OPN_INQ_01 + HEX_OPN_INQ_02 + HEX_OPN_INQ_03 + HEX_OPN_INQ_04
-HEX_OPN_CRE =~ HEX_OPN_CRE_01 + HEX_OPN_CRE_02 + HEX_OPN_CRE_03 + HEX_OPN_CRE_04
-HEX_OPN_UNC =~ HEX_OPN_UNC_01 + HEX_OPN_UNC_02 + HEX_OPN_UNC_03 + HEX_OPN_UNC_04
-
-# Privacy
-NFP_INF =~ NFP_INF_01 + NFP_INF_02 + NFP_INF_03 + NFP_INF_04
-NFP_PSY =~ NFP_PSY_01 + NFP_PSY_02 + NFP_PSY_03 + NFP_PSY_04
-NFP_PHY =~ NFP_PHY_01 + NFP_PHY_02 + NFP_PHY_03 + NFP_PHY_04
-NFP_SOC =~ NFP_SOC_01 + NFP_SOC_02 + NFP_SOC_03 + NFP_SOC_04
-NFP_GOV =~ NFP_GOV_01 + NFP_GOV_02 + NFP_GOV_03 + NFP_GOV_04
-NFP_COM =~ NFP_COM_01 + NFP_COM_02 + NFP_COM_03 + NFP_COM_04
-NFP_ANO =~ NFP_ANO_01 + NFP_ANO_02 + NFP_ANO_03 + NFP_ANO_04
-NFP_GEN =~ NFP_GEN_01 + NFP_GEN_02 + NFP_GEN_03 + NFP_GEN_04
-
-NFP_INF + NFP_PSY + NFP_PHY + NFP_SOC + NFP_GOV + NFP_COM + NFP_ANO + NFP_GEN ~ HEX_HOH_SIN + HEX_HOH_FAI + HEX_HOH_GRE + HEX_HOH_MOD + HEX_EMO_FEA + HEX_EMO_ANX + HEX_EMO_DEP + HEX_EMO_SEN + HEX_EXT_SSE + HEX_EXT_BOL + HEX_EXT_SOC + HEX_EXT_LIV + HEX_AGR_FOR + HEX_AGR_GEN + HEX_AGR_FLX + HEX_AGR_PAT + HEX_CNS_ORG + HEX_CNS_DIL + HEX_CNS_PER + HEX_CNS_PRU + HEX_OPN_AES + HEX_OPN_INQ + HEX_OPN_CRE + HEX_OPN_UNC + AGE + GEN + ETH + REL + COL + INC + CON
-"
-fit_reg <- sem(model_reg, d, estimator = "ML", fixed.x = TRUE)
-summary(fit_reg, standardized = TRUE)
-
-# get standardized data
-d_reg <- 
-  standardizedsolution(fit_reg, ci = TRUE)
-```
-
-```{r fig.width=10, fig.height=9}
-# make table
-tab_reg <- 
-  d_reg %>% 
-  as.data.frame() %>% 
-  filter(op == "~", lhs %in% vars_pri) %>% 
-  select("Need for privacy" = lhs, "Predictor" = rhs, Estimate = est.std, ci.lower, ci.upper) %>% 
-  mutate(Predictor = factor(Predictor, levels = c(vars_pers_fac, vars_ses), labels = c(vars_pers_fac_txt, vars_ses_txt)),
-         `Need for privacy` = factor(`Need for privacy`, levels = c(vars_pri), labels = c(vars_pri_txt)),
-         Predictor_cat = c(vars_pers_dim_txt %>% rep(each = 4), "Sociodemographics" %>% rep(7)) %>% rep(length(vars_pri_txt)))
-
-# make figure
-reg_fig <- ggplot(tab_reg, aes(x = Estimate, y = Predictor)) + 
-  coord_cartesian(xlim = c(-.5, .5)) +
-  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
-  geom_vline(xintercept = -.1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
-  geom_vline(xintercept = .1, lwd = .75, colour = "darkgrey", linetype = "dashed") + 
-  geom_errorbarh(aes(xmin = ci.lower, xmax = ci.upper),
-                lwd = .75, height = .2, position = position_dodge(-.7)) +
-  geom_point(size = 1.5, position = position_dodge(-.7)) +
-  scale_x_continuous(breaks = c(-.3, 0, .3)) + 
-  theme(
-    axis.title.y = element_blank(),
-    plot.title = element_text(hjust = .5),
-    # panel.spacing = unit(.9, "lines"),
-    text = element_text(size = 12),
-    axis.text.y = element_text(hjust = 1),
-    legend.position = "none"
-    ) + 
-    facet_grid(Predictor_cat ~ `Need for privacy`, scales = "free_y")
-suppressWarnings(print(reg_fig, warning = F))
-
-ggsave("figures/fig_reg.png", width = 9, height = 10)
-```
+# Save Workspace
 
 ```{r cache=F}
-save.image("data/workspace.RData")
+save.image("data/workspace_2.RData")
 ```

### 2024-04-12 index.Rmd
deleting large files

@@
 
-- You can either read the paper [in your browser](proposal.html) or download it as [pdf](proposal.pdf). 
-- You can also find the detailed code and summaries of the [analyses](analyses.html) reported in the paper
+- You can either read the paper [in your browser](manuscript.html) or download it as [pdf](manuscript.pdf). 
+- You can also read the [Stage 1 submission](proposal.html).
+- The data are shared on [AUSSDA](https://data.aussda.at/citation?persistentId=doi:10.11587/IC66GC) and can be used for scientific purposes.
 
-This website is produced directly from the project's [github repository](https://github.com/tdienlin/who_needs_privacy_rr).
-You can download the material and the data, file an issue, or submit a pull request.
+This website is produced directly from the project's [github repository](https://github.com/tdienlin/who_needs_privacy_rr). You can download the material, file an issue, or submit a pull request.

### 2024-04-12 items.rmd
deleting large files

@@
 title: "Items"
+subtitle: "Data-set: Need for Privacy and Personality"
+author: "Tobias Dienlin & Miriam Metzger"
+date: "2024-04-05"
+# output:
+#   html_document:
+#     toc: TRUE
+#     toc_float:
+#       collapsed: FALSE
+#       toc_depth: 3
 output:
-  html_document:
+  pdf_document:
     toc: TRUE
-    toc_float:
-      collapsed: FALSE
-      toc_depth: 3
-# output: pdf_document
+    toc_depth: 1
 bibliography: 
@@
 ---
+
+# Suggested citation
+
+Dienlin, Tobias; Metzger, Miriam, 2024, "Need for Privacy and Personality", https://doi.org/10.11587/IC66GC, AUSSDA.
+
+This document is licenced under a [Creative Commons Attribution 4.0 International Licence](https://creativecommons.org/licenses/by/4.0/).
+
+```{r, out.width = "200px", fig.align='center', echo=F}
+knitr::include_graphics("../Data/license.png")
+```
+
+\newpage
+
+# Overview
+
+ <!-- - For a pdf of all items, click here. -->
+ <!-- - For the actual questionnaire, click here. -->
 
@@
 
-(-3) Strongly Disagree, (-2) Disagree, (-1) Slightly Disagree, (0) Neutral, (1) Slightly Agree (2) Agree, (3) Strongly Agree
+(-3) Strongly Disagree, (-2) Disagree, (-1) Somewhat Disagree, (0) Neutral, (1) Somewhat Agree (2) Agree, (3) Strongly Agree
 
@@
  2. \$1.000 - \$4.000
- 3. > \$4.000
+ 3. \> \$4.000
 

### 2024-04-12 manuscript.Rmd
- Rendered website
deleting large files

@@
 Need for privacy was measured in relation to social, psychological, and physical privacy from other individuals (horizontal privacy); need for privacy from government agencies and companies (vertical privacy); as well as need for informational privacy, anonymity, and general privacy (both horizontal and vertical privacy).
-A sample of 1,576 respondents representative of the U.S.
+A sample of 1,550 respondents representative of the U.S.
 in terms of age, gender, and ethnicity was collected.
-The results showed several substantial relationships: More extraverted people needed substantially more privacy.
-People less honest, less fair, and less altruistic needed more privacy, lending some support to the nothing to hide-argument.
+The results showed several substantial relationships: More extraverted and more agreeable people needed substantially less privacy.
+People less fair and less altruistic needed more psychological privacy, social privacy, and anonymity, lending some support to the 'nothing to hide-argument'.
+Emotionality and conscientiousness showed varied relations with need for privacy.
 More conservative respondents needed more privacy from the government."
@@
 ```{r setup, include=F}
-# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
+devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
 library(devtools)
@@
 
-load("data/workspace_2.RData")
+load("data/workspace_3.RData")
 
@@
 
-<!-- The increasing digitization of everyday life has catapulted  -->
-<!-- which has led to several sweeping societal changes such as the commodification and monetization of personal information [@sevignaniPrivacyCapitalismAge2016],  -->
 Privacy is a major topic of public discourse and academic interest [@dienlinPrivacyDeadLong2023].
 Yet despite its importance, to date we still know surprisingly little about the relation between privacy and personality [@masurSituationalPrivacySelfdisclosure2018, p. 155].
-<!-- Why do some people desire more and some people desire less privacy? -->
 What can we infer about a person if they desire more privacy?
 Are they more introverted, more risk-averse, or more traditional?
-<!-- Or do they have more to hide? -->
 Asking these questions seems relevant, not least because people who desire more privacy are often regarded with suspicion, having to justify why they want to be left alone. 
@@
 
-<!-- This study therefore seeks to understand how the need for privacy is related to dimensions and facets of personality. -->
-
-<!-- It states that data mining and surveillance by government entities poses no threat to the privacy of law-abiding citizens, and is only problematic for people who are engaged in illegal activities who want to hide their information [@soloveVeGotNothing2007, p.
-753].
--->
-<!-- Summarized as “If you have nothing to hide, you have nothing to fear”, it implies that people who desire more privacy are also more likely to be involved in incriminating activities.  -->
-<!-- It is true that people who commit crimes and who are insincere would indeed benefit from greater privacy.  -->
-<!-- However, there exist many alternative reasons as to why people feel a greater or lesser need for privacy.  -->
-<!-- Among those reasons are dispositional explanations.  -->
-<!-- For example, people who need more privacy may be simply more introverted, hesitant, or prudent.  -->
-
-<!-- A better understanding of the relation between personality and privacy is thus useful to illuminate the full range of human motivation for desiring privacy, and thus understanding individual decision-making and behavior surrounding personal privacy.
--->
-<!-- Several theories argue that personality determines privacy behaviors [@masurSituationalPrivacySelfdisclosure2018, p. 155].  -->
-<!-- However, to date there is almost no empirical research that can be used to develop well-informed hypotheses.  -->
-
 ## Privacy and Personality
 
-<!-- We first outline our own understanding of privacy, because the theoretical concept of privacy is multidisciplinary, complicated, and contested [@nissenbaumPrivacyContextTechnology2010, p.
-71].
--->
 Privacy captures a _withdrawal_ from others or from society in general [@westinPrivacyFreedom1967].
@@
 1293).
-<!-- The need for privacy, then, captures "[a]n individual’s need to selectively control the access of others to the individual self with the aim of achieving a desired level of physical or psychological privacy [...]") [@trepteNeedPrivacy2017, p.1].
--->
-<!-- Finally, one can also distinguish between the objective privacy context (e.g., how many users can actually read a post on an SNS?), subjective privacy perceptions (e.g., how many users people _think_ can read a post on an SNS?), and resulting privacy behaviors (e.g., how much do people self-disclose?) [@dienlinPrivacyProcessModel2014].
--->
 Building on these understandings of privacy, in this study we employ a multifaceted model of need for privacy. 
@@
 The HEXACO model stands in the tradition of the Big Five approach [@johnBigFiveTrait1999].
-<!-- and represents a broad understanding of personality-->
 It includes six factors (discussed below), which have four specific facets each. 
-In addition, the HEXACO model includes a sixth factor not present in the Big Five labeled honesty-humility (plus a meta-facet called altruism), which seem particularly well-suited to investigate the nothing-to-hide-argument.
+In addition, the HEXACO model includes a sixth factor not present in the Big Five labeled honesty-humility, plus a meta-facet called altruism, which seem particularly well-suited to investigate the nothing-to-hide-argument.
 
@@
 
-So far, only few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
+So far, only a few studies have analyzed the relation between personality and need for privacy empirically [@hosmanRelationshipsNeedPrivacy1991; @pedersenPersonalityCorrelatesPrivacy1982, see below].
 Moreover, we are not aware of a viable theory specifically connecting privacy and personality.
 Due to the dearth of empirical studies and the lack of theory, in this study we hence adopt an exploratory perspective.
-<!-- In order to guide the selection of personality dimensions that might explain need for privacy best, it is useful to determine why people actually feel they need privacy.  -->
 
@@
 Accordingly, privacy satisfies other more fundamental needs such as safety, sexuality, recovery, or contemplation.
-@westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (i.e., the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
+@westinPrivacyFreedom1967 similarly defined four ultimate purposes of privacy: (1) self-development (the integration of experiences into meaningful patterns), (2) autonomy (the desire to avoid being manipulated and dominated), (3) emotional release (the release of tension from social role demands), and (4) protected communication (the ability to foster intimate relationships).
 Privacy facilitates self-disclosure [@dienlinPrivacyProcessModel2014], and thereby social support, relationships, and intimacy [@omarzuDisclosureDecisionModel2000].
@@
 Being cut-off from others can diminish flourishing, nurture deviant behavior, or introduce power asymmetries [@altmanEnvironmentSocialBehavior1975]. 
-<!-- The fact that privacy fosters self-disclosure also presents a potential risk, because others might disagree, disapprove, or misuse the information [@petronioCommunicationPrivacyManagement2010].
--->
 And privacy can also help conceal wrongdoing or crime.
 
-<!-- To understand why people desire privacy, we can also adopt an evolutionary perspective. -->
 Privacy has strong evolutionary roots [@acquistiHowPrivacyMay2022].
@@
 Results showed greater cheating among students in the privacy condition, suggesting that in situations with more privacy people are less honest. 
-<!-- While this shows a connection between privacy and dishonesty, other studies more directly support the notion that a desire for privacy is related to increased dishonesty. -->
 In a longitudinal sample with 457 respondents in Germany [@treptePrivacySelfdisclosureSocial2013], people who felt they needed more privacy were also less authentic (and therefore, arguably, also less honest and sincere) on their online social network profiles (_r_ = -.48).
 People who needed more privacy were also less authentic in their personal relationships (_r_ = -.28).
-<!-- Together, these studies suggest the possibility that lack of honesty may relate to an increased need for privacy, especially when it comes to government surveillance.    -->
 
@@
 Everyone, including law-abiding citizens, have legitimate reasons to hide specific aspects of their lives [@soloveVeGotNothing2007].
-A recent study confirmed this notion, finding that also those people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].
+A recent study confirmed this notion, finding that people who explicitly endorsed the statement that they would have nothing to hide still engaged in several privacy protective behaviors [@colnagoThereReversePrivacy2023].
 Our argument is rather that people lower on the honesty HEXACO factor may feel a greater need for privacy.
 Considering all the evidence, it seems more plausible to us that lack of honesty may indeed relate to an increased need for privacy, and perhaps especially when it comes to privacy from authorities such as government agencies.
-<!-- , as governments have the legitimate power to prosecute illegal activities.  -->
-<!-- Next, it seems plausible that lack of integrity may relate to an increased need for anonymity, as anonymity makes it more difficult for both government and social agents to identify and address potential wrongdoers.
--->
-<!-- Finally, lack of integrity may also relate to an increased need for privacy from other people, as most other people will disapprove of immoral or illegal activities, and could even reveal those activities to authorities.
--->
 
@@
 
-<!-- Need for privacy might relate to a person’s level of emotionality.  -->
-Emotionality is captured by the facets fearfulness, anxiety, dependence, and sentimentality.
+Emotionality is captured by the facets of fearfulness, anxiety, dependence, and sentimentality.
 People who are anxious may be more likely to view social interactions as risky or threatening [especially with strangers or weak ties, @granovetterStrengthWeakTies1973].
@@
 Comprising the facets social self-esteem, social boldness, sociability, and liveliness, extraversion is arguably the factor that should correspond most closely to need for privacy. 
-<!-- This especially pertains to the sociability facet, which captures whether people prefer to spend their time alone or with company.  -->
-<!-- It is plausible that  -->
 Conceptually, social privacy and sociability are closely related.
@@
 Moreover, conscientious people are more concerned about their privacy [@junglasPersonalityTraitsConcern2008].
-<!-- But as discussed above, especially with regard to privacy from government surveillance, risk averse people could also desire _less_ privacy, so that the government is able to avert potential threats.
--->
-<!-- In sum, think that it is most plausible that people who are more risk averse also desire more privacy in all three contexts measured in this study. -->
 
@@
 
-### Socio-demographic variables
+### Sociodemographic variables
 
@@
 Ethnicity might also correspond to the need for privacy, perhaps because members of minority groups desire more privacy from the government, although not necessarily from other people. 
-Some minorities groups (e.g., Black or Native Americans) often report lower levels of trust in white government representatives [@kochRacialMinoritiesTrust2019], which might increase the desire of privacy from government agencies.
+Some minority groups (e.g., Black or Native Americans) often report lower levels of trust in white government representatives [@kochRacialMinoritiesTrust2019], which might increase the desire of privacy from government agencies.
 Last, we will examine whether one’s political position is related to the need for privacy. 
@@
 This section describes how we determined the sample size, data exclusions, the analyses, and all measures in the study.
-The Study was conducted as an online questionnaire, programmed with Qualtrics.
+The study was conducted as an online questionnaire, programmed with Qualtrics.
 The survey can be found in the [online supplementary material](https://osf.io/e47yw/files/osfstorage/65c363e69b32ca0b4397f002).
@@
 We only considered effects at least as great as _r_ = .10 as sufficiently relevant to support an effect's existence [@cohenPowerPrimer1992]. 
-<!-- Note that the final analyses will be conducted using structural equation modeling (SEM), for which exact power analyses are difficult to obtain.
--->
-<!-- We therefore conducted preliminary power analyses using two-sided bivariate correlations.  -->
 To estimate power, we simulated data.
 We set the correlation between two exemplary latent factors of personality and privacy variable to be $\Psi$ = .10 (the SESOI).
-We, furthermore, set the latent factor loadings to be $\lambda$ = .85.
-<!-- Hence, the following power analyses are not exact but rather a rough guide to get a better idea of the required minimum sample size. -->
-<!-- Oftentimes, researchers opt for an alpha error of 5% and a power of 80% (i.e., beta error of 20%). -->
+We furthermore set the latent factor loadings to be $\lambda$ = .85.
 Adopting an exploratory perspective, and not wanting to miss actually existing effects, we considered both alpha and beta errors to be equally relevant, resulting in balanced/identical alpha and beta errors [@rouderThereFreeLunch2016].
@@
 A power analysis with an alpha and beta error of 10% and an effect size of _r_ = .10 revealed that we required a sample size of _N_ = `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
-To account for potential attrition (see below), we oversampled by five percent, leading to a planned sample size of N = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
-<!-- Hence, we will use two inference criteria: Effects need to show a _p_-value of below _p_ = 10% and an effect size of at least _r_ = .10.  -->
-In the end, `r n_finished` respondents successfully finished our study, slightly exceeding our plans.
+To account for potential attrition (see below), we over-sampled by five percent, leading to a planned sample size of _N_ = `r round(power_80[["HEX_HOH_SIN~~NFP_PHY"]]*.05, 0) + power_80[["HEX_HOH_SIN~~NFP_PHY"]]`.
+In the end, `r n_finished` respondents finished our study, of which we could use `r n_final`, which slightly exceeds our required sample size.
 
@@
 We planned to conservatively remove participants with clear response patterns.
-However, as no clear patterns emerged we maintained all participants.
+`r patterns %>% length() %>% english %>% str_to_title()` participants were excluded because they showed clear patterns, such as straight-lining.
 We automatically excluded participants who missed the two attention checks we implemented.
@@
 Participants who missed one attention check were checked individually regarding response patterns.
-Again, no clear patterns emerged.
+No clear patterns emerged.
 We planned to remove participants below the minimum participation age of 18 years.
@@
 We removed `r n_speeding %>% english::english()` participants for this reason.
-<!-- We will exclude respondents if they answer fewer than 50% of all questions.  -->
 
-We planned to impute missing responses using multiple imputation with predictive mean matching (ten datasets, five iterations, using variables that correlate at least with _r_ = .10). 
+We planned to impute missing responses using multiple imputation with predictive mean matching (ten data-sets, five iterations, using variables that correlate at least with _r_ = .10). 
 However, as there were only `r n_miss(d)` answers missing in total (`r round(prop_miss(d) * 100, 3)` percent), we decided not to impute any data.
-The final sample size was _N_ = `r nrow(d)`.
+The final sample size was _N_ = `r n_final`.
 
@@
 
-<!-- We will test items for potential ceiling and floor effects.  -->
-<!-- If means are below 1.5 or above 6.5, these items will be excluded. -->
 The factorial validity of the measures and the relations were tested using structural equation modeling. 
@@
 We tested each scale in a confirmatory factor analysis. 
-To assess model fit, we used more liberal fit criteria to avoid overfitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
+To assess model fit, we used more liberal fit criteria to avoid over-fitting (CFI > .90, TLI > .90, RMSEA < .10, SRMR < .10) [@klinePrinciplesPracticeStructural2016]. 
 In cases of misfit, we conservatively altered models using an a priori defined analysis pipeline (see online supplementary material).
@@
 If means were below 1.5 or above 6.5, we preregistered to exclude these items.
-However, as no item was outside these threshold, no items were excluded.
+However, as no item was outside these thresholds, no items were excluded.
 
@@
 To get a first idea of the variables' potential causal relations, we also planned to run latent structural regression models.
-However, because model fit was not acceptable we analyzed the potential effects in a multiple regression using the mean values of the observed scores. 
-<!-- We will also test which individual items best predict need for privacy. -->
+However, because model fit was not acceptable, in exploratory analyses we investigated the potential effects in a multiple regression using the mean values of the observed scores.
 
@@
 We planned to use fully latent SEM because we consider it superior to regular analyses such as correlation or regression using manifest variables [@klinePrinciplesPracticeStructural2016]. 
-However, as several of the scales showed suboptimal fit, we decided to report the more conservative correlations of average scores.
-In the online supplementary material (OSM) we also share the results of alternative analyses, such as fully latent SEMs.
+However, when all measures were analyzed together in one single SEM model fit was subpar.
+We hence decided to report the more conservative correlations of average scores.
+In the online supplementary material, we also share the results of alternative analyses, such as fully latent SEMs.
 
@@
 All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
-A list of all the items that we were used are reported in the online supplementary material. 
+A list of all items that we were used are reported in the online supplementary material. 
 The personality and privacy items were presented in random order, and the sociodemographic questions were asked at the end.
-Online we also report all item statistics and their distribution plots.
+In the online supplementary material we also report all item statistics and their distribution plots.
 
 [^2]: Note that the HEXACO inventory normally uses 5-point scales. 
-Because we were not interested in comparing absolute values across studies, we used 7-point scales to have a uniform answer format across all items.
+Because we were not interested in comparing absolute values across studies, we used 7-point scales to have a uniform answer format.
 
@@
 Ad-hoc scales were validated using the following procedure:
-We (a) collected qualitative feedback from three different privacy experts;[^experts]
-(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, assessed convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; (d) analyzed all items in confirmatory factor analyses as outlined above.
+We (a) collected qualitative feedback from three privacy experts;[^experts]
+(b) followed the procedure implemented by @patalayAssessingReadabilitySelfreported2018 to test (and adapt) the items using four established readability indices (i.e., Flesch–Kincaid reading grade, Gunning Fog Index, Coleman Liau Index, and the Dale–Chall Readability Formula); (c) like @frenerDevelopmentValidationNeed2023, assessed convergent validity by collecting single-item measures of privacy concern and privacy behavior, for which we expect to find small to moderate correlations; and (d) analyzed all items in confirmatory factor analyses as outlined above.
 
@@
 
-Personality were measured using the HEXACO personality inventory. 
-The inventory consists of six factors with four facets each, including the additional meta scale of "altruism".
+Personality was measured using the HEXACO personality inventory. 
+The inventory consists of six factors with four facets each, including the additional meta scale of "altruism."
 
@@
 However, some measures such as altruism, unconventionality, or anonymity showed insufficient reliability.
-Instead of strongly adapting measures, we decided to maintain the initial factor structure and did not delete any items or did not introduce substantial changes to the factors.
+Instead of strongly adapting measures, we decided to maintain the initial factor structure and did not delete any items and we did not introduce substantial changes to the factors.
 For an overview of all measures, their descriptives and factorial validity, see Table \@ref(tab:tab-des).
@@
 The only exception was the relation between privacy concerns and the need for social privacy, which was very small (_r_ = .09).
-Similarly, if respondents reported higher needs of privacy they also engaged in more privacy behaviors, with coefficients ranging from _r_ = .20 to _r_ = .71
+If respondents reported higher needs for privacy they also engaged in more privacy behaviors, with coefficients ranging from _r_ = .20 to _r_ = .71
 The only exception was the relation between privacy behavior and the need for social privacy, which was virtually nonexistent (_r_ = .01), and the need for physical privacy, which was very small (_r_ = .09).
 See online supplementary material for all results.
-
-People who reported being less honest and humble needed more anonymity (`r get_res("Honesty humility", "Anonymity")`).
-Looking at facets, more anonymity was needed by people who reported being less fair (`r get_res("Fairness", "Anonymity")`), less modest (`r get_res("Modesty", "Anonymity")`), and less altruistic (`r get_res("Altruism", "Anonymity")`).
-However, less sincere people needed less privacy from companies (`r get_res("Sincerity", "Companies")`) and less privacy in general (`r get_res("Sincerity", "General")`).
-Effects were small or small-to-medium sized.
-
-Several relations between emotionality and need for privacy were found.
-More emotional people needed less psychological privacy (`r get_res("Emotionality", "Psychological")`), less privacy from the government (`r get_res("Emotionality", "Government")`), less anonymity (`r get_res("Emotionality", "Anonymity")`)---but also more physical privacy (`r get_res("Emotionality", "Physical")`).
-More anxious respondents needed substantially more social (`r get_res("Anxiety", "Social")`) and physical privacy (`r get_res("Anxiety", "Physical")`).
-Similarly, more fearful respondents needed more social (`r get_res("Fearfulness", "Social")`) and physical privacy (`r get_res("Fearfulness", "Physical")`).
-More dependent participants generally needed less privacy, including less psychological (`r get_res("Dependence", "Psychological")`) and social privacy (`r get_res("Dependence", "Social")`), less privacy from the government (`r get_res("Dependence", "Government")`), and less informational (`r get_res("Dependence", "Informational")`) and general privacy (`r get_res("Dependence", "General")`).
-A similar picture for more sentimental participants emerged, who needed less psychological (`r get_res("Sentimentality", "Psychological")`) and social privacy (`r get_res("Sentimentality", "Social")`) and less anonymity (`r get_res("Sentimentality", "Anonymity")`).
-
-More extraverted people reported they needed a lot less privacy.
-They wanted less psychological privacy (`r get_res("Extraversion", "Psychological")`), social privacy (`r get_res("Extraversion", "Social")`), and physical privacy (`r get_res("Extraversion", "Physical")`), less informational privacy (`r get_res("Extraversion", "Informational")`) and less anonymity (`r get_res("Extraversion", "Anonymity")`).
-Effect sizes were oftentimes large.
-All facets showed virtually the same relations, with small differences in effect sizes.
-
-More agreeable participants showed a similar pattern, needing less psychological (`r get_res("Agreeableness", "Psychological")`), social privacy (`r get_res("Agreeableness", "Social")`), and physical privacy (`r get_res("Agreeableness", "Physical")`).
-The facets showed virtually the same pattern.
-Effect sizes were substantial, but on the whole smaller than those for extraversion.
-
-Although more conscientious respondents generally needed less privacy, the pattern was varied.
-More conscientious respondents needed less psychological (`r get_res("Conscientiousness", "Psychological")`) and less social privacy (`r get_res("Conscientiousness", "Social")`), as well as less anonymity (`r get_res("Conscientiousness", "Anonymity")`).
-However, when asked about privacy in general more conscientious people responded to need more (`r get_res("Conscientiousness", "General")`).
-Looking at facets of conscientiousness, more organized people needed less social privacy (`r get_res("Organization", "Social")`) and less anonymity (`r get_res("Organization", "Anonymity")`). 
-More prudent participants needed less anonymity (`r get_res("Prudence", "Anonymity")`).
-More diligent people needed less psychological (`r get_res("Diligence", "Psychological")`), social (`r get_res("Diligence", "Social")`), and physical privacy (`r get_res("Diligence", "Physical")`) as well as less anonymity (`r get_res("Diligence", "Anonymity")`).
-At the same time, more perfectionist respondents reported needing more informational (`r get_res("Perfectionism", "Informational")`) and more general privacy (`r get_res("Perfectionism", "General")`).
-
-Whether or not respondents were open to new experiences was largely unrelated to how much privacy they needed.
-Only three facets showed relevant but still small relations. 
-Respondents who reported being more creative needed less psychological (`r get_res("Creativeness", "Psychological", "tab_cor")`) and less social privacy (`r get_res("Creativeness", "Social")`). 
-More inquisitive respondents needed less physical privacy (`r get_res("Inquisitiveness", "Physical")`).
 
@@
 
-Not many meaningful relations between sociodemographic variables and need for privacy were found.
-Older participants needed less social (`r get_res("Age", "Social")`) and less physical privacy (`r get_res("Age", "Physical")`). 
-Male participants needed more anonymity (`r get_res("Male", "Anonymity")`). 
-Less social privacy was needed by people in a relationship (`r get_res("Relationship", "Social")`), with a college degree (`r get_res("College", "Social")`), and with higher income (`r get_res("Income", "Social")`).
-People with higher income also reported needing less physical privacy (`r get_res("Income", "Physical")`). 
-More politically conservative respondents reported needing more privacy from the government (`r get_res("Conservatism", "Government")`).
+People who reported being less honest and humble needed more anonymity (`r get_res("Honesty humility", "Anonymity")`).
+Looking at facets, more anonymity was needed by people who reported being less fair (`r get_res("Fairness", "Anonymity")`), less modest (`r get_res("Modesty", "Anonymity")`), and less altruistic (`r get_res("Altruism", "Anonymity")`).
+People who reported being less fair needed more psychological (`r get_res("Fairness", "Psychological")`), social (`r get_res("Fairness", "Social")`), and physical privacy (`r get_res("Fairness", "Physical")`).
+Similarly, people who reported being less altruistic also needed substantially more psychological (`r get_res("Altruism", "Psychological")`), social (`r get_res("Altruism", "Social")`), and physical privacy (`r get_res("Altruism", "Physical")`).
+However, less sincere people needed less privacy from companies (`r get_res("Sincerity", "Companies")`) and less privacy in general (`r get_res("Sincerity", "General")`).
+Effects were small to medium in size.
 
-In Table \@ref(tab:tab-dim), we report how the personality dimensions predicted need for privacy.
-In Table \@ref(tab:tab-fac), we report how the personality facets predicted need for privacy.
-In Table \@ref(tab:tab-ses), we report how sociodemographics predicted need for privacy.
-In Figure \@ref(fig:fig-cor), you can find how all variables---dimensions, facets, and sociodemographics---predicted the need for privacy.
+Several relations between emotionality and need for privacy were found.
+More emotional people needed less psychological privacy (`r get_res("Emotionality", "Psychological")`), less privacy from the government (`r get_res("Emotionality", "Government")`), less anonymity (`r get_res("Emotionality", "Anonymity")`)---but also needed more physical privacy (`r get_res("Emotionality", "Physical")`).
+More anxious respondents needed substantially more social (`r get_res("Anxiety", "Social")`) and physical privacy (`r get_res("Anxiety", "Physical")`).
+Similarly, more fearful respondents needed more social (`r get_res("Fearfulness", "Social")`) and physical privacy (`r get_res("Fearfulness", "Physical")`).
+More dependent participants generally needed less privacy, including less psychological (`r get_res("Dependence", "Psychological")`) and social privacy (`r get_res("Dependence", "Social")`), less privacy from the government (`r get_res("Dependence", "Government")`), and less informational (`r get_res("Dependence", "Informational")`) and general privacy (`r get_res("Dependence", "General")`).
+A similar picture for more sentimental participants emerged, who needed less psychological (`r get_res("Sentimentality", "Psychological")`) and social privacy (`r get_res("Sentimentality", "Social")`) and less anonymity (`r get_res("Sentimentality", "Anonymity")`).
+
+More extraverted people reported they needed a lot less privacy.
+They wanted less psychological privacy (`r get_res("Extraversion", "Psychological")`), social privacy (`r get_res("Extraversion", "Social")`), and physical privacy (`r get_res("Extraversion", "Physical")`), less informational privacy (`r get_res("Extraversion", "Informational")`) and less anonymity (`r get_res("Extraversion", "Anonymity")`).
+Effect sizes were oftentimes large.
+All facets showed virtually the same relations, with small differences in effect sizes.
+
+More agreeable participants showed a similar pattern.
+They needed less psychological (`r get_res("Agreeableness", "Psychological")`), social privacy (`r get_res("Agreeableness", "Social")`), and physical privacy (`r get_res("Agreeableness", "Physical")`).
+The facets showed virtually the same pattern.
+Effect sizes were substantial, but on the whole smaller than those for extraversion.
+
+Although more conscientious respondents generally needed less privacy, the pattern was varied.
+More conscientious respondents needed less psychological (`r get_res("Conscientiousness", "Psychological")`) and less social privacy (`r get_res("Conscientiousness", "Social")`), as well as less anonymity (`r get_res("Conscientiousness", "Anonymity")`).
+However, when asked about privacy in general more conscientious people responded to need more (`r get_res("Conscientiousness", "General")`).
+More conscientious people also needed more privacy from companies (`r get_res("Conscientiousness", "Companies")`).
+Looking at facets of conscientiousness, more organized people needed less social privacy (`r get_res("Organization", "Social")`) and less anonymity (`r get_res("Organization", "Anonymity")`). 
+More prudent participants needed less anonymity (`r get_res("Prudence", "Anonymity")`).
+More diligent people needed less psychological (`r get_res("Diligence", "Psychological")`), social (`r get_res("Diligence", "Social")`), and physical privacy (`r get_res("Diligence", "Physical")`) as well as less anonymity (`r get_res("Diligence", "Anonymity")`)---but also more privacy from companies (`r get_res("Diligence", "Companies")`)
+At the same time, more perfectionist respondents reported needing more informational (`r get_res("Perfectionism", "Informational")`) privacy, privacy from companies (`r get_res("Perfectionism", "Companies")`), and more general privacy (`r get_res("Perfectionism", "General")`).
+
+Whether or not respondents were open to new experiences was in most cases unrelated to how much privacy they needed.
+People more open to experiences needed more privacy from companies (`r get_res("Openness", "Companies")`) and more privacy in general (`r get_res("Openness", "General")`).
+Three facets showed relevant but still small relations. 
+Respondents who reported being more creative needed less psychological (`r get_res("Creativeness", "Psychological", "tab_cor")`) and less social privacy (`r get_res("Creativeness", "Social")`). 
+More inquisitive respondents needed less physical privacy (`r get_res("Inquisitiveness", "Physical")`) but more privacy from companies (`r get_res("Inquisitiveness", "Companies")`).
 
@@
 
-In exploratory analyses we analyzed how personality facets might have potentially caused need for privacy.
-We found that the psychological need for privacy was explained by two variables.
-The need for psychological privacy was potentially reduced by extraversion (`r get_res("Extraversion", "Psychological", "tab_reg")`) and by emotionality (`r get_res("Emotionality", "Psychological", "tab_reg")`).
-The need for informational privacy was also potentially affected by extraversion and emotionality.
-Being more extraverted substantially decreased the need for psychological privacy (`r get_res("Extraversion", "Social", "tab_reg")`), as did being more emotional (`r get_res("Emotionality", "Social", "tab_reg")`).
-Physical privacy was determined by again extraversion, but also by agreeableness and conscientiousness.
-Being more extraverted potentially decreased the need for physical privacy (`r get_res("Extraversion", "Physical", "tab_reg")`); 
-being more agreeable likewise decreased the need for physical privacy (`r get_res("Agreeableness", "Physical", "tab_reg")`);
-however, being more conscientious increased the need for physical privacy (`r get_res("Conscientiousness", "Physical", "tab_reg")`).
-The need for privacy from the government was potentially affected by the two factors of openness and conservatism.
-Being more open to new experiences potentially increased the need for privacy from the government (`r get_res("Openness", "Government", "tab_reg")`), as did being more politically conservative (`r get_res("Conservatism", "Government", "tab_reg")`).
-The need for privacy from companies was potentially affected by the same two factors.
-Being more open to new experiences potentially increased the need for privacy from companies (`r get_res("Openness", "Companies", "tab_reg")`), as did being more politically conservative (`r get_res("Conservatism", "Companies", "tab_reg")`).
-Being extraverted and conscientious potentially affected the need for informational privacy.
+Not many meaningful relations between sociodemographic variables and need for privacy were found.
+Older participants needed less social (`r get_res("Age", "Social")`) and less physical privacy (`r get_res("Age", "Physical")`). 
+Male participants needed more anonymity (`r get_res("Male", "Anonymity")`). 
+Less social privacy was needed by people in a relationship (`r get_res("Relationship", "Social")`), with a college degree (`r get_res("College", "Social")`), and with higher income (`r get_res("Income", "Social")`).
+People with higher income also reported needing less physical privacy (`r get_res("Income", "Physical")`). 
+More politically conservative respondents reported needing more privacy from the government (`r get_res("Conservatism", "Government")`).
+
+In Table \@ref(tab:tab-dim), we report how the personality dimensions predicted need for privacy.
+In Table \@ref(tab:tab-fac), we report how the personality facets predicted need for privacy.
+In Table \@ref(tab:tab-ses), we report how sociodemographics predicted need for privacy.
+Figure \@ref(fig:fig-cor) summarizes how all of the variables---dimensions, facets, and sociodemographics---predicted the need for privacy.
 
@@
 
-Whereas being more extraverted likely decreased the need for informational privacy (`r get_res("Extraversion", "Informational", "tab_reg")`), being more conscientious likely increased the need for informational privacy (`r get_res("Conscientiousness", "Informational", "tab_reg")`).
-The need for anonymity was potentially affected by extraversion.
+In exploratory analyses we analyzed how personality facets might have potentially caused need for privacy.
+We found that the need for psychological privacy was explained by two variables: extraversion (`r get_res("Extraversion", "Psychological", "tab_reg")`) and emotionality (`r get_res("Emotionality", "Psychological", "tab_reg")`).
+The need for social privacy was also potentially affected by extraversion and emotionality.
+Being more extraverted substantially decreased the need for psychological privacy (`r get_res("Extraversion", "Social", "tab_reg")`), as did being more emotional (`r get_res("Emotionality", "Social", "tab_reg")`).
+Physical privacy was determined by again extraversion, but also by agreeableness and conscientiousness.
+Being more extraverted appeared to decrease the need for physical privacy (`r get_res("Extraversion", "Physical", "tab_reg")`); 
+being more agreeable likewise decreased the need for physical privacy (`r get_res("Agreeableness", "Physical", "tab_reg")`);
+however, being more conscientious increased the need for physical privacy (`r get_res("Conscientiousness", "Physical", "tab_reg")`).
+The need for privacy from the government was affected by the two factors of openness and conservatism.
+Being more open to new experiences potentially increased the need for privacy from the government (`r get_res("Openness", "Government", "tab_reg")`), as did being more politically conservative (`r get_res("Conservatism", "Government", "tab_reg")`).
+The need for privacy from companies was affected by the openness to new experiences only. 
+Being more open to new experiences potentially increased the need for privacy from companies (`r get_res("Openness", "Companies", "tab_reg")`).
+Being extraverted and conscientious affected the need for informational privacy.
+Whereas being more extraverted decreased the need for informational privacy (`r get_res("Extraversion", "Informational", "tab_reg")`), being more conscientious increased the need for informational privacy (`r get_res("Conscientiousness", "Informational", "tab_reg")`) in our data.
+The need for anonymity was meaningfully affected only by extraversion.
 More extraverted people need less anonymity (`r get_res("Extraversion", "Anonymity", "tab_reg")`).
-Finally, the general need for privacy was potentially affected by four variables.
-Being extraverted again likely decreased the general need for privacy (`r get_res("Conservatism", "Companies", "tab_reg")`).
-However, the general need for privacy was potentially increased by being more conscientious (`r get_res("Conscientiousness", "General", "tab_reg")`), more conservative (`r get_res("Conservatism", "General", "tab_reg")`), and more open to experiences (`r get_res("Openness", "General", "tab_reg")`).
+Finally, the general need for privacy was affected by four variables.
+Being extraverted again decreased the general need for privacy (`r get_res("Extraversion", "General", "tab_reg")`).
+However, the general need for privacy was increased by being more conscientious (`r get_res("Conscientiousness", "General", "tab_reg")`), more conservative (`r get_res("Conservatism", "General", "tab_reg")`), and more open to experiences (`r get_res("Openness", "General", "tab_reg")`).
 
-In Figure \@ref(fig:fig-reg), you can find how privacy dimensions and sociodemographics potentially affected the need for privacy.
+Figure \@ref(fig:fig-reg) shows how privacy dimensions and sociodemographics potentially affected the need for privacy.
 
@@
 In this study we analyzed the relation between personality and need for privacy.
-The data came from _N_ = `r n_used` respondents from the US, representative in terms of age, gender, and ethnicity. 
-The results showed several meaningful relations between personality and need for privacy that were statistically significant (_p_ < 10%) and not trivial in size (i.e., 90% CI _r_ $\geq$ .10).
-In a multiple regression with all personality dimensions and sociodemographic variables, we also explored potential causal effects.
+The data came from _N_ = `r n_final` respondents from the US, representative in terms of age, gender, and ethnicity. 
+The results showed several meaningful relations between personality and need for privacy that were statistically significant and not trivial in size (i.e., 90% CI _r_ $\geq$ .10).
 
@@
 The personality factor next closely related to need for privacy was agreeableness. 
-Although this finding aligned with our prior expectation, we were surprised by the strength of the relations.
 More agreeable respondents needed less privacy in general.
 In particular, more agreeable respondents needed substantially less psychological, social, and physical privacy.
-More agreeable people have fewer conflicts with others, are more easy to get along with.
-They likely see others less as a threat, and hence have a reduced need for privacy.
-No relevant relations with need for privacy from government and companies exist, suggesting that agreeableness---a personality trait mostly relevant in interpersonal contexts---might not extend to the need for privacy in these public domains.
+Although this finding aligned with our prior expectation, we were surprised by the strength of the relations.
+Because more agreeable people have fewer conflicts with others and are more easy to get along with, they likely see others less as a threat, and hence have a reduced need for privacy.
+Like as was found for extraversion, no relevant relations with need for privacy from government and companies exist, suggesting that agreeableness and extraversion---personality traits mostly relevant in interpersonal contexts---might not extend to the need for privacy in these public domains.
 
-In analyzing how the honesty humility factor relates to need for privacy, we analyzed the nothing-to-hide argument.
+In analyzing how the honesty humility factor relates to need for privacy, we investigated the nothing-to-hide argument.
 As expected, our results provided support for the nothing-to-hide argument, especially with regard to the need for anonymity.
@@
 Respondents who were less fair and less altruistic also needed more psychological, social, and physical privacy.
-Less honest participants required more anonymity and privacy from other people, be it psychologically, socially, or physically.
+Less honest participants desired more anonymity and privacy from other people, be it psychologically, socially, or physically.
+These findings align with a recent study indicating that individuals with lower levels of honesty are more inclined to seek anonymity online, for example to engage in toxic communication [@nitschinskWhyPeopleSometimes2023].
 However, honesty was unrelated to the need for privacy from government and companies or informational and general privacy.
 If anything, people who were more sincere actually desired more privacy from companies and more privacy in general.
-So although less honest people needed more privacy in several dimensions, this pattern is not general but varied and nuanced.
+So although less honest people needed more privacy in several dimensions, this pattern is not uni-dimensional but somewhat varied and nuanced.
 
@@
 At the same time, they needed more physical privacy. 
-Whereas they want closer bonds to people close to them, they are wary of strangers entering their personal spaces.
+Whereas they may want tighter relational bonds to people close to them, they appear to be warier of strangers entering their personal physical spaces.
 Fearful and anxious people wanted more social and more physical privacy, while dependent and sensitive people wanted less.
-It seems that more emotional people have subtle and varied approach- versus avoidance preferences.
+It seems that more emotional people have a subtle and varied approach to privacy depending on the nature of their emotionality. 
+This is consistent with research on discrete emotions which finds that certain negative emotions---fear and anxiety in particular---evoke the aversive motivational system that facilitates avoidance behaviors, whereas other emotions, possibly including dependence and social sensitivity, activate an appetitive motivational system that facilitates approach behaviors [@phafApproachAvoidanceAffect2014].
 
-Contrary to our expectations, conscientiousness showed a varied relation with need for privacy.
+Contrary to our expectations, conscientiousness showed varied relations with need for privacy.
 More conscientious people needed less psychological and social privacy and less anonymity.
-Asked about privacy in general, however, they answered they needed more.
-This relations was driven by the subscale perfectionism.
-More perfectionist people preferred both more informational privacy and more privacy in general---perhaps to have more options and leeway to adapt plans. 
+Asked about privacy from companies and privacy in general, however, they answered they needed more.
+More perfectionist people preferred both more informational privacy, privacy from companies, and more privacy in general---perhaps to have more options and leeway to adapt plans or hide imperfections.
 More diligent people needed less privacy from other people, less psychological privacy, and less physical privacy. 
-Speculating about a potential explanation, we could imagine that similar to the nothing-to-hide argument more diligent people might have less to be afraid of.
+Speculating about a potential explanation, we could imagine that similar to the nothing-to-hide argument more diligent people might have less to be afraid of and so are more open to public scrutiny.
 
-Although openness might be the opposite of privacy semantically, empirically next to no meaningful relations with need for privacy were found.
-The main dimension showed no relevant relationships.
+Although openness might be the opposite of privacy semantically, empirically only a handful of meaningful relations with need for privacy were found.
+And interestingly, the main dimension showed that more open people actually wanted more privacy from companies and more privacy in general.
 The facet creativity was meaningfully related to psychological and social privacy, such that more creative people needed less psychological and social privacy.
@@
 More inquisitive people needed less physical privacy from others.
-They might see others as a resource, valuing closer exchanges with people unknown to them.
+They, too, might see others as a resource, valuing closer exchanges with people unknown to them.
 
@@
 It is an open question as to whether this relation represents a developmental mechanism or a difference between cohorts.
-With increasing age social relations become more sparse, and perhaps to compensate older people prefer more contact with others.
+Research suggests that older people have fewer social interactions than younger people [@ortiz-ospinaTimeUse2024], which could result in a lower need for social and physical privacy.
 But it could also be a difference between cohorts. 
-Younger people nowadays have fewer social contacts than before, often attributed to increases in time spent online.
+Younger people nowadays have fewer in-person social contacts than before, often attributed to increases in time spent online [@twengeLessInpersonSocial2019].
 Hence, it could also be that younger generations prefer more solitude than the generations beforehand.
@@
 We expected that males would desire more psychological privacy but less social and physical privacy than females.
-Although in our data these relations were statistically significant as well, the effects sizes were too small to be considered meaningful.
+Although in our data these relations were statistically significant, the effects sizes were too small to be considered meaningful.
 The only meaningful gender effect we found was with regard to anonymity.
 Males needed more anonymity than females.
+This finding is in line with the fact that women more readily view themselves as vulnerable and targets for victimization than do men [@lewynMenWomenCrime1993].
 
 People in relationships needed less social privacy.
-This makes sense as being in a relationship implies a minimum openness to committing to others. 
+This makes sense as being in a relationship implies a minimum commitment of openness to others. 
 Contrary to our expectations, respondents with a college degree and with greater income all reported lower levels of need for social privacy.
-Having fewer educational and financial resources might result in fewer social opportunities, reflecting in an increased need for social privacy. 
+Having fewer educational and financial resources might result in greater social stigma, leading to an increased need for social privacy. 
 More politically conservative respondents needed more privacy from the government---which we expected given the general political tendencies of conservatives to prefer fewer state regulations and interferences.
 Finally, no meaningful relations with ethnicity were found.
-For example, contrary to what we expected we did not find that minority groups desired more privacy from the government.
+For example, contrary to what we expected we did not find that minority groups desired more privacy from the government in our data.
 
-Finally, we also looked at the potential impact of personality on need for privacy.
-Results were comparable, in that extraversion turned out to be the major cause of need for privacy.
-However, there were also some changes.
-Most notably, when controlling for other personality dimensions and sociodemographics, results implied that being more conscientious increases the need for physical, informational, and general privacy.
+Based on correlations, the results above analyzed the variables' relationships.
+To analyze the potential impact of personality on need for privacy, in exploratory analyses we also ran several multiple regression analyses, in which we controlled for the respective personality variables and sociodemographics.
+Results were comparable, in that extraversion turned out to be the major potential cause of need for privacy.
+However, there were also some differences.
+Most notably, results implied that being more conscientious increases the need for physical, informational, and general privacy.
 Similarly, being more open to new experiences might increase the need for privacy from the government, from companies, and for privacy in general.
-Finally, multiple regression results suggested that being conservative does not only increase the need for privacy from the government, but also from companies and for privacy in general.
+Finally, multiple regression results suggested that being conservative does not only increase the need for privacy from the government but also for privacy in general.
 All other sociodemographic variables ceased to be significant.
@@
 First, it makes sense to differentiate different levels of need for privacy.
-Many personality traits showed meaningful relations with some dimension, but no or even opposite relations with others.
-To illustrate, whereas more conscientious people desired less psychological privacy and less privacy from other, when asked about privacy in general they needed more. 
-General need for privacy rather represents a cognitive appraisal, whereas social or psychological privacy might be more experienced and psychological.
+Many personality traits showed meaningful relations with some dimension, yet no or even opposite relations with others.
+To illustrate, whereas more conscientious people desired less psychological privacy and less privacy from other, when asked about privacy in general and privacy from companies they needed more. 
+General need for privacy may rather represent a cognitive appraisal, whereas social or psychological privacy might be more experienced-based and psychological. 
+In any case, our results argue for a more rather than less nuanced strategy for measuring privacy attitudes.
 
-Second, the need for privacy from companies and the government, both vertical forms of privacy, showed next to no meaningful relations with personality.
-Most relations were found on the horizontal level, suggesting that personality shows more strongly in these more social and interpersonal aspects of privacy.
+Second, the need for privacy from companies and the government, both vertical forms of privacy, showed only a couple of meaningful relations with personality.
+The most notable relation was that conservative people needed substantially more privacy from the government.
+Most relations between privacy needs and personality were found for forms of horizontal privacy, suggesting that personality has more influence on the more social and interpersonal aspects of privacy.
+So while the demographic variable of political ideology more strongly affected vertical privacy needs, personality aspects appear to better explain horizontal privacy needs.
 
@@
 Although desiring more anonymity was related to less honesty, fairness, and altruism, these relations were not particularly large.
-Next, needing anonymity is insufficient to assume reduced honesty.
-Our results underscore that many other personality aspects related to an increased need of anonymity.
+Next, it is insufficient to assume that anonymity is needed only by people with reduced honesty.
 Less emotional, less extraverted, and more conscientious people also needed more anonymity.
@@
 This leads to our fourth general observation. 
-Our main interest was to determine what predicts the need for privacy.
+Our main interest was to determine the personality factors predicting the need for privacy. 
 What can we learn about a person given their need for privacy? 
-We analyzed these questions in correlation analyses.
-In addition, we also explored the potential causal effects in a multiple regression.
-Here, a somewhat different picture emerged.
-Several correlations we found might not be the results of a causal processes.
-At the same time, some causal effects might also be surpressed in correlation analyses.
+We first analyzed this question in correlation analyses. 
+But in additionally exploring potential causal effects in a multiple regression, a somewhat different picture emerged. 
+The results suggest that several of the correlations we found might not be the result of a causal processes. 
+At the same time, some causal effects might also be suppressed in correlation analyses.
+More research better suited at uncovering causal relations is needed to address this question.
 
@@
 Likewise, some measures such as altruism, unconventionality, or anonymity showed low reliability. 
-The results of these variables need to be interpreted more cautiously.
-Instead of deleting items or changing the factor structure, to avoid overfitting we decided to maintain the measures' original factor structure.
+The results of these variables thus need to be interpreted more cautiously.
 
+Instead of deleting items or changing the factor structure, to avoid over-fitting we decided to maintain the measures’ original factor structure.
 For this reason, instead of reporting the results from latent structural equation modelling, we reported the results of the correlations of the observed variables' means. 
-We report the results of the latent analyses online.
+Interested readers can find the results of the latent analyses in our online supplementary material.
 The results are highly comparable, with the major difference that effect sizes in the latent models tended to be larger.
 The results reported here are hence more conservative and likely underestimate the true effect sizes.
+This underscores the need for further optimizing measures of personality and privacy. 
+We hope this study is a catalyst for future work in this area.
 
@@
 
-All the stimuli, presentation materials, participant data, analysis scripts, and a reproducible version of the manuscript can be found on the open science framework (https://osf.io/e47yw/).
-The paper also has a companion website where all materials can be accessed (https://tdienlin.github.io/Who_Needs_Privacy_RR/proposal.html).
+All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the open science framework (https://osf.io/e47yw/).
+The paper also has a companion website where all materials can be accessed (https://tdienlin.github.io/Who_Needs_Privacy_RR).
 
@@
 
-The data are shared on the open science framework (https://osf.io/e47yw/) and on github.
+The data are shared as a scientific use file on AUSSDA [@dienlinNeedPrivacyPersonality2024].

### 2024-04-12 power_analyses.Rmd
deleting large files

@@
 ---
-title: "power_analyses"
-author: "Tobias Dienlin"
-date: "2024-01-14"
-output: html_document
+title: "Power Analyses"
+output:
+  html_document:
+    toc: TRUE
+    toc_float:
+      collapsed: FALSE
+    toc_depth: 2
+    code_folding: hide
+    df_print: paged
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r knitr-setup, include=F}
+set.seed(170819)
+
+knitr::opts_chunk$set(
+  warning=F, 
+  echo=T, 
+  error=F, 
+  message=F, 
+  cache = T, 
+  tidy=T, 
+  dev = 'pdf', 
+  cache.extra = knitr::rand_seed,
+  fig.height = 6,
+  fig.width = 8
+  )
+
+options(
+  digits = 3, 
+  width = 150,
+  max.print = 100000000
+  )
 ```
 
-```{r}
+```{r results=F, }
 library(lavaan)

### 2024-04-12 questionnaire.rmd
deleting large files

--- 2024-04-12 items.rmd
@@
 ---
-title: "Items"
+title: "Questionnaire"
 subtitle: "Data-set: Need for Privacy and Personality"
@@
 output:
-  pdf_document:
-    toc: TRUE
-    toc_depth: 1
+  pdf_document
 bibliography: 
@@
 ```
-
-\newpage
-
-# Overview
-
- <!-- - For a pdf of all items, click here. -->
- <!-- - For the actual questionnaire, click here. -->
-
-All items were answered on a 7-point scale with the following options:
-
-"To what extent do you agree or disagree with the following statements?"
-
-(-3) Strongly Disagree, (-2) Disagree, (-1) Somewhat Disagree, (0) Neutral, (1) Somewhat Agree (2) Agree, (3) Strongly Agree
-
-# Personality
-
-@leePsychometricPropertiesHEXACO1002018
-
-## Honesty Humility
-### Sincerity
-
- 1. If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
- 1. I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
- 1. If I want something from someone, I will laugh at that person's worst jokes.
- 1. I wouldn't pretend to like someone just to get that person to do favors for me.
-
-### Fairness
-
- 1. If I knew that I could never get caught, I would be willing to steal a million dollars.
- 1. I would be tempted to buy stolen property if I were financially tight.
- 1. I would never accept a bribe, even if it were very large.
- 1. I’d be tempted to use counterfeit money if I were sure I could get away with it.
-
-### Greed Avoidance
-
- 1. Having a lot of money is not especially important to me.
- 1. I would like to live in a very expensive, high-class neighborhood.
- 1. I would like to be seen driving around in a very expensive car.
- 1. I would get a lot of pleasure from owning expensive luxury goods.
-
-### Modesty
-
- 1. I am an ordinary person who is no better than others.
- 1. I wouldn’t want people to treat me as though I were superior to them.
- 1. I think that I am entitled to more respect than the average person is.
- 1. I want people to know that I am an important person of high status.
-
-## Emotionality
-### Fearfulness
-
- 1. I would feel afraid if I had to travel in bad weather conditions.
- 1. I don’t mind doing jobs that involve dangerous work.
- 1. When it comes to physical danger, I am very fearful.
- 1. Even in an emergency I wouldn't feel like panicking.
-
-### Anxiety
-
- 1. I sometimes can't help worrying about little things.
- 1. I worry a lot less than most people do.
- 1. I rarely, if ever, have trouble sleeping due to stress or anxiety.
- 1. I get very anxious when waiting to hear about an important decision.
-
-### Dependence
- 1. When I suffer from a painful experience, I need someone to make me feel comfortable.
- 1. I can handle difficult situations without needing emotional support from anyone else.
- 1. Whenever I feel worried about something, I want to share my concern with another person.
- 1. I rarely discuss my problems with other people.
-
-### Sentimentality
-
- 1. I feel like crying when I see other people crying.
- 1. When someone I know well is unhappy, I can almost feel that person's pain myself.
- 1. I feel strong emotions when someone close to me is going away for a long time.
- 1. I remain unemotional even in situations where most people get very sentimental.
-
-## Extraversion
-### Social Self-Esteem
-
- 1. I feel reasonably satisfied with myself overall.
- 1. I think that most people like some aspects of my personality.
- 1. I feel that I am an unpopular person.
- 1. I sometimes feel that I am a worthless person.
-
-### Social Boldness
-
- 1. I rarely express my opinions in group meetings.
- 1. In social situations, I'm usually the one who makes the first move.
- 1. When I'm in a group of people, I'm often the one who speaks on behalf of the group.
- 1. I tend to feel quite self-conscious when speaking in front of a group of people.
-
-### Sociability
-
- 1. I avoid making "small talk" with people.
- 1. I enjoy having lots of people around to talk with.
- 1. I prefer jobs that involve active social interaction to those that involve working alone.
- 1. The first thing that I always do in a new place is to make friends.
-
-### Liveliness
-
- 1. I am energetic nearly all the time.
- 1. On most days, I feel cheerful and optimistic.
- 1. People often tell me that I should try to cheer up.
- 1. Most people are more upbeat and dynamic than I generally am.
-
-## Agreeableness
-### Forgiveness
-
- 1. I rarely hold a grudge, even against people who have badly wronged me.
- 1. My attitude toward people who have treated me badly is "forgive and forget".
- 1. If someone has cheated me once, I will always feel suspicious of that person.
- 1. I find it hard to fully forgive someone who has done something mean to me.
-
-### Gentleness
-
- 1. People sometimes tell me that I am too critical of others.
- 1. I generally accept people’s faults without complaining about them.
- 1. I tend to be lenient in judging other people.
- 1. Even when people make a lot of mistakes, I rarely say anything negative.
-
-### Flexibility
-
- 1. People sometimes tell me that I'm too stubborn.
- 1. I am usually quite flexible in my opinions when people disagree with me.
- 1. When people tell me that I’m wrong, my first reaction is to argue with them.
- 1. I find it hard to compromise with people when I really think I’m right.
-
-### Patience
-
- 1. People think of me as someone who has a quick temper.
- 1. I rarely feel anger, even when people treat me quite badly.
- 1. Most people tend to get angry more quickly than I do.
- 1. I find it hard to keep my temper when people insult me.
-
-## Conscientiousness
-### Organization
-
- 1. I clean my office or home quite frequently.
- 1. I plan ahead and organize things, to avoid scrambling at the last minute.
- 1. People often joke with me about the messiness of my room or desk.
- 1. When working, I sometimes have difficulties due to being disorganized.
-
-### Diligence
-
- 1. When working, I often set ambitious goals for myself.
- 1. I often push myself very hard when trying to achieve a goal.
- 1. Often when I set a goal, I end up quitting without having reached it.
- 1. I do only the minimum amount of work needed to get by.
-
-### Perfectionism
-
- 1. I often check my work over repeatedly to find any mistakes.
- 1. When working on something, I don't pay much attention to small details.
- 1. I always try to be accurate in my work, even at the expense of time.
- 1. People often call me a perfectionist.
-
-### Prudence
-
- 1. I make decisions based on the feeling of the moment rather than on careful thought.
- 1. I make a lot of mistakes because I don't think before I act.
- 1. I don’t allow my impulses to govern my behavior.
- 1. I prefer to do whatever comes to mind, rather than stick to a plan.
-
-## Openness
-### Aesthetic Appreciation
-
- 1. I would be quite bored by a visit to an art gallery.
- 1. I wouldn't spend my time reading a book of poetry.
- 1. If I had the opportunity, I would like to attend a classical music concert.
- 1. Sometimes I like to just watch the wind as it blows through the trees.
-
-### Inquisitiveness
-
- 1. I'm interested in learning about the history and politics of other countries.
- 1. I enjoy looking at maps of different places.
- 1. I would be very bored by a book about the history of science and technology.
- 1. I’ve never really enjoyed looking through an encyclopedia.
-
-### Creativeness
-
- 1. I would like a job that requires following a routine rather than being creative.
- 1. I would enjoy creating a work of art, such as a novel, a song, or a painting.
- 1. People have often told me that I have a good imagination.
- 1. I don't think of myself as the artistic or creative type.
-
-### Unconventionality
-
- 1. I think that paying attention to radical ideas is a waste of time.
- 1. I like people who have unconventional views.
- 1. I think of myself as a somewhat eccentric person.
- 1. I find it boring to discuss philosophy.
-
-## Altruism
-
- 1. I have sympathy for people who are less fortunate than I am.
- 1. I try to give generously to those in need.
- 1. It wouldn’t bother me to harm someone I didn’t like.
- 1. People see me as a hard-hearted person.
-
-# Need for privacy
-## Horizontal privacy
-### Psychological
-
-@frenerDevelopmentValidationNeed2021
-
- 1.	I don’t like to talk about personal issues with others unless they do it first.
- 2.	There are a lot of things about me that I don’t like to talk about with others.
- 3.	I prefer not to share my feelings and inner thoughts with others.
- 4.	I don't like it when others talk to me about their private issues. (new)
-
-### Physical
-
-@frenerDevelopmentValidationNeed2021
-
- 1.	I don’t like it when strangers come too close to me.
- 2.	I don’t like to stand in a dense crowd of people.
- 3.	I don’t like to sit next to a stranger on a subway, bus, or plane.
- 4.	I hate it when people enter my personal space uninvited. (new)
-
-### Social
-
-@dienlinWhoNeedsPrivacy2019
-
- 1.	I don’t feel comfortable interacting with other people. [@harrisonDevelopmentDesirePrivacy1993]
- 2.	I often want to be alone. (new)
- 3.	I’m a fairly anti-social person. (new)
- 4.	I prefer to work independently in most situations. (new)
-
-## Vertical privacy
-### Privacy from Government
-
-@dienlinWhoNeedsPrivacy2019
-
- 1.	I need government agencies to respect my privacy, even if that makes catching criminals harder.
- 2.	I don’t want the government to gather data about me, even if that makes it harder to spend tax income effectively.
- 3.	I don’t want government agencies to monitor my communication, even if that stops terrorist attacks.
- 4.	I feel I need to protect my privacy from government agencies.
-
-### Privacy from Companies
-
-New, self-designed.
-
- 1. I’m willing to pay more for products or services so that companies don’t have to sell my data.
- 2. I’m happy to give up a little bit of privacy so that I can use certain apps or services for free.
- 3. I don’t want companies to collect data about me, even if that makes their services worse.
- 4. I feel I need to protect my privacy from companies.
-
-## General privacy
-### Informational
-
-@frenerDevelopmentValidationNeed2021
-
- 1.	I would prefer that little is known about me.
- 2.	I don’t want my personal data to be publicly accessible.
- 3.	It is important to me that records pertaining to me remain confidential. [@harrisonDevelopmentDesirePrivacy1993]
- 4.	I prefer that others cannot easily find information about me on the Internet. (new)
-
-### Privacy need anonymity
-
-@dienlinWhoNeedsPrivacy2019
-
- 1.	I would prefer to use a fake account on social network sites to preserve my privacy.
- 2.	I feel I need to avoid places with video surveillance.
- 3.	I prefer not to carry my driver’s license or ID with me all the time to preserve my privacy.
- 4.	I need to be able to surf the Internet anonymously. (new)
-
-### General Need for privacy
-
-New, self-designed.
-
- 1.	I need a lot of privacy.
- 2.	Privacy is very important to me.
- 3.	I think a lot about how I can protect my privacy.
- 4.	I value privacy a lot.
-
-# Privacy other
-## Concerns
-
-I'm very much concerned about my privacy in general.
-
-## Behavior
-
-I often take safety measures to protect my privacy.
-
-# Sociodemographics
-
-## Age
-
-How old are you?
-
-## Gender
-
-How do you describe yourself?
-
- 1. Man
- 2. Woman
- 3. Third gender / other
-
-## Ethnicity
-
-With what ethnicity do you identify with?
-
- 1. White
- 2. Other
-
-## Relationship status
-
-Are you currently in a romantic partnership or relation with another person?
-
- 1. No
- 2. Yes
-
-## College
-
-Please indicate the highest degree you have completed
-
- 1. No college degree
- 2. College degree
-
-## Income
-
-About how much money do you have at your disposal each month?
-
- 1. < \$1.000
- 2. \$1.000 - \$4.000
- 3. \> \$4.000
-
-## Politics
-
-Where would you position yourself politically?
-
- - Extremely liberal
- - Liberal
- - Somewhat liberal
- - Neutral
- - Somewhat conservative
- - Conservative
- - Extremely conservative
-
-## Literature

### 2024-04-12 results.RmD
deleting large files

--- 2024-02-08 analyses.RmD
@@
 ---
-title: "Who needs privacy? Exploring the relations between need for privacy and personality"
-subtitle: "Analyses"
+title: "Results"
 output:
@@
 knitr::opts_chunk$set(
-  warning=F, 
-  echo=F, 
-  error=F, 
-  message=F, 
-  cache = T, 
-  tidy=T, 
-  dev = 'pdf', 
-  cache.extra = knitr::rand_seed
+  warning=F
+  , echo=T
+  , error=F
+  , message=F
+  , cache=T
+  , tidy=T
+  # , dev = 'pdf'
+  # , cache.extra = knitr::rand_seed
+  , fig.height = 4
+  , fig.width = 6
   )
@@
 # Set-Up
-## Packages
-
-```{r r-setup, include=T, echo=T, results='hide'}
+
+We first load the required packages.
+
+```{r packages, include=T, echo=T, results='hide', cache=F}
 # install packages
@@
 library(corrplot)
-library(devtools)
 library(easystats)
-library(GGally)
 library(ggplot2)
-library(haven)
 library(kableExtra)
@@
 library(magrittr)
-library(mice)
 library(MVN)
@@
 library(psych)
-library(quanteda.textstats)
-library(pwr)
-library(semPlot)
 library(sjlabelled)
-library(simsem)
 library(semTools)
@@
 library(td)
-
-load("data/workspace_1.RData")
+```
+
+We then load the cleaned data.
+
+```{r data, include=T, echo=T, results='hide', cache=T}
+load("data/workspace_2.RData")
 source("custom_functions.R")
@@
 
-```{r data-wrangling}
-# d <- read_spss("data/Need+for+Privacy_February+27%2C+2023_13.45.sav")
-d_raw <- sjlabelled::read_spss(
-  "data/Need+for+Privacy_February+6%2C+2024_15.56.sav",
-  convert.factors = FALSE
-  )
-```
-
-### Data-Wrangling
-
-```{r data-inverting}
-vars_invert <- c(
-  "HEX_HOH_SIN_01", "HEX_HOH_SIN_03",
-  "HEX_HOH_FAI_01", "HEX_HOH_FAI_02", "HEX_HOH_FAI_04",
-  "HEX_HOH_GRE_02", "HEX_HOH_GRE_03", "HEX_HOH_GRE_04",
-  "HEX_HOH_MOD_03", "HEX_HOH_MOD_04",
-  "HEX_EMO_FEA_02", "HEX_EMO_FEA_04",
-  "HEX_EMO_ANX_02", "HEX_EMO_ANX_03",
-  "HEX_EMO_DEP_02", "HEX_EMO_DEP_04",
-  "HEX_EMO_SEN_04",
-  "HEX_EXT_SSE_03", "HEX_EXT_SSE_04",
-  "HEX_EXT_BOL_01", "HEX_EXT_BOL_04",
-  "HEX_EXT_SOC_01",
-  "HEX_EXT_LIV_03", "HEX_EXT_LIV_04",
-  "HEX_AGR_FOR_03", "HEX_AGR_FOR_04",
-  "HEX_AGR_GEN_01",
-  "HEX_AGR_FLX_01", "HEX_AGR_FLX_03", "HEX_AGR_FLX_04",
-  "HEX_AGR_PAT_01", "HEX_AGR_PAT_04",
-  "HEX_CNS_ORG_03", "HEX_CNS_ORG_04",
-  "HEX_CNS_DIL_03", "HEX_CNS_DIL_04",
-  "HEX_CNS_PER_02",
-  "HEX_CNS_PRU_01", "HEX_CNS_PRU_02", "HEX_CNS_PRU_04",
-  "HEX_OPN_AES_01", "HEX_OPN_AES_02",
-  "HEX_OPN_INQ_03", "HEX_OPN_INQ_04",
-  "HEX_OPN_CRE_01", "HEX_OPN_CRE_04",
-  "HEX_OPN_UNC_01", "HEX_OPN_UNC_04",
-  "HEX_ALT_03", "HEX_ALT_04",
-  "NFP_COM_02"
-)
-
-d <-
-  d_raw %>% 
-  rename(
-    COL = COL_,
-    REL = REL_
-    ) %>%
-  mutate(
-    across(all_of(vars_invert),
-    ~ 8 - .x
-         ),
-    male = case_match(
-      GEN,
-      c(2, 3) ~ 0,
-      1 ~ 1),
-    age = case_match(
-      AGE,
-      1 ~ 1,
-      2 ~ 2,
-      3 ~ 3,
-      4 ~ 4,
-      5 ~ 7,
-      6 ~ 5,
-      7 ~ 6),
-    white = case_match(
-      ETH,
-      2 ~ 0,
-      1 ~ 1),
-    relation = case_match(
-      REL,
-      2 ~ 1,
-      1 ~ 0),
-    college = case_match(
-      COL,
-      2 ~ 1,
-      1 ~ 0),
-    conserv = CON,
-    income = INC
-  ) 
-```
-
-### Labels
-
-```{r data-labels}
-# define vars and labels
-vars_ses <- c("age", "male", "white", "relation", "college", "income", "conserv")
-vars_ses_txt <- c("Age", "Male", "White", "Relationship", "College", "Income", "Conservatism")
-
-vars_pers_fac <- c("HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD",
-                   "HEX_ALT",
-                   "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN", 
-                   "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV", 
-                   "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT", 
-                   "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU", 
-                   "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
-vars_pers_fac_txt <- c("Sincerity", "Fairness", "Greed avoidance", "Modesty", 
-                       "Altruism",
-                       "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
-                       "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
-                       "Forgiveness", "Gentleness", "Flexibility", "Patience", 
-                       "Organization", "Diligence", "Perfectionism", "Prudence", 
-                       "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality")
-
-vars_pers_hoh <- 
-  c("HEX_HOH", "HEX_HOH_SIN", "HEX_HOH_FAI", "HEX_HOH_GRE", "HEX_HOH_MOD", "HEX_ALT")
-vars_pers_emo <- 
-  c("HEX_EMO", "HEX_EMO_FEA", "HEX_EMO_ANX", "HEX_EMO_DEP", "HEX_EMO_SEN")
-vars_pers_ext <- 
-  c("HEX_EXT", "HEX_EXT_SSE", "HEX_EXT_BOL", "HEX_EXT_SOC", "HEX_EXT_LIV")
-vars_pers_agr <- 
-  c("HEX_AGR", "HEX_AGR_FOR", "HEX_AGR_GEN", "HEX_AGR_FLX", "HEX_AGR_PAT")
-vars_pers_cns <- 
-  c("HEX_CNS", "HEX_CNS_ORG", "HEX_CNS_DIL", "HEX_CNS_PER", "HEX_CNS_PRU")
-vars_pers_opn <- 
-  c("HEX_OPN", "HEX_OPN_AES", "HEX_OPN_INQ", "HEX_OPN_CRE", "HEX_OPN_UNC")
-
-vars_pers_all <- 
-  c(
-    vars_pers_hoh, 
-    vars_pers_emo, 
-    vars_pers_ext, 
-    vars_pers_agr, 
-    vars_pers_cns,
-    vars_pers_opn
-    )
-
-vars_pers_all_txt <- 
-  c("Honesty humility", 
-      "Sincerity", "Fairness", "Greed avoidance", "Modesty", "Altruism",
-    "Emotionality", 
-      "Fearfulness", "Anxiety", "Dependence", "Sentimentality", 
-    "Extraversion",
-      "Social self-esteem", "Social boldness", "Sociability", "Liveliness",
-    "Agreeableness",
-      "Forgiveness", "Gentleness", "Flexibility", "Patience",
-    "Conscientiousness",
-      "Organization", "Diligence", "Perfectionism", "Prudence", 
-    "Openness",
-      "Aesthetic\nappreciation", "Inquisitiveness", "Creativeness", "Unconventionality"
-    )
-
-vars_pred_all_txt <- 
-  c(
-    vars_pers_all_txt,
-    vars_ses_txt
-    )
-
-vars_pers_dim <- c("HEX_HOH", "HEX_EMO", "HEX_EXT", "HEX_AGR", "HEX_CNS", "HEX_OPN")
-vars_pers_dim_txt <- c("Honesty humility", "Emotionality", "Extraversion", 
-                       "Agreeableness", "Conscientiousness", "Openness")
-
-vars_pri <- c("NFP_PSY", "NFP_SOC", "NFP_PHY", 
-              "NFP_GOV", "NFP_COM", 
-              "NFP_INF", "NFP_ANO", "NFP_GEN")
-vars_pri_txt <- c("Psychological", "Social", "Physical", 
-                  "Government", "Companies", 
-                  "Informational", "Anonymity", "General")
-vars_pri_txt_brk <- c("Psycho-\nlogical", "Social", "Physical", 
-                  "Govern-\nment", "Companies", 
-                  "Infor-\nmational", "Anony-\nmity", "General")
-vars_pri_txt_abr <- c("Psych.", "Social", "Phys.", 
-                  "Gov.", "Comp.", 
-                  "Inform.", "Anonym.", "General")
-
-vars_pers_pri <- c(vars_pers_fac, vars_pri)
-```
-
-## Means
-
-```{r}
-# Person means per facet
-
-d %<>%
-  mutate(
-    HEX_HOH_M = rowMeans(select(., starts_with("HEX_HOH"))),
-    HEX_EMO_M = rowMeans(select(., starts_with("HEX_EMO"))),
-    HEX_EXT_M = rowMeans(select(., starts_with("HEX_EXT"))),
-    HEX_AGR_M = rowMeans(select(., starts_with("HEX_AGR"))),
-    HEX_CNS_M = rowMeans(select(., starts_with("HEX_CNS"))),
-    HEX_OPN_M = rowMeans(select(., starts_with("HEX_OPN"))),
-    HEX_ALT_M = rowMeans(select(., starts_with("HEX_ALT_0"))),
-    HEX_AGR_FLX_M = rowMeans(select(., starts_with("HEX_AGR_FLX_0"))),
-    HEX_AGR_FOR_M = rowMeans(select(., starts_with("HEX_AGR_FOR_0"))),
-    HEX_AGR_GEN_M = rowMeans(select(., starts_with("HEX_AGR_GEN_0"))),
-    HEX_AGR_PAT_M = rowMeans(select(., starts_with("HEX_AGR_PAT_0"))),
-    HEX_CNS_DIL_M = rowMeans(select(., starts_with("HEX_CNS_DIL_0"))),
-    HEX_CNS_ORG_M = rowMeans(select(., starts_with("HEX_CNS_ORG_0"))),
-    HEX_CNS_PER_M = rowMeans(select(., starts_with("HEX_CNS_PER_0"))),
-    HEX_CNS_PRU_M = rowMeans(select(., starts_with("HEX_CNS_PRU_0"))),
-    HEX_EMO_ANX_M = rowMeans(select(., starts_with("HEX_EMO_ANX_0"))),
-    HEX_EMO_DEP_M = rowMeans(select(., starts_with("HEX_EMO_DEP_0"))),
-    HEX_EMO_FEA_M = rowMeans(select(., starts_with("HEX_EMO_FEA_0"))),
-    HEX_EMO_SEN_M = rowMeans(select(., starts_with("HEX_EMO_SEN_0"))),
-    HEX_EXT_BOL_M = rowMeans(select(., starts_with("HEX_EXT_BOL_0"))),
-    HEX_EXT_LIV_M = rowMeans(select(., starts_with("HEX_EXT_LIV_0"))),
-    HEX_EXT_SOC_M = rowMeans(select(., starts_with("HEX_EXT_SOC_0"))),
-    HEX_EXT_SSE_M = rowMeans(select(., starts_with("HEX_EXT_SSE_0"))),
-    HEX_HOH_FAI_M = rowMeans(select(., starts_with("HEX_HOH_FAI_0"))),
-    HEX_HOH_GRE_M = rowMeans(select(., starts_with("HEX_HOH_GRE_0"))),
-    HEX_HOH_MOD_M = rowMeans(select(., starts_with("HEX_HOH_MOD_0"))),
-    HEX_HOH_SIN_M = rowMeans(select(., starts_with("HEX_HOH_SIN_0"))),
-    HEX_OPN_AES_M = rowMeans(select(., starts_with("HEX_OPN_AES_0"))),
-    HEX_OPN_CRE_M = rowMeans(select(., starts_with("HEX_OPN_CRE_0"))),
-    HEX_OPN_INQ_M = rowMeans(select(., starts_with("HEX_OPN_INQ_0"))),
-    HEX_OPN_UNC_M = rowMeans(select(., starts_with("HEX_OPN_UNC_0"))),
-    NFP_ANO_M = rowMeans(select(., starts_with("NFP_ANO_0"))),
-    NFP_COM_M = rowMeans(select(., starts_with("NFP_COM_0"))),
-    NFP_GEN_M = rowMeans(select(., starts_with("NFP_GEN_0"))),
-    NFP_GOV_M = rowMeans(select(., starts_with("NFP_GOV_0"))),
-    NFP_INF_M = rowMeans(select(., starts_with("NFP_INF_0"))),
-    NFP_PHY_M = rowMeans(select(., starts_with("NFP_PHY_0"))),
-    NFP_PSY_M = rowMeans(select(., starts_with("NFP_PSY_0"))),
-    NFP_SOC_M = rowMeans(select(., starts_with("NFP_SOC_0")))
-  )
-
-# item means
-c_m <- 
-  c(
-    HEX_ALT_m     = mean(d$HEX_ALT_M, na.rm = T),
-    HEX_AGR_FLX_m = mean(d$HEX_AGR_FLX_M, na.rm = T),
-    HEX_AGR_FOR_m = mean(d$HEX_AGR_FOR_M, na.rm = T),
-    HEX_AGR_GEN_m = mean(d$HEX_AGR_GEN_M, na.rm = T),
-    HEX_AGR_PAT_m = mean(d$HEX_AGR_PAT_M, na.rm = T),
-    HEX_CNS_DIL_m = mean(d$HEX_CNS_DIL_M, na.rm = T),
-    HEX_CNS_ORG_m = mean(d$HEX_CNS_ORG_M, na.rm = T),
-    HEX_CNS_PER_m = mean(d$HEX_CNS_PER_M, na.rm = T),
-    HEX_CNS_PRU_m = mean(d$HEX_CNS_PRU_M, na.rm = T),
-    HEX_EMO_ANX_m = mean(d$HEX_EMO_ANX_M, na.rm = T),
-    HEX_EMO_DEP_m = mean(d$HEX_EMO_DEP_M, na.rm = T),
-    HEX_EMO_FEA_m = mean(d$HEX_EMO_FEA_M, na.rm = T),
-    HEX_EMO_SEN_m = mean(d$HEX_EMO_SEN_M, na.rm = T),
-    HEX_EXT_BOL_m = mean(d$HEX_EXT_BOL_M, na.rm = T),
-    HEX_EXT_LIV_m = mean(d$HEX_EXT_LIV_M, na.rm = T),
-    HEX_EXT_SOC_m = mean(d$HEX_EXT_SOC_M, na.rm = T),
-    HEX_EXT_SSE_m = mean(d$HEX_EXT_SSE_M, na.rm = T),
-    HEX_HOH_FAI_m = mean(d$HEX_HOH_FAI_M, na.rm = T),
-    HEX_HOH_GRE_m = mean(d$HEX_HOH_GRE_M, na.rm = T),
-    HEX_HOH_MOD_m = mean(d$HEX_HOH_MOD_M, na.rm = T),
-    HEX_HOH_SIN_m = mean(d$HEX_HOH_SIN_M, na.rm = T),
-    HEX_OPN_AES_m = mean(d$HEX_OPN_AES_M, na.rm = T),
-    HEX_OPN_CRE_m = mean(d$HEX_OPN_CRE_M, na.rm = T),
-    HEX_OPN_INQ_m = mean(d$HEX_OPN_INQ_M, na.rm = T),
-    HEX_OPN_UNC_m = mean(d$HEX_OPN_UNC_M, na.rm = T),
-    NFP_ANO_m     = mean(d$NFP_ANO_M, na.rm = T),
-    NFP_COM_m     = mean(d$NFP_COM_M, na.rm = T),
-    NFP_GEN_m     = mean(d$NFP_GEN_M, na.rm = T),
-    NFP_GOV_m     = mean(d$NFP_GOV_M, na.rm = T),
-    NFP_INF_m     = mean(d$NFP_INF_M, na.rm = T),
-    NFP_PHY_m     = mean(d$NFP_PHY_M, na.rm = T),
-    NFP_PSY_m     = mean(d$NFP_PSY_M, na.rm = T),
-    NFP_SOC_m     = mean(d$NFP_SOC_M, na.rm = T),
-    HEX_HOH_m     = mean(d$HEX_HOH_M, na.rm = T),
-    HEX_EMO_m     = mean(d$HEX_EMO_M, na.rm = T),
-    HEX_EXT_m     = mean(d$HEX_EXT_M, na.rm = T),
-    HEX_AGR_m     = mean(d$HEX_AGR_M, na.rm = T),
-    HEX_CNS_m     = mean(d$HEX_CNS_M, na.rm = T),
-    HEX_OPN_m     = mean(d$HEX_OPN_M, na.rm = T)
-  )
-
-# item standard deviation
-c_sd <- 
-  c(
-    HEX_ALT_sd     = sd(d$HEX_ALT_M, na.rm = T),
-    HEX_AGR_FLX_sd = sd(d$HEX_AGR_FLX_M, na.rm = T),
-    HEX_AGR_FOR_sd = sd(d$HEX_AGR_FOR_M, na.rm = T),
-    HEX_AGR_GEN_sd = sd(d$HEX_AGR_GEN_M, na.rm = T),
-    HEX_AGR_PAT_sd = sd(d$HEX_AGR_PAT_M, na.rm = T),
-    HEX_CNS_DIL_sd = sd(d$HEX_CNS_DIL_M, na.rm = T),
-    HEX_CNS_ORG_sd = sd(d$HEX_CNS_ORG_M, na.rm = T),
-    HEX_CNS_PER_sd = sd(d$HEX_CNS_PER_M, na.rm = T),
-    HEX_CNS_PRU_sd = sd(d$HEX_CNS_PRU_M, na.rm = T),
-    HEX_EMO_ANX_sd = sd(d$HEX_EMO_ANX_M, na.rm = T),
-    HEX_EMO_DEP_sd = sd(d$HEX_EMO_DEP_M, na.rm = T),
-    HEX_EMO_FEA_sd = sd(d$HEX_EMO_FEA_M, na.rm = T),
-    HEX_EMO_SEN_sd = sd(d$HEX_EMO_SEN_M, na.rm = T),
-    HEX_EXT_BOL_sd = sd(d$HEX_EXT_BOL_M, na.rm = T),
-    HEX_EXT_LIV_sd = sd(d$HEX_EXT_LIV_M, na.rm = T),
-    HEX_EXT_SOC_sd = sd(d$HEX_EXT_SOC_M, na.rm = T),
-    HEX_EXT_SSE_sd = sd(d$HEX_EXT_SSE_M, na.rm = T),
-    HEX_HOH_FAI_sd = sd(d$HEX_HOH_FAI_M, na.rm = T),
-    HEX_HOH_GRE_sd = sd(d$HEX_HOH_GRE_M, na.rm = T),
-    HEX_HOH_MOD_sd = sd(d$HEX_HOH_MOD_M, na.rm = T),
-    HEX_HOH_SIN_sd = sd(d$HEX_HOH_SIN_M, na.rm = T),
-    HEX_OPN_AES_sd = sd(d$HEX_OPN_AES_M, na.rm = T),
-    HEX_OPN_CRE_sd = sd(d$HEX_OPN_CRE_M, na.rm = T),
-    HEX_OPN_INQ_sd = sd(d$HEX_OPN_INQ_M, na.rm = T),
-    HEX_OPN_UNC_sd = sd(d$HEX_OPN_UNC_M, na.rm = T),
-    NFP_ANO_sd     = sd(d$NFP_ANO_M, na.rm = T),
-    NFP_COM_sd     = sd(d$NFP_COM_M, na.rm = T),
-    NFP_GEN_sd     = sd(d$NFP_GEN_M, na.rm = T),
-    NFP_GOV_sd     = sd(d$NFP_GOV_M, na.rm = T),
-    NFP_INF_sd     = sd(d$NFP_INF_M, na.rm = T),
-    NFP_PHY_sd     = sd(d$NFP_PHY_M, na.rm = T),
-    NFP_PSY_sd     = sd(d$NFP_PSY_M, na.rm = T),
-    NFP_SOC_sd     = sd(d$NFP_SOC_M, na.rm = T),
-    HEX_HOH_sd     = sd(d$HEX_HOH_M, na.rm = T),
-    HEX_EMO_sd     = sd(d$HEX_EMO_M, na.rm = T),
-    HEX_EXT_sd     = sd(d$HEX_EXT_M, na.rm = T),
-    HEX_AGR_sd     = sd(d$HEX_AGR_M, na.rm = T),
-    HEX_CNS_sd     = sd(d$HEX_CNS_M, na.rm = T),
-    HEX_OPN_sd     = sd(d$HEX_OPN_M, na.rm = T)
-  )
-```
-
-# Missing data
-
-First filter those who didn't finish the questionnaire.
-
-```{r}
-d %<>%
-  filter(
-    Progress == 100
-  )
-
-n_finished <- nrow(d)
-```
-
-Let's first inspect missing data.
-
-How many missing do we have?
-
-```{r}
-n_miss(d)
-prop_miss(d)
-```
-
-Only 23 cells are missing -- which is very little. To be precise, 0.00006 percent only.
-
-Which variables are affected?
-
-```{r}
-miss_var_summary(d) %>% 
-  head(19)
-```
-
-Missing answers vary randomly across variables.
-
-How about participants?
-
-```{r}
-miss_case_summary(d)
-```
-
-Only six participants with missing data, and even then, not much. We hence decided to keep everyone.
-
-# Quality checks
-
-We preregistered to remove participants faster than 3 standard deviations than the median response time.
-
-```{r cache=F}
-# Median response time
-time_med <- median(d$Duration__in_seconds_)
-
-# Average response time
-time_m <- mean(d$Duration__in_seconds_) / 60
-
-# Standard deviation
-time_sd <- sd(d$Duration__in_seconds_)
-
-# filter speeders
-time_crit_init <- time_med - (3 * time_sd) # minimum time on survey
-```
-
-However, this made little sense. The median response time was `r time_med` and the standard deviation `r time_sd`. Hence, three SDs below median was `r time_crit_init`, hence not informative.
-
-Instead, we decided to remove respondents who took less than five minutes answering the questionnaire, which we considered unreasonably fast.
-
-```{r cache=F}
-time_crit <- 5 * 60
-
-# count number of speeders
-n_speeding <- 
-  nrow(
-    filter(
-      d, 
-      Duration__in_seconds_ < time_crit
-      )
-    )
-
-# Deletion of fast respondents
-d <- 
-  filter(
-    d, 
-    Duration__in_seconds_ >= time_crit
-    )
-
-n_used <- nrow(d)
-```
-
-Average response time was `r time_m %>% round(0)` minutes. We removed `r n_speeding` because they answered the survey unreasonably fast.
-
-Let's inspect for potential response patterns.
-
-# Sociodemographics
+# Items Characteristics
+
+In what follows, we report item characteristics.
+
+## Sociodemographics
 
@@
 
-Let's first inspect age. Here, the age categories were as follows:
-
-1: Under 18 years old
-2: 18-24 years old 
-3: 25-34 years old 
-4: 35-44 years old 
-5: 45-54 years old 
-6: 55-64 years old 
-7: 65+ years old
-
-```{r}
-table(d$AGE)
+### Age
+
+```{r}
+d$age %>% 
+  sjlabelled::as_label() %>% 
+  data_tabulate()
 ```
@@
 age_m <- 
-  mean(d$AGE)
+  mean(d$age)
 ```
@@
 
-Let's next inspect gender. Categories were:
-
-1: "Man" 
-2: "Woman" 
-3: "Third gender / Other"
-
-```{r}
-table(d$GEN) %>% 
-  prop.table() %>% 
-  round(2)
+### Gender
+
+```{r}
+d$GEN %>% 
+  sjlabelled::as_label() %>% 
+  data_tabulate()
 ```
@@
 
-Let's next inspect education. Categories were:
-
-1: "No college degree" 
-2: "College degree"
-
-```{r}
-table(d$COL) %>% 
-  prop.table() %>% 
-  round(2)
+### Education
+
+```{r}
+d$COL %>% 
+  sjlabelled::as_label() %>% 
+  data_tabulate()
 ```
@@
 
-Let's next inspect ethnicity. Answer categories were as follows:
-
-1: "White"
-2: "Other"
-
-```{r}
-table(d$ETH) %>%
-  prop.table() %>% 
-  round(2)
+### Ethnicity
+
+```{r}
+d$ETH %>% 
+  sjlabelled::as_label() %>% 
+  data_tabulate()
 ```
@@
 
-# Items
-
-All items were answered on a 7-point scale with the following options:
+### Political orientation
+
+```{r}
+d$CON %>% 
+  sjlabelled::as_label() %>% 
+  data_tabulate()
+```
+
+We see a certain bias toward participants being liberal as opposed to conservative.
+
+## Personality
+
+All following items were answered on a 7-point scale with the following options:
 
@@
 
-## Ceiling/Floor effects
+### Ceiling/Floor effects
 
@@
 ```{r}
+d_extremes <-
   d %>%
@@
     2,  mean, na.rm = T
-  )
-```
-
-No item below floor (1.5) or ceiling (6.5) thresholds.
-
-## Personality
+  ) %>% 
+  as.data.frame() %>% 
+  select(Mean = ".") %>% 
+  arrange(Mean)
+```
+
+Lowest values:
+
+```{r}
+head(d_extremes)
+```
+
+No item below floor (1.5) threshold.
+
+Highest values:
+
+```{r}
+tail(d_extremes)
+```
+
+No item above ceiling (6.5) thresholds.
+
 ### Honesty Humility
@@
 
- - If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
- - I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
- - If I want something from someone, I will laugh at that person's worst jokes.
- - I wouldn't pretend to like someone just to get that person to do favors for me.
+ 1. If I want something from a person I dislike, I will act very nicely toward that person in order to get it.
+ 1. I wouldn't use flattery to get a raise or promotion at work, even if I thought it would succeed.
+ 1. If I want something from someone, I will laugh at that person's worst jokes.
+ 1. I wouldn't pretend to like someone just to get that person to do favors for me.
 
@@
 plot_hist(name)
-
+```
+
+```{r}
 mardia(
@@
 
- - If I knew that I could never get caught, I would be willing to steal a million dollars.
- - I would be tempted to buy stolen property if I were financially tight.
- - I would never accept a bribe, even if it were very large.
- - I’d be tempted to use counterfeit money, if I were sure I could get away with it.
+ 1. If I knew that I could never get caught, I would be willing to steal a million dollars.
+ 1. I would be tempted to buy stolen property if I were financially tight.
+ 1. I would never accept a bribe, even if it were very large.
+ 1. I’d be tempted to use counterfeit money, if I were sure I could get away with it.
 
@@
 
- - Having a lot of money is not especially important to me.
- - I would like to live in a very expensive, high-class neighborhood.
- - I would like to be seen driving around in a very expensive car.
- - I would get a lot of pleasure from owning expensive luxury goods.
+ 1. Having a lot of money is not especially important to me.
+ 1. I would like to live in a very expensive, high-class neighborhood.
+ 1. I would like to be seen driving around in a very expensive car.
+ 1. I would get a lot of pleasure from owning expensive luxury goods.
 
@@
 
- - I am an ordinary person who is no better than others.
- - I wouldn’t want people to treat me as though I were superior to them.
- - I think that I am entitled to more respect than the average person is.
- - I want people to know that I am an important person of high status.
+ 1. I am an ordinary person who is no better than others.
+ 1. I wouldn’t want people to treat me as though I were superior to them.
+ 1. I think that I am entitled to more respect than the average person is.
+ 1. I want people to know that I am an important person of high status.
 
@@
 
- - I would feel afraid if I had to travel in bad weather conditions.
- - I don’t mind doing jobs that involve dangerous work.
- - When it comes to physical danger, I am very fearful.
- - Even in an emergency I wouldn't feel like panicking.
+ 1. I would feel afraid if I had to travel in bad weather conditions.
+ 1. I don’t mind doing jobs that involve dangerous work.
+ 1. When it comes to physical danger, I am very fearful.
+ 1. Even in an emergency I wouldn't feel like panicking.
 
@@
 
- - I sometimes can't help worrying about little things.
- - I worry a lot less than most people do.
- - I rarely, if ever, have trouble sleeping due to stress or anxiety.
- - I get very anxious when waiting to hear about an important decision.
+ 1. I sometimes can't help worrying about little things.
+ 1. I worry a lot less than most people do.
+ 1. I rarely, if ever, have trouble sleeping due to stress or anxiety.
+ 1. I get very anxious when waiting to hear about an important decision.
 
@@
 
- - When I suffer from a painful experience, I need someone to make me feel comfortable.
- - I can handle difficult situations without needing emotional support from anyone else.
- - Whenever I feel worried about something, I want to share my concern with another person.
- - I rarely discuss my problems with other people.
+ 1. When I suffer from a painful experience, I need someone to make me feel comfortable.
+ 1. I can handle difficult situations without needing emotional support from anyone else.
+ 1. Whenever I feel worried about something, I want to share my concern with another person.
+ 1. I rarely discuss my problems with other people.
 
@@
 
- - I feel like crying when I see other people crying.
- - When someone I know well is unhappy, I can almost feel that person's pain myself.
- - I feel strong emotions when someone close to me is going away for a long time.
- - I remain unemotional even in situations where most people get very sentimental.
+ 1. I feel like crying when I see other people crying.
+ 1. When someone I know well is unhappy, I can almost feel that person's pain myself.
+ 1. I feel strong emotions when someone close to me is going away for a long time.
+ 1. I remain unemotional even in situations where most people get very sentimental.
 
@@
 
- - HEX_EMO with	HEX_EMO_FEA_04
+ 1. HEX_EMO with	HEX_EMO_FEA_04
 
@@
 
- - I feel reasonably satisfied with myself overall.
- - I think that most people like some aspects of my personality.
- - I feel that I am an unpopular person.
- - I sometimes feel that I am a worthless person.
+ 1. I feel reasonably satisfied with myself overall.
+ 1. I think that most people like some aspects of my personality.
+ 1. I feel that I am an unpopular person.
+ 1. I sometimes feel that I am a worthless person.
 
@@
 
- - I rarely express my opinions in group meetings.
- - In social situations, I'm usually the one who makes the first move.
- - When I'm in a group of people, I'm often the one who speaks on behalf of the group.
- - I tend to feel quite self-conscious when speaking in front of a group of people.
+ 1. I rarely express my opinions in group meetings.
+ 1. In social situations, I'm usually the one who makes the first move.
+ 1. When I'm in a group of people, I'm often the one who speaks on behalf of the group.
+ 1. I tend to feel quite self-conscious when speaking in front of a group of people.
 
@@
 
- - I avoid making "small talk" with people.
- - I enjoy having lots of people around to talk with.
- - I prefer jobs that involve active social interaction to those that involve working alone.
- - The first thing that I always do in a new place is to make friends.
+ 1. I avoid making "small talk" with people.
+ 1. I enjoy having lots of people around to talk with.
+ 1. I prefer jobs that involve active social interaction to those that involve working alone.
+ 1. The first thing that I always do in a new place is to make friends.
 
@@
 
- - I am energetic nearly all the time.
- - On most days, I feel cheerful and optimistic.
- - People often tell me that I should try to cheer up.
- - Most people are more upbeat and dynamic than I generally am.
+ 1. I am energetic nearly all the time.
+ 1. On most days, I feel cheerful and optimistic.
+ 1. People often tell me that I should try to cheer up.
+ 1. Most people are more upbeat and dynamic than I generally am.
 
@@
 
- - I rarely hold a grudge, even against people who have badly wronged me.
- - My attitude toward people who have treated me badly is "forgive and forget".
- - If someone has cheated me once, I will always feel suspicious of that person.
- - I find it hard to fully forgive someone who has done something mean to me.
+ 1. I rarely hold a grudge, even against people who have badly wronged me.
+ 1. My attitude toward people who have treated me badly is "forgive and forget".
+ 1. If someone has cheated me once, I will always feel suspicious of that person.
+ 1. I find it hard to fully forgive someone who has done something mean to me.
 
@@
 
- - People sometimes tell me that I am too critical of others.
- - I generally accept people’s faults without complaining about them.
- - I tend to be lenient in judging other people.
- - Even when people make a lot of mistakes, I rarely say anything negative.
+ 1. People sometimes tell me that I am too critical of others.
+ 1. I generally accept people’s faults without complaining about them.
+ 1. I tend to be lenient in judging other people.
+ 1. Even when people make a lot of mistakes, I rarely say anything negative.
 
@@
 
- - People sometimes tell me that I'm too stubborn.
- - I am usually quite flexible in my opinions when people disagree with me.
- - When people tell me that I’m wrong, my first reaction is to argue with them.
- - I find it hard to compromise with people when I really think I’m right.
+ 1. People sometimes tell me that I'm too stubborn.
+ 1. I am usually quite flexible in my opinions when people disagree with me.
+ 1. When people tell me that I’m wrong, my first reaction is to argue with them.
+ 1. I find it hard to compromise with people when I really think I’m right.
 
@@
 
- - People think of me as someone who has a quick temper.
- - I rarely feel anger, even when people treat me quite badly.
- - Most people tend to get angry more quickly than I do.
- - I find it hard to keep my temper when people insult me.
+ 1. People think of me as someone who has a quick temper.
+ 1. I rarely feel anger, even when people treat me quite badly.
+ 1. Most people tend to get angry more quickly than I do.
+ 1. I find it hard to keep my temper when people insult me.
 
@@
 
- - I clean my office or home quite frequently.
- - I plan ahead and organize things, to avoid scrambling at the last minute.
- - People often joke with me about the messiness of my room or desk.
- - When working, I sometimes have difficulties due to being disorganized.
+ 1. I clean my office or home quite frequently.
+ 1. I plan ahead and organize things, to avoid scrambling at the last minute.
+ 1. People often joke with me about the messiness of my room or desk.
+ 1. When working, I sometimes have difficulties due to being disorganized.
 
@@
 
- - When working, I often set ambitious goals for myself.
- - I often push myself very hard when trying to achieve a goal.
- - Often when I set a goal, I end up quitting without having reached it.
- - I do only the minimum amount of work needed to get by.
+ 1. When working, I often set ambitious goals for myself.
+ 1. I often push myself very hard when trying to achieve a goal.
+ 1. Often when I set a goal, I end up quitting without having reached it.
+ 1. I do only the minimum amount of work needed to get by.
 
@@
 
- - I often check my work over repeatedly to find any mistakes.
- - When working on something, I don't pay much attention to small details.
- - I always try to be accurate in my work, even at the expense of time.
- - People often call me a perfectionist.
+ 1. I often check my work over repeatedly to find any mistakes.
+ 1. When working on something, I don't pay much attention to small details.
+ 1. I always try to be accurate in my work, even at the expense of time.
+ 1. People often call me a perfectionist.
 
@@
 
- - I make decisions based on the feeling of the moment rather than on careful thought.
- - I make a lot of mistakes because I don't think before I act.
- - I don’t allow my impulses to govern my behavior.
- - I prefer to do whatever comes to mind, rather than stick to a plan.
+ 1. I make decisions based on the feeling of the moment rather than on careful thought.
+ 1. I make a lot of mistakes because I don't think before I act.
+ 1. I don’t allow my impulses to govern my behavior.
+ 1. I prefer to do whatever comes to mind, rather than stick to a plan.
 
@@
 
- - I would be quite bored by a visit to an art gallery.
- - I wouldn't spend my time reading a book of poetry.
- - If I had the opportunity, I would like to attend a classical music concert.
- - Sometimes I like to just watch the wind as it blows through the trees.
+ 1. I would be quite bored by a visit to an art gallery.
+ 1. I wouldn't spend my time reading a book of poetry.
+ 1. If I had the opportunity, I would like to attend a classical music concert.
+ 1. Sometimes I like to just watch the wind as it blows through the trees.
 
@@
 
- - I'm interested in learning about the history and politics of other countries.
- - I enjoy looking at maps of different places.
- - I would be very bored by a book about the history of science and technology.
- - I’ve never really enjoyed looking through an encyclopedia.
+ 1. I'm interested in learning about the history and politics of other countries.
+ 1. I enjoy looking at maps of different places.
+ 1. I would be very bored by a book about the history of science and technology.
+ 1. I’ve never really enjoyed looking through an encyclopedia.
 
@@
 
- - I would like a job that requires following a routine rather than being creative.
- - I would enjoy creating a work of art, such as a novel, a song, or a painting.
- - People have often told me that I have a good imagination.
- - I don't think of myself as the artistic or creative type.
+ 1. I would like a job that requires following a routine rather than being creative.
+ 1. I would enjoy creating a work of art, such as a novel, a song, or a painting.
+ 1. People have often told me that I have a good imagination.
+ 1. I don't think of myself as the artistic or creative type.
 
@@
 
- - I think that paying attention to radical ideas is a waste of time.
- - I like people who have unconventional views.
- - I think of myself as a somewhat eccentric person.
- - I find it boring to discuss philosophy.
+ 1. I think that paying attention to radical ideas is a waste of time.
+ 1. I like people who have unconventional views.
+ 1. I think of myself as a somewhat eccentric person.
+ 1. I find it boring to discuss philosophy.
 
@@
 
- - I have sympathy for people who are less fortunate than I am.
- - I try to give generously to those in need.
- - It wouldn’t bother me to harm someone I didn’t like.
- - People see me as a hard-hearted person.
+ 1. I have sympathy for people who are less fortunate than I am.
+ 1. I try to give generously to those in need.
+ 1. It wouldn’t bother me to harm someone I didn’t like.
+ 1. People see me as a hard-hearted person.
 
@@
 
-```{r}
+```{r hex-model}
 model_hex <- "
@@
 
-```{r}
+```{r nfp-model}
 model_pri <- "
@@
   round(2) %>% 
-  as.data.frame
+  as.data.frame %>% 
+  select(PRI_CON, PRI_BEH)
 tab_conval
@@
 
-# Export factor scores
-
-```{r cache=F}
+## Export factor scores
+
+To increase precision, we export the latents variables's factor scores as preregistered.
+
+```{r factor-scores, cache=T}
 d <- 
@@
 
-# Item errors
-
-```{r}
+## Item errors
+
+As preregistered, we also test analyses using observed mean measures of scales while accounting for their error variance. Hence, we estimate error variance according to Kline.
+
+```{r item-errors}
 # Extract variance
@@
 
-Let's first look at relations between need for privacy and personality factors.
-
-```{r results-dims}
+Let's look at relations between need for privacy and personality dimensions.
+
+We first do so in an SEM using latent factors.
+
+```{r results-dims, warning=T}
 model_dim <- "
@@
 
-Doesn't converge. Hence let's use means of observed values for personality and for privacy. Let's specify errors as preregistered.
-
-```{r}
+Throws two warnings (covariance matrix of latent variables and residuals is not positive definite).
+Fit is also poor.
+Hence let's use means of observed values for personality and for privacy.
+Let's specify errors as preregistered.
+
+```{r warning=T}
 model_dim_err <- "
@@
 ```
-Throws a warning: "covariance matrix of latent variables is not positive definite." Let's hence look at correlations of observed mean scores.
+
+Similarly, throws a warning: "covariance matrix of latent variables is not positive definite." Let's hence look at correlations of observed mean scores.
 Also do in subsequent analyses (i.e., facets and SES), to maintain comparability.
@@
 
-```{r results-facets}
+```{r results-facets, eval=T, warning=T}
 model_fac <- "
+
 # Personality
@@
 
-```{r}
+```{r warning=T}
 # make table
@@
   select(
-    vars_ses,
+    all_of(
+      vars_ses
+      ),
+    all_of(
      paste0(vars_pri, "_M") 
+    )
   ) %>%
@@
 
-```{r}
+```{r warning=T}
 model_reg <- "
-NFP_INF_M + NFP_PSY_M + NFP_PHY_M + NFP_SOC_M + NFP_GOV_M + NFP_COM_M + NFP_ANO_M + NFP_GEN_M ~ HEX_HOH_M + HEX_EMO_M + HEX_EXT_M + HEX_AGR_M + HEX_CNS_M + HEX_OPN_M +  + age + male + white + relation + college + income + conserv
+NFP_INF_M + NFP_PSY_M + NFP_PHY_M + NFP_SOC_M + NFP_GOV_M + NFP_COM_M + NFP_ANO_M + NFP_GEN_M ~ HEX_HOH_M + HEX_EMO_M + HEX_EXT_M + HEX_AGR_M + HEX_CNS_M + HEX_OPN_M + age + male + white + relation + college + income + conserv
 "
@@
 
-```{r cache=F}
+```{r cache=T}
 # Extract model fit indices: CFI, TLI, RMSEA, SRMR
@@
 
-```{r cache=F, fig.height=6, fig.width=12}
+```{r figcorr, cache=T, fig.height=9, fig.width=12, eval=T}
 # First extract data
@@
   scale_y_discrete(limits=rev) +
-  scale_color_manual(values = c("grey", "black")) +
   labs(
@@
     ) + 
+  scale_color_manual(values = c("grey", "black")) +
   facet_grid(category ~ `Need for privacy`, scales = "free_y")
@@
 
-```{r fig.height=6, fig.width=12}
+```{r fig-reg, fig.height=6, fig.width=12}
 tab_reg <- 
@@
 
-```{r cache=F}
-save.image("data/workspace_2.RData")
-```
+```{r cache=T}
+save.image("data/workspace_3.RData")
+```

### 2024-04-12 custom_functions.R

@@ -46,11 +46,11 @@ get_res <- function(predictor_var, privacy_var, object = "tab_cor"){
     } else {
       "_r_ = "  
     },
-    my_round(dat$Estimate, "std"),
+    td::my_round(dat$Estimate, "std"),
     ", 90% CI ",
-    my_round(dat$CI_low, "std"),
+    td::my_round(dat$CI_low, "std"),
     ", ",
-    my_round(dat$CI_high, "std"),
+    td::my_round(dat$CI_high, "std"),
     ""
   )
 }

### 2024-04-12 power_analyses.Rmd
reknitted manuscript removed unnecessary files

@@
 
-## Detailed: Simple
+## Detailed
 
@@
 power_80 <- findPower(power_tab, "N", 0.90)
-power_80["HEX_HOH_SIN~~NFP_PHY"]
 ```
+
+A power of 80% would imply collecting `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]` participants.
 

### 2024-04-12 items.rmd
- updated items file

--- 2023-03-07 items.rmd
@@
 title: "Items"
+subtitle: "Data-set: Need for Privacy and Personality"
+author: "Tobias Dienlin & Miriam Metzger"
+date: "2024-04-05"
 output:
@@
       toc_depth: 3
-# output: pdf_document
+# output:
+#   pdf_document:
+#     toc: TRUE
+#     toc_depth: 1
 bibliography: 
@@
 ---
+
+# Overview
+
+ <!-- - For a pdf of all items, click here. -->
+ <!-- - For the actual questionnaire, click here. -->
 

### 2024-04-12 manuscript.Rmd
reknitted manuscript removed unnecessary files
- rerendered ms

@@
 
-note: |
-  This paper is in-principle-accepted at as a Stage 1 Registered Report at Collabra.
+# note: |
+  # This paper is in-principle-accepted at as a Stage 1 Registered Report at Collabra.
 
@@
 # classoption       : "man"
-# output: html_document
+# output            : html_document
 output            : papaja::apa6_pdf

### 2024-05-23 manuscript.Rmd
- updated for revision of IPA

@@
 # classoption       : "man"
-# output            : html_document
-output            : papaja::apa6_pdf
+output            : html_document
+# output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 ```{r setup, include=F}
-devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
+# devtools::install_github("tdienlin/td@v.0.0.2.5")  # uncomment to install
 library(devtools)
@@
 Afterward, we predicted privacy using the more specific facets. 
-To get a first idea of the variables' potential causal relations, we also planned to run latent structural regression models.
+To get a first idea of the variables' potential causal relations [@groszTabooExplicitCausal2020a], we also planned to run latent structural regression models.
 However, because model fit was not acceptable, in exploratory analyses we investigated the potential effects in a multiple regression using the mean values of the observed scores.
@@
   caption = "Factorial validity of all measures.",
-  font_size = "small",
-  escape = FALSE
+  font_size = "footnotesize",
+  escape = FALSE,
+  note = "REL: Reliability measured via McDonald's Omega; CFI = Comparative Fit Index; TLI = Tucker-Lewis Index; SRMR = Standardized Root Mean Square Residual; RMSEA = Root Mean Square Error of Approximation"
   )
@@
 See online supplementary material for all results.
+
+People who reported being less honest and humble needed more anonymity (`r get_res("Honesty humility", "Anonymity")`).
+Looking at facets, more anonymity was needed by people who reported being less fair (`r get_res("Fairness", "Anonymity")`), less modest (`r get_res("Modesty", "Anonymity")`), and less altruistic (`r get_res("Altruism", "Anonymity")`).
+People who reported being less fair needed more psychological (`r get_res("Fairness", "Psychological")`), social (`r get_res("Fairness", "Social")`), and physical privacy (`r get_res("Fairness", "Physical")`).
+Similarly, people who reported being less altruistic also needed substantially more psychological (`r get_res("Altruism", "Psychological")`), social (`r get_res("Altruism", "Social")`), and physical privacy (`r get_res("Altruism", "Physical")`).
+However, less sincere people needed less privacy from companies (`r get_res("Sincerity", "Companies")`) and less privacy in general (`r get_res("Sincerity", "General")`).
+Effects were small to medium in size.
+
+Several relations between emotionality and need for privacy were found.
+More emotional people needed less psychological privacy (`r get_res("Emotionality", "Psychological")`), less privacy from the government (`r get_res("Emotionality", "Government")`), less anonymity (`r get_res("Emotionality", "Anonymity")`)---but also needed more physical privacy (`r get_res("Emotionality", "Physical")`).
+More anxious respondents needed substantially more social (`r get_res("Anxiety", "Social")`) and physical privacy (`r get_res("Anxiety", "Physical")`).
+Similarly, more fearful respondents needed more social (`r get_res("Fearfulness", "Social")`) and physical privacy (`r get_res("Fearfulness", "Physical")`).
+More dependent participants generally needed less privacy, including less psychological (`r get_res("Dependence", "Psychological")`) and social privacy (`r get_res("Dependence", "Social")`), less privacy from the government (`r get_res("Dependence", "Government")`), and less informational (`r get_res("Dependence", "Informational")`) and general privacy (`r get_res("Dependence", "General")`).
+A similar picture for more sentimental participants emerged, who needed less psychological (`r get_res("Sentimentality", "Psychological")`) and social privacy (`r get_res("Sentimentality", "Social")`) and less anonymity (`r get_res("Sentimentality", "Anonymity")`).
+
+More extraverted people reported they needed a lot less privacy.
+They wanted less psychological privacy (`r get_res("Extraversion", "Psychological")`), social privacy (`r get_res("Extraversion", "Social")`), and physical privacy (`r get_res("Extraversion", "Physical")`), less informational privacy (`r get_res("Extraversion", "Informational")`) and less anonymity (`r get_res("Extraversion", "Anonymity")`).
+Effect sizes were oftentimes large.
+All facets showed virtually the same relations, with small differences in effect sizes.
+
+More agreeable participants showed a similar pattern.
+They needed less psychological (`r get_res("Agreeableness", "Psychological")`), social (`r get_res("Agreeableness", "Social")`), and physical privacy (`r get_res("Agreeableness", "Physical")`).
+The facets showed virtually the same pattern.
+Effect sizes were substantial, but on the whole smaller than those for extraversion.
+
+Although more conscientious respondents generally needed less privacy, the pattern was varied.
+More conscientious respondents needed less psychological (`r get_res("Conscientiousness", "Psychological")`) and less social privacy (`r get_res("Conscientiousness", "Social")`), as well as less anonymity (`r get_res("Conscientiousness", "Anonymity")`).
+However, when asked about privacy in general more conscientious people responded to need more (`r get_res("Conscientiousness", "General")`).
+More conscientious people also needed more privacy from companies (`r get_res("Conscientiousness", "Companies")`).
+Looking at facets of conscientiousness, more organized people needed less social privacy (`r get_res("Organization", "Social")`) and less anonymity (`r get_res("Organization", "Anonymity")`). 
+More prudent participants needed less anonymity (`r get_res("Prudence", "Anonymity")`).
+More diligent people needed less psychological (`r get_res("Diligence", "Psychological")`), social (`r get_res("Diligence", "Social")`), and physical privacy (`r get_res("Diligence", "Physical")`) as well as less anonymity (`r get_res("Diligence", "Anonymity")`)---but also more privacy from companies (`r get_res("Diligence", "Companies")`)
+At the same time, more perfectionist respondents reported needing more informational (`r get_res("Perfectionism", "Informational")`) privacy, privacy from companies (`r get_res("Perfectionism", "Companies")`), and more general privacy (`r get_res("Perfectionism", "General")`).
+
+Whether or not respondents were open to new experiences was in most cases unrelated to how much privacy they needed.
+People more open to experiences needed more privacy from companies (`r get_res("Openness", "Companies")`) and more privacy in general (`r get_res("Openness", "General")`).
+Three facets showed relevant but still small relations. 
+Respondents who reported being more creative needed less psychological (`r get_res("Creativeness", "Psychological", "tab_cor")`) and less social privacy (`r get_res("Creativeness", "Social")`). 
+More inquisitive respondents needed less physical privacy (`r get_res("Inquisitiveness", "Physical")`) but more privacy from companies (`r get_res("Inquisitiveness", "Companies")`).
+
+In Table \@ref(tab:tab-dim), we report how the personality dimensions predicted need for privacy.
+In Table \@ref(tab:tab-fac), we report how the personality facets predicted need for privacy.
 
@@
 
-People who reported being less honest and humble needed more anonymity (`r get_res("Honesty humility", "Anonymity")`).
-Looking at facets, more anonymity was needed by people who reported being less fair (`r get_res("Fairness", "Anonymity")`), less modest (`r get_res("Modesty", "Anonymity")`), and less altruistic (`r get_res("Altruism", "Anonymity")`).
-People who reported being less fair needed more psychological (`r get_res("Fairness", "Psychological")`), social (`r get_res("Fairness", "Social")`), and physical privacy (`r get_res("Fairness", "Physical")`).
-Similarly, people who reported being less altruistic also needed substantially more psychological (`r get_res("Altruism", "Psychological")`), social (`r get_res("Altruism", "Social")`), and physical privacy (`r get_res("Altruism", "Physical")`).
-However, less sincere people needed less privacy from companies (`r get_res("Sincerity", "Companies")`) and less privacy in general (`r get_res("Sincerity", "General")`).
-Effects were small to medium in size.
+Not many meaningful relations between sociodemographic variables and need for privacy were found.
+Older participants needed less social (`r get_res("Age", "Social")`) and less physical privacy (`r get_res("Age", "Physical")`). 
+Male participants needed more anonymity (`r get_res("Male", "Anonymity")`). 
+Less social privacy was needed by people in a relationship (`r get_res("Relationship", "Social")`), with a college degree (`r get_res("College", "Social")`), and with higher income (`r get_res("Income", "Social")`).
+People with higher income also reported needing less physical privacy (`r get_res("Income", "Physical")`). 
+More politically conservative respondents reported needing more privacy from the government (`r get_res("Conservatism", "Government")`).
 
-Several relations between emotionality and need for privacy were found.
-More emotional people needed less psychological privacy (`r get_res("Emotionality", "Psychological")`), less privacy from the government (`r get_res("Emotionality", "Government")`), less anonymity (`r get_res("Emotionality", "Anonymity")`)---but also needed more physical privacy (`r get_res("Emotionality", "Physical")`).
-More anxious respondents needed substantially more social (`r get_res("Anxiety", "Social")`) and physical privacy (`r get_res("Anxiety", "Physical")`).
-Similarly, more fearful respondents needed more social (`r get_res("Fearfulness", "Social")`) and physical privacy (`r get_res("Fearfulness", "Physical")`).
-More dependent participants generally needed less privacy, including less psychological (`r get_res("Dependence", "Psychological")`) and social privacy (`r get_res("Dependence", "Social")`), less privacy from the government (`r get_res("Dependence", "Government")`), and less informational (`r get_res("Dependence", "Informational")`) and general privacy (`r get_res("Dependence", "General")`).
-A similar picture for more sentimental participants emerged, who needed less psychological (`r get_res("Sentimentality", "Psychological")`) and social privacy (`r get_res("Sentimentality", "Social")`) and less anonymity (`r get_res("Sentimentality", "Anonymity")`).
-
-More extraverted people reported they needed a lot less privacy.
-They wanted less psychological privacy (`r get_res("Extraversion", "Psychological")`), social privacy (`r get_res("Extraversion", "Social")`), and physical privacy (`r get_res("Extraversion", "Physical")`), less informational privacy (`r get_res("Extraversion", "Informational")`) and less anonymity (`r get_res("Extraversion", "Anonymity")`).
-Effect sizes were oftentimes large.
-All facets showed virtually the same relations, with small differences in effect sizes.
-
-More agreeable participants showed a similar pattern.
-They needed less psychological (`r get_res("Agreeableness", "Psychological")`), social privacy (`r get_res("Agreeableness", "Social")`), and physical privacy (`r get_res("Agreeableness", "Physical")`).
-The facets showed virtually the same pattern.
-Effect sizes were substantial, but on the whole smaller than those for extraversion.
-
-Although more conscientious respondents generally needed less privacy, the pattern was varied.
-More conscientious respondents needed less psychological (`r get_res("Conscientiousness", "Psychological")`) and less social privacy (`r get_res("Conscientiousness", "Social")`), as well as less anonymity (`r get_res("Conscientiousness", "Anonymity")`).
-However, when asked about privacy in general more conscientious people responded to need more (`r get_res("Conscientiousness", "General")`).
-More conscientious people also needed more privacy from companies (`r get_res("Conscientiousness", "Companies")`).
-Looking at facets of conscientiousness, more organized people needed less social privacy (`r get_res("Organization", "Social")`) and less anonymity (`r get_res("Organization", "Anonymity")`). 
-More prudent participants needed less anonymity (`r get_res("Prudence", "Anonymity")`).
-More diligent people needed less psychological (`r get_res("Diligence", "Psychological")`), social (`r get_res("Diligence", "Social")`), and physical privacy (`r get_res("Diligence", "Physical")`) as well as less anonymity (`r get_res("Diligence", "Anonymity")`)---but also more privacy from companies (`r get_res("Diligence", "Companies")`)
-At the same time, more perfectionist respondents reported needing more informational (`r get_res("Perfectionism", "Informational")`) privacy, privacy from companies (`r get_res("Perfectionism", "Companies")`), and more general privacy (`r get_res("Perfectionism", "General")`).
-
-Whether or not respondents were open to new experiences was in most cases unrelated to how much privacy they needed.
-People more open to experiences needed more privacy from companies (`r get_res("Openness", "Companies")`) and more privacy in general (`r get_res("Openness", "General")`).
-Three facets showed relevant but still small relations. 
-Respondents who reported being more creative needed less psychological (`r get_res("Creativeness", "Psychological", "tab_cor")`) and less social privacy (`r get_res("Creativeness", "Social")`). 
-More inquisitive respondents needed less physical privacy (`r get_res("Inquisitiveness", "Physical")`) but more privacy from companies (`r get_res("Inquisitiveness", "Companies")`).
+In Table \@ref(tab:tab-ses), we report how sociodemographics predicted need for privacy.
+Figure \@ref(fig:fig-cor) summarizes how all of the variables---dimensions, facets, and sociodemographics---predicted the need for privacy.
 
@@
 
-Not many meaningful relations between sociodemographic variables and need for privacy were found.
-Older participants needed less social (`r get_res("Age", "Social")`) and less physical privacy (`r get_res("Age", "Physical")`). 
-Male participants needed more anonymity (`r get_res("Male", "Anonymity")`). 
-Less social privacy was needed by people in a relationship (`r get_res("Relationship", "Social")`), with a college degree (`r get_res("College", "Social")`), and with higher income (`r get_res("Income", "Social")`).
-People with higher income also reported needing less physical privacy (`r get_res("Income", "Physical")`). 
-More politically conservative respondents reported needing more privacy from the government (`r get_res("Conservatism", "Government")`).
-
-In Table \@ref(tab:tab-dim), we report how the personality dimensions predicted need for privacy.
-In Table \@ref(tab:tab-fac), we report how the personality facets predicted need for privacy.
-In Table \@ref(tab:tab-ses), we report how sociodemographics predicted need for privacy.
-Figure \@ref(fig:fig-cor) summarizes how all of the variables---dimensions, facets, and sociodemographics---predicted the need for privacy.
-
 ```{r fig-cor, fig.cap="Results of bivariate correlations between personality and need for privacy.
@@
 
-In exploratory analyses we analyzed how personality facets might have potentially caused need for privacy.
+In exploratory analyses we analyzed how personality facets might have potentially caused need for privacy, using multiple regressions in which we controlled for all personality dimensions and sociodemographic variables.
 We found that the need for psychological privacy was explained by two variables: extraversion (`r get_res("Extraversion", "Psychological", "tab_reg")`) and emotionality (`r get_res("Emotionality", "Psychological", "tab_reg")`).
@@
 Contrary to our expectations, older participants desired less privacy from others, both socially and physically. 
+This was surprising, for example given that older people report increased online privacy concern [@kezerAgeDifferencesPrivacy2016].
 It is an open question as to whether this relation represents a developmental mechanism or a difference between cohorts.
@@
 
-Based on correlations, the results above analyzed the variables' relationships.
-To analyze the potential impact of personality on need for privacy, in exploratory analyses we also ran several multiple regression analyses, in which we controlled for the respective personality variables and sociodemographics.
+The results above are based on correlations and analyzed the variables' relationships.
+To analyze the potential impact of personality on need for privacy, in exploratory analyses we also ran several multiple regression analyses.
+Here, we estimated the relations between each personality and need for privacy dimension while controlling for all other personality dimensions and sociodemographics.
 Results were comparable, in that extraversion turned out to be the major potential cause of need for privacy.
@@
 
-Looking at the results more broadly, we make four general observations.
+Looking at the results more broadly, we make five general observations.
 First, it makes sense to differentiate different levels of need for privacy.
@@
 We first analyzed this question in correlation analyses. 
-But in additionally exploring potential causal effects in a multiple regression, a somewhat different picture emerged. 
-The results suggest that several of the correlations we found might not be the result of a causal processes. 
-At the same time, some causal effects might also be suppressed in correlation analyses.
-More research better suited at uncovering causal relations is needed to address this question.
+However, when we further explored potential causal effects using multiple regression analysis [@groszTabooExplicitCausal2020a], a somewhat different picture emerged. 
+Several of the bivariate relationships we initially observed disappeared. 
+These results suggest that some of the correlations we found might not be due to a direct causal process but could instead be explained by shared variance with a third confounding factor. 
+Additionally, some causal effects that were not apparent in the correlation analyses became significant in the multiple regressions. 
+Specifically, conservatism became more relevant when we included additional control variables, suggesting that an increase in conservatism leads to a greater desire for anonymity and privacy in general.
+
+Finally, our results have significant implications for privacy theory, suggesting new avenues for further research. 
+Given the close relationship between personality and privacy, it is worthwhile to examine how personality traits interact with specific privacy models and theories. 
+For instance, personality could influence the privacy calculus model [@kezerGettingPrivacyCalculus2022]. 
+Extraverted individuals, who tend to view others as resources, might perceive greater benefits in sharing information online and therefore be more open in their sharing behaviors. 
+Conversely, anxious individuals, who are more likely to see others as threats, might have heightened concerns about privacy, leading to a reduced willingness to share information online.
 
@@
 This underscores the need for further optimizing measures of personality and privacy.
-We hope this study is a catalyst for future work in this area.
+
+In our exploratory analyses, we aimed to investigate the potential causal effects of personality on the need for privacy by controlling for potential confounders, including other personality dimensions and sociodemographic variables.
+However, it is important to note that this is only a preliminary approach, as there are likely additional variables that could further explain the relationships. 
+Future research should explore the potential causal relationships in a more systematic and comprehensive manner.
+
+Our findings are specific to the U.S. context. 
+Previous research indicates that although privacy is a universal concept, attitudes and practices vary significantly across different cultures and countries [@altmanPrivacyRegulationCulturally1977]. 
+It is possible that the relationship between personality and the need for privacy manifests differently in various settings. 
+We hope this study will serve as a catalyst for future research in this area.
 

### 2024-05-23 results.RmD
- updated for revision of IPA

@@
   ) + 
-  coord_cartesian(xlim = c(-.7, .3)) +
+  coord_cartesian(xlim = c(-.8, .4)) +
   geom_vline(xintercept = 0, lwd = .5, colour = "darkgrey") + 
@@
   scale_x_continuous(
-    breaks = c(-.6, -.4, -.2, 0, .2, .4),
-    labels = c("-.6", "-.4", "-.2", "0", ".2", ".4")
+    breaks = c(-.8, -.6, -.4, -.2, 0, .2, .4),
+    labels = c("-.8", "-.6", "-.4", "-.2", "0", ".2", ".4")
     ) + 
@@
     axis.text.y = element_text(hjust = 1),
-    axis.text.x = element_text(size = 10),
+    axis.text.x = element_text(size = 8),
     legend.position = "none"
@@
   scale_x_continuous(
-    breaks = c(-.8, -.6, -.4, -.2, 0, .2, .4),
-    labels = c("-.8", "-.6", "-.4", "-.2", "0", ".2", ".4")
+    breaks = c(-.8, -.6, -.4, -.2, 0, .2),
+    labels = c("-.8", "-.6", "-.4", "-.2", "0", ".2")
     ) + 

### 2024-07-04 analysis_pipeline.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

@@
     toc: TRUE
-    toc_float:
-      collapsed: FALSE
+    # toc_float:
+    #   collapsed: FALSE
     toc_depth: 3

### 2024-07-04 data_prep.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

@@
     toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+    # toc_float:
+    #   collapsed: FALSE
+    toc_depth: 3
     code_folding: show

### 2024-07-04 index.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

@@
 Exploring the relations between need for privacy and personality_.
-The paper is currently submitted to the journal Collabra as registered report.
+The paper published at the journal Collabra as registered report.
 The report is based on an [older paper](https://osf.io/m23bn) that was already submitted to Collabra but rejected.
-This paper now addresses the [feedback from the original submission](reviews.pdf) and considers the original paper a prestudy.
+This paper now addressed the [feedback from the original submission](reviews.pdf) and considers the original paper a prestudy.
 
@@
 This website is produced directly from the project's [github repository](https://github.com/tdienlin/who_needs_privacy_rr). You can download the material, file an issue, or submit a pull request.
+
+Please cite as follows:
+
+Dienlin, T., & Metzger, M. (2024). Who Needs Privacy? Exploring the Relations Between Need for Privacy and Personality. _Collabra: Psychology_, 10(1), 120402. https://doi.org/10.1525/collabra.120402

### 2024-07-04 items.rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

@@
     toc: TRUE
-    toc_float:
-      collapsed: FALSE
-      toc_depth: 3
+    # toc_float:
+    #   collapsed: FALSE
+    toc_depth: 2
 # output:

### 2024-07-04 items_readability.Rmd
deleting large files
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

@@
     toc: TRUE
-    toc_float:
-      collapsed: FALSE
-    toc_depth: 2
+    # toc_float:
+    #   collapsed: FALSE
+    toc_depth: 3
     code_folding: hide
@@
 }
-```
-
-```{r data-wrangling}
-d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")
 ```

### 2024-07-04 manuscript.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

@@
 # classoption       : "man"
-output            : html_document
-# output            : papaja::apa6_pdf
+# output            : html_document
+output            : papaja::apa6_pdf
 # output            : papaja::apa6_word
@@
 All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
-A list of all items that we were used are reported in the online supplementary material. 
+A list of all items that we used are reported in the online supplementary material. 
 The personality and privacy items were presented in random order, and the sociodemographic questions were asked at the end.
@@
 General need for privacy may rather represent a cognitive appraisal, whereas social or psychological privacy might be more experienced-based and psychological. 
-In any case, our results argue for a more rather than less nuanced strategy for measuring privacy attitudes.
+In any case, our results argue for a more rather than less nuanced strategy for measuring privacy attitudes.y
 
@@
 
-The data are shared as a scientific use file on AUSSDA [@dienlinNeedPrivacyPersonality2024].
+The data are shared as a scientific use file on AUSSDA at https://doi.org/10.11587/IC66GC [@dienlinNeedPrivacyPersonality2024].
